### 2020-10-31 Modules/HPBW_apndx.tex
Initial Overleaf Import

We now compute the squared norm of \eqref{eq_Hdphi0}, equate it to $1/2$ and compute the value of $N\dTheta/2$ for large $N$. To this end, we denote $\gamma\triangleq\dTheta/2$, giving rise to
\begin{equation*}
    \resizebox{1\linewidth}{!}{
        \begin{split}
            \abs{\Hr_{\dTheta,\dPhi=0,r}\rBrace{\omega}}^{2}&=
             \frac{\rBrace{1-r}^{2}\Dp{\gamma,N}{2}}{\abs{\exp\rBrace{j(N-1)\gamma}-r\D{\gamma}{N}}^{2}}
             \\&
             \overset{N\gg1}{\approx}\frac{\rBrace{1-r}^{2}\Dp{\gamma,N}{2}}{1-2r\cos{\rBrace{N\gamma}}\D{\gamma}{N}+r^{2}\Dp{\gamma,N}{2}}.
        \end{split}
    }
\end{equation*}
Equating to $1/2$, leads to
\begin{equation*}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            \rBrace{r^{2}-4r+2}\Dp{\gamma,N}{2}+2r\cos{\rBrace{N\gamma}}\D{\gamma}{N}-1 = 0.
        \end{split}
    % }
\end{equation*}
Since for large $N$, the mainlobe beamwidth goes to zero, we approximate $\sin(\gamma)$ with $\gamma$. Also defining $x\triangleq{}N\gamma=N\dTheta/2$ we obtain \eqref{eq_HPBW}.

### 2020-10-31 Modules/IEEE_journal_paper_Intro.tex
Initial Overleaf Import

general field of array processing has been thoroughly studied throughout several decades.
The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving signal to noise ratio (SNR) \cite{verdu1998multiuser}, and many more. 
\par A uniform linear array (ULA) has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF). For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.
\par In pursuit of spatial performance improvement, namely higher spatial separation and selectivity of arriving signals, many approaches were suggested.  
One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
Another approach, involving different array geometries, examined minimum redundancy arrays \cite{moffet1968minimum,pillai1985new,pillai1987statistical,Kupershtein2013}, aiming to reduce the spatial ambiguity. The basic concept was minimization of the inter-element spacing redundancy in order to increase the overall resolution. Adaptive processing schemes \cite{frost1972algorithm,manolakis2000statistical}, being a wide and active  research area, were also suggested trying to adaptively estimate and suppress the noise component in impinging signals by minimization of the receiver's output energy with some constraints.
\par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g. narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?''
\par Achieving spatial IIR response has also motivated other works.
In \cite{wen2013extending} two methods were considered.
The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain. The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array. 
Surely, the former approach heavily relies on the accuracy of the delay estimation and the latter approach does not achieve a recursive spatial response. In both cases, there is no true spatial feedback between the array and the source of interest.
Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
\par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.
To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
\par The novelty, compared to traditional array processing, is the incorporation of spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
Note that the initial stimulus can be generated by the target or the array itself. In the text to follow, we assume this is the latter. 
Furthermore, as opposed to the passive target case (i.e., a target which merely reflects the impinging signal), one may consider a cooperative target, which receives, enhances and re-transmits the signal back to the array. 
\par The outline of this paper is as follows. We first formulate the classic spatial beamforming setup in Sec.~\ref{sec:setup}. Then, in Sec.~\ref{sec_introduceFeedback}, we propose our novel feedback-based architecture, and formulate its spatial response.
Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback. Specifically, we compute the array beamwidth, its peak-to-sidelobe ratio and the array directivity, showing significant improvement compared to traditional beamforming without spatial feedback. 
In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors. We then suggest a strategy which mitigates this sensitivity. Finally, concluding remarks are given in Sec.~\ref{sec_conclusions}.
\section{Beamforming}\label{sec:setup}
In this section, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented.
Consider an $N$-element ULA with inter-element spacing $\delta$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$. We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
Focusing on a far field localization problem, DOA and target range are to be estimated. Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, reflects back from the target and re-impinges the array, with total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
In this this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and hermitian transpose of the matrix $\vecnot{A}$ respectively.
\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
\begin{equation}
x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
\label{eqn:noFeedbackULA_singleSensor_temporal}
\end{equation}
where $\tau_{n}=n\delta\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write 
\[
\vecnot{\F{x}}\rBrace{\omega}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}
\]
where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
\begin{equation}
    \label{eq:d}
    d_{n}\rBrace{\omega} = \exp{\rBrace{-j\omega\tau_{n}}}.
\end{equation}
Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in frequency domain
\begin{equation}
    \label{eq_Z}
    Z\rBrace{\omega} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
\end{equation}
Defining the electric phase to be
\begin{equation}\label{eq:thetaULA}
\theta=\omega{\delta\cos\Brack{\thetaD}}/{c},
\end{equation}
we rewrite \eqref{eq_Z} as 
\[
Z\rBrace{\omega} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
\]
hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to FIR filter design~\cite{van1988beamforming,benesty2018}. 
\ifdefined\useOmega \else 
Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest this paper, where possible.
\fi
\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest. Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.). 
As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rater than using pulse based signals. 
% The suggested structure is elaborated in Sec.~\ref{sec_introduceFeedback} and shown to be equivalent to IIR filter design.
\section{Feedback Beamforming}
\label{sec_introduceFeedback}
In this section, a feedback-based architecture is proposed for spatial signal processing.
Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIRBasicArch}), 
we propose to use the same concept in the spatial domain.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
            \put (60, 50){\footnotesize{$\beta_{0}$}}
            \put (60, 30){\footnotesize{$\beta_{1}$}}
            \put (60, 10){\footnotesize{$\beta_{2}$}}
            \put (36, 30){\footnotesize{$\alpha_{1}$}}
            \put (36, 10){\footnotesize{$\alpha_{2}$}}
            \put (10, 50){\footnotesize{$x$}}
            \put (85, 50){\footnotesize{$y$}}
            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
        \end{overpic}
    \end{center}
    \caption{Direct form II $2^{nd}$ order IIR architecture.}
    \label{fig_IIRBasicArch}
\end{figure}
The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}. The beamformer's output and the feedback signal are synthesized with two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.
Also, the FB block is marked (dashed line) for later use.
Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to a plain delay-and-sum (DS) beamformer.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.95\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR-diagram/SpatialIIR_VER8.png}
            \put (14, 39){\footnotesize{$\sum_{n=0}^{N-1}\beta^{*}_{n}x_{n}$}}
            \put (54, 39){\footnotesize{$\sum_{n=0}^{N-1}\alpha^{*}_{n}x_{n}$}}
            \put (24.25, 50){\footnotesize{$x_{0}$}}
            \put (35, 50){\footnotesize{$x_{1}$}}
            \put (55, 50){\footnotesize{$x_{N-1}$}}
            \put (30.5, 66){\footnotesize{$\delta$}}
            \put (89, 96){\footnotesize{$\vpt$}}
            \put (58, 58){\footnotesize{$\vpi{N-1}$}}
            \put (37, 58){\footnotesize{$\vpi{1}$}}
            \put (26.5, 58){\footnotesize{$\vpi{0}$}}
            \put (41.5, 64.5){\footnotesize{$\theta_{g}$}}
            \put (19, 11.25){\large{$+$}}
            \put (61.25, 27.25){\large{$+$}}
            \put (47, 11.75){$s$}
            \put (35.25, 11.75){$n$}
            \put (21,4){$z$}
            \put (63.5,14){$\Tx$}
            \put (1, 51){$\text{FB}_{\vAlpha,\vBeta}$}
        \end{overpic}
    \end{center}
    \caption{
    The proposed feedback beamformer.
    The spatial feedback is obtained by continuous re-transmission of $\Tx$ to the target at $\vpt$.
    We designate the feedback beamformer block (dashed line) for later use.
    }
    \label{fig:Proposed_spatialIIR_ARCH}
\end{figure}
\subsection*{Obtained spatial response}
\input{./Modules/Spatial_IIR-MathDerivations.tex}
\section{Fisher Information Matrix}
\label{sec_FIM}
\input{./Modules/estimation_CRLB_appendix.tex}
\section{Performance Analysis}
\label{sec_Performance}
In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.  
\subsection*{Error terms}
In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
\begin{equation}\label{eq:alpha_beta_hat}
\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
\end{equation}
introducing the estimated steering vector 
\begin{equation}\label{eq:d_hat}
\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
\end{equation}
Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
\begin{equation}\label{eq:SF_CB}
    \resizebox{.894\linewidth}{!}{
        \begin{split}
            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
        \end{split}
    }
\end{equation}
where \[
\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
\]
is the normalized Dirichlet kernel and
we define the DOA, range and gain error terms 
\[
\dTheta\triangleq\theta\omegaB-\hat{\theta}\omegaB,\ \dPhi\triangleq\phi\omegaB-\hat{\phi}\omegaB,\ 
r\triangleq g/\hat{g},
\]
respectively.
\ifdefined\useOmega\else
We then define four fundamental scenarios:
\fi
\begin{itemize}
    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Steer error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
\end{itemize}
\ifdefined\showTodo
{
    \subsection*{Small estimation error analysis - \textbf{TO BE REMOVED - kept only for the todos}}
    \label{subsection_ArrayPerformance_TayolrAnalysis}
    \myTodo{inline}{\textbf{DONE:}\\ maybe to call this subsection 'small error analysis'}
    Plugging (\ref{eqn_CB_coefSet}) into (\ref{eqn:GeneralFeedbackTransferFunction}) and denoting $\D{N}{x} \triangleq \frac{\sin{\rBrace{Nx}}}{\sin{\rBrace{x}}}$ results in the general \coefSetName{} beampattern \myTodo{inline}{\textbf{DONE}\\you need to define the delta expressions (the errors)}
    \begin{equation*}
        h_{\coefSetName{}}\rBrace{\theta,\omega}
        =
        \frac{
        \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
        }{
        N - \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
        }.
    \end{equation*}
    For the evaluation of the various array parameters, we define the normalized beampattern \myTodo{inline}{\textbf{DONE:}\\not very readable. Consider writing a multiplication of two terms. Suggesting that you write the expression in eq(5) as $H(\theta,\phi)$ and here you'll have $H(\hat{\theta}, \hat{\phi})/ H(\theta,\phi)$}
    \begin{equation}
        \label{eqn_arrPerformance_beamwidth_3dB}
        \Hr{\theta}{\tau}{}\triangleq\fbBpRatio.
    \end{equation}
    \myTodo{inline}{\textbf{DONE:}\\this next section is very long. Suggesting that you express (10) in terms of the errors $\Delta\theta,\;\Delta\phi$, and then simply state that the second order Taylor expansion of those errors around zero gives (12). One more issue which I think might cause us some headache is that we cannot assure that $\Delta\phi$ (you call it $\Delta\tau$) is indeed close to zero, as this term fluctuates very fast. But we will think about it later on. Maybe something with wideband signal stimulus will solve this issue.}
    The pursuit for analytic dependencies between $\Hr{\theta}{\tau}{}$, $\dTheta$ and $\dPhi$, as in \cite{van2004optimum}, lead to expressing $\Hr{\theta}{\tau}{}$'s multivariate Taylor expansion, setting $\dTheta,\dPhi$ as the variables. Simulations have shown that $2^{nd}$ Taylor expansion achieves very accurate results, thus we use it to express the array parameters. As commonly known, the Taylor expansion of a multivariate analyzable function $f\rBrace{\vx}$ around $\vx_{0}$ where $\vx \in \mathbb{R}_{M\times1},$ is 
    \begin{equation}
        \label{eqn_h_Tylor_dTheta_dTau}
        \evalat{f\rBrace{\vx}}{\vx\to\vx_{0}}=\sum_{n=0}^{\infty}\frac{1}{n!}\rBrace{\sum_{i=1}^{M}(x_{i}-x_{0i})\frac {\partial}{\partial x_i} }^n f(x_k)|_{x_k=x_{k0}},
    \end{equation}
    where $\frac{\partial}{\partial x_i}$ is the derivative operator and $i\in\left[1\hdots{}M\right]$. Reducing (\ref{eqn_h_Tylor_dTheta_dTau}) to its $2^{nd}$ form (i.e $f(x,y)=\sum_{n=0}^{\infty} \frac 1 {n!}\rBrace{x\frac {\partial}{\partial x}+y\frac {\partial}{\partial y} }^n f(x,y)|_{(x,y)=(0,0)}$), combined with the binomial formula, $(x+y)^{n}=\sum _{k=0}^{n}{\binom {n}{k}}x^{n-k}y^{k},$ multiple iterations of L'Hôpital's rule and algebraic simplification finally yields
    \begin{equation}
        \begin{split}
            \evalat{\Hr{\theta}{\tau}{}_{\coefSetName{}}}{\dTheta\to0,\dPhi\to0} \approx\ & 1 
            \\+&\frac{\binom{2}{0}}{2!}\frac{-\rBrace{N - 1}\rBrace{N-4r+2Nr+1}}{6\rBrace{r-1}^{2}}\dTheta^{2}
            \\+&\frac{\binom{2}{1}}{2!}\frac{-r\omega\rBrace{N - 1}}{\rBrace{r-1}^{2}}\dTheta\dPhi
            \\+&\frac{\binom{2}{2}}{2!}\frac{-2r\omega^{2}}{\rBrace{r-1}^{2}}\dPhi^{2}
        \end{split}
    \end{equation}
}
\else
\fi
\subsection*{The normalized beampattern}
\label{subsection_spatialIIR_normBP}
As commonly done for ULA performance analysis \cite{van2004optimum}, we analyze the normalized response (i.e., where the peak main lobe gain is set to $0_{dB}$). Henceforth, setting $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ we define the normalized response
\begin{equation}
    \label{eq_narmalized_pattern}
    %\resizebox{.89\linewidth}{!}{
    \begin{split}
        \HrTPr\omegaB&\triangleq
        \frac{
        \HbaFB
        }{
        H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}\omegaB
        }
         =
        \frac{
        \HbaFB
        }{
        r/\rBrace{1-r}
        },
        % \\
        % &=\frac{\rBrace{1-r}^{2}\Dp{\dTheta/2,N}{2}}{1+r^{2}\Dp{\dTheta/2,N}{2}-2r\D{\dTheta/2}{N}\cos{\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}},
    \end{split}
    %}
\end{equation}
where the $\Delta\theta,\Delta\phi,r$ subscripts express the DOA, range and gain errors dependency, respectively.
%Also, $\abs{\HrTPr}$ is defined to be the beampattern.
Plugging \eqref{eq:SF_CB} into \eqref{eq_narmalized_pattern} yields 
\begin{equation}\label{eq_generalH}
    \resizebox{0.89\linewidth}{!}{
        \begin{split}
             \HrTPr\omegaB=
             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.
        \end{split}
        }
\end{equation}
Note that the known \cite{van2004optimum} normalized response of standard ULA is obtained by setting $r=0$ (i.e., cancelling the feedback) 
$$
\Hr_{\Delta\theta,\Delta\phi=0,r=0}\omegaB=
             \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}}.
$$
Considering the steering error scenario (i.e., $\dTheta\neq0,\ \dPhi=0$) first, where 
\begin{equation}\label{eq_Hdphi0}
\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB=
             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}},
\end{equation}
we evaluate the FB's beamwidth, sidelobe level and directivity and compare them to those of the standard ULA.
\ifdefined\useOmega
To simplify the exposition, we shall suppress the $\omega$ dependency in the following sections (i.e. $\HrTPr \triangleq \HrTPr\omegaB$) where possible.
\fi
\vfill
\subsection*{Half power beamwidth}
\input{./Modules/arrayPerformance_beamwidth.tex}
\subsection*{Sidelobes attenuation}
\ifdefined\showDev
    \fbox{
    \begin{minipage}{0.9\linewidth}
    \textbf{development specifics}\\
    Let $f\rBrace{\dTheta} \triangleq \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}},$ such that $\Hr_{\Delta\theta,\Delta\phi=0,r=0}\omegaB = \frac{f\rBrace{\dTheta}}{1-rf\rBrace{\dTheta}}.$ Then, we compute the beampattern's derivative and state that
    \begin{equation*}
    % \resizebox{0.9\linewidth}{!}{
        \begin{split}
            &\frac{\partial}{\partial\dTheta}\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB &\\
            &=\frac{\Dp{\dTheta/2,N}{'}\rBrace{1-r\D{\dTheta/2}{N}}-\D{\dTheta/2}{N}\rBrace{-r\Dp{\dTheta/2,N}{'}}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}
            \\
            &=\frac{\Dp{\dTheta/2,N}{'}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}.
        \end{split}
        % }
    \end{equation*}
    It follows that the sidelobes of the feedback-based beampattern are located at the same angles as the in the ULA case.
    \end{minipage}
    }
\else
\fi
By taking a derivative of $\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB$ with respect to $\dTheta$ it can be easily verified that the beampattern's extrema points are located exactly as in the standard ULA beampattern. Specifically, the sidelobes locations are
\begin{equation}
    \label{eqn_CB_sidelobesLocations}
    \Delta\theta_{\text{sidelobe}} = \frac{\rBrace{2m+1}\pi}{N}\ \forall m\in\cBrace{\pm 1,\pm 2,\hdots}.
\end{equation}
Our main interest is with the first sidelobe (i.e. $m=1$), therefore we evaluate \eqref{eq_Hdphi0} at $\Delta\theta = 3\pi/N$, which results in
\begin{equation}
    \abs{\Hr_{{3\pi}/{N},0,r}\omegaB}^2
    =
    \frac{
    2\rBrace{1-r}^{2}
    }{
    \rBrace{N^{2}-2Nr}\rBrace{1-\cos{\rBrace{\frac{3\pi}{N}}}}+2r^{2}
    }
    \label{eq_HSidelobes}
\end{equation}
and for large $N$ values 
\begin{equation*}
    \lim_{N\rightarrow\infty}\abs{\Hr_{3\pi/N,0,r}\omegaB}=\frac{
    2\rBrace{1-r}
    }{
    3\pi
    }.
\end{equation*}
\ifdefined\showDev
    \fbox{
    \begin{minipage}{0.9\linewidth}
    \textbf{development specifics}\\
    We know that \eqref{eq_Hdphi0} can be rewritten as
    \begin{equation*}
        \begin{split}
            \Hr_{\Delta\theta,\Delta\phi=0,r=0} \omegaB=
            \frac{
            \rBrace{1-\cos{\rBrace{N\dTheta}}}\rBrace{1-r}^{2}
            }{
            \begin{split}
                N^{2}&\rBrace{1-\cos{\dTheta}}+r^{2}\rBrace{1-\cos{N\dTheta}}
                \\
                &+Nr\Bigg(1+\cos{\rBrace{\rBrace{N-1}\dTheta}}
                \\
                &-\cos{\rBrace{N\dTheta}-\cos{\rBrace{\dTheta}}}\Bigg)
            \end{split}
            }
        \end{split}
    \end{equation*}
    Using the symbolic toolbox in MATLAB, setting $\dTheta=3\pi/N$, results in \eqref{eq_HSidelobes}.
    \end{minipage}
    }
\else
\fi
\par For standard ULA, the gain of the first sidelobe is known to be $2/3\pi$ \cite{van2004optimum}, which implies that the first sidelobe is smaller by a factor of $1-r$ compared to standard ULA.
Specifically, in perfect gain match scenario (i.e., $r\to{}1$) , the sidelobes vanish. 
\subsection*{Array directivity}
The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
\begin{equation}\label{eq_D}
    \mathcal{D}\rBrace{N,r} = \frac{\Hr_{\Delta\theta=0,\Delta\phi=0,r}}{\frac{1}{2\pi}\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta} = \frac{2\pi}{\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta},
\end{equation}
measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 
\begin{equation}\label{eq_D_result}
    \mathcal{D}\rBrace{N,r} \approx \frac{N-r}{1-r},
\end{equation}
where the standard ULA's known result is obtained for $r=0$.
Also, for $N\geq2$, $\lim_{r\rightarrow 1}\mathcal{D}\rBrace{N,r}=\infty$, implying infinite directivity for the perfectly gain-matched FB. 
\par Finally, expressing the improvement in directivity compared to the standard ULA, assuming large $N$ values, gives rise to
\begin{equation}\label{eq_Dimprovement}
\lim_{N\to\infty}\frac{\mathcal{D}\rBrace{N,r}}{\mathcal{D}\rBrace{N,0}}
=\frac{N/\rBrace{1-r}}{N}=\frac{1}{1-r}.
\end{equation}
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.75\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/directivity_expr.eps}
            \put (20, 10){\footnotesize{$N$}}
            \put (72, 6){\footnotesize{$r$}}
            \put (16.5, 70){\footnotesize{Numerical integration}}
            \put (16.5, 65){\footnotesize{$\rBrace{N-r}/\rBrace{1-r}$}}
            \put (-9, 45){\footnotesize{$\mathcal{D}\rBrace{N,r}$}}
        \end{overpic}
    \end{center}
     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}. Difference between the numerical integration result and the suggested analytic expression is around $\sim{1e^{-9}}$.}
    \label{fig_directivity}
\end{figure}
\subsection*{Summary}
To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance} 
\begin{table}[h!]
    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
    \centering
    \resizebox{1\linewidth}{!}{
        \begin{tabular}{||c c c c||}
            \hline
            & ULA & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 
            \hline\hline
            HPBW & $ 1.4/N$ & $1.4/\rBrace{f(r)N}$ & $f\rBrace{r}$ times smaller\\ 
            \thead{FIRST\\SIDELOBE\\GAIN} & $2/3\pi$ & $2\rBrace{1-r}/3\pi$ & \thead{smaller by a factor of $1-r$\\for $N\gg{}1$} \\
            DIRECTIVITY & $N$ & $\rBrace{N-r}/\rBrace{1-r}$ & \thead{$1/\rBrace{1-r}$ times higher \\ for $N\gg{}1$}\\
            [1ex] 
            \hline
         \end{tabular}
     }
    \label{table_arrayPerformance}
\end{table}

### 2020-10-31 Modules/Spatial_IIR-MathDerivations.tex
Initial Overleaf Import

Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
\begin{equation}
    \label{eqn:SingleSensorTemporalEquality}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            x_{n}(t) = g\rBrace{s\rBrace{t-\tau_{pd}-\tau_{n}}
            +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd}-\tau_{n}}}},
        \end{split}
    % }
\end{equation}
where the first term on the right-hand-side (RHS) represents the contribution of the transmitted waveform $s(t)$ to the $n$'th array element and the second term represents the feedback contribution of the re-transmitted array signal to this same element.
Expressing the Fourier transform of \eqref{eqn:SingleSensorTemporalEquality},
\begin{equation}
    \label{eqn_singleSensorFourier}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            X_{n} =
            g\Bigg( & \F{s}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            \\&+\sum_{m=0}^{N-1}
            {
            \alpha^{*}_{m}\omegaB\F{x}_{m}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            }\Bigg),
        \end{split}
    % }
\end{equation}
and its vector from,
$$
\F{\vx} = g\rBrace{\F{s}+\vAlphaH \F{\vx}}\vd\exp{\rBrace{-j\omega\tau\_{pd}}},
$$
we find that it can be simplified to
$$
\F{\vx} =g\rBrace{I-g\vd\vAlphaH{}e^{-j\omega\tau_{pd}}}^{-1}\vd\F{s}\exp{\rBrace{-j\omega\tau_{pd}}}.
$$
Then, denoting
\[
\phi\triangleq\omega\tau_{pd}
\]
as the round-trip signal propagation related electrical phase and using the Woodbury matrix identity \cite{woodbury1950inverting}, we find that
$$
\F{\vx}
=
\frac{    
g\vd\exp{\rBrace{-j\phi}}
}{
1 - g\aHd{}\exp{\rBrace{-j\phi}}
}\F{s}.
$$
Let $z=\vBetaH{}\vecnot{x}+\text{n}$ be the beamformer's output (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), with Fourier transform $Z$. Considering the noiseless case $\rBrace{\text{i.e., n}=0}$, the frequency response of the FB is 
\begin{equation}
\label{eqn:GeneralFeedbackTransferFunction}
\Hba
\triangleq
\frac{\F{z}}{\F{s}} 
=
\frac{    
g\bHd{}\exp\rBrace{-j\phi}
}{
1 - g\aHd{}\exp\rBrace{-j\phi}
}.
\end{equation}
\par Note that this architecture achieves a controllable (via setting of $\vBeta$ and $\vAlpha$) and recursive (non-trivial denominator) spatial response.
As will be shown, high directivity and narrow beamwidth are obtainable by proper selection of the weights. Compared to traditional beamformers (i.e., without feedback), the performance improvement will be expressed in terms of increased aperture, narrower beamwidth and improved sidelobe attenuation.
One may observe that opposed to traditional beamformers, the array response, $\Hba,$ is not only influenced by the impinging signal DOA, for it is also range selective due to its $\phi$ dependency.
As demonstrated in Fig.~\ref{fig_rangeAzimuthSelectivity}, the combination of both angular and range selectivity enables the designer to enhance signals arriving from specific locations (grey area) rather than only specific directions.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/azimuthRangSelectivity.png}
            \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
            \put (30.5, 47){\rotatebox{0}{\footnotesize{Enhanced radial slice}}}
        \end{overpic}
    \end{center}
    \caption{
    % A visualization of the spatial area selectivity concept.
    Combining both radial selectivity and DOA-based selectivity allows to localize the transmitter.
    }
    \label{fig_rangeAzimuthSelectivity}
\end{figure}

### 2020-10-31 Modules/abstractEnglish.tex
Initial Overleaf Import

State-of-the-art array processing methods, ranging from high-order statistics to adaptive configuration, require costly computing efforts in pursuit for spatial performance improvement.
A feedback based approach is introduced in the context of localization, featuring low complexity and high spatial performance in the excess of integrating a transmitter to the array.  
In the proposed scheme, a signal is continuously re-transmitted between the array and the target of interest.
Considering ideal scenarios, the feedback beamformer virtually achieves an infinite aperture, increasing the available spatial information about the target and significantly improves the array's spatial performance.
Using a traditional beamforming performance analysis, the beamwidth, peak to side-lobe ratio, array directivity and white noise sensitivity are evaluated for the feedback based array.
A significant improvement in all aspects is shown, while thoroughly discussing the conditions for enhanced performance.
As a practical and robust implementation of the feedback-based localization concept, an application of low estimation errors sensitivity, 
is presented and analyzed.

### 2020-10-31 Modules/arrayPerformance_beamwidth.tex
Initial Overleaf Import

The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
It marks the DOA where the beampattern's energy reduces to half of its maximal value.
For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
$$\dThetaHPBW/2= 1.4/N.$$
\par In App.~\ref{apdx_HPBW} we extend this known result for any $r\geq 0$. It turns out that for large $N$, the HPBW is obtained by solving for $x$ the equality
\begin{equation}\label{eq_HPBW}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            \rBrace{r^{2}-4r+2}\frac{\sin{\rBrace{x}}^{2}}{x^{2}}+r\frac{\sin{\rBrace{2x}}}{x}-1=0
        \end{split}
    % }
\end{equation}
where we define $x\triangleq{} N\dTheta_{HPBW}/2$. In Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} we plot the numerical solution of \eqref{eq_HPBW} for various values of $r$ and $N$, showing that $x$ reaches its limit around $N=20$. Also note that for $r=0$ we obtain the known result of standard ULA with the limiting factor of $1.4$.
Having the limiting factors for various values of the gain mismatch $r$, we investigate the feedback related improvement and express the HPBW by
\[
\dThetaHPBW/2\approx \frac{1.4}{f(r)N}.
\]
Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA. 
Numerical evaluation (see Fig.~\ref{fig_feedbackULA_beamwidth_limit_r_dependent}) shows that $f(r)$ may be approximated with a second order polynomial
\begin{equation}
    \label{eq_Bapprox}
    f\rBrace{r}\approx\frac{1.4}{\rBrace{1-r}\rBrace{-0.4r+1.4}}.
\end{equation}
Note that for accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity.
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/spatial_IIR_MATLAB/arrayParameters/HPBW_vs_N_various_r.eps}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 62.5) {\footnotesize{$r=0$}}
            \put (50, 54) {\footnotesize{$r=0.1$}}
            \put (50, 39.5) {\footnotesize{$r=0.3$}}
            \put (50, 28.5) {\footnotesize{$r=0.5$}}
            \put (50, 19.75) {\footnotesize{$r=0.7$}}
            \put (50, 12.5) {\footnotesize{$r=0.9$}}
            \put (50, 2) {\footnotesize{$N$}}
        \end{overpic}
    \end{center}
     \caption{Plot of $x=N\dThetaHPBW/2$ vs. $N$, for various $r$ values, obtained by numerically solving \eqref{eq_HPBW}.}
    \label{fig_feedbackULA_HPBW_Nx_vs_N_variousR}
\end{figure}
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/HPBW_limit_vs_r.eps}
            \put (39.5, 63.5) {\scriptsize{Numerical solution of \eqref{eq_HPBW}}}
            \put (39.5, 58.25) {\scriptsize{Polynomial fitting \eqref{eq_Bapprox}}}
            \put (39.5, 52.5) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (85, 75) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 2) {\footnotesize{$r$}}
        \end{overpic}
    \end{center}
    \caption{Evaluation of $N\dThetaHPBW/2$ for $N=100$ and its approximation $1.4/f\rBrace{r}$  (marked by red diamonds). $f\rBrace{r}$ is also presented, in logarithmic scale (dotted curve).} 
    \label{fig_feedbackULA_beamwidth_limit_r_dependent}
\end{figure}

### 2020-10-31 Modules/estimation_CRLB_appendix.tex
Initial Overleaf Import

A possible evaluation for the contribution of the presented feedback mechanism is to measure the additional information in the system.
To this end, the FIM, denoted by $\vecnot{J}$, will now be calculated with respect to the DOA $\rBrace{\thetaD}$ and range $\rBrace{\phi}$ parameters. 
As the feedback-based transfer function (\ref{eqn:GeneralFeedbackTransferFunction}) is expressed in frequency domain, we rely on \cite{zeira1990frequency} to express the frequency domain FIM as well. 
\par The $\vBrace{k,l}$'th FIM element, may be expressed as
\begin{equation}\label{eq_FIM_kl_full}
    \resizebox{.9\linewidth}{!}{
        \begin{split}
            J_{k,l}\rBrace{\vEta} 
            =&
            \Re\cBrace{
            \frac{1}{2\pi}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            {
            \frac{1}{\Phi\rBrace{\omega}}
            \mathfrak{F}^{*}\left\{
            \frac{\partial z(t)}{\partial\eta_{k}}
            \right\}
            \mathfrak{F}\left\{
            \frac{\partial z(t)}{\partial\eta_{l}}
            \right\}
            d\omega
            }}
            \\ &+
            \frac{T}{4\pi}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            \frac{1}{\Phi^{2}\rBrace{\omega}}
            \rBrace{\frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{k}}}^{\ast}
            \frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{l}}
            d\omega
        \end{split}
    }
\end{equation}
where $ \vEta = [\thetaD,\phi]^{T} $ is the parameters vector, $\Re$ stands for the real-part extraction operator, $k,l \in\cBrace{1,2}$, $\Phi\rBrace{\omega}$ is the noise spectrum, $\mathfrak{F}$ is the Fourier transform operator, $T$ is the measurement observation interval and $\omega_{s}$ is the signal bandwidth. 
For simplicity, $\text{n}\rBrace{t}$ is assumed to be a white Gaussian with some constant power spectral density $\Phi(\omega)=\sigma^2$ and independent of the estimated parameters $\vEta$. Hence, the second term in the right-hand-side of \eqref{eq_FIM_kl_full} vanishes. 
Assuming continuously differentiable functions, where order alteration of the Fourier transform and the differentiation operations is allowed, \eqref{eq_FIM_kl_full} simplifies to
\begin{equation}
    \label{eq_beamPatternFreqDomain_FIM}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            J_{kl}\rBrace{\vEta} = 
            \Re\cBrace{
            \frac{1}{2\pi\sigma^2}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            {
            \rBrace{\frac{\partial{}\F{z}\rBrace{\omega}}{\partial\eta_{k}}}^{\ast}
            \frac{\partial{}\F{z}\rBrace{\omega}}{\partial\eta_{l}}
            d\omega
            }}
        \end{split}.
    % }
\end{equation}
Expressing the steering vector derivative with respect to $\thetaD$, results in
\begin{equation}\label{eq_vdDiff}
\frac{\partial\vd}{\partial\thetaD}=\vecnot{A}\omegaB\vd
\end{equation}
where $\vecnot{A}\omegaB$ is an $N\times{}N$ diagonal matrix with
\[
A_{ii}\omegaB=-j\omega\frac{\partial \tau_{i}}{\partial{\thetaD}}\ \  \forall{i\in\cBrace{0\hdots{}N-1}}.
\]
It is worth mentioning that \eqref{eq_vdDiff} is relevant even for arbitrary arrays (not necessarily ULA) when smooth and slowly changing radiation patterns are assumed.
In App.~\ref{apdx_clacFim} we compute the FIM terms, concluding that
\begin{equation}
    \label{eqn_FIMelements}
    \resizebox{.91\linewidth}{!}{
        \begin{split}
            &J_{11}=J_{\thetaD\thetaD}
            =
            \frac{1}{2\pi\sigma^{2}}\int_{-\omega_{s}/2}^{\omega_{s}/2}{\frac{
            \lBrace{g\vBetaH{}\vecnot{A}\omegaB\vd-g^{2}\vBetaH{}B\omegaB\vAlphaC\ePhi{-}}^{2}
            }{
            \lBrace{1-g\aHd\ePhi{-}}^{4}
            }\lBrace{\F{s}\rBrace{\omega}}^{2}d\omega}
            \\
            &J_{22}=J_{\phi\phi}
            =
            \frac{1}{2\pi\sigma^{2}}\int_{-\omega_{s}/2}^{\omega_{s}/2}{\frac{
            \lBrace{g\bHd}^{2}
            }{
            \lBrace{1-g\aHd\ePhi{-}}^{4}
            }\lBrace{\F{s}\rBrace{\omega}}^{2}d\omega}.
        \end{split}
    }
\end{equation}
where $\vecnot{B}\omegaB\triangleq\vd\vdT{}\vecnot{A}\omegaB-\vecnot{A}\omegaB\vd\vdT.$ 
% Generalizing the conventional beamformer (CB) \cite{van2004optimum}, such that the feedback weights are
% \begin{equation}\label{eq:alpha_beta_opt}
% \vAlpha_{\text{CB,opt}}=\frac{\vdC\exp\rBrace{j\phi}}{\hat{g}\norm{\vd}^2}
% \end{equation}
% where $\hat{g}$ is the channel gain estimate, both maximizes the FIM diagonal elements (via denominator minimization) and nulls it's cross-terms (see App.~\ref{apdx_clacFim}), thus significantly increases the available information.
% Assuming perfect knowledge of the target's location, while
Aiming to maximize the FIM diagonal elements via denominator (i.e., $\lBrace{1-g\aHd\ePhi{-}}$) minimization, the optimal feedback weights are 
\begin{equation}\label{eq:alpha_beta_opt}
\vAlphaC_{\text{CB,opt}}=\frac{\vdC\exp\rBrace{j\phi}}{\hat{g}\norm{\vd}^2},
\end{equation}
where $\hat{g}$ is the channel gain estimate.
This choice of weights may be interpreted as a generalized version of the conventional beamformer (CB) \cite{van2004optimum}. 
Furthermore, setting $\vBeta=\vBeta_{\text{CB,opt}}=\vAlpha_{\text{CB,opt}}$, is shown (see App.~\ref{apdx_clacFim}) to nullify the FIM cross terms, such that $J_{12}=J_{\thetaD,\phi}=J_{21}=J_{\phi\thetaD}=0.$
\par Note that setting the feedback weights as in \eqref{eq:alpha_beta_opt} requires perfect knowledge of the target's range, since $\phi$ is range dependant.
Also, the reader may notice that   assuming $\hat{g}=g$, this choice of optimal weights nullifies the denominator of  \eqref{eqn:GeneralFeedbackTransferFunction}. Thus, theoretically, the FIM becomes infinite when the transfer function \eqref{eqn:GeneralFeedbackTransferFunction} is unstable due to positive and coherent feedback between the beamformer and the target. 
In practice, though, there will be unavoidable errors, and perfect knowledge of target's location and the channel gain is usually unknown.
In Sec.~\ref{sec_Performance}, we quantify the effect of such errors and discuss its influence on the array performance.

### 2020-10-31 Modules/sec_conclusions.tex
Initial Overleaf Import

\section{Conclusions}
\label{sec_conclusions}
Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's residing spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using two frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par Future study of the feedback beamforming concept may be applied to other array processing applications other than localization.
Furthermore, it is worthwhile to inspect other interesting choices of coefficients rather than the conventional-beamformer generalization, other waveforms and associated processing schemes, to extend the results to dynamic/multiple targets and to consider sensors with general radiation patterns.
Also, one may consider generalizing the suggested architecture to multiple-input-multiple-output systems, enabling a steered/focused (rather than omni-directional) feedback transmission.

### 2020-10-31 Modules/sec_rangeSensitivityError.tex
Initial Overleaf Import

\section{Range Error Sensitivity}
\label{sec_sim}
In this section, we investigate $\HrTPr$ for the general case, where also range misalignment phase term $\dPhi$ is possibly non zero. In Fig.~\ref{fig_hDUDTContour}, we plot $\abs{\HrTPr}$ in logarithmic scale, with respect to both steer and range misalignments.
Close inspection of the range error related beampattern behaviour sheds light to some important points.
First, we notice that although setting $r\to1$ (i.e., close to perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks. 
Next, as evident from \eqref{eq_generalH}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).
To establish our final observation, we first recall that
\[
\phi\triangleq\omega\tau_{pd}=\frac{2\pi R_{\text{rt}}}{\lambda},
\]
where $R_{\text{rt}}=2R$ is the round-trip distance between the array and the target of interest. 
Define
\[
\Delta R_{\text{rt}}\omegaB=\frac{\dPhi\lambda}{2\pi} 
\]
to be the range estimation error.
Figure~\ref{fig_rangError} shows that even minor range errors of $\Delta R_{\text{rt}}\sim0.1\lambda$ significantly distort the beampattern.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=.9\linewidth, 
        % grid, 
        tics=10,
        % trim={<left> <lower> <right> <upper>}
        trim={0cm 0cm 1.5cm 0cm}
        ]{./Media/spatialIIR_amb_N3_all_r.eps}
            \put (91, 74) {\footnotesize{dB}}
            \put (-2, 22) {$\frac{\dPhi}{\pi}$}
            \put (5, 74) {\footnotesize{$r=0.4$}}
            \put (51, 74) {\footnotesize{$r=0.6$}}
            \put (5, 38) {\footnotesize{$r=0.7$}}
            \put (51, 38) {\footnotesize{$r=0.8$}}
            \put (19, 3) {\footnotesize{$\dTheta/\pi$}}
        \end{overpic}
    \end{center}
    \caption{Evaluation of $10\log_{10}\abs{\Hr_{\dTheta,\dPhi,r}}^2$, considering both steer ($\dTheta$) and range related ($\dPhi$) errors. Centered in each plot, is the 3dB main lobe (white color fill), exemplifying that as the gain mismatch $r$ is set closer to one, we observe an increase of the spatial selectivity (regarding  both $\dTheta$ and $\dPhi$).}
  \label{fig_hDUDTContour}
\end{figure}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        % grid, 
        tics=10,
        % trim={<left> <lower> <right> <upper>}
        trim={0 0 0 0}
        ]{./Media/spatialIIR_amb_N3r04_multiPeak.eps}
            \put (83, 71) {\tiny{dB}}
            \put (42, -0.5) {\scriptsize{$\dTheta/\pi$}}
            \put (0, 37) {$\frac{\dPhi}{\pi}$}
        \end{overpic}
    \end{center}
    \caption{Evaluation of $10\log_{10}\abs{\Hr_{\dTheta,\dPhi,r=0.4}}^2$ for $-3\pi\leq\dPhi\leq 3\pi$. The response is $2\pi$ periodic.}
  \label{fig_hDUDTContour_mutliPeak}
\end{figure}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        % grid, 
        tics=10,
        % trim={<left> <lower> <right> <upper>}
        trim={0 0 0 0}
        ]{./Media/rangeError_r06.eps}
            \put (-1, 74) {\footnotesize{$10\log_{10}\abs{\Hr_{\dTheta,\dPhi,r}}^2$}}
            \put (46, -1) {\footnotesize{$\dTheta/\pi$}}
            \put (0, 37) {\footnotesize{dB}}
            \put (92, 40) {\footnotesize{$\Delta R_{\text{rt}}=0.1\lambda$}}
            \put (92, 50) {\footnotesize{$\Delta R_{\text{rt}}=0.3\lambda$}}
            \put (92, 30) {\footnotesize{$\Delta R_{\text{rt}}=0$}}
        \end{overpic}
    \end{center}
    \caption{Evaluation of the array response (where $r=0.4$) for several values of range error $\Delta R_{\text{rt}}$ . Even minor range errors significantly distort the beampattern.}
  \label{fig_rangError}
\end{figure}
\par At first glance, this sensitivity to range errors renders the system being too sensitive for any practical use.
This leads us to seek robust implementations, as elaborated in Sec.~\ref{sec_app}.

### 2020-10-31 Modules/stabilityEnhancement_freqPairApproach.tex
Initial Overleaf Import

As demonstrated in the previous section, the beampattern \eqref{eq_generalH} is sensitive to range errors.
We now propose an architecture which obtains the desired beampattern $\Hr_{\Delta\theta,\Delta\phi\to0,r}$ even for relatively large range errors $\Delta R_{\text{rt}}$. Also, we show that the suggested architecture achieves high performance at moderately low signal-to-noise ratio (SNR) scenarios.

\subsection*{Intuition}
Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_generalH} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies. 
Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible. 
Instead, we suggest simultaneous transmission of several frequencies in order to resolve the range error sensitivity. In the following, we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$.

\subsection*{Suggested processing scheme}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.9\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR_APP.png}
            \put (12.5, 64){$\text{FB}_{\vAlphaI{1},\vBetaI{1}}$}
            \put (61, 64){$\text{FB}_{\vAlphaI{2},\vBetaI{2}}$}
            \put (4.5, 59){$z_{1}\rBrace{t}$}
            \put (54, 59){$z_{2}\rBrace{t}$}
            \put (12.9, 41.5){$\text{BPF}_{\omega_{1}}$}
            \put (61.65, 41.5){$\text{BPF}_{\omega_{2}}$}
            \put (6, 51.5){+}
            \put (55, 51.5){+}
            \put (16, 51.5){\footnotesize{$\text{n}_{1}\rBrace{t}$}}
            \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
            \put (24.5, 59){\footnotesize{$\Tx_{1}\rBrace{t}$}}
            \put (73.5, 59){\footnotesize{$\Tx_{2}\rBrace{t}$}}
            \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
            \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
            \put (18.25, 13){\footnotesize{Harmonic mean}}
            \put (32, 2){$Z_{\text{DF}}$}
            \put (54.75, 24){$\Sigma$}
            \put (21.75, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
            \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
        \end{overpic}
    \end{center}
    \caption{Dual-frequency beamformer, consisting of two independent FB blocks and narrowband bandpass filters. The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the Fourier coefficients in $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF beamformer's output.}
    \label{fig_app}
\end{figure}
In Fig.~\ref{fig_app}, we demonstrate the use of two independently configured FB instances (see also Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), where each instance is designed to treat a specific frequency band.
A bandpass filter $\text{BPF}_{\omega_{i}},\;i=1,2$ filters a narrowband slice around $\omega_{i}=2\pi f_i$. These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$. 
The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ describe the additive noise.

Note that in the suggested architecture we do not add array elements, but merely double the beamformer processing effort. 
\par For each FB block, its output is given by
\[
z_{i}(t)=H_{\vBetaI{i},\vAlphaI{i}}\rBrace{\omega_{i}}\exp{\rBrace{j\omega_{i}t}}\ \ {i\in\cBrace{1,2}},
\]
where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}, we compute the reciprocal of each frequency response, average, and compute the reciprocal again. This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
\begin{equation}
    \label{eqn_HDF_def}
    Z_{\text{DF}} = \abs{H^{-1}_{\vBetaI{1}\vAlphaI{1}}\rBrace{\omega_{1}}+H^{-1}_{\vBetaI{2},\vAlphaI{2}}\rBrace{\omega_{2}}}^{-1}.
\end{equation}
% Note that, as in IIR filters, the system stabilizes after a certain period, therefore the Fourier weights should be calculated after stabilization.
% As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
\ifdefined\useOmega
Straight forward derivations, Allowing $g$ to be frequency dependent, leads to
\else
For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
Also, $r_i\triangleq{}\gI{i}/\gIHat{i}$ is denoted to be the gain mismatch at $\omega_i$.

\begin{theorem}
\label{thrm_DF}
Consider the architecture suggested in Fig.~\ref{fig_app}, and let \textit{$\vAlphaI{i},\vBetaI{i}$} be the coefficients of the $i$'th FB. Then setting 
\begin{equation}\label{eqn_simpleBeta}
    \vAlphaI{1}~=~\vBetaI{1},\ \vAlphaI{2}=-\vBetaI{2}=\vBrace{1/\gIHat{2},0,\hdots,0},
\end{equation}
results in 
\begin{equation}
    Z_{\text{DF}} = \lBrace{\frac{\gI{1}\vBetaHI{1}\vdI{1}}{1-
    \rBrace{\gI{1}\vBetaHI{1}\vdI{1}/r_{2}}\exp\rBrace{-j\rBrace{\phiI{1}-\phiI{2}}}
    }},
    \label{eqn_H_DF_general}
\end{equation}
\end{theorem}

\begin{proof}
See App.~\ref{apdx_thrm_DF}. 
\end{proof}
\par Assuming close frequencies, $Z_{\text{DF}}$ in  \eqref{eqn_H_DF_general} closely resembles the single frequency (SF) beampattern in  \eqref{eqn:GeneralFeedbackTransferFunction}, where the range related phase $\phi$ is now replaced by  $\phiI{1}-\phiI{2}=(\omega_1-\omega_2)\tau_{pd}$. 
Hence, one may significantly mitigate the range mismatch distortion of the beampattern by selecting close stimuli frequencies.
% Also, $\tau_n$ is arbitrary, hence the discussion is not restricted to a specific array geometry.
We also note that throughout the development of \eqref{eqn_H_DF_general}, we did not assume any specific array geometry, hence this result is valid for arbitrary arrays and not just ULA.
\subsection*{Numerical example}
Consider a radio frequency carrier of $10$~GHz and typical range error of $\Delta{}R_{\text{rt}}=10$~m, which is $333\frac{1}{3}\lambda$ (assuming  speed of light, $c=3\cdot 10^{8}$~m/s). The single frequency beampattern distortion, being periodic in $\lambda$, will closely resemble the $0.3\lambda$ error plot presented in Fig.~\ref{fig_rangError}. Assume that we aim to achieve a maximal phase error of $\Delta \phi=0.01\pi$. Hence, when using DF architecture, the dictated frequency separation must satisfy
\begin{equation}\label{eq_DF_phErr}
\abs{(\omega_1-\omega_2)\frac{\Delta{}R_{\text{rt}}}{c}}<0.01\pi.
\end{equation}
or equivalently, for maximal range error of $10$~m, a frequency separation of
\[
\abs{f_1-f_2}<0.005 c/\Delta{}R_{\text{rt}}=150 \,\text{kHz}
\]
is required.

\subsection*{Dual frequency simulation}
We now simulate \eqref{eqn_H_DF_general} for the DF structured FB,
generalizing the $\coefSetName$ approach and setting
\begin{equation*}
    \vBetaCI{1}=\frac{-\vdHatIC{1}\exp\rBrace{j\rBrace{\phiIHat{1}-\phiIHat{2}}}}{\hat{\gI{1}}\norm{\vdHatI{1}}^2}.
\end{equation*}
% where $\vdHatI{1}$ is the estimated steering vector, as in \eqref{eq:d_hat}.
With this choice, and similarly to \eqref{eq:SF_CB}, \eqref{eqn_H_DF_general} becomes
\begin{equation}
    \label{eqn_H_DF_CB}
    \resizebox{.89\linewidth}{!}{
        \begin{split}
            H_{\text{DF,\coefSetName}}\rBrace{\omega} =
            \lBrace{\frac{r_{1}\D{\dTheta/2}{N}}{1-
            \kappa\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\phiI{2}-\phiI{1}+(N-1)\dTheta/2}}}
            },
        \end{split}
    }
\end{equation}
where $\kappa\triangleq{}r_{1}/r_{2}$ is the gain mismatch ratio.
For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both feedback beamformers are mismatched.
\par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer. Evidently, even in the noisy case, the DF beamformer achieves close-to-ideal beampattern, while the SF beamformer suffers severe distortions.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_dualfreq_rangeErrorHighSnr.eps}
            \put (48, 43){\scriptsize{Ideal}}
            \put (48, 37.5){\scriptsize{SF}\tiny{$_{\Delta{}R_{\text{rt}}=10_{m}}$}}
            \put (48, 32){\scriptsize{DF}\tiny{$_{\Delta{}R_{\text{rt}}=10_{m}}$}}
            \put (2, 37.5){\footnotesize{dB}}
            \put (47,0){\footnotesize{$\thetaD/\pi$}}
        \end{overpic}
    \end{center}
    \caption{Simulating the 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR. For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$. 
    The (modulus $\lambda$) range error is $\Delta{}R_{\text{rt}}=0.3\lambda$.
    The single frequency (SF) beamformer (red squares) and the dual-frequency (DF) solution (green diamonds) are compared to the ideal response  $\Delta{}R_{\text{rt}}=0$ (blue dots) as a reference. 
    }
    \label{fig_dualfreq_rangeErrorHighSnr}
\end{figure}
% \begin{figure}[t!]
%     \begin{center}
%         \begin{overpic}[width=0.9\linewidth, 
%         % grid, 
%         tics=10,
%         % trim={<left> <lower> <right> <upper>}
%         trim={1.75cm 0 1.75cm 0}
%         ]{./Media/fig_dualfreq_rangeErrorLowSnr.eps}
%             \put (42.25, 17.5){\scriptsize{Ideal}}
%             \put (42.25, 14.5){\scriptsize{SF}}
%             \put (42.25, 11.5){\scriptsize{DF}}
%             \put (-1, 26.5){\footnotesize{dB}}
%             \put (22, 0){\footnotesize{$\thetaD/\pi$}}
%             \put (74.5, 0){\footnotesize{$\thetaD/\pi$}}
%             \put (19,17){\scriptsize{$\text{SNR}=6_{dB}$}}
%             \put (71.5,17){\scriptsize{$\text{SNR}=0_{dB}$}}
%         \end{overpic}
%     \end{center}
%     \caption{Directional response of the 3 element ULA, as in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr}, simulated for the noisy scenario. The additive noises $\text{n}_1(t)$ and $\text{n}_2(t)$ (see Fig.~\ref{fig_app}), are set to obtain SNR of $6_{dB}$ (left plot) and $0_{dB}$ (right plot).}
%     \label{fig_dualfreq_perfectAlignLowSnr}
% \end{figure}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=.9\linewidth, 
        % grid, 
        tics=10,
        % trim={<left> <lower> <right> <upper>}
        trim={1.75cm 0 1.75cm 0}
        ]{./Media/fig_dualfreq_rangeErrorLowSnr_NEW.eps}
            \put (9, 30){\scriptsize{Ideal}}
            \put (9, 25.5){\scriptsize{SF}}
            \put (9, 21){\scriptsize{DF}}
            \put (-4, 60){\footnotesize{dB}}
            \put (53, 60){\footnotesize{dB}}
            \put (25, 20){\footnotesize{dB}}
            \put (20, 42){\footnotesize{$\thetaD/\pi$}}
            \put (77, 42){\footnotesize{$\thetaD/\pi$}}
            \put (49, 2){\footnotesize{$\thetaD/\pi$}}
            \put (16,52){\scriptsize{$\text{SNR}=6_{dB}$}}
            \put (74,52){\scriptsize{$\text{SNR}=0_{dB}$}}
            \put (44.5,12){\scriptsize{$\text{SNR}=-6_{dB}$}}
            \put (4,42.5){\footnotesize{(a)}}
            \put (60.5,42.5){\footnotesize{(b)}}
            \put (32,2){\footnotesize{(c)}}
        \end{overpic}
    \end{center}
    \caption{Directional response of the 3 element ULA, as in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr}, simulated for the noisy scenario. The additive noises $\text{n}_1(t)$ and $\text{n}_2(t)$ (see Fig.~\ref{fig_app}), are set to obtain SNRs of $6$~dB (a), $0$~dB (b) and $-6$~dB (c).}
    \label{fig_dualfreq_perfectAlignLowSnr}
\end{figure}

### 2020-10-31 front/abbrevs.tex
Initial Overleaf Import

% Just write down your abbervations here - or comment-out the command

\abbreviationsAndNotation{
\begin{tabular}{p{2cm}@{:\quad}l}
QED & quod erat demonstratum \\
$c$ & the speed of light \\
$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
\end{tabular}
}

### 2020-11-06 Modules/sec_prlm_arrPerf.tex
Preliminaries copied - before process

Numerous performance measures are utilized for evaluating the microphone array capabilities. 
Each of the measures aims to quantify a significant aspect of either the response of an array to the signal environment or of the sensitivity to an array design error.
First, we review the concept of beampatterns. 
Beampatterns are the main tool in assessing an array performance as they express the beamformer response for various frequencies and signal angles. 
Let $P\rBrace{\omega,\theta}$ denote the frequency and DOA dependent beamformer response. It is given by:
\begin{equation}
P\rBrace{\omega,\theta}=\sum_{m=0}^{M-1}e^{-j\omega\tau_{m}w_{m}^{*}}=\vecnot{w}^{H}\vecnot{v}\rBrace{\omega,\theta}    
\end{equation}
where $\vecnot{w}=\vBrace{w_{0},\dots,w_{M-1}}^{T}$ and $^{H}$ denotes Hermitian transpose operation, and let $D\rBrace{\omega,\theta}$ denote the beampattern of a given beamformer. 
It is expressed by:
\begin{equation}
D\rBrace{\omega,\theta}=20\log_{10}\abs{P\rBrace{\omega,\theta}},
\end{equation}
where $\abs{\cdot}$ denotes the absolute value. 
For a given angular frequency $\omega$, the beampattern $D\rBrace{\omega,\theta}$ is a function of the angle $\theta$ and the beamwidth is measured in terms of $\theta$.
In this work, the beamwidth is measured between the two lowest values at both sides of the main lobe.
\par
A major challenge in practical beamformer applications is the potential sensitivity to mismatches between the actual array attributes and the model used to derive the desired beamformer. 
In practical applications, mismatches can occur either by array location perturbations, production faults or filter perturbations. 
The sensitivity function often used as a criterion for assessing the affect of mismatches on the array response is defined in \cite{van2004optimum} by:
\begin{equation}
T_{se}=A^{-1}_{w}=\abs{\abs{\vecnot{w}}}^{2},
\end{equation}
where $A_{w}^{-1}$ is the inverse expression of the white noise gain given by $A_{w}=\text{SNR}_{out}\rBrace{k}/\text{SNR}_{in}\rBrace{k}$ and $\vecnot{w}$ is the weight vector corresponding to all of the FIR filter channels in the $k$-th frequency bin. Therefore, as the white noise gain increases, the sensitivity decreases and the array would be more robust to mismatch.

### 2020-11-06 Modules/sec_prlm_propWaveField.tex
Preliminaries copied - before process

In array signal processing, propagating waves carry signals from the source to the array.
Therefore, these signals are represented in the time-space domain. The space domain is represented by either the three dimensional Cartesian coordinates $\rBrace{x,y,z}$ or the three dimensional spherical coordinates $\rBrace{r,\phi,\theta}$, where $0 \leq \phi \leq 2\pi$, $0 \leq \theta \leq \pi$ are the azimuth and elevation angles, respectively. The time domain is represented by $t$.
Finally, let $f\rBrace{t,\vecnot{r}}$ denote the time-space representation of the input signal, where $\vecnot{r}$ is the radius-vector in the three-dimensional system. The relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
$f\rBrace{t,x,y,z}$ describes the signal impinging the microphone array. The physics of propagation within a homogeneous (constant speed of propagation), dispersion free (no signal degradation due to other frequencies) and lossless (no signal gain attenuation) medium is described by the wave equation:
\begin{equation}
\label{eq_prlm_waveEq}
\nabla^{2}f\rBrace{t,x,y,z}=\frac{1}{c^2}\frac{\partial^{2}f\rBrace{t,x,y,z}}{\partial{t^{2}}}
\end{equation}
Where $\nabla^{2}$ represents the Laplacian operator and $c$ represents the wave's velocity.
\begin{figure}[h!]
    \begin{center}
        \begin{overpic}[width=0.5\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_coordinates.png}
            % \put (50, 62.5) {\footnotesize{$r=0$}}
        \end{overpic}
    \end{center}
     \caption{A three dimensional coordinate system with Cartesian and spherical coordinates.}
    \label{fig_coordinates}
\end{figure}
Let $f_p\rBrace{t,x,y,z}$ denote a possible solution to \eqref{eq_prlm_waveEq} of a complex exponential form:
\begin{equation}
\label{eq_prlm_waveEq_pSol}
f_p\rBrace{t,x,y,z} = A\exp{j\rBrace{\omega{t}-k_{x}x-k_{y}y-k_{z}z}}
\end{equation}
Where $A$ is a complex constant, $\omega$ denotes a constant temporal frequency and $k_{x}x,k_{y},k_{z}$ are real constants. 
Substituting \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} yields:
\begin{equation}
\label{eq_prlm_waveEq_subs}
k_{x}^{2}-k_{y}^{2}-k_{z}^{2} = \frac{\omega^{2}}{c^{2}}.
\end{equation}
This solution is called a monochromatic plane wave. The term plane wave is derived from the fact that at any given time, $t_{0}$, the value of $f\rBrace{t_{0},x,y,z}$ is the same at all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$.
Finally, writing the solution to \eqref{eq_prlm_waveEq} using vector notation we obtain:
\begin{equation}
\label{eq_prlm_waveEq_finSol}
f\rBrace{t,\vecnot{x}}=A\exp{j\rBrace{\omega{t}-\vecnot{k}\vecnot{x}}}.
\end{equation}
Let $\vecnot{k}\vecnot{x}=constant$ denote planes of constant phase. 
If the signal $f\rBrace{t,\vecnot{x}}$ is indeed propagating, planes of constant phase move by small steps of $\delta{\vecnot{x}}$, with small time increments of $\delta{t}$, i.e. $f\rBrace{t+\delta{t},\vecnot{x}+\delta{\vecnot{x}}} = f\rBrace{t,\vecnot{x}}$, which yields
\begin{equation}
\omega\delta{t}-\vecnot{k}\delta\vecnot{x}=0.
\end{equation}
Assuming $\delta\vecnot{x}$ and $\vecnot{k}$ have the same direction, $\vecnot{k}\delta\vecnot{x} = \abs{\vecnot{k}}\abs{\delta\vecnot{x}}$ and $\frac{\delta{\vecnot{x}}}{\delta{t}} = \frac{\omega}{\abs{\vecnot{k}}}$, where $\frac{\delta{\vecnot{x}}}{\delta{t}}$ can designate the propagation speed of the plane wave. 
Since $\vecnot{k}$ and $\omega$ are related by $\abs{\vecnot{k}}^{2}=\frac{\omega^{2}}{c^{2}}$, we have
\begin{equation}
\label{eq_prlm_waveEq_stepsEq}
\frac{\delta{\vecnot{x}}}{\delta{t}}=c,
\end{equation}
Assuming that $c>0$.
Thus, the speed of propagation is indeed $c$.
Let $\lambda$ denote the distance the plane wave propagated during a single temporal period of $T=\frac{2\pi}{\omega}$.
This distance is referred to as the \emph{wavelength}. 
Due to its spatial traits, after one period the monochromatic plane wave appears the same as one period before, but moved forward.
Let $\vecnot{k}$ denote the \emph{wavelength vector}. 
Its magnitude $\abs{\vecnot{k}}$ expresses the number of cycles in radians per meter of length that the plane wave has exhibited in the propagation direction.
Using \eqref{eq_prlm_waveEq_stepsEq} with $delta{t} = \frac{2\pi}{\omega}$, we obtain:
\begin{equation}
\lambda=\delta{\vecnot{x}}=\frac{2\pi}{\abs{\vecnot{k}}}.
\end{equation}
Therefore, the wavenumber vector can be considered to represent spatial frequency, similarly to the manner $\omega$ represents temporal frequency.

### 2020-11-06 Modules/sec_prlm_sensorArrays.tex
Preliminaries copied - before process

Microphone arrays consist of sets of microphones positioned in a way to function as a directional acoustic antenna. 
Microphone arrays are utilized for filtering signals in a space-time field. 
Filtering is enabled by exploitation of the incoming signals spatial characteristics. 
A desirable spatial filtering, i.e., beamforming, should result in enhancement of signals of interest, originated in a specific direction, while forcing suppression of undesired signals originated in other directions.
Microphone arrays are utilized for solving many signal processing problems: dereverberation, localization of a single source, noise reduction and source separation \cite{cohen2004multichannel,habets2006dual,pavlidi2013real}.
\par 
Numerous factors must be taken into consideration when designing a microphone array configuration.
Initially, the geometry of the microphone array plays an important role in the formulation of the processing algorithms, as it forces fundamental constraints on the array’s operation. 
In most cases, the array geometry is the first consideration in array design due to practical and physical constraints of the design. 
Therefore, the degree of freedom in choosing the array geometry is limited. 
Nevertheless, in some other crucial problems such as noise reduction or source separation, the geometry of the array may have little importance. 
For instance, Uniform Linear Arrays (ULA) can only handle one source direction at a time resulting in uncertainties and possibly direction ambiguities.
Therefore, ULA configurations must be ruled out when handling several signal sources.
Other array geometries such as non-uniform linear arrays and circular arrays, have been studied in the field \cite{liu2008design,van2004optimum}.
This work is based on ULA and therefore we elaborate on this geometry.
A conventional beamformer \cite{van2004optimum} is composed of a ULA of microphones. 
That is, the microphones are positioned on an axis with a uniform spacing between the microphones.
The general expression of the microphone positioning in a ULA is given by:
\begin{equation}
x_{m}=m\cdot{d}, m=0, 1, \dots, M-1
\end{equation}
where $m$ denotes the microphone index; $x_{m}$ denotes the position of the microphone having index $m$, where $x_{m} = 0$ corresponds to the left-hand side of the array, i.e., the location where the microphone indexed by $m = 0$ is positioned; $d$ denotes the spacing between microphones, and $M$ is the array size, i.e., the number of microphones in the array, as demonstrated in Fig.~\ref{fig_ULA}.
\begin{figure}[h!]
    \begin{center}
        \begin{overpic}[width=0.5\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_ULA.png}
            % \put (50, 62.5) {\footnotesize{$r=0$}}
        \end{overpic}
    \end{center}
     \caption{A uniform linear array of size M and spacing d.}
    \label{fig_ULA}
\end{figure}

### 2020-11-06 Modules/sec_prlm_timeSpaceSig.tex
Preliminaries copied - before process

The incoming signals are spatially sampled by the array microphones, then the samples are processed to attenuate signals from undesired directions and extract the signal from a desired direction. 
A spatial response of the microphone array is obtained via a beam (main-lobe) directed to the desired signal while nulls are directed to the undesired signals.
\begin{figure}[ht!]
    \begin{center}
        \begin{overpic}[width=0.5\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_ULA_imping.png}
            % \put (50, 62.5) {\footnotesize{$r=0$}}
        \end{overpic}
    \end{center}
     \caption{A simple beamformer design.}
    \label{fig_ULA_imping}
\end{figure}
Fig.~\ref{fig_ULA_imping} illustrates a beamformer design based on a ULA of Fig.~\ref{fig_ULA}.
Let $\vecnot{f}\rBrace{t,\vecnot{x}}$ denote the set of signals sampled by the microphone array at time $t$, expressed by
\begin{equation}
\vecnot{f}\rBrace{t,\vecnot{x}} = \vBrace{f\rBrace{t,x_{0}},\dots,f\rBrace{t,x_{M-1}}}^{T},
\end{equation}
where $x_{m}$ denotes the microphone position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
The beamformer output $y\rBrace{t}$ is expressed by:
\begin{equation}
y\rBrace{t} = \sum_{m=0}^{M-1}{f\rBrace{t,x_{m}}\omega_{m}^{*}},
\end{equation}
where $\omega_{m}$ is a complex weight of the microphone having index $m$, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
The simplest beamformer design architecture has uniform weights, $\omega_{m}=\frac{1}{M}, m=0,\dots,M-1$.
Let $f_{\omega}\rBrace{t,x} = e^{j\omega{t}}$ denote a plane wave propagating at angular frequency $\omega$, and let $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ denote the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
The wave signals spatially sampled by the microphone array inputs are given by:
\begin{equation}
\label{eq_prlm_timeSpace_outputVec}
\vecnot{f}\rBrace{t,x} = \vBrace{f_{\omega}\rBrace{t-\tau_{0}}, \dots, f_{\omega}\rBrace{t-\tau_{M-1}}}^{T}, \tau_{m} = \frac{\sin{\theta}\cdot{}x_{m}}{c},
\end{equation}
where $\tau_{m}$ is the propagation delay for the incoming signal and $c$ is the wave's velocity in the medium.
A value of $\tau_{m}=0, \forall{m}$ implies a DOA of $\theta = 0$, i.e. a plane wave parallel to the array, propagating perpendicularly to the array.
Let $\kappa=\frac{\omega}{c}\sin{\theta}=\frac{2\pi}{\lambda}\sin{\theta}$ denote the wavenumber for plane waves in a locally homogeneous medium, where λ denotes the wavelength corresponding to the angular frequency $\vecnot{v}\rBrace{\kappa}$ denote the \emph{array manifold vector} \cite{van2004optimum}, featuring all of the spatial characteristics of the microphone array.
Based on \eqref{eq_prlm_timeSpace_outputVec}, and the definition of κ above, the manifold vector can be expressed as
\begin{equation}
\vecnot{v}\rBrace{\kappa}=\vBrace{e^{-j\kappa{}x_{0}},\dots,e^{-j\kappa{}x_{M-1}}}^{T}.
\end{equation}

### 2020-11-06 main/prelims.tex
Preliminaries copied - before process

\chapter{Preliminaries}
\label{chap:prelims}

In this chapter, we overview the theoretical basis of the thesis. 
In section 1...
In section 2...
In section 3...

\begin{definition}
The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
\end{definition}

\section{Propagating Wave Fields}
\label{sec:prlm_propWaveField}
\input{Modules/sec_prlm_propWaveField}
\section{Sensor arrays}
\label{sec:prlm_sensorArrays}
\input{Modules/sec_prlm_sensorArrays}
\section{Time-Space Signals}
\label{sec:prlm_timeSpaceSig}
\input{Modules/sec_prlm_timeSpaceSig}
\section{Sensor array performance measure}
\label{sec:prlm_sensorArrayPerf}
\input{Modules/sec_prlm_arrPerf}
\section{Finite Impulse Response Based Spatial Filtering}
\label{sec:prlm_FIR}
\input{Modules/sec_prlm_FIR}
\section{Infinite Impulse Response Filters}
\label{sec:prlm_IIR}
\section{Fisher Information Matrix}
\label{sec:prlm_FIM}

Let's define some concept we'll be using throughout the thesis.

### 2020-12-25 Modules/IEEE_journal_paper_Intro.tex
Before applying meeting#1's comments

@@
 \par A uniform linear array (ULA) has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
-The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
+The array size and the number of its elements ($N$) have significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
 For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.
 \par In pursuit of spatial performance improvement, namely higher spatial separation and selectivity of arriving signals, many approaches were suggested.  
-One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
+One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging on missing sensors.
 Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
@@
 \par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g.
-narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?''
-\par Achieving spatial IIR response has also motivated other works.
+narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the spatial domain processing methods which will be analogous to temporal domain IIR filtering?''
+\par Achieving a spatial IIR response has also motivated other works.
 In \cite{wen2013extending} two methods were considered.
 The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain.
-The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array.
+The second approach suggested to consider overlapping subsets of one large ULA as a finite approximation to an infinite array.
 Surely, the former approach heavily relies on the accuracy of the delay estimation and the latter approach does not achieve a recursive spatial response.
 In both cases, there is no true spatial feedback between the array and the source of interest.
-Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
+Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in the temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.
-To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
-\par The novelty, compared to traditional array processing, is the incorporation of spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
-Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
+To this end, we arbitrarily choose to formulate the problem in the context of localization, hence our goal is to estimate the direction and the range of some target of interest. 
+\par The novelty, compared to traditional array processing, is the incorporation of a spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
+Assuming the target of interest has a mirror-like behaviour (i.e.
+reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
 Note that the initial stimulus can be generated by the target or the array itself. In the text to follow, we assume this is the latter. 
@@
 Finally, concluding remarks are given in Sec.~\ref{sec_conclusions}.
-\section{Beamforming}\label{sec:setup}
-In this section, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented.
-Consider an $N$-element ULA with inter-element spacing $\delta$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$.
-We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
-Focusing on a far field localization problem, DOA and target range are to be estimated.
-Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
-For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
-Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, reflects back from the target and re-impinges the array, with total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
-In this this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
-$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
-Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and hermitian transpose of the matrix $\vecnot{A}$ respectively.
-\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
-\begin{equation}
-x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
-\label{eqn:noFeedbackULA_singleSensor_temporal}
-\end{equation}
-where $\tau_{n}=n\delta\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
-Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write
-\[
-\vecnot{\F{x}}\rBrace{\omega}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}
-\]
-where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
-\begin{equation}
-    \label{eq:d}
-    d_{n}\rBrace{\omega} = \exp{\rBrace{-j\omega\tau_{n}}}.
-\end{equation}
-Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in frequency domain
-\begin{equation}
-    \label{eq_Z}
-    Z\rBrace{\omega} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
-\end{equation}
-Defining the electric phase to be
-\begin{equation}\label{eq:thetaULA}
-\theta=\omega{\delta\cos\Brack{\thetaD}}/{c},
-\end{equation}
-we rewrite \eqref{eq_Z} as 
-\[
-Z\rBrace{\omega} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
-\]
-hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to FIR filter design~\cite{van1988beamforming,benesty2018}.
-\ifdefined\useOmega \else 
-Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest this paper, where possible.
-\fi
-\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest.
-Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.).
-As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
-Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rater than using pulse based signals. 
-% The suggested structure is elaborated in Sec.~\ref{sec_introduceFeedback} and shown to be equivalent to IIR filter design.
-\section{Feedback Beamforming}
-\label{sec_introduceFeedback}
-In this section, a feedback-based architecture is proposed for spatial signal processing.
-Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIRBasicArch}), 
-we propose to use the same concept in the spatial domain.
-\begin{figure}[t!]
-    \begin{center}
-        \begin{overpic}[width=0.6\linewidth, 
-        % grid, 
-        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
-            \put (60, 50){\footnotesize{$\beta_{0}$}}
-            \put (60, 30){\footnotesize{$\beta_{1}$}}
-            \put (60, 10){\footnotesize{$\beta_{2}$}}
-            \put (36, 30){\footnotesize{$\alpha_{1}$}}
-            \put (36, 10){\footnotesize{$\alpha_{2}$}}
-            \put (10, 50){\footnotesize{$x$}}
-            \put (85, 50){\footnotesize{$y$}}
-            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
-            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
-        \end{overpic}
-    \end{center}
-    \caption{Direct form II $2^{nd}$ order IIR architecture.}
-    \label{fig_IIRBasicArch}
-\end{figure}
-The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}.
-The beamformer's output and the feedback signal are synthesized with two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.
-Also, the FB block is marked (dashed line) for later use.
-Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to a plain delay-and-sum (DS) beamformer.
-\begin{figure}[t!]
-    \begin{center}
-        \begin{overpic}[width=0.95\linewidth, 
-        % grid, 
-        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR-diagram/SpatialIIR_VER8.png}
-            \put (14, 39){\footnotesize{$\sum_{n=0}^{N-1}\beta^{*}_{n}x_{n}$}}
-            \put (54, 39){\footnotesize{$\sum_{n=0}^{N-1}\alpha^{*}_{n}x_{n}$}}
-            \put (24.25, 50){\footnotesize{$x_{0}$}}
-            \put (35, 50){\footnotesize{$x_{1}$}}
-            \put (55, 50){\footnotesize{$x_{N-1}$}}
-            \put (30.5, 66){\footnotesize{$\delta$}}
-            \put (89, 96){\footnotesize{$\vpt$}}
-            \put (58, 58){\footnotesize{$\vpi{N-1}$}}
-            \put (37, 58){\footnotesize{$\vpi{1}$}}
-            \put (26.5, 58){\footnotesize{$\vpi{0}$}}
-            \put (41.5, 64.5){\footnotesize{$\theta_{g}$}}
-            \put (19, 11.25){\large{$+$}}
-            \put (61.25, 27.25){\large{$+$}}
-            \put (47, 11.75){$s$}
-            \put (35.25, 11.75){$n$}
-            \put (21,4){$z$}
-            \put (63.5,14){$\Tx$}
-            \put (1, 51){$\text{FB}_{\vAlpha,\vBeta}$}
-        \end{overpic}
-    \end{center}
-    \caption{
-    The proposed feedback beamformer.
-    The spatial feedback is obtained by continuous re-transmission of $\Tx$ to the target at $\vpt$.
-    We designate the feedback beamformer block (dashed line) for later use.
-    }
-    \label{fig:Proposed_spatialIIR_ARCH}
-\end{figure}
-\subsection*{Obtained spatial response}
-\input{./Modules/Spatial_IIR-MathDerivations.tex}
-\section{Fisher Information Matrix}
-\label{sec_FIM}
-\input{./Modules/estimation_CRLB_appendix.tex}
-\section{Performance Analysis}
-\label{sec_Performance}
-In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance: Beamwidth, peak-to-sidelobe level, and directivity.
-Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.
-\subsection*{Error terms}
-In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
-Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
-\begin{equation}\label{eq:alpha_beta_hat}
-\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
-\end{equation}
-introducing the estimated steering vector 
-\begin{equation}\label{eq:d_hat}
-\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
-\end{equation}
-Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
-\begin{equation}\label{eq:SF_CB}
-    \resizebox{.894\linewidth}{!}{
-        \begin{split}
-            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
-        \end{split}
-    }
-\end{equation}
-where \[
-\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
-\]
-is the normalized Dirichlet kernel and
-we define the DOA, range and gain error terms 
-\[
-\dTheta\triangleq\theta\omegaB-\hat{\theta}\omegaB,\ \dPhi\triangleq\phi\omegaB-\hat{\phi}\omegaB,\ 
-r\triangleq g/\hat{g},
-\]
-respectively.
-\ifdefined\useOmega\else
-We then define four fundamental scenarios:
-\fi
-\begin{itemize}
-    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Steer error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
-    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
-\end{itemize}
-\ifdefined\showTodo
-{
-    \subsection*{Small estimation error analysis - \textbf{TO BE REMOVED - kept only for the todos}}
-    \label{subsection_ArrayPerformance_TayolrAnalysis}
-    \myTodo{inline}{\textbf{DONE:}\\ maybe to call this subsection 'small error analysis'}
-    Plugging (\ref{eqn_CB_coefSet}) into (\ref{eqn:GeneralFeedbackTransferFunction}) and denoting $\D{N}{x} \triangleq \frac{\sin{\rBrace{Nx}}}{\sin{\rBrace{x}}}$ results in the general \coefSetName{} beampattern \myTodo{inline}{\textbf{DONE}\\you need to define the delta expressions (the errors)}
-    \begin{equation*}
-        h_{\coefSetName{}}\rBrace{\theta,\omega}
-        =
-        \frac{
-        \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
-        }{
-        N - \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
-        }.
-    \end{equation*}
-    For the evaluation of the various array parameters, we define the normalized beampattern \myTodo{inline}{\textbf{DONE:}\\not very readable.
-Consider writing a multiplication of two terms.
-Suggesting that you write the expression in eq(5) as $H(\theta,\phi)$ and here you'll have $H(\hat{\theta}, \hat{\phi})/ H(\theta,\phi)$}
-    \begin{equation}
-        \label{eqn_arrPerformance_beamwidth_3dB}
-        \Hr{\theta}{\tau}{}\triangleq\fbBpRatio.
-    \end{equation}
-    \myTodo{inline}{\textbf{DONE:}\\this next section is very long.
-Suggesting that you express (10) in terms of the errors $\Delta\theta,\;\Delta\phi$, and then simply state that the second order Taylor expansion of those errors around zero gives (12).
-One more issue which I think might cause us some headache is that we cannot assure that $\Delta\phi$ (you call it $\Delta\tau$) is indeed close to zero, as this term fluctuates very fast.
-But we will think about it later on.
-Maybe something with wideband signal stimulus will solve this issue.}
-    The pursuit for analytic dependencies between $\Hr{\theta}{\tau}{}$, $\dTheta$ and $\dPhi$, as in \cite{van2004optimum}, lead to expressing $\Hr{\theta}{\tau}{}$'s multivariate Taylor expansion, setting $\dTheta,\dPhi$ as the variables.
-Simulations have shown that $2^{nd}$ Taylor expansion achieves very accurate results, thus we use it to express the array parameters.
-As commonly known, the Taylor expansion of a multivariate analyzable function $f\rBrace{\vx}$ around $\vx_{0}$ where $\vx \in \mathbb{R}_{M\times1},$ is
-    \begin{equation}
-        \label{eqn_h_Tylor_dTheta_dTau}
-        \evalat{f\rBrace{\vx}}{\vx\to\vx_{0}}=\sum_{n=0}^{\infty}\frac{1}{n!}\rBrace{\sum_{i=1}^{M}(x_{i}-x_{0i})\frac {\partial}{\partial x_i} }^n f(x_k)|_{x_k=x_{k0}},
-    \end{equation}
-    where $\frac{\partial}{\partial x_i}$ is the derivative operator and $i\in\left[1\hdots{}M\right]$.
-Reducing (\ref{eqn_h_Tylor_dTheta_dTau}) to its $2^{nd}$ form (i.e $f(x,y)=\sum_{n=0}^{\infty} \frac 1 {n!}\rBrace{x\frac {\partial}{\partial x}+y\frac {\partial}{\partial y} }^n f(x,y)|_{(x,y)=(0,0)}$), combined with the binomial formula, $(x+y)^{n}=\sum _{k=0}^{n}{\binom {n}{k}}x^{n-k}y^{k},$ multiple iterations of L'Hôpital's rule and algebraic simplification finally yields
-    \begin{equation}
-        \begin{split}
-            \evalat{\Hr{\theta}{\tau}{}_{\coefSetName{}}}{\dTheta\to0,\dPhi\to0} \approx\ & 1 
-            \\+&\frac{\binom{2}{0}}{2!}\frac{-\rBrace{N - 1}\rBrace{N-4r+2Nr+1}}{6\rBrace{r-1}^{2}}\dTheta^{2}
-            \\+&\frac{\binom{2}{1}}{2!}\frac{-r\omega\rBrace{N - 1}}{\rBrace{r-1}^{2}}\dTheta\dPhi
-            \\+&\frac{\binom{2}{2}}{2!}\frac{-2r\omega^{2}}{\rBrace{r-1}^{2}}\dPhi^{2}
-        \end{split}
-    \end{equation}
-}
-\else
-\fi
-\subsection*{The normalized beampattern}
-\label{subsection_spatialIIR_normBP}
-As commonly done for ULA performance analysis \cite{van2004optimum}, we analyze the normalized response (i.e., where the peak main lobe gain is set to $0_{dB}$).
-Henceforth, setting $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ we define the normalized response
-\begin{equation}
-    \label{eq_narmalized_pattern}
-    %\resizebox{.89\linewidth}{!}{
-    \begin{split}
-        \HrTPr\omegaB&\triangleq
-        \frac{
-        \HbaFB
-        }{
-        H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}\omegaB
-        }
-         =
-        \frac{
-        \HbaFB
-        }{
-        r/\rBrace{1-r}
-        },
-        % \\
-        % &=\frac{\rBrace{1-r}^{2}\Dp{\dTheta/2,N}{2}}{1+r^{2}\Dp{\dTheta/2,N}{2}-2r\D{\dTheta/2}{N}\cos{\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}},
-    \end{split}
-    %}
-\end{equation}
-where the $\Delta\theta,\Delta\phi,r$ subscripts express the DOA, range and gain errors dependency, respectively.
-%Also, $\abs{\HrTPr}$ is defined to be the beampattern.
-Plugging \eqref{eq:SF_CB} into \eqref{eq_narmalized_pattern} yields 
-\begin{equation}\label{eq_generalH}
-    \resizebox{0.89\linewidth}{!}{
-        \begin{split}
-             \HrTPr\omegaB=
-             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.
-        \end{split}
-        }
-\end{equation}
-Note that the known \cite{van2004optimum} normalized response of standard ULA is obtained by setting $r=0$ (i.e., cancelling the feedback) 
-$$
-\Hr_{\Delta\theta,\Delta\phi=0,r=0}\omegaB=
-             \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}}.
-$$
-Considering the steering error scenario (i.e., $\dTheta\neq0,\ \dPhi=0$) first, where 
-\begin{equation}\label{eq_Hdphi0}
-\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB=
-             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}},
-\end{equation}
-we evaluate the FB's beamwidth, sidelobe level and directivity and compare them to those of the standard ULA.
-\ifdefined\useOmega
-To simplify the exposition, we shall suppress the $\omega$ dependency in the following sections (i.e. $\HrTPr \triangleq \HrTPr\omegaB$) where possible.
-\fi
-\vfill
-\subsection*{Half power beamwidth}
-\input{./Modules/arrayPerformance_beamwidth.tex}
-\subsection*{Sidelobes attenuation}
-\ifdefined\showDev
-    \fbox{
-    \begin{minipage}{0.9\linewidth}
-    \textbf{development specifics}\\
-    Let $f\rBrace{\dTheta} \triangleq \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}},$ such that $\Hr_{\Delta\theta,\Delta\phi=0,r=0}\omegaB = \frac{f\rBrace{\dTheta}}{1-rf\rBrace{\dTheta}}.$ Then, we compute the beampattern's derivative and state that
-    \begin{equation*}
-    % \resizebox{0.9\linewidth}{!}{
-        \begin{split}
-            &\frac{\partial}{\partial\dTheta}\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB &\\
-            &=\frac{\Dp{\dTheta/2,N}{'}\rBrace{1-r\D{\dTheta/2}{N}}-\D{\dTheta/2}{N}\rBrace{-r\Dp{\dTheta/2,N}{'}}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}
-            \\
-            &=\frac{\Dp{\dTheta/2,N}{'}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}.
-        \end{split}
-        % }
-    \end{equation*}
-    It follows that the sidelobes of the feedback-based beampattern are located at the same angles as the in the ULA case.
-    \end{minipage}
-    }
-\else
-\fi
-By taking a derivative of $\Hr_{\Delta\theta,\Delta\phi=0,r}\omegaB$ with respect to $\dTheta$ it can be easily verified that the beampattern's extrema points are located exactly as in the standard ULA beampattern.
-Specifically, the sidelobes locations are
-\begin{equation}
-    \label{eqn_CB_sidelobesLocations}
-    \Delta\theta_{\text{sidelobe}} = \frac{\rBrace{2m+1}\pi}{N}\ \forall m\in\cBrace{\pm 1,\pm 2,\hdots}.
-\end{equation}
-Our main interest is with the first sidelobe (i.e. $m=1$), therefore we evaluate \eqref{eq_Hdphi0} at $\Delta\theta = 3\pi/N$, which results in
-\begin{equation}
-    \abs{\Hr_{{3\pi}/{N},0,r}\omegaB}^2
-    =
-    \frac{
-    2\rBrace{1-r}^{2}
-    }{
-    \rBrace{N^{2}-2Nr}\rBrace{1-\cos{\rBrace{\frac{3\pi}{N}}}}+2r^{2}
-    }
-    \label{eq_HSidelobes}
-\end{equation}
-and for large $N$ values 
-\begin{equation*}
-    \lim_{N\rightarrow\infty}\abs{\Hr_{3\pi/N,0,r}\omegaB}=\frac{
-    2\rBrace{1-r}
-    }{
-    3\pi
-    }.
-\end{equation*}
-\ifdefined\showDev
-    \fbox{
-    \begin{minipage}{0.9\linewidth}
-    \textbf{development specifics}\\
-    We know that \eqref{eq_Hdphi0} can be rewritten as
-    \begin{equation*}
-        \begin{split}
-            \Hr_{\Delta\theta,\Delta\phi=0,r=0} \omegaB=
-            \frac{
-            \rBrace{1-\cos{\rBrace{N\dTheta}}}\rBrace{1-r}^{2}
-            }{
-            \begin{split}
-                N^{2}&\rBrace{1-\cos{\dTheta}}+r^{2}\rBrace{1-\cos{N\dTheta}}
-                \\
-                &+Nr\Bigg(1+\cos{\rBrace{\rBrace{N-1}\dTheta}}
-                \\
-                &-\cos{\rBrace{N\dTheta}-\cos{\rBrace{\dTheta}}}\Bigg)
-            \end{split}
-            }
-        \end{split}
-    \end{equation*}
-    Using the symbolic toolbox in MATLAB, setting $\dTheta=3\pi/N$, results in \eqref{eq_HSidelobes}.
-    \end{minipage}
-    }
-\else
-\fi
-\par For standard ULA, the gain of the first sidelobe is known to be $2/3\pi$ \cite{van2004optimum}, which implies that the first sidelobe is smaller by a factor of $1-r$ compared to standard ULA.
-Specifically, in perfect gain match scenario (i.e., $r\to{}1$) , the sidelobes vanish. 
-\subsection*{Array directivity}
-The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
-\begin{equation}\label{eq_D}
-    \mathcal{D}\rBrace{N,r} = \frac{\Hr_{\Delta\theta=0,\Delta\phi=0,r}}{\frac{1}{2\pi}\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta} = \frac{2\pi}{\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta},
-\end{equation}
-measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
-For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
-Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 
-\begin{equation}\label{eq_D_result}
-    \mathcal{D}\rBrace{N,r} \approx \frac{N-r}{1-r},
-\end{equation}
-where the standard ULA's known result is obtained for $r=0$.
-Also, for $N\geq2$, $\lim_{r\rightarrow 1}\mathcal{D}\rBrace{N,r}=\infty$, implying infinite directivity for the perfectly gain-matched FB. 
-\par Finally, expressing the improvement in directivity compared to the standard ULA, assuming large $N$ values, gives rise to
-\begin{equation}\label{eq_Dimprovement}
-\lim_{N\to\infty}\frac{\mathcal{D}\rBrace{N,r}}{\mathcal{D}\rBrace{N,0}}
-=\frac{N/\rBrace{1-r}}{N}=\frac{1}{1-r}.
-\end{equation}
-\begin{figure}[t]
-    \begin{center}
-        \begin{overpic}[width=0.75\linewidth, 
-        %grid, 
-        tics=10,trim=0 0 0 0]{./Media/directivity_expr.eps}
-            \put (20, 10){\footnotesize{$N$}}
-            \put (72, 6){\footnotesize{$r$}}
-            \put (16.5, 70){\footnotesize{Numerical integration}}
-            \put (16.5, 65){\footnotesize{$\rBrace{N-r}/\rBrace{1-r}$}}
-            \put (-9, 45){\footnotesize{$\mathcal{D}\rBrace{N,r}$}}
-        \end{overpic}
-    \end{center}
-     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.
-Difference between the numerical integration result and the suggested analytic expression is around $\sim{1e^{-9}}$.}
-    \label{fig_directivity}
-\end{figure}
-\subsection*{Summary}
-To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance} 
-\begin{table}[h!]
-    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
-    \centering
-    \resizebox{1\linewidth}{!}{
-        \begin{tabular}{||c c c c||}
-            \hline
-            & ULA & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 
-            \hline\hline
-            HPBW & $ 1.4/N$ & $1.4/\rBrace{f(r)N}$ & $f\rBrace{r}$ times smaller\\ 
-            \thead{FIRST\\SIDELOBE\\GAIN} & $2/3\pi$ & $2\rBrace{1-r}/3\pi$ & \thead{smaller by a factor of $1-r$\\for $N\gg{}1$} \\
-            DIRECTIVITY & $N$ & $\rBrace{N-r}/\rBrace{1-r}$ & \thead{$1/\rBrace{1-r}$ times higher \\ for $N\gg{}1$}\\
-            [1ex] 
-            \hline
-         \end{tabular}
-     }
-    \label{table_arrayPerformance}
-\end{table}

### 2020-12-25 Modules/abstractHebrew.tex
Before applying meeting#1's comments

שיערוך מאפיינים מתוך מדידות הינו מושא לעניין רב עוד מראשית ימי המדע, כשחוקי הפיזיקה נלמדו בעזרת תצפיות ומדידות.
עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון להלחמת מידע ממספר מדידות בו זמנית.
אחד התחומים בהם עלה משמעותית הצורך בדיוק השיערוך, היה העיבוד המרחבי - קרי שיערוך פרמטרים מרחביים מתוך מדידות. 
עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה.
\par
מאז ועד ימינו, עיבוד מערכי רגשים
\textenglish{(sensors arrays)}
התפתח לכדי תחום מחקר הנותן מענה למגוון רחב של בעיות, ביניהן איכון (מערכות רדאר, סונאר ונגזרותיהן) מטרות על סמך אותות שנפלטים או מוחזרים מהן - הנחשבת לותיקה ביותר בתחום.
עם השנים והתקדמות המדע, נעשה שימוש במערכים לפתרון בעיות נוספות.
\par
במערכות תקשורת, הצורך בסינון מרחבי הוא מן המעלה הראשונה, שכן במציאות מרובת המשדרים והמקלטים, במידה ולא היה שימוש במערכים, הפרעות הדדיות היו מונעות את פענוח האות הנקלט. במקביל, לא רק סינון אלא גם הכוונת אלומת השידור הפכה לאפשרית בזכות השימוש בו-זמנית במספר רב של משדרים
\textenglish{(phased array)}
ובכך הושגו גם חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.
\par
מוקד עניין נוסף, הינו האפליקציות הרפואיות שהתאפשרו בזכות השימוש במערכים. 
בדימות רפואית למשל, כדוגמת 
\textenglish{CT, MRI, EEG}
וכו', רופאים מייצרים באופן בלתי פולשני מודלים של פנים גוף האדם המשמשים לפענוח מצבים רפואיים ותכנון מדויק של הליכים - ובכך מונעים סיכון רב מהמטופלים.
\par
בעשורים האחרונים, עם הגחת הטלפונים הניידים לעולם, עלה הצורך בסינון אותות דיבור מתוך בליל מקורות אקוסטיים, שכן הדובר כבר אינו נמצא בין כותלי ביתו בשקט יחסי.
לשם כך, המכשירים הניידים מצוידים במערכי מיקרופונים אשר מסננים את אות הדובר על פי כיוון הגעתו ומאפייניו הסטטיסטיים.
\par
דוגמא מעניינת נוספת בתחום האסטרונומיה, שם נוכחו המדענים כי תצפיות אופטיות מוגבלות ביכולתן ובכמות המידע שניתן להפיק מהן, היא השימוש במערכי אנטנות, הנפרשים על פני שטחים עצומים בכדי לממש טלסקופים רבי עוצמה ודיוק, העושים שימוש באותות אלקטרומגנטיים באורכי גל שלא בתחום הנראה.
\par
ככלל, בין תחומי מחקר אלו, מתקיימת תרומה הדדית רחבת היקף ורב המסקנות העולות מכל תחום בנפרד משמשות בסיס למחקר ופיתוח בתחומים אחרים ולהפך. 
בנוסף, בבסיס כל מגוון תחומי המחקר, ישנו שימוש בתחום מחקר ותיק ועשיר עוד יותר - הוא השימוש במסננים בכדי להפיק את המידע הרצוי (אות או מאפיין) מהאות הנקלט.  
\par
בבסיס תורת הסינון, שתי אבני בניין מרכזיות - קרי שני סוגי מסננים.
האחד, מסנן בעל תגובה להלם סופית 
\textenglish{FIR}
הינו מישקול וסכימת סט דגימות לכדי מוצא "מסונן".
השני לעומת זאת, משתמש בהיזון חוזר, ובכך מייצר תגובה אינסופית להלם - ועל כך שמו
\textenglish{IIR}
.
לשם תכן מסננים מסופק מפרט התגובה בתדר, בו מפורטים התדרים שאמורים לעבור, אלו שאמורים לחוות דיכוי ומידת הדיכוי הרצויה.
על פי מפרט זה, המתכנן בוחר את סוג המסנן ואת המשקלות שבו.
בעוד המסנן בעל התגובה הסופית להלם מאפשר הימנעות מעיוותים באות (תכונת הפאזה הלינארית - קרי ללא דיספרסיה), המסנן בעל התגובה האינסופית מאפשר חיסכון משמעותי (לעיתים בסדרי גודל) במשאבים לשם עמידה במפרט דומה.
איך לכך, בהתאם לאפליקציה ולמפרט, על המתכנן לבחור במסנן המתאים ביותר תוך הבאה בחשבון של כלל השיקולים - משאבים, עלות וכו'.
\par
עד כה, למיטב ידיעתנו, בכל תחומי המחקר המערבים עיבוד מרובה רגשים אבן הבניין היחידה שבשימוש הינה המסנן בעל התגובה הסופית בתדר, שכן בין אם מעורב שידור במערכת (כמו במכם, תקשורת, דימות רפואית וכו') ובין אם לאו, אין היזון חוזר של האות הנקלט חזרה אל מושא המדידה.
עובדה זו עוררה את תהייתנו ובעטייה חיפשנו את המקביל המרחבי למסנן בעל התגובה האינסופית - בכדי ליהנות מהיתרונות שבו.
במהלך המחקר המקדים, נוכחנו לדעת כי שאלה זו התעוררה גם במוחם של חוקרים אחרים, אך לאחר בחינת פרסומיהם נוכחנו כי פתרונם אינו מממש בצורה מלאה את רעיון ההיזון החוזר אלא מנסה למצוא דרכים עקיפות - בכך חושף עצמו לשגיאות ועיוותים משמעותיים.
\par
לשם המחשת הפתרון שמוצע, עבודה זו מתמקדת בתחום האיכון - בסביבה אקוסטית או אלקטרו מגנית.
מוצעת איפוא, מערכת מבוססת מערך לינארי בעל מרווחים אחידים בין הרגשים
\textenglish{ULA}
כאשר בראשיתו, בנוסף על הרגש,  ישנו משדר.
על פניו, מערכת דומה למכ"ם, השולח אות ומשערך את מיקומי מטרות על פי האות החוזר.
החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק אות מלאכותי הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך.
ניתוח המערכת מרמז כי ע"י שליטה במשקלות המסנן המייצר את האות החוזר, ניתן להפיק את היתרונות הרבים הטמונים במסנן בעל התגובה האינסופית.
\par
לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי - אבן נגף משמעותית בנסיון למציאת הפתרון.
עם זאת, לשמחתנו, נמצא גם פתרון פשוט וזול יחסית לבעיה, המגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.
הדמיות וניתוח נוספים מאשררים כי הפתרון קביל ומשיג תוצאות שבתרחישים אידיאלים נוטות לכדי שלמות.
בנוסף על האיכון הזוויתי שחווה שיפור משמעותי בביצועיו, כתופעת לוואי, מתכנן המערך יכול גם לקבוע גבולות מרחק לסינון ובכך לייצר מערכת איכון שמזהה לא רק כיוון אלא מיקום מדויק של מטרות.

### 2020-12-25 Modules/arrayPerformance_beamwidth.tex
Before applying meeting#1's comments

@@
 The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
-It marks the DOA where the beampattern's energy reduces to half of its maximal value.
+It represents the DOA where the beampattern's energy reduces to half of its maximal value.
 For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
@@
 \end{equation}
-Note that for accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity.
+Note that for an accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity.
 \begin{figure}[t]

### 2020-12-25 Modules/estimation_CRLB_appendix.tex
Before applying meeting#1's comments

@@
 To this end, the FIM, denoted by $\vecnot{J}$, will now be calculated with respect to the DOA $\rBrace{\thetaD}$ and range $\rBrace{\phi}$ parameters. 
-As the feedback-based transfer function (\ref{eqn:GeneralFeedbackTransferFunction}) is expressed in frequency domain, we rely on \cite{zeira1990frequency} to express the frequency domain FIM as well. 
+As the feedback-based transfer function (\ref{eqn:GeneralFeedbackTransferFunction}) is expressed in the frequency domain, we rely on \cite{zeira1990frequency} to express the frequency domain FIM as well.
 \par The $\vBrace{k,l}$'th FIM element, may be expressed as
@@
 where $ \vEta = [\thetaD,\phi]^{T} $ is the parameters vector, $\Re$ stands for the real-part extraction operator, $k,l \in\cBrace{1,2}$, $\Phi\rBrace{\omega}$ is the noise spectrum, $\mathfrak{F}$ is the Fourier transform operator, $T$ is the measurement observation interval and $\omega_{s}$ is the signal bandwidth.
-For simplicity, $\text{n}\rBrace{t}$ is assumed to be a white Gaussian with some constant power spectral density $\Phi(\omega)=\sigma^2$ and independent of the estimated parameters $\vEta$.
-Hence, the second term in the right-hand-side of \eqref{eq_FIM_kl_full} vanishes.
+For simplicity, $\text{n}\rBrace{t}$ is assumed to be white Gaussian with some constant power spectral density $\Phi(\omega)=\sigma^2$ and independent of the estimated parameters $\vEta$.
+Hence, the second term in the RHS of \eqref{eq_FIM_kl_full} vanishes.
 Assuming continuously differentiable functions, where order alteration of the Fourier transform and the differentiation operations is allowed, \eqref{eq_FIM_kl_full} simplifies to
@@
 \begin{equation}\label{eq_vdDiff}
-\frac{\partial\vd}{\partial\thetaD}=\vecnot{A}\omegaB\vd
+\frac{\partial\vd}{\partial\thetaD}=\vecnot{A}\vd
 \end{equation}
-where $\vecnot{A}\omegaB$ is an $N\times{}N$ diagonal matrix with
+where $\vecnot{A}$ is an $N\times{}N$ diagonal matrix with
 \[
-A_{ii}\omegaB=-j\omega\frac{\partial \tau_{i}}{\partial{\thetaD}}\ \  \forall{i\in\cBrace{0\hdots{}N-1}}.
+A_{ii}=-j\omega\frac{\partial \tau_{i}}{\partial{\thetaD}}\ \  \forall{i\in\cBrace{0\hdots{}N-1}}.
 \]
@@
             \frac{1}{2\pi\sigma^{2}}\int_{-\omega_{s}/2}^{\omega_{s}/2}{\frac{
-            \lBrace{g\vBetaH{}\vecnot{A}\omegaB\vd-g^{2}\vBetaH{}B\omegaB\vAlphaC\ePhi{-}}^{2}
+            \lBrace{g\vBetaH{}\vecnot{A}\vd-g^{2}\vBetaH{}B\vAlphaC\ePhi{-}}^{2}
             }{
@@
 \end{equation}
-where $\vecnot{B}\omegaB\triangleq\vd\vdT{}\vecnot{A}\omegaB-\vecnot{A}\omegaB\vd\vdT.$ 
+where $\vecnot{B}\triangleq\vd\vdT{}\vecnot{A}-\vecnot{A}\vd\vdT.$ 
 % Generalizing the conventional beamformer (CB) \cite{van2004optimum}, such that the feedback weights are

### 2020-12-25 Modules/sec_conclusions.tex
Before applying meeting#1's comments

@@
-\section{Conclusions}
-\label{sec_conclusions}
 Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
-It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's residing spatial information, thus enabling high localization accuracy.
+It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
 The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
 It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
-Fortunately, using two frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
+Fortunately, using a dual-frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
 Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.

### 2020-12-25 Modules/sec_prlm_FIM.tex
Before applying meeting#1's comments

In the parameter estimation problems, we obtain information about the parameter from asample of data coming from the underlying probability distribution. 
A natural question is:how much information can a sample of data provide about the unknown parameter? 
This section introduces such a measure for information, and we can also see that this informationmeasure can be used to find bounds on the variance of estimators, and it can be used toapproximate the sampling distribution of an estimator obtained from a large sample, andfurther be used to obtain an approximate confidence interval in case of large sample.
In this section, we consider a random variable $X$ for which the pdf or pmf is $f\rBrace{x|\theta}$, wehre $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.
Intuitively, if an event has small probability, then the occurrence of this eventbrings us much information. 
For a random variable $X \sim f\rBrace{x|\theta}$, if $\theta$ were the true value ofthe parameter, the likelihood function should take a big value, or equivalently, the derivativelog-likelihood function should be close to zero, and this is the basic principle of maximumlikelihood estimation.
We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function, and
\begin{equation*}
    l^{\prime}\rBrace{x|\theta} = \frac{\partial}{\partial\theta}\log{f\rBrace{x|\theta}}=\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}
\end{equation*}
where $f^{\prime}\rBrace{x|\theta}$ is the derivative of $f\rBrace{x|\theta}$ with respect to $\theta$.
Similarly, we denote the second order derivative of $f\rBrace{x|\theta}$ with respect to $\theta$ as $f^{\prime\prime}\rBrace{x|\theta}$.
According to the above analysis, if $l^{\prime}\rBrace{X|\theta}$ is close to zero, then it is expected, thus the random variable does not provide much information about $\theta$;
on the other hand, if $\abs{l^{\prime}\rBrace{X|\theta}}$ or $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ is large, the random variable provides much information about $\theta$.
Thus, we can use $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ to measure the amount of information provided by $X$.
however, since $X$ is a random variable, we should consider the average case. Thus, we introduce the following definition:
\begin{definition}
\emph{Fisher information} (for $\theta$) contained in the random variable $X$ is defined as:
\begin{equation}
\label{eq_prlm_FI_def}
    I\rBrace{\theta}=E_{\theta}\cBrace{\abs{l^{\prime}\rBrace{X|\theta}}^{2}}=\int{}\abs{l^{\prime}\rBrace{X|\theta}}^{2}f\rBrace{x|\theta}dx.
\end{equation}
\end{definition}
We assume that we can exchange the order of differentiation and integration, then
\begin{equation*}
    \int{}f^{\prime}\rBrace{x|\theta}dx=\frac{\partial}{\partial\theta}\int{}f\rBrace{x|\theta}dx=0.
\end{equation*}
Similarly,
\begin{equation*}
    \int{}f^{\prime\prime}\rBrace{x|\theta}dx=\frac{\partial^{2}}{\partial\theta^{2}}\int{}f\rBrace{x|\theta}dx=0.
\end{equation*}
It is easy to see that
\begin{equation*}
    E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=\int{}l^{\prime}\rBrace{x|\theta}f\rBrace{x|\theta}dx=\int{}\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}f\rBrace{x|\theta}dx=\int{}f^{\prime}\rBrace{x|\theta}=0
\end{equation*}
Therefore, the definition of Fisher information \eqref{eq_prlm_FI_def} can be rewritten as
\begin{equation}
\label{eq_prlm_IeqVar}
    I\rBrace{\theta}=\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}
\end{equation}.
Also, notice that
\begin{equation*}
    l^{\prime\prime}\rBrace{x|\theta}=\frac{\partial}{\partial\theta}\vBrace{\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}}=\frac{f^{\prime\prime}\rBrace{x|\theta}f\rBrace{x|\theta}-\abs{f^{\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}=\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}.
\end{equation*}
Therefore,
\begin{equation*}
    E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=\int{\vBrace{\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}}f\rBrace{x|\theta}}=\int{f^{\prime\prime}\rBrace{x|\theta}dx}-E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=-I\rBrace{\theta}.
\end{equation*}
Finally, we have another formula to calculate Fisher information:
\begin{equation}
\label{eq_prlm_Ifin}
    I\rBrace{\theta} = -E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=-\int{\vBrace{\frac{\partial^{2}}{\partial\theta^{2}}\log{f\rBrace{x|\theta}}f\rBrace{x|\theta}}dx}
\end{equation}.
To summarize, we have three methods to calculate Fisher information: equations \eqref{eq_prlm_FI_def}, \eqref{eq_prlm_IeqVar} and \eqref{eq_prlm_Ifin}.
In any problems, using \eqref{eq_prlm_Ifin} is the most convenient choice.
\subsection{Cram\'er-Rao Lower Bound and Asymptotic Distribution of Maximum Likelihood Estimators}
Suppose that we have a random sample $X_{1},\dots,X_{n}$ coming from a distribution for which the pdf or pmf is $f\rBrace{x|\theta},$ where the value of the parameter $\theta$ is unknown. 
We will show how to used Fisher information to determine the lower bound for the variance of an estimator of the parameter $\theta$.
\par
Let $\hat{\theta}=r\rBrace{X_{1},\dots,X_{n}}=r\rBrace{\vecnot{X}}$ be an arbitrary estimator of $\theta$.
Assume $E_{\theta}\rBrace{\hat{\theta}}=m\rBrace{\theta}$ and the variance of $\hat{\theta}$ is finite.
Let us consider the random variable $l^{\prime}\rBrace{\vecnot{X}|\theta}$, it can be shown that $E_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=0$ and that
\begin{equation}
\label{eq_prlm_covThetaLTag}
    \text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}=m^{\prime}\rBrace{\theta}.
\end{equation}.
By Cauchy-Schwartz inequality and the definition of $I_{n}\rBrace{\theta},$
\begin{equation*}
    \vBrace{\text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}
\end{equation*}
i.e.
\begin{equation*}
    \vBrace{m^{\prime}\rBrace{\theta}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}=nI\rBrace{\theta}=\text{Var}_{\theta}{\cBrace{\hat{\theta}}}
\end{equation*}
Finally, we get the lower bound of variance of an arbitrary estimator $\hat{\theta}$ as
\begin{equation}
\label{eq_prlm_CramerRao_lim}
    \text{Var}_{\theta}{\cBrace{\hat{\theta}}}\geq{}\frac{\vBrace{m^{\prime}\rBrace{\theta}}^{2}}{nI\rBrace{\theta}}
\end{equation}
The inequality \eqref{eq_prlm_CramerRao_lim} is called the \emph{information inequality}, and also known as the \emph{Cram\'er-Rao inequality} in honor of the Sweden statistician H. Cram\'er Indian statistician C. R. Rao who independently developed this inequality during the 1940s. 
The information inequality shows that as $I_{\theta}$ increases, the variance of the estimator decreases, therefore, the quality of the estimator increases, that is why the quantity is called “information”.
\par
If $\hat{\theta}$ is an unbiased estimator, then $m\rBrace{\theta}=E_{\theta}\rBrace{\hat{\theta}}=\theta$, $m^{\prime}\rBrace{\theta}=1$.
Hence, by the information inequality, for unbiased estimator $\hat{\theta}$,
\begin{equation*}
    \text{Var}_{\theta}\cBrace{\hat{\theta}}\geq\frac{1}{nI\rBrace{\theta}}.
\end{equation*}
The right hand side is always called the Cram\'er-Rao lower bound (CRLB): under certain conditions, no other unbiased estimator of the parameter $\theta$ based on an i.i.d sample of size $n$ can have a variance smaller than CRLB.
\subsection{The Multiple Parameter Case}
Suppose now there are more than one parameters in the distribution model, that is, the random variable $X\sim{}f\rBrace{x|\vecnot{\theta}}$ with $\vecnot{\theta}=\rBrace{\theta_{0},\dot,\theta_{k-1}}^{T}$.
We denote the log-likelihood function as
\begin{equation*}
    l\rBrace{\vecnot{\theta}}=\log{f\rBrace{x|\vecnot{\theta}}},
\end{equation*}
and its first order derivative with respect to $\vecnot{\theta}$ is a $k$-dimensional vector, which is
\begin{equation*}
    \frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial{}\vecnot{\theta}}=\rBrace{\frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial{}\theta_{0}},\dots,\frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial{}\theta_{k-1}}}^{T},
\end{equation*}
The second order derivative of $l\rBrace{\vecnot{\theta}}$ with respect to $\vecnot{\theta}$ is a $k\times{}k$ matrix, which is
\begin{equation*}
    \frac{\partial^{2}l\rBrace{\vecnot{\theta}}}{\partial{}\vecnot{\theta}^{2}}=\cBrace{\frac{\partial^{2}l\rBrace{\vecnot{\theta}}}{\partial{}\theta_{i}\partial{}\theta_{j}}}_{i,j\in\vBrace{0,\dots,k-1}}.
\end{equation*}
We define the \emph{Fisher information matrix} as
\begin{equation*}
    I\rBrace{\vecnot{\theta}}=E\cBrace{\frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial\vecnot{\theta}}\rBrace{\frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial\vecnot{\theta}}}^{T}}=\text{Cov}\cBrace{\frac{\partial{}l\rBrace{\vecnot{\theta}}}{\partial\vecnot{\theta}}}=-E\cBrace{\frac{\partial^{2}l\rBrace{\vecnot{\theta}}}{\partial{}\vecnot{\theta}^{2}}}.
\end{equation*}
Since the covariance matrix is symmetric and semi-positive definite, these properties hold for the Fisher information matrix as well.
\subsection{FIM applications}
Considering unbiased estimators, the CRLB for the multi-parameter case can be shown to be
\begin{equation}
\label{eq_prlm_multiVar_CRLB}
    \test{Cov}_{\vecnot{\theta}}\cBrace{\hat{\vecnot{\theta}}\rBrace{\vecnot{X}}}\geq{}I^{-1}\rBrace{\vecnot{\theta}}
\end{equation}
where the matrix inequality $A\geq{}B$ means that $A-B$ is positive semi-definite.
From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the measuring is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.

### 2020-12-25 Modules/sec_prlm_FIR_based_BF.tex
Before applying meeting#1's comments

Delay-and-sum beamformers, as shown in Fig.~\ref{XXX}, utilize a single weight for each microphone. 
This makes them ineffective when dealing with wideband signals, the signals of interest in speech and audio processing, as each of the signals is composed of various frequency components. 
In order to design a beamformer for wideband signals, the weight values in \eqref{XXX} must be altered for different frequencies in order to obtain the desired beamformer output. 
That is, the weights should be frequency dependent, i.e., in the form of $\vecnot{w}\rBrace{\omega}=\vBrace{w_{0}\rBrace{\omega},\dots,w_{M-1}\rBrace{\omega}}^{T}$. 
This can be acheived by introducing discrete FIR filters \cite{yan2005design,liu2010wideband}.
FIR filters perform temporal filtering in order to compensate for the phase differences of the input wideband signals’ various frequency components. 
Fig.\ref{XXX} shows the realization of frequency dependent weights by FIR filters connected to the microphone array.
Let $y\rBrace{t}$ denote the output of the FIR-based beamformer. 
It is expressed by:
\begin{equation}
y\rBrace{t}=\sum_{m=0}^{M-1}\sum_{n=0}^{N-1}f\rBrace{t-nT_{s},x_{m}}\cdot{}w_{m,n}^{*}
\end{equation}
where $N$ denotes the number of FIR filter coefficients connected to each of the $M$ sensors, $w_{m,n}^{*}$ is the $n$-th coefficient of the FIR filter connected to the microphone indexed by $m$, and $T_{s}$ denotes the delay between adjacent filter elements. 
Given a complex plane wave signal, the beamformer output is given by:
\begin{equation}
y\rBrace{t}=e^{j\omega{}t}P\rBrace{\omega,\theta}=e^{j\omega{}t}\sum_{m=0}^{M-1}\sum_{n=0}^{N-1}e^{-j\omega\rBrace{\tau_{m}+nT_{s}}}\cdot{}w_{m,n}^{*}
\end{equation}
Let $\vecnot{v}_{s}\rBrace{\omega,\theta}$ denote a \emph{stacked array manifold vector} of dimension $M\cdot{}N$, where each subvector of dimension $M$ epresents the array manifold vector associated with a specific FIR filter coefficient in \eqref{XXX}, i.e. the first subvector, $\vBrace{e^{-j\omega\tau_{0}},\dots,e^{-j\omega\tau_{M-1}}}^{T}$, is associated with the coefficient indexed by $n=0$ and all of the array microphones, indexed by $m=0,\dots,M-1$.
Thus, it is denoted by $\vecnot{v}_{0}\rBrace{\omega,\theta}$.
The second subvector, $\vBrace{e^{=j\omega\rBrace{\tau_{0}+T_{s}}},\dots,e^{=j\omega\rBrace{\tau_{M-1}+T_{s}}}}^{T}$, is associated with the coefficient indexed by $n=1$ and all of the array microphones.
Thus, it is denoted by $\vecnot{v}_{1}\rBrace{\omega,\theta}$, and so on.
This form of expression is called vector stacking, and $\vecnot{v}_{s}\rBrace{\omega,\theta}$ is given by:
\begin{align}
\vecnot{v}_{s}\rBrace{\omega,\theta} &= 
\begin{bmatrix}
   \vecnot{v}_{0}\rBrace{\omega,\theta} \\
   \vecnot{v}_{1}\rBrace{\omega,\theta} \\
   \vdots \\
   \vecnot{v}_{N-1}\rBrace{\omega,\theta}
\end{bmatrix}.
\end{align}
Given a ULA of $M$ sensors, sensor spacing $d$, and $M$ FIR filters, each composed of $N$ coefficients, and connected to a respective microphone. 
Then, from \eqref{XXX} and
\eqref{XXX}, the beamformer response can be expressed as:
\begin{equation}
    P\rBrace{\omega,\theta}=    \sum_{m=0}^{M-1}e^{-j\omega\tau_{m}}\sum_{n=0}^{N-1}e^{jn\omega{}T_{s}}\cdot{}w_{m,n}^{*}=\vecnot{w}_{s}^{H}\vecnot{v}_{s}\rBrace{\omega,\theta},
\end{equation}
where $\vecnot{w}_{s}$ denotes the composite stacked weight vector of dimension $M\cdot{}N$ created by vector stacking, having $\vecnot{w}_{0}=\vBrace{w_{0,0},w_{1,0},\dots,w_{M-1,0}}^{T}$ as its first subvector, $\vecnot{w}_{1}=\vBrace{w_{0,1},w_{1,1},\dots,w_{M-1,1}}^{T}$ as its second subvector, and so on.
The design specification of the FIR filters will be addressed in Chapter \ref{XXX}. Fig.\ref{XXX} illustrates an FIR beamformer architecture.

### 2020-12-25 Modules/sec_prlm_propWaveField.tex
Before applying meeting#1's comments

@@
-In array signal processing, propagating waves carry signals from the source to the array.
-Therefore, these signals are represented in the time-space domain.
+% In array signal processing, propagating waves carry signals from the source to the array.
+% Therefore, these signals are represented in the time-space domain.
 The space domain is represented by either the three dimensional Cartesian coordinates $\rBrace{x,y,z}$ or the three dimensional spherical coordinates $\rBrace{r,\phi,\theta}$, where $0 \leq \phi \leq 2\pi$, $0 \leq \theta \leq \pi$ are the azimuth and elevation angles, respectively.
 The time domain is represented by $t$.
-Finally, let $f\rBrace{t,\vecnot{r}}$ denote the time-space representation of the input signal, where $\vecnot{r}$ is the radius-vector in the three-dimensional system.
-The relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
-$f\rBrace{t,x,y,z}$ describes the signal impinging the microphone array.
-The physics of propagation within a homogeneous (constant speed of propagation), dispersion free (no signal degradation due to other frequencies) and lossless (no signal gain attenuation) medium is described by the wave equation:
+An elementary physical phenomenon is the spatial dynamics of waves, referred to as wave-propagation.
+The spatial location is noted by the Cartesian coordinates $\rBrace{x,y,z}$ or the three dimensional spherical coordinates $\rBrace{r,\phi,\theta}$, where $0 \leq \phi \leq 2\pi$, $0 \leq \theta \leq \pi$ are the azimuth and elevation angles, respectively.
+% Finally, let $f\rBrace{t,\vecnot{r}}$ denote the time-space representation of the input signal, where $\vecnot{r}$ is the radius-vector in the three-dimensional system. 
+% The relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
+Denoting $t$ as the time, the time-space representation of the a signal is $f\rBrace{t,\vecnot{r}}$ or , where the relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
+% $f\rBrace{t,x,y,z}$ describes the signal impinging the microphone array. 
+In a homogeneous, dispersion free and lossless medium the wave equation is:
 \begin{equation}
@@
 \end{equation}
-Where $\nabla^{2}$ represents the Laplacian operator and $c$ represents the wave's velocity.
+where $\nabla^{2}$ is the Laplacian operator and $c$ represents the wave's velocity in the medium.
 \begin{figure}[h!]
@@
 \end{figure}
-Let $f_p\rBrace{t,x,y,z}$ denote a possible solution to \eqref{eq_prlm_waveEq} of a complex exponential form:
+A possible solution to \eqref{eq_prlm_waveEq}, $f_p\rBrace{t,x,y,z}$, may be of a complex exponential form:
 \begin{equation}
@@
 Where $A$ is a complex constant, $\omega$ denotes a constant temporal frequency and $k_{x}x,k_{y},k_{z}$ are real constants. 
-Substituting \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} yields:
+Plugging \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} results in the \emph{monochromatic plane wave}:
 \begin{equation}
@@
 \end{equation}
-This solution is called a monochromatic plane wave.
-The term plane wave is derived from the fact that at any given time, $t_{0}$, the value of $f\rBrace{t_{0},x,y,z}$ is the same at all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$.
-Finally, writing the solution to \eqref{eq_prlm_waveEq} using vector notation we obtain:
+Using the plane wave notation emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same wave value and the vector notation of \eqref{eq_prlm_waveEq}'s solution is
 \begin{equation}
@@
 \end{equation}
-Let $\vecnot{k}\vecnot{x}=constant$ denote planes of constant phase. 
-If the signal $f\rBrace{t,\vecnot{x}}$ is indeed propagating, planes of constant phase move by small steps of $\delta{\vecnot{x}}$, with small time increments of $\delta{t}$, i.e.
+where $\vecnot{k}\vecnot{x}=constant$ are planes of constant wave value.
+The wave propagation can be described as the traveling of the planes, stating that small steps of both space $\delta{\vecnot{x}}$ and time $\delta{t}$ result in the same wave value i.e.
 $f\rBrace{t+\delta{t},\vecnot{x}+\delta{\vecnot{x}}} = f\rBrace{t,\vecnot{x}}$, which yields
@@
 \end{equation}
-Assuming that $c>0$.
-Thus, the speed of propagation is indeed $c$.
-Let $\lambda$ denote the distance the plane wave propagated during a single temporal period of $T=\frac{2\pi}{\omega}$.
-This distance is referred to as the \emph{wavelength}. 
-Due to its spatial traits, after one period the monochromatic plane wave appears the same as one period before, but moved forward.
+where $c>0$ is the wave velocity in the medium.
+The \emph{wavelength} ($\lambda$) denote the distance the plane wave propagated during a single temporal period of $T=\frac{2\pi}{\omega}$.
 Let $\vecnot{k}$ denote the \emph{wavelength vector}. 
 Its magnitude $\abs{\vecnot{k}}$ expresses the number of cycles in radians per meter of length that the plane wave has exhibited in the propagation direction.
-Using \eqref{eq_prlm_waveEq_stepsEq} with $delta{t} = \frac{2\pi}{\omega}$, we obtain:
+Using \eqref{eq_prlm_waveEq_stepsEq} with $\delta{t} = \frac{2\pi}{\omega}$, we obtain:
 \begin{equation}

### 2020-12-25 Modules/sec_prlm_sensorArrays.tex
Before applying meeting#1's comments

@@
-Microphone arrays consist of sets of microphones positioned in a way to function as a directional acoustic antenna. 
-Microphone arrays are utilized for filtering signals in a space-time field. 
-Filtering is enabled by exploitation of the incoming signals spatial characteristics. 
-A desirable spatial filtering, i.e., beamforming, should result in enhancement of signals of interest, originated in a specific direction, while forcing suppression of undesired signals originated in other directions.
-Microphone arrays are utilized for solving many signal processing problems: dereverberation, localization of a single source, noise reduction and source separation \cite{cohen2004multichannel,habets2006dual,pavlidi2013real}.
+% Microphone arrays consist of sets of microphones positioned in a way to function as a directional acoustic antenna. 
+% Microphone arrays are utilized for filtering signals in a space-time field. 
+% Filtering is enabled by exploitation of the incoming signals spatial characteristics. 
+% A desirable spatial filtering, i.e., beamforming, should result in enhancement of signals of interest, originated in a specific direction, while forcing suppression of undesired signals originated in other directions.
+% Microphone arrays are utilized for solving many signal processing problems: dereverberation, localization of a single source, noise reduction and source separation \cite{cohen2004multichannel,habets2006dual,pavlidi2013real}.
+Sensor arrays are sets of specifically positioned sensors, where every sensor's output is fused together with the rest, enabling the exploitation of spatial sampling.
+Instead of mere temporal sampling, the user also receives spatial information from the relations between samples which arrived at the same temporal snapshot from all sensors. 
+As in the temporal domain, where filters are specified with respect to the frequency domain, spatial filters are specified in the spatial frequency domain, i.e.
+DOA, where the equivalent of pass band are the DOAs of interest and the attenuated DOAs (nulls) are equivalent to the stop-band.
+Sensor arrays are used in numerous applications, ranging from source localization, through communication, medical applications, astronomy etc.
 \par 
-Numerous factors must be taken into consideration when designing a microphone array configuration.
-Initially, the geometry of the microphone array plays an important role in the formulation of the processing algorithms, as it forces fundamental constraints on the array’s operation. 
-In most cases, the array geometry is the first consideration in array design due to practical and physical constraints of the design. 
-Therefore, the degree of freedom in choosing the array geometry is limited. 
-Nevertheless, in some other crucial problems such as noise reduction or source separation, the geometry of the array may have little importance. 
-For instance, Uniform Linear Arrays (ULA) can only handle one source direction at a time resulting in uncertainties and possibly direction ambiguities.
-Therefore, ULA configurations must be ruled out when handling several signal sources.
-Other array geometries such as non-uniform linear arrays and circular arrays, have been studied in the field \cite{liu2008design,van2004optimum}.
+% Numerous factors must be taken into consideration when designing a microphone array configuration.
+% Initially, the geometry of the microphone array plays an important role in the formulation of the processing algorithms, as it forces fundamental constraints on the array’s operation. 
+% In most cases, the array geometry is the first consideration in array design due to practical and physical constraints of the design. 
+% Therefore, the degree of freedom in choosing the array geometry is limited. 
+% Nevertheless, in some other crucial problems such as noise reduction or source separation, the geometry of the array may have little importance. 
+% For instance, Uniform Linear Arrays (ULA) can only handle one source direction at a time resulting in uncertainties and possibly direction ambiguities.
+% Therefore, ULA configurations must be ruled out when handling several signal sources.
+% Other array geometries such as non-uniform linear arrays and circular arrays, have been studied in the field \cite{liu2008design,van2004optimum}.
+
+When designing a sensor array, multiple consideration are to be taken into account, ranging from physical characteristics e.g.
+area, weight and carrying platform, through performance related considerations such as accuracy, spatial selectivity, signal to noise ratio and even the financial aspect - i.e.
+costs should be considered.
+Obviously, the most fundamental array specification is its geometry, for it dictates the spatial (and mathematical) relations between simultaneous samples measured by the array's sensors, which also greatly influences the processing methods of the raw-data.
 This work is based on ULA and therefore we elaborate on this geometry.
-A conventional beamformer \cite{van2004optimum} is composed of a ULA of microphones. 
-That is, the microphones are positioned on an axis with a uniform spacing between the microphones.
-The general expression of the microphone positioning in a ULA is given by:
+A conventional beamformer \cite{van2004optimum} is considered to be ULA, i.e. uniformly spaced sensors, where the convention is that the ULA is place on the horizontal axis.
+The sensors are positioned according to:
 \begin{equation}
@@
 \end{equation}
-where $m$ denotes the microphone index; $x_{m}$ denotes the position of the microphone having index $m$, where $x_{m} = 0$ corresponds to the left-hand side of the array, i.e., the location where the microphone indexed by $m = 0$ is positioned; $d$ denotes the spacing between microphones, and $M$ is the array size, i.e., the number of microphones in the array, as demonstrated in Fig.~\ref{fig_ULA}.
+where $m$ is the sensors index; $x_{m}$ denotes the position of the $m$'th sensor,$p_{0} = 0$ corresponds to the left-hand side of the array, $d$ denotes the spacing between sensors, and $M$ is the array size, as demonstrated in Fig.~\ref{fig_ULA}.
 \begin{figure}[h!]

### 2020-12-25 Modules/sec_prlm_timeSpaceSig.tex
Before applying meeting#1's comments

@@
-The incoming signals are spatially sampled by the array microphones, then the samples are processed to attenuate signals from undesired directions and extract the signal from a desired direction. 
-A spatial response of the microphone array is obtained via a beam (main-lobe) directed to the desired signal while nulls are directed to the undesired signals.
+% The incoming signals are spatially sampled by the array microphones, then the samples are processed to attenuate signals from undesired directions and extract the signal from a desired direction. 
+% A spatial response of the microphone array is obtained via a beam (main-lobe) directed to the desired signal while nulls are directed to the undesired signals.
+As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken in the same time $t$.
+A basic sensor array based entity is the beamformer, which is designed to enhance signals from certain directions while suppressing other signals from unwanted directions, heuristically forming a beam directed to the enhanced direction.
 \begin{figure}[ht!]
@@
 Fig.~\ref{fig_ULA_imping} illustrates a beamformer design based on a ULA of Fig.~\ref{fig_ULA}.
-Let $\vecnot{f}\rBrace{t,\vecnot{x}}$ denote the set of signals sampled by the microphone array at time $t$, expressed by
+% Let $\vecnot{f}\rBrace{t,\vecnot{x}}$ denote the set of signals sampled by the microphone array at time $t$, expressed by
+A temporal snapshot measured by the array at time $t$ is
 \begin{equation}
@@
 where $x_{m}$ denotes the microphone position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
-The beamformer output $y\rBrace{t}$ is expressed by:
+Assuming simple, weight-and-sum beamformer, the output ($y\rBrace{t}$) is expressed by:
 \begin{equation}
-y\rBrace{t} = \sum_{m=0}^{M-1}{f\rBrace{t,x_{m}}\omega_{m}^{*}},
+y\rBrace{t} = \sum_{m=0}^{M-1}{f\rBrace{t,x_{m}}w_{m}^{*}},
 \end{equation}
-where $\omega_{m}$ is a complex weight of the microphone having index $m$, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
-The simplest beamformer design architecture has uniform weights, $\omega_{m}=\frac{1}{M}, m=0,\dots,M-1$.
-Let $f_{\omega}\rBrace{t,x} = e^{j\omega{t}}$ denote a plane wave propagating at angular frequency $\omega$, and let $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ denote the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
-The wave signals spatially sampled by the microphone array inputs are given by:
+where $w_{m}$ is a complex weight used for the $m$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
+Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at angular frequency $w$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
+The wave signals spatially sampled by the sensor array inputs are
 \begin{equation}
 \label{eq_prlm_timeSpace_outputVec}
-\vecnot{f}\rBrace{t,x} = \vBrace{f_{\omega}\rBrace{t-\tau_{0}}, \dots, f_{\omega}\rBrace{t-\tau_{M-1}}}^{T}, \tau_{m} = \frac{\sin{\theta}\cdot{}x_{m}}{c},
+\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t-\tau_{0}}, \dots, s\rBrace{t-\tau_{M-1}}}^{T}, \tau_{m} = \frac{\sin{\theta}\cdot{}x_{m}}{c},
 \end{equation}
 where $\tau_{m}$ is the propagation delay for the incoming signal and $c$ is the wave's velocity in the medium.
-A value of $\tau_{m}=0, \forall{m}$ implies a DOA of $\theta = 0$, i.e. a plane wave parallel to the array, propagating perpendicularly to the array.
-Let $\kappa=\frac{\omega}{c}\sin{\theta}=\frac{2\pi}{\lambda}\sin{\theta}$ denote the wavenumber for plane waves in a locally homogeneous medium, where λ denotes the wavelength corresponding to the angular frequency $\vecnot{v}\rBrace{\kappa}$ denote the \emph{array manifold vector} \cite{van2004optimum}, featuring all of the spatial characteristics of the microphone array.
-Based on \eqref{eq_prlm_timeSpace_outputVec}, and the definition of κ above, the manifold vector can be expressed as
+% A value of $\tau_{m}=0, \forall{m}$ implies a DOA of $\theta = 0$, i.e. a plane wave parallel to the array, propagating perpendicularly to the array.
+Let $\kappa=\frac{\omega}{c}\sin{\theta}=\frac{2\pi}{\lambda}\sin{\theta}$ denote the wavenumber for plane waves in a locally homogeneous medium, where $\lambda$ denotes the wavelength corresponding to the angular frequency $\vecnot{d}\rBrace{\kappa}$ denote the \emph{steering vector}, featuring all of the array's spatial characteristics.
+Based on \eqref{eq_prlm_timeSpace_outputVec}, and the definition of $\kappa$ above, the steering vector can be expressed as
 \begin{equation}
-\vecnot{v}\rBrace{\kappa}=\vBrace{e^{-j\kappa{}x_{0}},\dots,e^{-j\kappa{}x_{M-1}}}^{T}.
+\vecnot{d}\rBrace{\kappa}=\vBrace{e^{-j\kappa{}x_{0}},\dots,e^{-j\kappa{}x_{M-1}}}^{T}.
 \end{equation}

### 2020-12-25 main/intro.tex
Before applying meeting#1's comments

--- 2020-12-25 Modules/IEEE_journal_paper_Intro.tex
@@
-general field of array processing has been thoroughly studied throughout several decades.
+\chapter{Introduction}
+\label{chap:intro}
+The general field of array processing has been thoroughly studied throughout several decades.
 The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving signal to noise ratio (SNR) \cite{verdu1998multiuser}, and many more.
 \par A uniform linear array (ULA) has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
-The array size and the number of its elements ($N$) have significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
+The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
 For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.
 \par In pursuit of spatial performance improvement, namely higher spatial separation and selectivity of arriving signals, many approaches were suggested.  
-One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging on missing sensors.
+One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
 Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
@@
 \par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g.
-narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the spatial domain processing methods which will be analogous to temporal domain IIR filtering?''
-\par Achieving a spatial IIR response has also motivated other works.
+narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?''
+\par Achieving spatial IIR response has also motivated other works.
 In \cite{wen2013extending} two methods were considered.
 The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain.
-The second approach suggested to consider overlapping subsets of one large ULA as a finite approximation to an infinite array.
+The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array.
 Surely, the former approach heavily relies on the accuracy of the delay estimation and the latter approach does not achieve a recursive spatial response.
 In both cases, there is no true spatial feedback between the array and the source of interest.
-Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in the temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
+Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.
-To this end, we arbitrarily choose to formulate the problem in the context of localization, hence our goal is to estimate the direction and the range of some target of interest. 
-\par The novelty, compared to traditional array processing, is the incorporation of a spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
-Assuming the target of interest has a mirror-like behaviour (i.e.
-reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
+To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
+\par The novelty, compared to traditional array processing, is the incorporation of spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
+Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
 Note that the initial stimulus can be generated by the target or the array itself. In the text to follow, we assume this is the latter. 
 Furthermore, as opposed to the passive target case (i.e., a target which merely reflects the impinging signal), one may consider a cooperative target, which receives, enhances and re-transmits the signal back to the array.
-\par The outline of this paper is as follows.
+% \par The outline of this paper is as follows.
 We first formulate the classic spatial beamforming setup in Sec.~\ref{sec:setup}.
 Then, in Sec.~\ref{sec_introduceFeedback}, we propose our novel feedback-based architecture, and formulate its spatial response.
-Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
-In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback.
+% Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
+% In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback.
 Specifically, we compute the array beamwidth, its peak-to-sidelobe ratio and the array directivity, showing significant improvement compared to traditional beamforming without spatial feedback.
-In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors.
+% In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors.
 We then suggest a strategy which mitigates this sensitivity.

### 2020-12-25 main/prelims.tex
Before applying meeting#1's comments

@@
 
-In this chapter, we overview the theoretical basis of the thesis. 
-In section 1...
-In section 2...
-In section 3...
+As a preliminary discussion to the presentation of out contribution, we overview some the key theoretical basis of the thesis.
+In Sec.~\ref{sec:prlm_propWaveField}, the wave propagation, being the most basic concept for array processing, is discussed.
+It is then followed by a short overview of array-processing in Sec.~\ref{sec:prlm_sensorArrays}.
+To accommodate the discussion for spatial filtering, we also mention the time-space relation of spatially sampled signals in Sec.~\ref{sec:prlm_timeSpaceSig}.
+As an additional theoretical concept, arriving from the information theory, which will be used in the main chapter (Ch.~\ref{chap:firstchap}), is the Fisher Information Matrix, covered in Sec.~\ref{sec:prlm_FIM}.
+\par 
+For an easier reading treat each section as independent, where notations and symbols are each defined in the specific section and are not mutual, nor used in the main chapter.
 
-\begin{definition}
-The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
-\end{definition}
+% \begin{definition}
+% The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
+% \end{definition}
 
@@
 \input{Modules/sec_prlm_propWaveField}
+% \section{Digital Filter Design - Finite/Infinite Response Filters}
+% \label{sec:prlm_FILTERS}
+% \input{Modules/sec_prlm_FILTERS}
 \section{Sensor arrays}
@@
 \input{Modules/sec_prlm_timeSpaceSig}
-\section{Sensor array performance measure}
-\label{sec:prlm_sensorArrayPerf}
-\input{Modules/sec_prlm_arrPerf}
-\section{Finite Impulse Response Based Spatial Filtering}
-\label{sec:prlm_FIR}
-\input{Modules/sec_prlm_FIR}
-\section{Infinite Impulse Response Filters}
-\label{sec:prlm_IIR}
+% \section{Sensor array performance measure}
+% \label{sec:prlm_sensorArrayPerf}
+% \input{Modules/sec_prlm_arrPerf}
 \section{Fisher Information Matrix}
 \label{sec:prlm_FIM}
-
-Let's define some concept we'll be using throughout the thesis.
+\input{Modules/sec_prlm_FIM}

### 2020-12-25 Modules/paper_sec_prlms.tex
1. Intro exapnsion - WIP 2. Move appdxs to end of thesis - DONE

\section{Beamforming}\label{sec:setup}
In this section, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented.
Consider an $N$-element ULA with inter-element spacing $\delta$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$. We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
Focusing on a far field localization problem, DOA and target range are to be estimated. Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
\begin{equation}
x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
\label{eqn:noFeedbackULA_singleSensor_temporal}
\end{equation}
where $\tau_{n}=n\delta\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write 
\[
\vecnot{\F{x}}\rBrace{\omega}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}
\]
where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
\begin{equation}
    \label{eq:d}
    d_{n}\rBrace{\omega} = \exp{\rBrace{-j\omega\tau_{n}}}.
\end{equation}
Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in the frequency domain
\begin{equation}
    \label{eq_Z}
    Z\rBrace{\omega} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
\end{equation}
Defining the electric phase to be
\begin{equation}\label{eq:thetaULA}
\theta=\omega{\delta\cos\Brack{\thetaD}}/{c},
\end{equation}
we rewrite \eqref{eq_Z} as 
\[
Z\rBrace{\omega} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
\]
hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018}. 
Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest. Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.). 
As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals. 
% The suggested structure is elaborated in Sec.~\ref{sec_introduceFeedback} and shown to be equivalent to IIR filter design.
\section{Feedback Beamforming}
\label{sec_introduceFeedback}
In this section, a feedback-based architecture is proposed for spatial signal processing.
Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIRBasicArch}), 
we propose to use the same concept in the spatial domain.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.7\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
            \put (60, 50){\footnotesize{$\beta_{0}$}}
            \put (60, 30){\footnotesize{$\beta_{1}$}}
            \put (60, 10){\footnotesize{$\beta_{2}$}}
            \put (36, 30){\footnotesize{$\alpha_{1}$}}
            \put (36, 10){\footnotesize{$\alpha_{2}$}}
            \put (10, 50){\footnotesize{$x$}}
            \put (85, 50){\footnotesize{$y$}}
            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
        \end{overpic}
    \end{center}
    \caption{Direct form II $2^{nd}$ order IIR architecture.}
    \label{fig_IIRBasicArch}
\end{figure}
The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}. The beamformer's output and the feedback signal are synthesized using two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.
Also, the FB block is marked (dashed line) for later use.
Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to a plain delay-and-sum (DS) beamformer.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.95\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR-diagram/SpatialIIR_VER9.png}
            \put (14, 39){\footnotesize{$\sum_{n=0}^{N-1}\beta^{*}_{n}x_{n}$}}
            \put (54, 39){\footnotesize{$\sum_{n=0}^{N-1}\alpha^{*}_{n}x_{n}$}}
            \put (24.25, 50){\footnotesize{$x_{0}$}}
            \put (35, 50){\footnotesize{$x_{1}$}}
            \put (55, 50){\footnotesize{$x_{N-1}$}}
            \put (30.5, 66){\footnotesize{$\delta$}}
            \put (89, 96){\footnotesize{$\vpt$}}
            \put (58, 58){\footnotesize{$\vpi{N-1}$}}
            \put (37, 58){\footnotesize{$\vpi{1}$}}
            \put (26.5, 58){\footnotesize{$\vpi{0}$}}
            \put (41.5, 64.5){\footnotesize{$\theta_{d}$}}
            \put (19, 11.25){\large{$+$}}
            \put (61.25, 27.25){\large{$+$}}
            \put (47, 11.75){$s$}
            \put (35.25, 11.75){$n$}
            \put (21,4){$z$}
            \put (63.5,14){$\Tx$}
            \put (1, 51){$\text{FB}_{\vAlpha,\vBeta}$}
        \end{overpic}
    \end{center}
    \caption{
    The proposed feedback beamformer.
    The spatial feedback is obtained by continuous re-transmission of $\Tx$ to the target at $\vpt$.
    We designate the feedback beamformer block (dashed line) for later use.
    }
    \label{fig:Proposed_spatialIIR_ARCH}
\end{figure}
\subsection*{Obtained spatial response}
\input{./Modules/Spatial_IIR-MathDerivations.tex}
\section{Fisher Information Matrix}
\label{sec_FIM}
\input{./Modules/sec_FIM_and_CRLB.tex}
\section{Performance Analysis}
\label{sec_Performance}
In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.  
\subsection*{Error terms}
In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
\begin{equation}\label{eq:alpha_beta_hat}
\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
\end{equation}
introducing the estimated steering vector 
\begin{equation}\label{eq:d_hat}
\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
\end{equation}
Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
\begin{equation}\label{eq:SF_CB}
    \resizebox{.894\linewidth}{!}{
        \begin{split}
            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
        \end{split}
    }
\end{equation}
where \[
\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
\]
is the normalized Dirichlet kernel and
\[
\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
r\triangleq g/\hat{g},
\]
are defined as the DOA, range and gain error terms respectively.
In the following, four fundamental scenarios are considered:
\begin{itemize}
    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
\end{itemize}
\ifdefined\showTodo
{
    \subsection*{Small estimation error analysis - \textbf{TO BE REMOVED - kept only for the todos}}
    \label{subsection_ArrayPerformance_TayolrAnalysis}
    \myTodo{inline}{\textbf{DONE:}\\ maybe to call this subsection 'small error analysis'}
    Plugging (\ref{eqn_CB_coefSet}) into (\ref{eqn:GeneralFeedbackTransferFunction}) and denoting $\D{N}{x} \triangleq \frac{\sin{\rBrace{Nx}}}{\sin{\rBrace{x}}}$ results in the general \coefSetName{} beampattern \myTodo{inline}{\textbf{DONE}\\you need to define the delta expressions (the errors)}
    \begin{equation*}
        h_{\coefSetName{}}\rBrace{\theta,\omega}
        =
        \frac{
        \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
        }{
        N - \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
        }.
    \end{equation*}
    For the evaluation of the various array parameters, we define the normalized beampattern \myTodo{inline}{\textbf{DONE:}\\not very readable. Consider writing a multiplication of two terms. Suggesting that you write the expression in eq(5) as $H(\theta,\phi)$ and here you'll have $H(\hat{\theta}, \hat{\phi})/ H(\theta,\phi)$}
    \begin{equation}
        \label{eqn_arrPerformance_beamwidth_3dB}
        \Hr{\theta}{\tau}{}\triangleq\fbBpRatio.
    \end{equation}
    \myTodo{inline}{\textbf{DONE:}\\this next section is very long. Suggesting that you express (10) in terms of the errors $\Delta\theta,\;\Delta\phi$, and then simply state that the second order Taylor expansion of those errors around zero gives (12). One more issue which I think might cause us some headache is that we cannot assure that $\Delta\phi$ (you call it $\Delta\tau$) is indeed close to zero, as this term fluctuates very fast. But we will think about it later on. Maybe something with wideband signal stimulus will solve this issue.}
    The pursuit for analytic dependencies between $\Hr{\theta}{\tau}{}$, $\dTheta$ and $\dPhi$, as in \cite{van2004optimum}, lead to expressing $\Hr{\theta}{\tau}{}$'s multivariate Taylor expansion, setting $\dTheta,\dPhi$ as the variables. Simulations have shown that $2^{nd}$ Taylor expansion achieves very accurate results, thus we use it to express the array parameters. As commonly known, the Taylor expansion of a multivariate analyzable function $f\rBrace{\vx}$ around $\vx_{0}$ where $\vx \in \mathbb{R}_{M\times1},$ is 
    \begin{equation}
        \label{eqn_h_Tylor_dTheta_dTau}
        \evalat{f\rBrace{\vx}}{\vx\to\vx_{0}}=\sum_{n=0}^{\infty}\frac{1}{n!}\rBrace{\sum_{i=1}^{M}(x_{i}-x_{0i})\frac {\partial}{\partial x_i} }^n f(x_k)|_{x_k=x_{k0}},
    \end{equation}
    where $\frac{\partial}{\partial x_i}$ is the derivative operator and $i\in\left[1\hdots{}M\right]$. Reducing (\ref{eqn_h_Tylor_dTheta_dTau}) to its $2^{nd}$ form (i.e $f(x,y)=\sum_{n=0}^{\infty} \frac 1 {n!}\rBrace{x\frac {\partial}{\partial x}+y\frac {\partial}{\partial y} }^n f(x,y)|_{(x,y)=(0,0)}$), combined with the binomial formula, $(x+y)^{n}=\sum _{k=0}^{n}{\binom {n}{k}}x^{n-k}y^{k},$ multiple iterations of L'Hôpital's rule and algebraic simplification finally yields
    \begin{equation}
        \begin{split}
            \evalat{\Hr{\theta}{\tau}{}_{\coefSetName{}}}{\dTheta\to0,\dPhi\to0} \approx\ & 1 
            \\+&\frac{\binom{2}{0}}{2!}\frac{-\rBrace{N - 1}\rBrace{N-4r+2Nr+1}}{6\rBrace{r-1}^{2}}\dTheta^{2}
            \\+&\frac{\binom{2}{1}}{2!}\frac{-r\omega\rBrace{N - 1}}{\rBrace{r-1}^{2}}\dTheta\dPhi
            \\+&\frac{\binom{2}{2}}{2!}\frac{-2r\omega^{2}}{\rBrace{r-1}^{2}}\dPhi^{2}
        \end{split}
    \end{equation}
}
\else
\fi
\subsection*{The normalized beampattern}
\label{subsection_spatialIIR_normBP}
As commonly done for ULA performance analysis \cite{van2004optimum}, we analyze the normalized response (i.e., where the peak main lobe gain is set to $0_{dB}$). Henceforth, setting $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ we define the normalized response
\begin{equation}
    \label{eq_narmalized_pattern}
    %\resizebox{.89\linewidth}{!}{
    \begin{split}
        \HrTPr&\triangleq
        \frac{
        \HbaFB
        }{
        H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}
        }
         =
        \frac{
        \HbaFB
        }{
        r/\rBrace{1-r}
        },
        % \\
        % &=\frac{\rBrace{1-r}^{2}\Dp{\dTheta/2,N}{2}}{1+r^{2}\Dp{\dTheta/2,N}{2}-2r\D{\dTheta/2}{N}\cos{\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}},
    \end{split}
    %}
\end{equation}
where the $\Delta\theta,\Delta\phi,r$ subscripts express the DOA, range and gain errors dependency, respectively.
%Also, $\abs{\HrTPr}$ is defined to be the beampattern.
Plugging \eqref{eq:SF_CB} into \eqref{eq_narmalized_pattern} yields 
\begin{equation}\label{eq_generalH}
    \resizebox{0.89\linewidth}{!}{
        \begin{split}
             \HrTPr=
             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.
        \end{split}
        }
\end{equation}
Note that the known \cite{van2004optimum} normalized response of standard ULA is obtained by setting $r=0$ and $\Delta\phi=0$
$$
\Hr_{\Delta\theta,\Delta\phi=0,r=0}=
             \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}}.
$$
Considering the steering error scenario (i.e., $\dTheta\neq0,\ \dPhi=0$) first, where 
\begin{equation}\label{eq_Hdphi0}
\Hr_{\Delta\theta,\Delta\phi=0,r}=
             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}},
\end{equation}
we evaluate the FB's beamwidth, sidelobe level and directivity and compare them to those of the standard ULA.
\vfill
\subsection*{Half power beamwidth}
\input{./Modules/arrayPerformance_beamwidth.tex}
\subsection*{Sidelobes attenuation}
\ifdefined\showDev
    \fbox{
    \begin{minipage}{0.9\linewidth}
    \textbf{development specifics}\\
    Let $f\rBrace{\dTheta} \triangleq \D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{(N-1)\dTheta/2}},$ such that $\Hr_{\Delta\theta,\Delta\phi=0,r=0} = \frac{f\rBrace{\dTheta}}{1-rf\rBrace{\dTheta}}.$ Then, we compute the beampattern's derivative and state that
    \begin{equation*}
    % \resizebox{0.9\linewidth}{!}{
        \begin{split}
            &\frac{\partial}{\partial\dTheta}\Hr_{\Delta\theta,\Delta\phi=0,r} &\\
            &=\frac{\Dp{\dTheta/2,N}{'}\rBrace{1-r\D{\dTheta/2}{N}}-\D{\dTheta/2}{N}\rBrace{-r\Dp{\dTheta/2,N}{'}}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}
            \\
            &=\frac{\Dp{\dTheta/2,N}{'}}{\rBrace{1-r\D{\dTheta/2}{N}}^{2}}.
        \end{split}
        % }
    \end{equation*}
    It follows that the sidelobes of the feedback-based beampattern are located at the same angles as the in the ULA case.
    \end{minipage}
    }
\else
\fi
By taking a derivative of $\Hr_{\Delta\theta,\Delta\phi=0,r}$ with respect to $\dTheta$ it can be easily verified that the beampattern's extrema points are located exactly as in the standard ULA beampattern. Specifically, the sidelobes locations are
\begin{equation}
    \label{eqn_CB_sidelobesLocations}
    \Delta\theta_{\text{sidelobe}} = \frac{\rBrace{2m+1}\pi}{N}\ \forall m\in\cBrace{\pm 1,\pm 2,\hdots}.
\end{equation}
Our main interest is with the first sidelobe (i.e. $m=1$), therefore we evaluate \eqref{eq_Hdphi0} at $\Delta\theta = 3\pi/N$, which results in
\begin{equation}
    \abs{\Hr_{{3\pi}/{N},0,r}}^2
    =
    \frac{
    2\rBrace{1-r}^{2}
    }{
    \rBrace{N^{2}-2Nr}\rBrace{1-\cos{\rBrace{\frac{3\pi}{N}}}}+2r^{2}
    }
    \label{eq_HSidelobes}
\end{equation}
and for large $N$ values 
\begin{equation*}
    \lim_{N\rightarrow\infty}\abs{\Hr_{3\pi/N,0,r}}=\frac{
    2\rBrace{1-r}
    }{
    3\pi
    }.
\end{equation*}
\ifdefined\showDev
    \fbox{
    \begin{minipage}{0.9\linewidth}
    \textbf{development specifics}\\
    We know that \eqref{eq_Hdphi0} can be rewritten as
    \begin{equation*}
        \begin{split}
            \Hr_{\Delta\theta,\Delta\phi=0,r=0} =
            \frac{
            \rBrace{1-\cos{\rBrace{N\dTheta}}}\rBrace{1-r}^{2}
            }{
            \begin{split}
                N^{2}&\rBrace{1-\cos{\dTheta}}+r^{2}\rBrace{1-\cos{N\dTheta}}
                \\
                &+Nr\Bigg(1+\cos{\rBrace{\rBrace{N-1}\dTheta}}
                \\
                &-\cos{\rBrace{N\dTheta}-\cos{\rBrace{\dTheta}}}\Bigg)
            \end{split}
            }
        \end{split}
    \end{equation*}
    Using the symbolic toolbox in MATLAB, setting $\dTheta=3\pi/N$, results in \eqref{eq_HSidelobes}.
    \end{minipage}
    }
\else
\fi
\par For standard ULA, the gain of the first sidelobe is known to be $2/3\pi$ \cite{van2004optimum}, which implies that the first sidelobe is smaller by a factor of $1-r$ compared to standard ULA.
Specifically, in perfect gain match scenario (i.e., $r\to{}1$) , the sidelobes vanish. 
\subsection*{Array directivity}
The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
\begin{equation}\label{eq_D}
    \mathcal{D}\rBrace{N,r} = \frac{\Hr_{\Delta\theta=0,\Delta\phi=0,r}}{\frac{1}{2\pi}\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta} = \frac{2\pi}{\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta},
\end{equation}
measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 
\begin{equation}\label{eq_D_result}
    \mathcal{D}\rBrace{N,r} \approx \frac{N-r}{1-r},
\end{equation}
where the standard ULA's known result is obtained for $r=0$.
Also, for $N\geq2$, $\lim_{r\rightarrow 1}\mathcal{D}\rBrace{N,r}=\infty$, implying infinite directivity for the perfectly gain-matched FB. 
\par Finally, expressing the improvement in directivity compared to the standard ULA, assuming large $N$ values, gives rise to
\begin{equation}\label{eq_Dimprovement}
\lim_{N\to\infty}\frac{\mathcal{D}\rBrace{N,r}}{\mathcal{D}\rBrace{N,0}}
=\frac{N/\rBrace{1-r}}{N}=\frac{1}{1-r}.
\end{equation}
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.75\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/directivity_expr.eps}
            \put (20, 10){\footnotesize{$N$}}
            \put (72, 6){\footnotesize{$r$}}
            \put (16.5, 70){\footnotesize{Numerical integration}}
            \put (16.5, 65){\footnotesize{$\rBrace{N-r}/\rBrace{1-r}$}}
            \put (-9, 45){\footnotesize{$\mathcal{D}\rBrace{N,r}$}}
        \end{overpic}
    \end{center}
     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}. Difference between the numerical integration result and the suggested analytic expression is around $\sim{1e^{-9}}$.}
    \label{fig_directivity}
\end{figure}
\subsection*{Summary}
To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance} 
\begin{table}[h!]
    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
    \centering
    \resizebox{1\linewidth}{!}{
        \begin{tabular}{||c c c c||}
            \hline
            & ULA & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 
            \hline\hline
            HPBW & $ 1.4/N$ & $1.4/\rBrace{f(r)N}$ & Narrower by a factor of $f\rBrace{r}$\\ 
            \thead{FIRST\\SIDELOBE\\GAIN} & $2/3\pi$ & $2\rBrace{1-r}/3\pi$ & \thead{smaller by a factor of $1-r$\\for $N\gg{}1$} \\
            DIRECTIVITY & $N$ & $\rBrace{N-r}/\rBrace{1-r}$ & \thead{$1/\rBrace{1-r}$ times higher \\ for $N\gg{}1$}\\
            [1ex] 
            \hline
         \end{tabular}
     }
    \label{table_arrayPerformance}
\end{table}

### 2020-12-25 Modules/sec_FIM_and_CRLB.tex
1. Intro exapnsion - WIP 2. Move appdxs to end of thesis - DONE

--- 2020-12-25 Modules/estimation_CRLB_appendix.tex
@@
 A possible evaluation for the contribution of the presented feedback mechanism is to measure the additional information in the system.
-To this end, the FIM, denoted by $\vecnot{J}$, will now be calculated with respect to the DOA $\rBrace{\thetaD}$ and range $\rBrace{\phi}$ parameters. 
+To this end, the FIM (see App.~\ref{apdx:FIM}), denoted by $\vecnot{J}$, will now be calculated with respect to the DOA $\rBrace{\thetaD}$ and range $\rBrace{\phi}$ parameters. 
 As the feedback-based transfer function (\ref{eqn:GeneralFeedbackTransferFunction}) is expressed in the frequency domain, we rely on \cite{zeira1990frequency} to express the frequency domain FIM as well.

### 2020-12-25 main/intro.tex
1. Intro exapnsion - WIP 2. Move appdxs to end of thesis - DONE

@@
 The basic concept was minimization of the inter-element spacing redundancy in order to increase the overall resolution.
+The main advantage of the first (i.e.
+virtual array) over the latter (i.e.
+minimum redundancy) is the obtainable analytical expression for the improvement in spatial selectivity when using virtual arrays.
+In the minimum redundancy approach no such expression is available.
+On the other side, the computation effort is considerably higher when the 2-nd order statistics are computed.
+Although the $q$-th order statistics based approach promises substantial improvement, both noise sensitivity and impractical computation amount are dominant drawbacks, limiting the usage of such methods in practical applications.
 Adaptive processing schemes \cite{frost1972algorithm,manolakis2000statistical}, being a wide and active research area, were also suggested trying to adaptively estimate and suppress the noise component in impinging signals by minimization of the receiver's output energy with some constraints.
+In \cite{manolakis2000statistical}, two main approaches to adaptive processing are discussed.
+The block adaptive scheme (which is also called \textit{sample matrix inversion}) and the sample-by-sample method.
+In both methods, after a certain amount of time, the system refreshes the spatial filter coefficients, trying to better suppress the received noise.
+As in many adaptive processing applications, the two methods rely on steepest descend optimization, which expose the adaptive processing approach to errors related to optimization parameters choices such step size etc.
 \par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g.
@@
 The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array. 
-Surely, the former approach heavily relies on the accuracy of the delay estimation and the latter approach does not achieve a recursive spatial response.
-In both cases, there is no true spatial feedback between the array and the source of interest.
-Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
+The former approach heavily relies on the accuracy of the delay estimation which are amplified due to the fact that both the desired signal and the errors are continuously fed back into the filter.
+Close inspection of the latter approach reveals that even though the sub-arrays are each weighted separately, each sensor's output is eventually linearly weighted when taking into account all related sub-arrays.
+Clearly, this is just another possible implementation of basic FIR like ULA spatial processor, so in both cases, there is no true spatial feedback between the array and the source of interest.
+Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{Hum2009BeamformingFilters}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
+\par
+TODO: Elaborate on the 2/3D planar from (by order)
+\begin{itemize}
+    \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
+    \item Three-Dimensional Cone Filter Banks
+    \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
+    \item UWB Beamforming Using 2-D Beam Digital Filters
+\end{itemize}
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.

### 2021-01-08 Modules/Spatial_IIR-MathDerivations_EXT.tex
Before implementing Tsvi's comments

--- 2020-10-31 Modules/Spatial_IIR-MathDerivations.tex
@@
             {
-            \alpha^{*}_{m}\omegaB\F{x}_{m}
+            \alpha^{*}_{m}\F{x}_{m}
             \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
@@
 $$
-\F{\vx} = g\rBrace{\F{s}+\vAlphaH \F{\vx}}\vd\exp{\rBrace{-j\omega\tau\_{pd}}},
+\F{\vx} = g\rBrace{\F{s}+\vAlphaH \F{\vx}}\vd\exp{\rBrace{-j\omega\tau_{pd}}},
 $$
@@
 \par Note that this architecture achieves a controllable (via setting of $\vBeta$ and $\vAlpha$) and recursive (non-trivial denominator) spatial response.
-As will be shown, high directivity and narrow beamwidth are obtainable by proper selection of the weights.
+As will be shown, high directivity and narrow beamwidth are obtainable by a proper selection of the weights.
 Compared to traditional beamformers (i.e., without feedback), the performance improvement will be expressed in terms of increased aperture, narrower beamwidth and improved sidelobe attenuation.
-One may observe that opposed to traditional beamformers, the array response, $\Hba,$ is not only influenced by the impinging signal DOA, for it is also range selective due to its $\phi$ dependency.
+One may observe that opposed to traditional beamformers, the array response, $\Hba,$ is not only influenced by the impinging signal DOA, since it is also range selective due to its $\phi$ dependency.
 As demonstrated in Fig.~\ref{fig_rangeAzimuthSelectivity}, the combination of both angular and range selectivity enables the designer to enhance signals arriving from specific locations (grey area) rather than only specific directions.
@@
     \begin{center}
-        \begin{overpic}[width=0.65\linewidth, 
+        \begin{overpic}[width=0.75\linewidth, 
         % grid, 
@@
             \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
-            \put (30.5, 47){\rotatebox{0}{\footnotesize{Enhanced radial slice}}}
+            \put (32, 47){\rotatebox{0}{\footnotesize{Enhanced radial slice}}}
         \end{overpic}

### 2021-01-08 Modules/sec_future_coef.tex
Before implementing Tsvi's comments

As mentioned in Sec.~\ref{sec_introduceFeedback}, the reasoning for the selection of $\vecnot{\alpha}, \vecnot{\beta}$ as the conventional beamformer generalization, was the FIM related information considerations.
Obviously, there are many more possibilities/considerations to choosing the coefficient.
Some examples for such coefficient choosing schemes may include
\begin{itemize}
    \item Finite word affects
    \item Nulling of specific DOAs
    \item Setting all poles in a single DOA may lead to enhanced directivity
    \item General radiation patterns of the sensors
\end{itemize}
and many more.

### 2021-01-08 Modules/sec_future_dynamic.tex
Before implementing Tsvi's comments

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 2D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be translated into a dynamic propagation delay, $\tau_{pd}\rBrace{t}$.
It follows that an auxiliary temporal quantity should be defined, $t_{i}\rBrace{t}$, which links between the received signal's impinging moment $t$, and its corresponding reflecting moment in the target of interest.
Hence one may describe it as
\begin{equation}
    t_{i}\rBrace{t}=\underset{\tau}{\mathrm{arg}}\cBrace{\tau-t=\frac{R\rBrace{\tau}}{c}}.
\end{equation}
With $t_{i}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{i}\rBrace{t}}}}.
\end{equation}
One may consider the following research approaches for further investigation
\begin{itemize}
    \item \textbf{Modeling of target's location}
    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R_{0}+\rBrace{c+v_{\theta}}t}{c}$$, where $R_{0}$ and further development may lead to a closed form response like in the stationary case.
    In this manner, other component may be added to the positional equation.
    \item \textbf{Frame based processing}
    \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
\end{itemize}

### 2021-01-08 Modules/sec_future_multiTarget.tex
Before implementing Tsvi's comments

Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious expansion of \eqref{eqn:SingleSensorTemporalEquality} is 
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = \sum_{i=0}^{i=P-1}{\rBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
\end{equation}
where $\tau_{pd,i}$ is the delay of the signal which reflected from $p_{t,i}$.
Interesting directions of research may include
\begin{itemize}
    \item The affects of closely positioned targets
    \item Localization resolution
    \item Maximal number of simultaneously detected targets with respect to N
    \item Performance of independent super-positioned dual-frequency (see Sec.~\ref{sec_app}) systems.
\end{itemize}

### 2021-01-08 Modules/sec_future_wavfrom.tex
Before implementing Tsvi's comments

In practical RADAR related systems, the waveform of choice is pulse (chirp) based.
It holds some obvious advantages over the CW transmission such as
\begin{itemize}
    \item Lower power consumption
    \item Inherent nulling in the radial axis (localization)
    \item Possible match filters should allow the decision of weather to re-transmit or not
    \item In multi target scenario, there is a smaller chance of interference.
    \item The most interesting research option is the use of several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions, by merely selecting harmonic couples and filter coefficients, where each harmonic/coefficient set it pointed to a specific area.
    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
\end{itemize}

### 2021-01-08 Modules/sec_prlm_FIR_IIR.tex
Before implementing Tsvi's comments

A basic design entity in every signal processing scheme is the digital filter, which is the modern evolution of analog filters.
The design of the digital filter is a very established and thoroughly studied research area.
As stated in \cite{oppenheim1975digital} (and numerous other literature), two key filter types are used - i.e. Finite Impulse Response (FIR) and Infinite Impulse Response (IIR) filters.
This section will briefly overview the design methods and main flavours of each filter type and discuss in general of the pros and cons of them in order to provide proper motivation for the quest of finding the IIR analogy of the spatial FIR, as implied in Ch.~\ref{chap:intro}.
\subsection{FIR design}
The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equal to the number of taps in the final filter's configuration.
Determining it coefficients is generally done using windowing (weighted element-wise multiplication and truncation) of desired impulse response which is derived by the inverse Fourier transform of the desired frequency response.
Many window types have been suggested in literature, where Bartlet, Hanning, Humming and Blackman are among the most basic ones, each with its pros and cons.
I a nutshell, using a rectangular window, achieves the narrowest main lobe but also the highest side-lobes.
The other window types, achieve lower side-lobes at the expense of wider main-lobe.
The user may also increase the filter's order if side-lobe attenuation is of high importance, thus achieving narrower main-lobe. 
\subsection{IIR design}
The infinite response of the IIR filters originates in the inherent feedback which reuses output in the computing part, generating a loop which theoretically takes all input past samples into account for each output sample.
As there are many flavours of the IIR filters, we choose to elaborate on the elliptic filter, being the more common candidate for comparison to the FIR in the literature.
The basic concept behind the elliptic filter design is the allowing of equi-ripple around both pass and stop band which both relaxes the filter's constrains comparing to Chebyshev and Butterworth methods and allows the narowest transition band between the three filters.
The designer sets the allowed ripple magnitudes in both pass and stop bands and positions the transition band according to his needs.
A closed for transformation, described in \cite{oppenheim1975digital} is then used to convert the prototype low-pass filter to band-pass, band-stop or high-pass filters.
\subsection{Comparison}
The main advantage of FIR filters, commonly required in signal processing systems is the obtainable linear phase feature. A well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant, namely linearly dependent in the phase response derivative of the specific frequency.
Therefore, linear phase implies that the phase response's derivative (i.e. signal latency) is frequency independents, which prevent signal distortion.
The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
In this work, the signals are assumed to be narrow-band, which reduces the necessity of linear phase response, while when considering sensor arrays, the costs and the physical aperture are of very high importance, motivating the designers to try and reduce the number of elements in the array while still meeting the specifications.

### 2021-01-08 Modules/sec_prlm_localization.tex
Before implementing Tsvi's comments

In the wide and very active research field of parametric estimation, one subject of very high relevance to this thesis is the sensor-array based localization - i.e. positional parameters estimation of impinging signal which is measured by an array of sensors.
In this work, we focus on localization of signal sources in the far-field case, where free space signal propagation is assumed.
Following the classical methods overview in \cite{krim1996two},most localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
The basic difference between the two groups is the assumption of impinging signal's statistical model when using parametric approach, which leads to higher accuracy in the expense of computation effort.
In both approaches, the estimations are based on calculation of several hypothesis and choosing the peaks in the generated graph.
Considering the search for a single parameter (e.g. DOA in a 2D plane), the two approaches are pretty similar in the sense that in both, the processor computes the confidence in a predetermined set of hypothesis which is followed by a single dimension scan.
The difference is more evident when considering multiple parameter, such as spherical direction (i.e. azimuth and elevation) or even actual location adding also the distance to the target of interest.
In the spectral based, each parameter is estimated independently of the other parameters, resulting in several 1D scans (as the number of estimated parameters), where the parametric approach will result in a multi-dimensional search for the best fitted parameters set.
In the following, a basic overview of some classical algorithms is presented.
The earliest localization algorithms, which date back to world war II, are the beamforming based, e.g. the conventional Bartlet beamformer.
These methods, although appealing in terms of complexity and computation effort, suffer from fundamental limitation, e.g. its spatial performance depend solely on the array aperture and no improvement is achieved when more data is collected.
Another class of estimators, where a statistical model is assumed (which is also the drawback of those methods), is the parametric estimators such as Maximum-Likelihood \cite{TWODECADES-81/106} and Maximum-Entropy \cite{TWODECADES-23}.
Until the mid- 1970's, direction finding techniques required knowledge of the array directional sensitivity pattern in analytical form, and the task of the antenna designer was to build an array of antennas with a prespecified sensitivity pattern.
Trying to relax the need for such accuracy, also serving as the origin of the sub-space based approach, was the Multiple SIgnal Classification (MUSIC) \cite{MUSIC_} algorithm.
In general, the MUSIC algorithm consists of several stages:
\begin{itemize}
    \item Estimation of the covariance matrix
    \item Eigen decomposition - extracting the eigen values and its related eigen-vectors
    \item Estimating the number of sources
    \item Projecting the samples over the array manifold
    \item Finding the largest peaks according to the estimated number of sources
\end{itemize}
MUSIC essentially relieved the designer from the need of accurate radiation patterns by exploiting the reduction in analytical complexity that could be achieved by calibrating the array.
Thus, the array response calculation task was reduced to that of measuring and storing the response. 
Although MUSIC did not mitigate the computational complexity of solution to the DOA estimation problem, it did extend the applicability of high-resolution DOA estimation to arbitrary arrays of sensors.
Another, probably even more important breakthrough, was the introduction of the array manifold and noise space (hence its name - sub-space) which proved to be orthogonal, thus allowing the use of orthogonal projection.
In the very thorough review of classical algorithms \cite{TWODECADES}, two approaches - i.e. the parametric approach and ULA-specific algorithms are also discussed.
the parametric approach, where stochastic model is assumed and Maximum Likelihood (ML) and Stochastic Maximum Likelihood (SML) are employed, is less relevant to this work therefore not discussed.
In the set of ULA-specific algorithms, including ROOT-MUSIC \cite{ROOT_MUSIC}, ESPRIT (Estimation of Signal Parameters via Rotational Invariance Techniques) \cite{ESPRIT} and some iterative methods.
We choose to emphasize on the ESPRIT method, being an important milestone in the path to state-of-the-art algorithms.
In addition to using the rotational invariance of the signal sub-space eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - mitigating numerical problems associated with ill-conditioned matrices.
Following state-of-the-art developments \cite{BOOK-classicalAndModernDOA}, the sub-space based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm MUSIC} but also new and interesting approaches emerged
\begin{itemize}
    \item High Order Statistics (HOS, also refereed as comulants), which extracts more information from the samples' higher order moments, is a very active field of research due to some fundamental issues which are inherently resolved - i.e. the Gaussian noise vanishes in the 4th order statistics and the ability to resolve more DOAs than array elements.
    This approach, being costly in computation effort, became popular probably due to the recently available low-cost powerful computation.
    \item Sparsity based estimation, using non-Frobenius norm used in the algorithms development, has proved to improve estimation resolution in some cases \cite{LocalizationOfMultipleSpeaker}, namely high reverbrant acoustic scenarios, but is less relevant to this work therefore not elaborated.
    \item A very wide and active research field is the concept of cooperative localization related to mobile networks is growing at a very high rate due to the never-ending need for high-bandwidth and low-power communication of the mobile networks.
    It is also less relevant to this work.
    \item Naturally, also many trials of harnessing the promising concept of neural networks are being done, for example \cite{NNDOA}
\end{itemize}
In this work, we actually revisit the most basic approach - i.e. beamforming.

### 2021-01-08 Modules/sec_rangeSensitivityError_EXT.tex
Before implementing Tsvi's comments

--- 2020-10-31 Modules/sec_rangeSensitivityError.tex
@@
 \label{sec_sim}
-In this section, we investigate $\HrTPr$ for the general case, where also range misalignment phase term $\dPhi$ is possibly non zero.
+In this section, we investigate $\HrTPr$ for the general case, where the range misalignment phase term $\dPhi$ may also be non zero.
 In Fig.~\ref{fig_hDUDTContour}, we plot $\abs{\HrTPr}$ in logarithmic scale, with respect to both steer and range misalignments.
 Close inspection of the range error related beampattern behaviour sheds light to some important points.
-First, we notice that although setting $r\to1$ (i.e., close to perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks.
+First, we notice that although setting $r\to1$ (i.e., close to a perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks.
 Next, as evident from \eqref{eq_generalH}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).
@@
 \]
-where $R_{\text{rt}}=2R$ is the round-trip distance between the array and the target of interest. 
+where $R_{\text{rt}}=2R$ is the round-trip distance between the array and the target of interest and $\lambda$ is the wavelength. 
 Define
 \[
-\Delta R_{\text{rt}}\omegaB=\frac{\dPhi\lambda}{2\pi} 
+\Delta R_{\text{rt}}=\frac{\dPhi\lambda}{2\pi} 
 \]
 to be the range estimation error.
-Figure~\ref{fig_rangError} shows that even minor range errors of $\Delta R_{\text{rt}}\sim0.1\lambda$ significantly distort the beampattern.
+Fig.~\ref{fig_rangError} shows that even minor range errors of $\Delta R_{\text{rt}}\sim0.1\lambda$ significantly distort the beampattern.
 \begin{figure}[t!]

### 2021-01-08 Modules/stabilityEnhancement_freqPairApproach_EXT.tex
Before implementing Tsvi's comments

--- 2020-10-31 Modules/stabilityEnhancement_freqPairApproach.tex
@@
     \begin{center}
-        \begin{overpic}[width=0.9\linewidth, 
+        \begin{overpic}[width=0.99\linewidth, 
         % grid, 
@@
             \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
-            \put (18.25, 13){\footnotesize{Harmonic mean}}
+            \put (18.75, 13){\footnotesize{Harmonic mean}}
             \put (32, 2){$Z_{\text{DF}}$}
             \put (54.75, 24){$\Sigma$}
-            \put (21.75, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
+            \put (22, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
             \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
@@
 These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$.
-The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ describe the additive noise.
+The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ represents the additive noise.
 
@@
 where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
-Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}, we compute the reciprocal of each frequency response, average, and compute the reciprocal again.
+Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again.
 This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
@@
 % As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
-\ifdefined\useOmega
-Straight forward derivations, Allowing $g$ to be frequency dependent, leads to
-\else
 For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
@@
 Assume that we aim to achieve a maximal phase error of $\Delta \phi=0.01\pi$.
-Hence, when using DF architecture, the dictated frequency separation must satisfy
+Hence, when using the DF architecture, the dictated frequency separation must satisfy
 \begin{equation}\label{eq_DF_phErr}
@@
 \end{equation}
-or equivalently, for maximal range error of $10$~m, a frequency separation of
+or equivalently, for a maximal range error of $10$~m, a frequency separation of
 \[
@@
 For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both feedback beamformers are mismatched.
-\par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
+\par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves a near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
 In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer.
-Evidently, even in the noisy case, the DF beamformer achieves close-to-ideal beampattern, while the SF beamformer suffers severe distortions.
+Evidently, even in the noisy case, the DF beamformer achieves a close-to-ideal beampattern, while the SF beamformer suffers from severe distortions.
 \begin{figure}[t!]
@@
     \end{center}
-    \caption{Simulating the 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR.
+    \caption{Simulating a 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR.
 For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$.
@@
     \begin{center}
-        \begin{overpic}[width=.9\linewidth, 
+        \begin{overpic}[width=.99\linewidth, 
         % grid, 

### 2021-01-08 main/chap_futureResearch.tex
Before implementing Tsvi's comments

In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
As mentioned in Sec.~\ref{sec:setup}, we assumed a single target stationary scenario where the target's location is fixed.
Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios which obviously should be followed by a combined general scenario of multiple dynamic targets performance scenario.
Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
\section{Dynamic target}
\label{sec_future_dynamic}
\input{Modules/sec_future_dynamic}
\section{Multi-target scenario}
\label{sec_future_multiTarget}
\input{Modules/sec_future_multiTarget}
\section{Waveform modifications}
\label{sec_future_wavfrom}
\input{Modules/sec_future_wavfrom}
\section{Coefficients quality criteria}
\label{sec_future_coef}
\input{Modules/sec_future_coef}
% \section{Apply to other applications}
% \label{sec_future_applications}
% \input{Modules/sec_future_applications}

### 2021-01-08 main/intro.tex
Before implementing Tsvi's comments

@@
 Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{Hum2009BeamformingFilters}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
-\par
-TODO: Elaborate on the 2/3D planar from (by order)
-\begin{itemize}
-    \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
-    \item Three-Dimensional Cone Filter Banks
-    \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
-    \item UWB Beamforming Using 2-D Beam Digital Filters
-\end{itemize}
+% \par
+% TODO: Elaborate on the 2/3D planar from (by order)
+% \begin{itemize}
+%     \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
+%     \item Three-Dimensional Cone Filter Banks
+%     \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
+%     \item UWB Beamforming Using 2-D Beam Digital Filters
+% \end{itemize}
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.

### 2021-02-12 Modules/Spatial_IIR-MathDerivations.tex
Sent as draft No.2

@@
     % \resizebox{.91\linewidth}{!}{
-        \begin{split}
             X_{n} =
-            g\Bigg( & \F{s}
+            g\rBrace{\F{s}
             \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
-            \\&+\sum_{m=0}^{N-1}
+            +\sum_{m=0}^{N-1}
             {
-            \alpha^{*}_{m}\omegaB\F{x}_{m}
+            \alpha^{*}_{m}\F{x}_{m}
             \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
-            }\Bigg),
-        \end{split}
+            }},
     % }
@@
 \]
-as the round-trip signal propagation related electrical phase and using the Woodbury matrix identity \cite{woodbury1950inverting}, we find that
+as the round-trip signal propagation related electrical phase.
+We use the Sherman-Morrison formula \cite{sherman1950adjustment}, considered to be a result of the Woodbury matrix identity \cite{woodbury1950inverting}, stating that
+\begin{equation*}
+    \rBrace{I+\vecnot{u}\vecnot{v}^{T}}^{-1}=I-\frac{\vecnot{u}\vecnot{v}^{T}}{1+\vecnot{v}^{T}\vecnot{u}},
+\end{equation*}
+where $\vecnot{u},\vecnot{v}$ are two $N\times1$ vectors and $I$ is the identity matrix.   
+Setting $\vecnot{u}=-g\vecnot{d}\exp{\rBrace{-j\omega\tau}}$ and $\vecnot{v}=\vecnot{\alpha}^{*}$ gives rise to
+\begin{equation*}
+    \rBrace{I+-g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}^{-1} 
+    = I+\frac{g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
+\end{equation*}
+which results in
+\begin{equation*}
+    \frac{\rBrace{I-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}+g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}\vecnot{d}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}.
+\end{equation*}
+Obviously the numerator's 2nd and 3rd terms vanish using the commutativity concept stating that
+\begin{equation*}
+    \vecnot{\alpha}^{H}\vecnot{d}\vecnot{d} = \vecnot{d}\vecnot{\alpha}^{H}\vecnot{d}
+\end{equation*}
+which finally results in
 $$
@@
     \begin{center}
-        \begin{overpic}[width=0.65\linewidth, 
+        \begin{overpic}[width=0.55\linewidth, 
         % grid, 

### 2021-02-12 Modules/abstractEnglish_LOCAL.tex
Sent as draft No.2

State-of-the-art array processing methods, ranging from high-order statistics to adaptive configuration, require costly computing efforts in pursuit for spatial performance improvement.
\par 
Considering localization related applications, several processing approaches are to be found. The most approach is \emph{beamforming}, i.e scanning the area of interest and marking peaks in output energy as targets of interest.
Another approach, which is probably the most commonly used, is the subspace-based processing which tries to identify input signals that fit into the array's manifold using the orthogonal projection concept.
Statistical processing, although costly in terms of computation effort, is also in use, ranging from maximum-likelihood related schemes to higher-order-statistics using cumulants.
Newer approaches which are still in research stage use neural networking and sparsity algorithms.
\par
Although mush researched, in this work we revisit the \emph{beamforming} approach and suggest
a feedback based approach, featuring low complexity and high spatial performance in the mere excess of integrating a transmitter to the array, which in RADAR-like arrays is already in place.
In the proposed scheme, a signal is continuously re-transmitted between the array and the target of interest, thus creating a spatial loop which is shown to be equivalent of enlarging the array's aperture in terms of spatial resolution.
\par 
Using a traditional beamforming performance analysis, the beamwidth, peak to side-lobe ratio, array directivity and white noise sensitivity are evaluated for the feedback based array.
A significant improvement in all aspects is shown, while thoroughly discussing the conditions for enhanced performance.
Considering ideal scenarios, the feedback beamformer virtually achieves an infinite aperture, increasing the available spatial information about the target and significantly improves the array's spatial performance.
\par
Taking into account the unavoidable estimation errors and uncertainties, we find that the basic feedback integrated beamformer is very sensitive to even mild errors due to the high frequencies of practical carrier signals.
Seeking for a solution, bearing in mind that summing multiple harmonics produce also other lower / higher frequencies, we propose a practical and robust implementation of the feedback-based localization concept.
We then thoroughly analyse this \emph{dual-frequency} method and find that it features low and controllable estimation errors sensitivity in the mere expense of doubling the computation effort.

### 2021-02-12 Modules/abstractHebrew.tex
Sent as draft No.2

@@
 שיערוך מאפיינים מתוך מדידות הינו מושא לעניין רב עוד מראשית ימי המדע, כשחוקי הפיזיקה נלמדו בעזרת תצפיות ומדידות.
-עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון להלחמת מידע ממספר מדידות בו זמנית.
+עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון לעיבוד מקבילי של מידע ממספר רגשים.
 אחד התחומים בהם עלה משמעותית הצורך בדיוק השיערוך, היה העיבוד המרחבי - קרי שיערוך פרמטרים מרחביים מתוך מדידות. 
-עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה.
+עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה בדמות רדאר ה
+\textenglish{Mammut}
+שנבנה על ידי הגרמנים לזיהוי מוקדם של מטרות טסות בגבהים עד 8 ק"מ ומרחקים של עד 300 ק"מ.
 \par
@@
 במערכות תקשורת, הצורך בסינון מרחבי הוא מן המעלה הראשונה, שכן במציאות מרובת המשדרים והמקלטים, במידה ולא היה שימוש במערכים, הפרעות הדדיות היו מונעות את פענוח האות הנקלט.
-במקביל, לא רק סינון אלא גם הכוונת אלומת השידור הפכה לאפשרית בזכות השימוש בו-זמנית במספר רב של משדרים
+במקביל, לא רק סינון אלא גם הכוונת אלומת השידור הפכה לאפשרית בזכות השימוש במערכי מופע
 \textenglish{(phased array)}
@@
 \par
-לשם המחשת הפתרון שמוצע, עבודה זו מתמקדת בתחום האיכון - בסביבה אקוסטית או אלקטרו מגנית.
+למשל, עלתה הצעה לשערך את השהיית האות בין רגשים שכנים, וע"י כך לייצר היזון חוזר בצורה מלאכותית.
+גישה זו חשופה לשגיאות מדידה וחוטאת למטרת העיבוד המרחבי הטהור - שכן היא מערבת עיבוד זמני.
+הצעה נוספת היתה להתייחס לתת מערכים (מתוך מערך אחד) חופפים כאל הסחות זמניות של מערך אחד קטן יותר ובכך לייצר קירוב סופי לתגובת ההלם האינסופית.
+הצעה זו אינה אלא פרשנות שונה לעיבוד מבוסס 
+\textenglish{FIR}
+שכן בסופו של תהליך העיבוד הינו לינארי ומכיל מספר סופי של דגמים במערכת בכל זמן נתון.
+שיטה מעניינת, המהווה בסיס למחקר ענף, מטילה את הדגימה המרחבית והדגימה הזמנית אל מישור התדר, בו גל מישורי מיוצג על ידי קו ישר המוטה לפי זוית ההגעה של הגל הפוגע.
+בהמשך לכך, מסננים במרחב התדר הדו מימדי מתוכננים על מנת להגביר אותות שמגיעים מכיוונים רצויים.
+גישה זו בשימוש רחב בתחום החקר הסיסמי וסובלת בעיקר מחוסר היכולת לתכנן מסננים מדויקים היות והמסננים מחזוריים בתדר, עובדה הגורמת לעיוותים בקצוות מרחב התדר.
+עוד על כן, גם שיטה זו אינה סינון מרחבי טהור ולכן אינה מהווה פתרון לשאלת המחקר אותה ניסינו לפתור.
+\par
 מוצעת איפוא, מערכת מבוססת מערך לינארי בעל מרווחים אחידים בין הרגשים
@@
 כאשר בראשיתו, בנוסף על הרגש, ישנו משדר.
-על פניו, מערכת דומה למכ"ם, השולח אות ומשערך את מיקומי מטרות על פי האות החוזר.
-החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק אות מלאכותי הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך.
+על פניו, מערכת דומה למכ"ם, הפולט אות ומשערך את מיקומי מטרות על פי האות החוזר.
+החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק אות מלאכותי הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך, בכך נוצר היזון חוזר בין מהמערך והמטרה.
 ניתוח המערכת מרמז כי ע"י שליטה במשקלות המסנן המייצר את האות החוזר, ניתן להפיק את היתרונות הרבים הטמונים במסנן בעל התגובה האינסופית.

### 2021-02-12 Modules/apndx_directivityFit.tex
Sent as draft No.2

In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the numerical evaluation reaches rational fractions when rational values of $r$ were used.
Following that hint, we numerically swept various values of $N,r$ doublets, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the feedback beamformer.
In the following, we elaborate on the sweeping process it's technicalities.
\par The first step was to formulate the symbolic expression for $H$.
To this end, we used MATLAB\textsuperscript{\textregistered}'s symbolic toolbox, generating the symbolic response $H$.
Afterwards, the 2D sweep range was set, where as mentioned before, $r$ was set to be of rational values.
In each sweep step, an numerical integration was executed with specific values for $N$ and $r$.
Each result was fitted with it's next closest rational number with the help of MATLAB\textsuperscript{\textregistered}'s \emph{rats} auxiliary command.
After observing the results, we found that all of then obey the same expression as in \eqref{eq_D_result} for any tolerance, which increased the confidence in the suggested expression.
\par The printout of the code is presented as Table.~\ref{table_D}
\begin{table}[h!]
    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
    \centering
    %\resizebox{1\linewidth}{!}
    {
        \begin{tabular}{||c c c c c c c c c c||}
            \hline
            $r \textbackslash N$ & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ [0.5ex] 
            \hline\hline
            1/10     & 19/9  & 29/9  & 13/3  & 49/9  & 59/9  & 23/3  & 79/9  & 89/9  & 11   \\ [1ex] 
            1/5      & 9/4   & 7/2   & 19/4  & 6     & 29/4  & 17/2  & 39/4  & 11    & 49/4 \\ [1ex] 
            1/3      & 5/2   & 4     & 11/2  & 7     & 17/2  & 10    & 23/2  & 13    & 29/2 \\ [1ex] 
            1/2      & 3     & 5     & 7     & 9     & 11    & 13    & 15    & 17    & 19   \\ [1ex] 
            5/8      & 11/3  & 19/3  & 9     & 35/3  & 43/3  & 17    & 59/3  & 67/3  & 25   \\ [1ex] 
            3/4      & 5     & 9     & 13    & 17    & 21    & 25    & 29    & 33    & 37   \\ [1ex] 
            4/5      & 6     & 11    & 16    & 21    & 26    & 31    & 36    & 41    & 46   \\ [1ex] 
            \hline
         \end{tabular}
     }
    \label{table_D}
\end{table}
\section*{MATLAB\textsuperscript{\textregistered} Code}
\lstinputlisting[style=mcode]{Modules/directivityAnalysis.m}

### 2021-02-12 Modules/arrayPerformance_beamwidth_LOCAL.tex
Sent as draft No.2

--- 2020-12-25 Modules/arrayPerformance_beamwidth.tex
@@
-The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
-It represents the DOA where the beampattern's energy reduces to half of its maximal value.
-For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
-$$\dThetaHPBW/2= 1.4/N.$$
-\par In App.~\ref{apdx_HPBW} we extend this known result for any $r\geq 0$. It turns out that for large $N$, the HPBW is obtained by solving for $x$ the equality
+% The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
+% It represents the DOA where the beampattern's energy reduces to half of its maximal value.
+\par In App.~\ref{apdx_HPBW} we extend the known result of \eqref{eq_known_HBPW} for any $r\geq 0$. It turns out that for large $N$, the HPBW is obtained by solving for $x$ the equality
 \begin{equation}\label{eq_HPBW}
@@
 Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA.
-Numerical evaluation (see Fig.~\ref{fig_feedbackULA_beamwidth_limit_r_dependent}) shows that $f(r)$ may be approximated with a second order polynomial
+To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values (actually slicing a vertical column of Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} at $N=100$) and looked for proper polynomial approximation using MATLAB\textsuperscript{\textregistered}.
+It turns out that the 2-nd order polynomial best suits the computation and that the best fitted expression is 
 \begin{equation}

### 2021-02-12 Modules/paper_sec_prlms.tex
Sent as draft No.2

@@
-\section{Beamforming}\label{sec:setup}
-In this section, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented.
-Consider an $N$-element ULA with inter-element spacing $\delta$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$.
-We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
-Focusing on a far field localization problem, DOA and target range are to be estimated.
-Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
-For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
-Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
-In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
-$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
-Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
-\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
-\begin{equation}
-x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
-\label{eqn:noFeedbackULA_singleSensor_temporal}
-\end{equation}
-where $\tau_{n}=n\delta\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
-Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write
-\[
-\vecnot{\F{x}}\rBrace{\omega}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}
-\]
-where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
-\begin{equation}
-    \label{eq:d}
-    d_{n}\rBrace{\omega} = \exp{\rBrace{-j\omega\tau_{n}}}.
-\end{equation}
-Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in the frequency domain
-\begin{equation}
-    \label{eq_Z}
-    Z\rBrace{\omega} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
-\end{equation}
-Defining the electric phase to be
-\begin{equation}\label{eq:thetaULA}
-\theta=\omega{\delta\cos\Brack{\thetaD}}/{c},
-\end{equation}
-we rewrite \eqref{eq_Z} as 
-\[
-Z\rBrace{\omega} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
-\]
-hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018}.
-Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
-\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest.
-Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.).
-As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
-Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals. 
-% The suggested structure is elaborated in Sec.~\ref{sec_introduceFeedback} and shown to be equivalent to IIR filter design.
-\section{Feedback Beamforming}
+In this chapter, we revisit the most basic DOA estimation approach, i.e. beamforming, and present our novel feedback based architecture.
+The feedback based beamforming concept is introduced in Sec.~\ref{sec_introduceFeedback}.
+Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix.
+The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
+Considering practical scenarios, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.
+
+\section{Notations and problem setup}
 \label{sec_introduceFeedback}
 In this section, a feedback-based architecture is proposed for spatial signal processing.
-Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIRBasicArch}), 
+Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIR_arch}), 
 we propose to use the same concept in the spatial domain.
-\begin{figure}[t!]
-    \begin{center}
-        \begin{overpic}[width=0.7\linewidth, 
-        % grid, 
-        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
-            \put (60, 50){\footnotesize{$\beta_{0}$}}
-            \put (60, 30){\footnotesize{$\beta_{1}$}}
-            \put (60, 10){\footnotesize{$\beta_{2}$}}
-            \put (36, 30){\footnotesize{$\alpha_{1}$}}
-            \put (36, 10){\footnotesize{$\alpha_{2}$}}
-            \put (10, 50){\footnotesize{$x$}}
-            \put (85, 50){\footnotesize{$y$}}
-            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
-            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
-        \end{overpic}
-    \end{center}
-    \caption{Direct form II $2^{nd}$ order IIR architecture.}
-    \label{fig_IIRBasicArch}
-\end{figure}
 The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}.
@@
     \begin{center}
-        \begin{overpic}[width=0.95\linewidth, 
+        \begin{overpic}[width=0.5\linewidth, 
         % grid, 
@@
 \end{figure}
-\subsection*{Obtained spatial response}
+\subsection{Obtained spatial response}
 \input{./Modules/Spatial_IIR-MathDerivations.tex}
@@
 \input{./Modules/sec_FIM_and_CRLB.tex}
+\section{Temporal Stability}
+\label{sec_stability}
+\input{./Modules/sec_stability.tex}
 \section{Performance Analysis}
 \label{sec_Performance}
-In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance: Beamwidth, peak-to-sidelobe level, and directivity.
+In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity.
 Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.
-\subsection*{Error terms}
-In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
-Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
-\begin{equation}\label{eq:alpha_beta_hat}
-\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
-\end{equation}
-introducing the estimated steering vector 
-\begin{equation}\label{eq:d_hat}
-\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
-\end{equation}
-Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
-\begin{equation}\label{eq:SF_CB}
-    \resizebox{.894\linewidth}{!}{
-        \begin{split}
-            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
-        \end{split}
-    }
-\end{equation}
-where \[
-\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
-\]
-is the normalized Dirichlet kernel and
-\[
-\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
-r\triangleq g/\hat{g},
-\]
-are defined as the DOA, range and gain error terms respectively.
-In the following, four fundamental scenarios are considered:
-\begin{itemize}
-    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
-    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
-\end{itemize}
-\ifdefined\showTodo
-{
-    \subsection*{Small estimation error analysis - \textbf{TO BE REMOVED - kept only for the todos}}
-    \label{subsection_ArrayPerformance_TayolrAnalysis}
-    \myTodo{inline}{\textbf{DONE:}\\ maybe to call this subsection 'small error analysis'}
-    Plugging (\ref{eqn_CB_coefSet}) into (\ref{eqn:GeneralFeedbackTransferFunction}) and denoting $\D{N}{x} \triangleq \frac{\sin{\rBrace{Nx}}}{\sin{\rBrace{x}}}$ results in the general \coefSetName{} beampattern \myTodo{inline}{\textbf{DONE}\\you need to define the delta expressions (the errors)}
-    \begin{equation*}
-        h_{\coefSetName{}}\rBrace{\theta,\omega}
-        =
-        \frac{
-        \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
-        }{
-        N - \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
-        }.
-    \end{equation*}
-    For the evaluation of the various array parameters, we define the normalized beampattern \myTodo{inline}{\textbf{DONE:}\\not very readable.
-Consider writing a multiplication of two terms.
-Suggesting that you write the expression in eq(5) as $H(\theta,\phi)$ and here you'll have $H(\hat{\theta}, \hat{\phi})/ H(\theta,\phi)$}
-    \begin{equation}
-        \label{eqn_arrPerformance_beamwidth_3dB}
-        \Hr{\theta}{\tau}{}\triangleq\fbBpRatio.
-    \end{equation}
-    \myTodo{inline}{\textbf{DONE:}\\this next section is very long.
-Suggesting that you express (10) in terms of the errors $\Delta\theta,\;\Delta\phi$, and then simply state that the second order Taylor expansion of those errors around zero gives (12).
-One more issue which I think might cause us some headache is that we cannot assure that $\Delta\phi$ (you call it $\Delta\tau$) is indeed close to zero, as this term fluctuates very fast.
-But we will think about it later on.
-Maybe something with wideband signal stimulus will solve this issue.}
-    The pursuit for analytic dependencies between $\Hr{\theta}{\tau}{}$, $\dTheta$ and $\dPhi$, as in \cite{van2004optimum}, lead to expressing $\Hr{\theta}{\tau}{}$'s multivariate Taylor expansion, setting $\dTheta,\dPhi$ as the variables.
-Simulations have shown that $2^{nd}$ Taylor expansion achieves very accurate results, thus we use it to express the array parameters.
-As commonly known, the Taylor expansion of a multivariate analyzable function $f\rBrace{\vx}$ around $\vx_{0}$ where $\vx \in \mathbb{R}_{M\times1},$ is
-    \begin{equation}
-        \label{eqn_h_Tylor_dTheta_dTau}
-        \evalat{f\rBrace{\vx}}{\vx\to\vx_{0}}=\sum_{n=0}^{\infty}\frac{1}{n!}\rBrace{\sum_{i=1}^{M}(x_{i}-x_{0i})\frac {\partial}{\partial x_i} }^n f(x_k)|_{x_k=x_{k0}},
-    \end{equation}
-    where $\frac{\partial}{\partial x_i}$ is the derivative operator and $i\in\left[1\hdots{}M\right]$.
-Reducing (\ref{eqn_h_Tylor_dTheta_dTau}) to its $2^{nd}$ form (i.e $f(x,y)=\sum_{n=0}^{\infty} \frac 1 {n!}\rBrace{x\frac {\partial}{\partial x}+y\frac {\partial}{\partial y} }^n f(x,y)|_{(x,y)=(0,0)}$), combined with the binomial formula, $(x+y)^{n}=\sum _{k=0}^{n}{\binom {n}{k}}x^{n-k}y^{k},$ multiple iterations of L'Hôpital's rule and algebraic simplification finally yields
-    \begin{equation}
-        \begin{split}
-            \evalat{\Hr{\theta}{\tau}{}_{\coefSetName{}}}{\dTheta\to0,\dPhi\to0} \approx\ & 1 
-            \\+&\frac{\binom{2}{0}}{2!}\frac{-\rBrace{N - 1}\rBrace{N-4r+2Nr+1}}{6\rBrace{r-1}^{2}}\dTheta^{2}
-            \\+&\frac{\binom{2}{1}}{2!}\frac{-r\omega\rBrace{N - 1}}{\rBrace{r-1}^{2}}\dTheta\dPhi
-            \\+&\frac{\binom{2}{2}}{2!}\frac{-2r\omega^{2}}{\rBrace{r-1}^{2}}\dPhi^{2}
-        \end{split}
-    \end{equation}
-}
-\else
-\fi
-\subsection*{The normalized beampattern}
+\subsection{The normalized beampattern}
 \label{subsection_spatialIIR_normBP}
-As commonly done for ULA performance analysis \cite{van2004optimum}, we analyze the normalized response (i.e., where the peak main lobe gain is set to $0_{dB}$).
-Henceforth, setting $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ we define the normalized response
+Applying the \emph{normalized beampattern} concept of Sec.~\ref{sec:prlm_array_perf} to this work, we set $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ giving rise to
 \begin{equation}
@@
 \begin{equation}\label{eq_generalH}
-    \resizebox{0.89\linewidth}{!}{
+    %\resizebox{0.89\linewidth}{!}
+    {
         \begin{split}
@@
 we evaluate the FB's beamwidth, sidelobe level and directivity and compare them to those of the standard ULA.
-\vfill
-\subsection*{Half power beamwidth}
-\input{./Modules/arrayPerformance_beamwidth.tex}
-\subsection*{Sidelobes attenuation}
+\subsection{Half power beamwidth}
+\input{./Modules/arrayPerformance_beamwidth_LOCAL.tex}
+\subsection{Sidelobes attenuation}
 \ifdefined\showDev
@@
 Specifically, in perfect gain match scenario (i.e., $r\to{}1$) , the sidelobes vanish. 
-\subsection*{Array directivity}
-The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
+\subsection{Array directivity}
+In the context of this work, the directivity is expressed as
 \begin{equation}\label{eq_D}
@@
 \end{equation}
-measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
-For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
-Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 
+Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with
 \begin{equation}\label{eq_D_result}
@@
     \end{center}
-     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.
-Difference between the numerical integration result and the suggested analytic expression is around $\sim{1e^{-9}}$.}
+     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.}
     \label{fig_directivity}
 \end{figure}
-\subsection*{Summary}
-To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance} 
+\subsection{Summary}
+To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance}.
 \begin{table}[h!]
@@
     \centering
-    \resizebox{1\linewidth}{!}{
+    %\resizebox{1\linewidth}{!}
+    {
         \begin{tabular}{||c c c c||}
@@
 \end{table}
+Also, in Fig.~\ref{fig_perf} we demonstrate the HPBW and sidelobe attenuation for 3 elements ULA.
+As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA for in Fig.~\ref{fig_perf20}. 
+In Table.~\ref{table_arrayPerfEmp} we show the coherency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.
+As predicted, the results of Fig.~\ref{fig_perf20} are consistent with the theoretical expressions.
+\begin{figure}[t]
+    \begin{center}
+        \begin{overpic}[width=0.9\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/fig_performance.png}
+            \put (9, 36.5){$dB$}
+            \put (2, 20){$\abs{H}^{2}$}
+            \put (27, 0){$\theta_{d}/\pi$}
+            \put (34.5, 67){$r=0$}
+            \put (29, 63){\rotatebox{-90}{\tiny{HPBW = $0.1\pi$}}}
+            \put (40, 61){\tiny{$-19.08_{dB}$}}
+            \put (77.5, 67){$r=0.3$}
+            \put (73.14, 63){\rotatebox{-90}{\tiny{HPBW = $0.073\pi$}}}
+            \put (83.5, 58.5){\tiny{$-23.43_{dB}$}}
+            \put (34.5, 31.5){$r=0.6$}
+            \put (29, 27){\rotatebox{-90}{\tiny{HPBW = $0.043\pi$}}}
+            \put (40, 18.75){\tiny{$-31.09_{dB}$}}
+            \put (77.5, 31.5){$r=0.8$}
+            \put (73.14, 27){\rotatebox{-90}{\tiny{HPBW = $0.02\pi$}}}
+            \put (84.25, 13.5){\tiny{$-41.6_{dB}$}}
+        \end{overpic}
+    \end{center}
+     \caption{Simulating 3 elements ULA based feedback beamformer for $r$ values of 0, 0.3, 0.6 and 0.8.
+     The HPBW is marked with vertical red dashed line, where an auxiliary horizontal line of $\abs{H}^{2} = 1/2$ is also provided.
+     The sidelobe attenuation is cited in each plot in a textual fashion.}
+    \label{fig_perf}
+\end{figure}
+\begin{figure}[t]
+    \begin{center}
+        \begin{overpic}[width=0.9\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/fig_performance20.png}
+            \put (9, 36.5){$dB$}
+            \put (-3, 20){$\abs{H}^{2}$}
+            \put (27, 0){$\theta_{d}/\pi$}
+            \put (34.5, 67){$r=0$}
+            \put (29, 63){\rotatebox{-90}{\tiny{HPBW = $0.0605\pi$}}}
+            \put (32.25, 56.5){\tiny{$-26.38_{dB}$}}
+            \put (77.5, 67){$r=0.3$}
+            \put (73, 63){\rotatebox{-90}{\tiny{HPBW = $0.0454\pi$}}}
+            \put (79, 53.75){\tiny{$-32.06_{dB}$}}
+            \put (34.5, 31.25){$r=0.6$}
+            \put (29, 27){\rotatebox{-90}{\tiny{HPBW = $0.0259\pi$}}}
+            \put (40, 14){\tiny{$-41.21_{dB}$}}
+            \put (77.5, 31.25){$r=0.8$}
+            \put (73, 27){\rotatebox{-90}{\tiny{HPBW = $0.0127\pi$}}}
+            \put (84.25, 12.5){\tiny{$-52.55_{dB}$}}
+        \end{overpic}
+    \end{center}
+     \caption{Simulating 20 elements ULA for the sake of HPBW analysis.
+     As in Fig.~\ref{fig_perf}, $r$ values of 0, 0.3, 0.6 and 0.8 are simulated.
+     The HPBW is marked in the same manner also.}
+    \label{fig_perf20}
+\end{figure}
+\begin{table}[h!]
+    \caption{Performances of conventional beamformer $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.
+    Also comparison to expected theoretical expressions is provided.}
+    \centering
+    %\resizebox{1\linewidth}{!}
+    {
+        \begin{tabular}{||c | c c c | c c c||}
+            \hline
+            & \multicolumn{3}{c|}{HPBW [RAD]} & \multicolumn{3}{c||}{SIDELOBE GAIN [dB]} \\ [0.5ex]
+            \hline
+            Expected & \multicolumn{3}{c|}{$\frac{\rBrace{1-r}\rBrace{-0.4r+1.4}}{1.4}$} & \multicolumn{3}{c||}{$20\log{}\rBrace{\abs{\frac{2\rBrace{1-r}}{3\pi}}^{2}}$} \\ [0.5ex]
+            \hline
+            & Result & Expected & Error & Result & Expected & Error \\ [0.5ex] 
+            \hline\hline
+            $r=0$ & 0.0605 & 0.07 & 0.0095 & -26.38 & -26.93 & 0.55 \\ [0.5ex]
+            $r=0.3$ & 0.0454 & 0.0448 & 0.006 & -32.06 & -33.12 & 1.06 \\ [0.5ex]
+            $r=0.6$ & 0.0259 & 0.0232 & 0.0027 & -41.21 & -42.84 & 1.63 \\ [0.5ex]
+            $r=0.8$ & 0.0127 & 0.0108 & 0.0019 & -52.55 & -54.88 & 2.33 \\ [0.5ex]
+            \hline
+         \end{tabular}
+     }
+    \label{table_arrayPerfEmp}
+\end{table}

### 2021-02-12 Modules/sec_conclusions_LOCAL.tex
Sent as draft No.2

--- 2020-12-25 Modules/sec_conclusions.tex
@@
 Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
-\par Future study of the feedback beamforming concept may be applied to other array processing applications other than localization.
-Furthermore, it is worthwhile to inspect other interesting choices of coefficients rather than the conventional-beamformer generalization, other waveforms and associated processing schemes, to extend the results to dynamic/multiple targets and to consider sensors with general radiation patterns.
-Also, one may consider generalizing the suggested architecture to multiple-input-multiple-output systems, enabling a steered/focused (rather than omni-directional) feedback transmission.
+\par In the following, we overview some interesting leads for future study of the feedback beamforming concept.

### 2021-02-12 Modules/sec_future_dynamic.tex
Sent as draft No.2

@@
 The location dynamics may be translated into a dynamic propagation delay, $\tau_{pd}\rBrace{t}$.
-It follows that an auxiliary temporal quantity should be defined, $t_{i}\rBrace{t}$, which links between the received signal's impinging moment $t$, and its corresponding reflecting moment in the target of interest.
-Hence one may describe it as
+It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time. 
+Hence, we denote the moment of transmission $t_{i}\rBrace{t}$ as
 \begin{equation}
-    t_{i}\rBrace{t}=\underset{\tau}{\mathrm{arg}}\cBrace{\tau-t=\frac{R\rBrace{\tau}}{c}}.
+    % t_{i}\rBrace{t}=\underset{\tau}{\mathrm{argmin}}\cBrace{\tau=\frac{R\rBrace{\tau}}{c}}.
+    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ t - \tau = \frac{R\rBrace{t-\tau}}{c}}
 \end{equation}
@@
     \item \textbf{Modeling of target's location}
-    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R_{0}+\rBrace{c+v_{\theta}}t}{c}$$, where $R_{0}$ and further development may lead to a closed form response like in the stationary case.
-    In this manner, other component may be added to the positional equation.
+    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
+    In this manner, other components may be added to the positional equation.
     \item \textbf{Frame based processing}

### 2021-02-12 Modules/sec_future_wavfrom.tex
Sent as draft No.2

@@
     \item Lower power consumption
-    \item Inherent nulling in the radial axis (localization)
     \item Possible match filters should allow the decision of weather to re-transmit or not
@@
     \item The most interesting research option is the use of several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions, by merely selecting harmonic couples and filter coefficients, where each harmonic/coefficient set it pointed to a specific area.
-    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
+    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution by mere choosing multiple frequency couples which are simultaneously processed independently.
+    \par 
+    As a simple example, consider that the arena consists of $M$ zones of interest, where each zone may be described as a angular bounded radial slice (similar to the visualization of Fig.~\ref{fig_rangeAzimuthSelectivity}) which may be described as $$a_{m}=\cBrace{\vecnot{p}\ \middle\vert\  \theta_{d,m,\text{min}}<\text{DOA}\rBrace{\vecnot{p}}<\theta_{d,m,\text{max}}\ ,\ R_{m,\text{min}}<\norm{\vecnot{p}}<R_{m,\text{max}}}\ \forall\ m=0\dots{}M-1.$$
+    \par
+    Each zone will be assigned with matching couple of carrier frequencies ($\omega_{1,2}$) to cover its radial width (where the radial width is equivalent to $R_{\text{rt}}$ of \eqref{eq_DF_phErr}) and coefficient sets ($\vecnot{\alpha}_{m,i},\vecnot{\beta}_{m,i} \ \forall\ m=0\dots{}M-1, i=1,2$), which cover the zone's angular diameter which is equivalent to determining the desired beamwidth via setting the proper $\kappa$ of \eqref{eqn_H_DF_CB}.
+    \par
+    Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned feedback beamformer which simultaneously scans the entire arena.
 \end{itemize}

### 2021-02-12 Modules/sec_prlm_FIM.tex
Sent as draft No.2

@@
-In the parameter estimation problems, we obtain information about the parameter from asample of data coming from the underlying probability distribution. 
-A natural question is:how much information can a sample of data provide about the unknown parameter? 
-This section introduces such a measure for information, and we can also see that this informationmeasure can be used to find bounds on the variance of estimators, and it can be used toapproximate the sampling distribution of an estimator obtained from a large sample, andfurther be used to obtain an approximate confidence interval in case of large sample.
-In this section, we consider a random variable $X$ for which the pdf or pmf is $f\rBrace{x|\theta}$, wehre $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.
-Intuitively, if an event has small probability, then the occurrence of this eventbrings us much information. 
-For a random variable $X \sim f\rBrace{x|\theta}$, if $\theta$ were the true value ofthe parameter, the likelihood function should take a big value, or equivalently, the derivativelog-likelihood function should be close to zero, and this is the basic principle of maximumlikelihood estimation.
-We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function, and
-\begin{equation*}
-    l^{\prime}\rBrace{x|\theta} = \frac{\partial}{\partial\theta}\log{f\rBrace{x|\theta}}=\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}
-\end{equation*}
-where $f^{\prime}\rBrace{x|\theta}$ is the derivative of $f\rBrace{x|\theta}$ with respect to $\theta$.
-Similarly, we denote the second order derivative of $f\rBrace{x|\theta}$ with respect to $\theta$ as $f^{\prime\prime}\rBrace{x|\theta}$.
-According to the above analysis, if $l^{\prime}\rBrace{X|\theta}$ is close to zero, then it is expected, thus the random variable does not provide much information about $\theta$;
-on the other hand, if $\abs{l^{\prime}\rBrace{X|\theta}}$ or $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ is large, the random variable provides much information about $\theta$.
-Thus, we can use $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ to measure the amount of information provided by $X$.
-however, since $X$ is a random variable, we should consider the average case. Thus, we introduce the following definition:
-\begin{definition}
-\emph{Fisher information} (for $\theta$) contained in the random variable $X$ is defined as:
-\begin{equation}
-\label{eq_prlm_FI_def}
-    I\rBrace{\theta}=E_{\theta}\cBrace{\abs{l^{\prime}\rBrace{X|\theta}}^{2}}=\int{}\abs{l^{\prime}\rBrace{X|\theta}}^{2}f\rBrace{x|\theta}dx.
-\end{equation}
-\end{definition}
-We assume that we can exchange the order of differentiation and integration, then
-\begin{equation*}
-    \int{}f^{\prime}\rBrace{x|\theta}dx=\frac{\partial}{\partial\theta}\int{}f\rBrace{x|\theta}dx=0.
-\end{equation*}
-Similarly,
-\begin{equation*}
-    \int{}f^{\prime\prime}\rBrace{x|\theta}dx=\frac{\partial^{2}}{\partial\theta^{2}}\int{}f\rBrace{x|\theta}dx=0.
-\end{equation*}
-It is easy to see that
-\begin{equation*}
-    E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=\int{}l^{\prime}\rBrace{x|\theta}f\rBrace{x|\theta}dx=\int{}\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}f\rBrace{x|\theta}dx=\int{}f^{\prime}\rBrace{x|\theta}=0
-\end{equation*}
-Therefore, the definition of Fisher information \eqref{eq_prlm_FI_def} can be rewritten as
-\begin{equation}
-\label{eq_prlm_IeqVar}
-    I\rBrace{\theta}=\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}
-\end{equation}.
-Also, notice that
-\begin{equation*}
-    l^{\prime\prime}\rBrace{x|\theta}=\frac{\partial}{\partial\theta}\vBrace{\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}}=\frac{f^{\prime\prime}\rBrace{x|\theta}f\rBrace{x|\theta}-\abs{f^{\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}=\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}.
-\end{equation*}
-Therefore,
-\begin{equation*}
-    E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=\int{\vBrace{\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}}f\rBrace{x|\theta}}=\int{f^{\prime\prime}\rBrace{x|\theta}dx}-E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=-I\rBrace{\theta}.
-\end{equation*}
-Finally, we have another formula to calculate Fisher information:
+In the parameter estimation problems, we obtain information about the parameter from a sample of data coming from the underlying probability distribution. 
+A natural question is: how much information can a sample of data provide about the unknown parameter? 
+% This section introduces such a measure for information, and we can also see that this information measure can be used to find bounds on the variance of estimators, and it can be used to approximate the sampling distribution of an estimator obtained from a large sample, and further be used to obtain an approximate confidence interval in case of large sample.
+To this end, the FIM, which is the common tools for assessing the amount of available information in the sampled data is overviewed in the following.
+\par
+Consider a random variable $x$ for which the pdf is $f\rBrace{x|\theta}$, where $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.
+Intuitively, if an event has small probability, then the occurrence of this event brings us much information.
+For a random variable $X \sim f\rBrace{x|\theta}$, if $\theta$ were the true value of the parameter, the likelihood function should take a big value, or equivalently, the derivative log-likelihood function should be close to zero, and this is the basic principle of maximum likelihood estimation.
+We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function which follows that the Fisher information may be expressed \cite{van2004detection} as 
+% We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function, and
+% \begin{equation*}
+%     l^{\prime}\rBrace{x|\theta} = \frac{\partial}{\partial\theta}\log{f\rBrace{x|\theta}}=\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}
+% \end{equation*}
+% where $f^{\prime}\rBrace{x|\theta}$ is the derivative of $f\rBrace{x|\theta}$ with respect to $\theta$.
+% Similarly, we denote the second order derivative of $f\rBrace{x|\theta}$ with respect to $\theta$ as $f^{\prime\prime}\rBrace{x|\theta}$.
+% According to the above analysis, if $l^{\prime}\rBrace{X|\theta}$ is close to zero, then it is expected, thus the random variable does not provide much information about $\theta$;
+% on the other hand, if $\abs{l^{\prime}\rBrace{X|\theta}}$ or $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ is large, the random variable provides much information about $\theta$.
+% Thus, we can use $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ to measure the amount of information provided by $X$.
+% however, since $X$ is a random variable, we should consider the average case. Thus, we introduce the following definition:
+% \begin{definition}
+% \emph{Fisher information} (for $\theta$) contained in the random variable $X$ is defined as:
+% \begin{equation}
+% \label{eq_prlm_FI_def}
+%     I\rBrace{\theta}=E_{\theta}\cBrace{\abs{l^{\prime}\rBrace{X|\theta}}^{2}}=\int{}\abs{l^{\prime}\rBrace{X|\theta}}^{2}f\rBrace{x|\theta}dx.
+% \end{equation}
+% \end{definition}
+% We assume that we can exchange the order of differentiation and integration, then
+% \begin{equation*}
+%     \int{}f^{\prime}\rBrace{x|\theta}dx=\frac{\partial}{\partial\theta}\int{}f\rBrace{x|\theta}dx=0.
+% \end{equation*}
+% Similarly,
+% \begin{equation*}
+%     \int{}f^{\prime\prime}\rBrace{x|\theta}dx=\frac{\partial^{2}}{\partial\theta^{2}}\int{}f\rBrace{x|\theta}dx=0.
+% \end{equation*}
+% It is easy to see that
+% \begin{equation*}
+%     E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=\int{}l^{\prime}\rBrace{x|\theta}f\rBrace{x|\theta}dx=\int{}\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}f\rBrace{x|\theta}dx=\int{}f^{\prime}\rBrace{x|\theta}=0
+% \end{equation*}
+% Therefore, the definition of Fisher information \eqref{eq_prlm_FI_def} can be rewritten as
+% \begin{equation}
+% \label{eq_prlm_IeqVar}
+%     I\rBrace{\theta}=\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}
+% \end{equation}.
+% Also, notice that
+% \begin{equation*}
+%     l^{\prime\prime}\rBrace{x|\theta}=\frac{\partial}{\partial\theta}\vBrace{\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}}=\frac{f^{\prime\prime}\rBrace{x|\theta}f\rBrace{x|\theta}-\abs{f^{\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}=\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}.
+% \end{equation*}
+% Therefore,
+% \begin{equation*}
+%     E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=\int{\vBrace{\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}}f\rBrace{x|\theta}}=\int{f^{\prime\prime}\rBrace{x|\theta}dx}-E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=-I\rBrace{\theta}.
+% \end{equation*}
+% Finally, we have another formula to calculate Fisher information:
 \begin{equation}
@@
 \end{equation}.
-To summarize, we have three methods to calculate Fisher information: equations \eqref{eq_prlm_FI_def}, \eqref{eq_prlm_IeqVar} and \eqref{eq_prlm_Ifin}.
-In any problems, using \eqref{eq_prlm_Ifin} is the most convenient choice.
+% To summarize, we have three methods to calculate Fisher information: equations \eqref{eq_prlm_FI_def}, \eqref{eq_prlm_IeqVar} and \eqref{eq_prlm_Ifin}.
+% In any problems, using \eqref{eq_prlm_Ifin} is the most convenient choice.
 \subsection{Cram\'er-Rao Lower Bound and Asymptotic Distribution of Maximum Likelihood Estimators}
-Suppose that we have a random sample $X_{1},\dots,X_{n}$ coming from a distribution for which the pdf or pmf is $f\rBrace{x|\theta},$ where the value of the parameter $\theta$ is unknown. 
-We will show how to used Fisher information to determine the lower bound for the variance of an estimator of the parameter $\theta$.
-\par
-Let $\hat{\theta}=r\rBrace{X_{1},\dots,X_{n}}=r\rBrace{\vecnot{X}}$ be an arbitrary estimator of $\theta$.
-Assume $E_{\theta}\rBrace{\hat{\theta}}=m\rBrace{\theta}$ and the variance of $\hat{\theta}$ is finite.
-Let us consider the random variable $l^{\prime}\rBrace{\vecnot{X}|\theta}$, it can be shown that $E_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=0$ and that
-\begin{equation}
-\label{eq_prlm_covThetaLTag}
-    \text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}=m^{\prime}\rBrace{\theta}.
-\end{equation}.
-By Cauchy-Schwartz inequality and the definition of $I_{n}\rBrace{\theta},$
-\begin{equation*}
-    \vBrace{\text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}
-\end{equation*}
-i.e.
-\begin{equation*}
-    \vBrace{m^{\prime}\rBrace{\theta}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}=nI\rBrace{\theta}=\text{Var}_{\theta}{\cBrace{\hat{\theta}}}
-\end{equation*}
-Finally, we get the lower bound of variance of an arbitrary estimator $\hat{\theta}$ as
-\begin{equation}
-\label{eq_prlm_CramerRao_lim}
-    \text{Var}_{\theta}{\cBrace{\hat{\theta}}}\geq{}\frac{\vBrace{m^{\prime}\rBrace{\theta}}^{2}}{nI\rBrace{\theta}}
-\end{equation}
-The inequality \eqref{eq_prlm_CramerRao_lim} is called the \emph{information inequality}, and also known as the \emph{Cram\'er-Rao inequality} in honor of the Sweden statistician H.
+% Suppose that we have a random sample $X_{1},\dots,X_{n}$ coming from a distribution for which the pdf or pmf is $f\rBrace{x|\theta},$ where the value of the parameter $\theta$ is unknown. 
+% We will show how to use Fisher information to determine the lower bound for the variance of an estimator of the parameter $\theta$.
+% \par
+% Let $\hat{\theta}=r\rBrace{X_{1},\dots,X_{n}}=r\rBrace{\vecnot{X}}$ be an arbitrary estimator of $\theta$.
+% Assume $E_{\theta}\rBrace{\hat{\theta}}=m\rBrace{\theta}$ and the variance of $\hat{\theta}$ is finite.
+% Let us consider the random variable $l^{\prime}\rBrace{\vecnot{X}|\theta}$, it can be shown that $E_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=0$ and that
+% \begin{equation}
+% \label{eq_prlm_covThetaLTag}
+%     \text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}=m^{\prime}\rBrace{\theta}.
+% \end{equation}.
+% By Cauchy-Schwartz inequality and the definition of $I_{n}\rBrace{\theta},$
+% \begin{equation*}
+%     \vBrace{\text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}
+% \end{equation*}
+% i.e.
+In practical applications, where signal is noised and parameters cannot be accurately estimated, having a closed form expression for the FIM naturally leads to seek for a performance bound that will help the user to know when available information is fully utilized.
+% \begin{equation*}
+%     \vBrace{m^{\prime}\rBrace{\theta}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}=nI\rBrace{\theta}=\text{Var}_{\theta}{\cBrace{\hat{\theta}}}
+% \end{equation*}
+% Finally, we get the lower bound of variance of an arbitrary estimator $\hat{\theta}$ as
+Such a bound for unbiased estimators is \cite{van2004detection}
+% \begin{equation}
+% \label{eq_prlm_CramerRao_lim}
+%     \text{Var}_{\theta}{\cBrace{\hat{\theta}}}\geq{}\frac{\vBrace{m^{\prime}\rBrace{\theta}}^{2}}{nI\rBrace{\theta}}
+% \end{equation}
+% where 
+% The inequality \eqref{eq_prlm_CramerRao_lim} is called the \emph{information inequality}, and also known as the \emph{Cram\'er-Rao inequality} in honor of the Sweden statistician H.
 Cram\'er Indian statistician C.
@@
 Rao who independently developed this inequality during the 1940s.
-The information inequality shows that as $I_{\theta}$ increases, the variance of the estimator decreases, therefore, the quality of the estimator increases, that is why the quantity is called “information”.
-\par
-If $\hat{\theta}$ is an unbiased estimator, then $m\rBrace{\theta}=E_{\theta}\rBrace{\hat{\theta}}=\theta$, $m^{\prime}\rBrace{\theta}=1$.
-Hence, by the information inequality, for unbiased estimator $\hat{\theta}$,
+% The information inequality shows that as $I_{\theta}$ increases, the variance of the estimator decreases, therefore, the quality of the estimator increases, that is why the quantity is called “information”.
+% \par
+% If $\hat{\theta}$ is an unbiased estimator, then $m\rBrace{\theta}=E_{\theta}\rBrace{\hat{\theta}}=\theta$, $m^{\prime}\rBrace{\theta}=1$.
+% Hence, by the information inequality, for unbiased estimator $\hat{\theta}$,
 \begin{equation*}
@@
 \label{eq_prlm_multiVar_CRLB}
-    \test{Cov}_{\vecnot{\theta}}\cBrace{\hat{\vecnot{\theta}}\rBrace{\vecnot{X}}}\geq{}I^{-1}\rBrace{\vecnot{\theta}}
+    \text{Cov}_{\vecnot{\theta}}\cBrace{\hat{\vecnot{\theta}}\rBrace{\vecnot{X}}}\geq{}I^{-1}\rBrace{\vecnot{\theta}}
 \end{equation}
@@
 From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the measuring is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.
+\subsection{Frequency Domain Cram\'er-Rao Bound for Gaussian Processes}
+The interesting work of \cite{zeira1990frequency} (which also specifically states its contribution to localization applications) enables the generalization of the CRLB to the frequency domain, which is of high relevance to this work (see Sec.\ref{sec_FIM}).
+Assuming Gaussian processes, the results of \cite{whittle1953analysis} are utilized together with further development to find that 
+\begin{equation}\label{eq_FIM_kl_full_REAL}
+    %\resizebox{.9\linewidth}{!}
+    {
+        \begin{split}
+            J_{k,l}\rBrace{\vEta} 
+            =&
+            %\Re\cBrace{
+            \frac{1}{2\pi}
+            \int_{-\omega_{s}/2}^{\omega_{s}/2}
+            {
+            \frac{1}{\Phi\rBrace{\omega}}
+            \mathfrak{F}^{*}\left\{
+            \frac{\partial z(t)}{\partial\eta_{k}}
+            \right\}
+            \mathfrak{F}\left\{
+            \frac{\partial z(t)}{\partial\eta_{l}}
+            \right\}
+            d\omega
+            }%}
+            \\ &+
+            \frac{T}{4\pi}
+            \int_{-\omega_{s}/2}^{\omega_{s}/2}
+            \frac{1}{\Phi^{2}\rBrace{\omega}}
+            \rBrace{\frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{k}}}^{\ast}
+            \frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{l}}
+            d\omega
+        \end{split}
+    }
+\end{equation}
+which is conveniently generalized to the complex data case used in this work as \eqref{eq_FIM_kl_full}.

### 2021-02-12 Modules/sec_prlm_FIR_IIR.tex
Sent as draft No.2

@@
 A basic design entity in every signal processing scheme is the digital filter, which is the modern evolution of analog filters.
-The design of the digital filter is a very established and thoroughly studied research area.
+The design of the digital filter is very well established and thoroughly studied research field.
 As stated in \cite{oppenheim1975digital} (and numerous other literature), two key filter types are used - i.e. Finite Impulse Response (FIR) and Infinite Impulse Response (IIR) filters.
-This section will briefly overview the design methods and main flavours of each filter type and discuss in general of the pros and cons of them in order to provide proper motivation for the quest of finding the IIR analogy of the spatial FIR, as implied in Ch.~\ref{chap:intro}.
-\subsection{FIR design}
-The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equal to the number of taps in the final filter's configuration.
-Determining it coefficients is generally done using windowing (weighted element-wise multiplication and truncation) of desired impulse response which is derived by the inverse Fourier transform of the desired frequency response.
-Many window types have been suggested in literature, where Bartlet, Hanning, Humming and Blackman are among the most basic ones, each with its pros and cons.
-I a nutshell, using a rectangular window, achieves the narrowest main lobe but also the highest side-lobes.
-The other window types, achieve lower side-lobes at the expense of wider main-lobe.
-The user may also increase the filter's order if side-lobe attenuation is of high importance, thus achieving narrower main-lobe. 
-\subsection{IIR design}
-The infinite response of the IIR filters originates in the inherent feedback which reuses output in the computing part, generating a loop which theoretically takes all input past samples into account for each output sample.
-As there are many flavours of the IIR filters, we choose to elaborate on the elliptic filter, being the more common candidate for comparison to the FIR in the literature.
-The basic concept behind the elliptic filter design is the allowing of equi-ripple around both pass and stop band which both relaxes the filter's constrains comparing to Chebyshev and Butterworth methods and allows the narowest transition band between the three filters.
-The designer sets the allowed ripple magnitudes in both pass and stop bands and positions the transition band according to his needs.
-A closed for transformation, described in \cite{oppenheim1975digital} is then used to convert the prototype low-pass filter to band-pass, band-stop or high-pass filters.
-\subsection{Comparison}
-The main advantage of FIR filters, commonly required in signal processing systems is the obtainable linear phase feature.
+This section will briefly overview the design methods and the analogy of ULA based beamforming to the temporal FIR filtering, as implied in Ch.~\ref{chap:intro}.
+\par Each digital filters belong in one of two architectures
+\begin{itemize}
+    \item \textbf{FIR design}\\
+    The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equal to the number of taps in the final filter's configuration as in Fig.~\ref{fig_FIR_arch}.
+    \item \textbf{IIR design}\\
+    IIR filters may be viewed as a generalization of the FIR delay-and-sum architecture, where delayed instances of the array's output are fed back to the summation as in Fig.~\ref{fig_IIR_arch}, theoretically generating an infinite loop where each output sample is affected by all past input samples.
+\end{itemize}
+\begin{figure}[h!]
+    \begin{center}
+        \begin{overpic}[width=0.7\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/BASIC_FIR_FILTER_ARCH.png}
+            \put (13, 36){\footnotesize{$s$}}
+            \put (22, 22){\footnotesize{$\beta_{0}$}}
+            \put (38.75, 22){\footnotesize{$\beta_{1}$}}
+            \put (55.5, 22){\footnotesize{$\beta_{2}$}}
+            \put (80.75, 22){\footnotesize{$\beta_{N-1}$}}
+            \put (85, 10){\footnotesize{$z$}}
+        \end{overpic}
+    \end{center}
+    \caption{An FIR based filtering of signal $s$ with the $\vecnot{\beta}$ as the coefficients, generating a filtered signal $z$.}
+    \label{fig_FIR_arch}
+\end{figure}
+\begin{figure}[h!]
+    \begin{center}
+        \begin{overpic}[width=0.7\linewidth, 
+        % grid, 
+        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
+            \put (60, 50){\footnotesize{$\beta_{0}$}}
+            \put (60, 30){\footnotesize{$\beta_{1}$}}
+            \put (60, 10){\footnotesize{$\beta_{2}$}}
+            \put (36, 30){\footnotesize{$\alpha_{1}$}}
+            \put (36, 10){\footnotesize{$\alpha_{2}$}}
+            \put (10, 50){\footnotesize{$s$}}
+            \put (85, 50){\footnotesize{$z$}}
+            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
+            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
+        \end{overpic}
+    \end{center}
+    \caption{Direct form II $2^{nd}$ order IIR architecture, where the FIR part is the $\vecnot{\beta}$ coefficients and the recursive part is implemented via the $\vecnot{\alpha}$ set.}
+    \label{fig_IIR_arch}
+\end{figure}
+\par In the following, we revisit the basic interpretation of the ULA as the spatial equivalent to the temporal FIR filter \cite{van1988beamforming} where DOA is shown to be the matching spatial entity to the temporal frequency, hence the \emph{conventional beamformer} \cite{van2004optimum} is merely the spatial version of temporal domain FIR filtering.
+To this end, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented next.
+\par Consider an $N$-element ULA with inter-element spacing $d$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$.
+We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
+Focusing on a far field localization problem, DOA and target range are to be estimated.
+Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
+For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
+Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
+\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
+\begin{equation}
+x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
+\label{eqn:noFeedbackULA_singleSensor_temporal}
+\end{equation}
+where $\tau_{n}=nd\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
+Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write
+\[
+\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}\rBrace{\theta}}}
+\]
+where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
+\begin{equation}
+    \label{eq:d}
+    d_{n}\rBrace{\omega,\theta_{d}} = \exp{\rBrace{-j\omega\tau_{n}\rBrace{\theta}}}.
+\end{equation}
+Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in the frequency domain
+\begin{equation}
+    \label{eq_Z}
+    Z\rBrace{\omega,\theta_{d}} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
+\end{equation}
+Defining the electric phase to be
+\begin{equation}\label{eq:thetaULA}
+\theta=\omega{d\cos\Brack{\thetaD}}/{c},
+\end{equation}
+we rewrite \eqref{eq_Z} as 
+\[
+Z\rBrace{\omega,\theta} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
+\]
+hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018}.
+Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
+\par It is well known \cite{rabiner1974some} that IIR filters have several appealing advantages over their matching (in number of elements) FIR versions.
 A well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant, namely linearly dependent in the phase response derivative of the specific frequency.
-Therefore, linear phase implies that the phase response's derivative (i.e. signal latency) is frequency independents, which prevent signal distortion.
-The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
-In this work, the signals are assumed to be narrow-band, which reduces the necessity of linear phase response, while when considering sensor arrays, the costs and the physical aperture are of very high importance, motivating the designers to try and reduce the number of elements in the array while still meeting the specifications.
+Therefore, linear phase implies that the phase response's derivative (i.e.
+signal latency) is constant which implies all input frequencies will reside in the processor for the exact same time, preventing dispersion which practically causes pulse widening.
+Due to this important property, many applications which are sensitive to signal distortions, especially communication based systems, chose the FIR architecture.
+Acquainted with the analogy between frequency and DOA, it seems that when localization applications are considered, where the DOA resolution criteria is more important than the consistency of detection latency between separate DOAs, the linear phase property is less relevant.
+\par The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
+Concluding that spatial linear phase response in DOA domain is not a necessity, combined with the known efficiency of the IIR architecture and the need for smaller and cheaper arrays, the motivation for finding the spatial version of the temporal IIR is complete.
+\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest.
+Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.).
+As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
+Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals.

### 2021-02-12 Modules/sec_prlm_array_perf.tex
Sent as draft No.2

As mentioned in Chapter.~\ref{chap:intro}, array processing serves in many different application, each with its unique requirements, setup and constraints - hence performance criteria are application dependent.
In this work, we focus on localization related applications and suggest a new architecture.
Hence, to analyse the presented scheme, we use classic localization-related performance measurements as the comparison is to known localization related array processing schemes.
\par
To this end, we follow the classic \cite{van2004optimum} performance analysis, elaborated in the following.
Those criteria are then used to quantify the presented architecture's performance in Chapter.\ref{chap:firstchap}.
\subsection{Beampattern}
Considering DOA estimators, the main tool for assessing an array's localization performance is expressing it's response to impinging signals with respect to the signal's DOA.
\begin{figure}
  \centering
  \begin{subfigure}[b]{0.49\linewidth}
    % \includegraphics[width=\linewidth]{./Media/fig_commonBp_1.png}
    \begin{overpic}[width=\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_commonBp_1.png}
            \put (19, 58){\tiny{$N\!=\!3$}}
            \put (19, 47){\tiny{$N\!=\!6$}}
            \put (19, 34){\tiny{$N\!=\!12$}}
    \end{overpic}
    \caption{}
    \label{fig_common_bps1}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.4\linewidth}
    \begin{overpic}[width=\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_commonBp_2.png}
            \put (81, 63.5){\tiny{$N\!=\!3$}}
            \put (76, 57){\tiny{$N\!=\!6$}}
            \put (76, 53){\tiny{$N\!=\!12$}}
    \end{overpic}
    \caption{}
    \label{fig_common_bps2}
  \end{subfigure}
  \caption{Two common ways of visualizing the array's response in the 2D planar case.
  In both plots, a comparison between the conventional beamformer's responses of 3,6 and 12 elements arrays is emulated. 
  In Fig.~\ref{fig_common_bps1}, the response is presented on the interval of 0 to $\pi$ with units of dB.
  In Fig.~\ref{fig_common_bps2}, a polar plot is presented with same units for the response gain but the DOA is in degrees.}
  \label{fig_common_bps}
\end{figure}
Although may be dependant in various parameters, for the sake of simplicity, we consider a planar (i.e. azimuth without elevation) DOA-only dependant array response (i.e. the \emph{beampattern})
\begin{equation}
B\rBrace{\theta} = 20\log_{10}\abs{Z\rBrace{\theta}}.
\end{equation}
The beampttern is commonly presented in a graphical manner as exemplified in Fig.~\ref{fig_common_bps}.
It's characteristics, such as lobes width, attenuation and positioning are then analysed and compared between different schemes.
The analysis can theoretical, when the beampattern's mathematical expression is known or graphical analysis for empirical scenarios.
In this work, as we deal with 2D planar localization problems, we find the presentation of Fig.~\ref{fig_common_bps1} most suitable.
The horizontal axis, being the DOAs of the impinging signal, may be presented in various ways where units may be degrees radians etc.
Also, as the DOA is periodical one should also choose the centering, for example when the beampattern is steered towards different angles and the author wants to center the mainlobe.
In this work, we follow choose to use \cite{van2004optimum}'s $\psi$-space, i.e.
\begin{equation}
    \psi\rBrace{\theta_{d}}=\frac{2\pi}{\lambda}\cos{\theta_{d}}\cdot{}d,
\end{equation}
where $\lambda$ is the impinging signal's wavelength.
The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA}. 
Also, we choose to plot beampatterns using $\Delta\psi = \psi\rBrace{\theta_{d}} - \psi\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, for it centers the mainlobe, enabling convenient comparison.
\subsection{The normalized beampattern}
As the absolute output gain is system dependent, comparing two different is not possible where their maximal gain of the mainlobe are different.
Therefore, a common practice \cite{van2004optimum} when analysing the array's spatial performance, is to normalize the beampattern such that the mainlobe's output gain at it's peak is 1 (0dB), thus enabling convenient comparable measures extraction.
This quantity will be referred as $\mathcal{H}$.
\subsection{Half power beamwidth}
Considering localization problems, possibly the main interest is spatial resolution, related to localization accuracy and distinction of spatially close objects, where ``close`` can be interpreted as small physical distance between objects of interest or objects that may be physically distant from each other but from the array's perspective are in relatively similar.
\par
Relating to the beampttern, the spatial resolution is obviously linked to the main lobe's width, i.e. higher resolution is acheived as the main lobe thins. 
Hence to unify the analysis, the Half Power BeamWidth (HPBW) is defined to be the 3-dB beamwidth, i.e. the point where $\abs{B\rBrace{\psi}}^{2} = 0.5$ or $\abs{B\rBrace{\psi}} = 1/\sqrt{2}$.
For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
\begin{equation}
    \label{eq_known_HBPW}
    \dThetaHPBW/2= 1.4/N.
\end{equation}
\par
Obviously, we aim to show that the presented architecture increases the resolution, comparing to other arrays by proving that the beamwidth shrinks.
%
%
%
\subsection{Sidelobes attenuation}
As the beampattern consists of multiple harmonics (as the number of elements $N$), sidelobes occur when the some harmonics are summed, showing as peaks other than the mainlobe.
As this is an unwanted result, the height and their rate of decrease are measured aiming to prefer arrays where their height is reduced and the decrease rate is increased.
%
%
%
\subsection{Directivity}
The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
\begin{equation}\label{eq_D}
    \mathcal{D}\rBrace{N,r} = \frac{\Hr_{\Delta\theta=0,\Delta\phi=0,r}}{\frac{1}{2\pi}\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta} = \frac{2\pi}{\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta},
\end{equation}
measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.

### 2021-02-12 Modules/sec_prlm_localization.tex
Sent as draft No.2

@@
 In this work, we focus on localization of signal sources in the far-field case, where free space signal propagation is assumed.
-Following the classical methods overview in \cite{krim1996two},most localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
-The basic difference between the two groups is the assumption of impinging signal's statistical model when using parametric approach, which leads to higher accuracy in the expense of computation effort.
-In both approaches, the estimations are based on calculation of several hypothesis and choosing the peaks in the generated graph.
-Considering the search for a single parameter (e.g.
-DOA in a 2D plane), the two approaches are pretty similar in the sense that in both, the processor computes the confidence in a predetermined set of hypothesis which is followed by a single dimension scan.
-The difference is more evident when considering multiple parameter, such as spherical direction (i.e. azimuth and elevation) or even actual location adding also the distance to the target of interest.
-In the spectral based, each parameter is estimated independently of the other parameters, resulting in several 1D scans (as the number of estimated parameters), where the parametric approach will result in a multi-dimensional search for the best fitted parameters set.
-In the following, a basic overview of some classical algorithms is presented.
-The earliest localization algorithms, which date back to world war II, are the beamforming based, e.g. the conventional Bartlet beamformer.
-These methods, although appealing in terms of complexity and computation effort, suffer from fundamental limitation, e.g.
-its spatial performance depend solely on the array aperture and no improvement is achieved when more data is collected.
-Another class of estimators, where a statistical model is assumed (which is also the drawback of those methods), is the parametric estimators such as Maximum-Likelihood \cite{TWODECADES-81/106} and Maximum-Entropy \cite{TWODECADES-23}.
+Following the classical methods overview in \cite{krim1996two},localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
+The spectral based estimators steer the array (mechanically or by beamforming) to a set of DOAs, searching for peaks in the received energy, where each peak is treated as a resolved emitter when greater than a certain threshold.
+This approach of spatial filtering, is considered to suffers from fundamental
+limitations, namely ``its performance, is directly dependent upon the physical size of the array (the aperture), regardless of the available data collection time and signal-to-noise ratio (SNR)`` \cite{krim1996two}.
+Although trials were made to increase the resolution of an array given a certain aperture, this notion remains intact to these days.
+In this contribution we tackle this statement as will shown in Chapter\ref{chap:firstchap}.
+The later approach, of parameter estimation assumes a physical model of the experimental scenario, which serve a basis for the development of spatio-temporal estimators which takes advantage not only from the spatial diversity but also from the temporal information collected via sequential time separated snapshots in order to increase the overall SNR.
+Such methods, not only enabled the increase of spatial filtering resolution, but also allowed the implementation of data processing algorithms, more sophisticated than a mere search with a steered array.
+In the following, a basic overview of some classical algorithms are presented.
+The earliest localization algorithms, which date back to world war II, are the beamforming based, e.g. the conventional Bartlet \cite{van2004optimum} and Capon's \cite{capon1969high} beamformers.
+Early examples of parametric estimators, are the Maximum-Likelihood \cite{macdonald1969optimum,schweppe1968sensor} and Maximum-Entropy \cite{ables1974maximum} which assume a known PDF to the received signal and estimate the desired parameters according to empirical results and fitting the closest matching PDF.
 Until the mid- 1970's, direction finding techniques required knowledge of the array directional sensitivity pattern in analytical form, and the task of the antenna designer was to build an array of antennas with a prespecified sensitivity pattern.
-Trying to relax the need for such accuracy, also serving as the origin of the sub-space based approach, was the Multiple SIgnal Classification (MUSIC) \cite{MUSIC_} algorithm.
-In general, the MUSIC algorithm consists of several stages:
-\begin{itemize}
-    \item Estimation of the covariance matrix
-    \item Eigen decomposition - extracting the eigen values and its related eigen-vectors
-    \item Estimating the number of sources
-    \item Projecting the samples over the array manifold
-    \item Finding the largest peaks according to the estimated number of sources
-\end{itemize}
+Trying to relax the need for such accuracy, also serving as the origin of the sub-space based approach, was the Multiple SIgnal Classification (MUSIC) \cite{schmidt1986multiple} algorithm.
 MUSIC essentially relieved the designer from the need of accurate radiation patterns by exploiting the reduction in analytical complexity that could be achieved by calibrating the array.
@@
 Although MUSIC did not mitigate the computational complexity of solution to the DOA estimation problem, it did extend the applicability of high-resolution DOA estimation to arbitrary arrays of sensors.
-Another, probably even more important breakthrough, was the introduction of the array manifold and noise space (hence its name - sub-space) which proved to be orthogonal, thus allowing the use of orthogonal projection.
-In the very thorough review of classical algorithms \cite{TWODECADES}, two approaches - i.e. the parametric approach and ULA-specific algorithms are also discussed.
-the parametric approach, where stochastic model is assumed and Maximum Likelihood (ML) and Stochastic Maximum Likelihood (SML) are employed, is less relevant to this work therefore not discussed.
-In the set of ULA-specific algorithms, including ROOT-MUSIC \cite{ROOT_MUSIC}, ESPRIT (Estimation of Signal Parameters via Rotational Invariance Techniques) \cite{ESPRIT} and some iterative methods.
-We choose to emphasize on the ESPRIT method, being an important milestone in the path to state-of-the-art algorithms.
-In addition to using the rotational invariance of the signal sub-space eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - mitigating numerical problems associated with ill-conditioned matrices.
+Another, probably even more important breakthrough, was the introduction of the orthogonal array manifold noise spaces, thus allowing the use of orthogonal projection in order to mitigate the noise effects.
+Another important parametric approach related algorithm, is the ESPRIT (Estimation of Signal Parameters via Rotational Invariance Techniques) \cite{ESPRIT}, serving as a milestone in the path to state-of-the-art algorithms.
+In addition to using the rotational invariance of the signal sub-space eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - thus mitigating numerical problems associated with ill-conditioned matrices.
 Following state-of-the-art developments \cite{BOOK-classicalAndModernDOA}, the sub-space based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm MUSIC} but also new and interesting approaches emerged
 \begin{itemize}
-    \item High Order Statistics (HOS, also refereed as comulants), which extracts more information from the samples' higher order moments, is a very active field of research due to some fundamental issues which are inherently resolved - i.e.
-the Gaussian noise vanishes in the 4th order statistics and the ability to resolve more DOAs than array elements.
+    \item High Order Statistics (HOS, also refereed as cumulants), which extracts more information from the samples' higher order moments, is a very active field of research due to some fundamental issues which are inherently resolved - i.e.
+the Gaussian noise vanishes in the 4th order statistics and the ability to resolve more DOAs than array elements \cite{chevalier2006high}.
     This approach, being costly in computation effort, became popular probably due to the recently available low-cost powerful computation.
-    \item Sparsity based estimation, using non-Frobenius norm used in the algorithms development, has proved to improve estimation resolution in some cases \cite{LocalizationOfMultipleSpeaker}, namely high reverbrant acoustic scenarios, but is less relevant to this work therefore not elaborated.
+    \item Inspired by the vast research field of sparse representations some algorithms \cite{nadiri2014localization} use non-Frobenius norm (i.e.
+$L^{p}$ norms where $p<2$), in order improve estimation resolution under high reverberation acoustic scenarios.
     \item A very wide and active research field is the concept of cooperative localization related to mobile networks is growing at a very high rate due to the never-ending need for high-bandwidth and low-power communication of the mobile networks.
-    It is also less relevant to this work.
-    \item Naturally, also many trials of harnessing the promising concept of neural networks are being done, for example \cite{NNDOA}
+    \item Naturally, also many trials of harnessing the promising concept of neural networks are being done, for example \cite{shareef2008localization}.
 \end{itemize}
-In this work, we actually revisit the most basic approach - i.e. beamforming.
+In this work, we actually revisit the most basic approach - i.e. beamforming which resides under the spectral based algorithms.

### 2021-02-12 Modules/sec_prlm_propWaveField.tex
Sent as draft No.2

@@
 \end{equation}
-Where $A$ is a complex constant, $\omega$ denotes a constant temporal frequency and $k_{x}x,k_{y},k_{z}$ are real constants. 
+Where $A$ is a complex constant, $\omega$ denotes temporal radial frequency and $k_{x}x,k_{y},k_{z}$ are real constants. 
 Plugging \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} results in the \emph{monochromatic plane wave}:
@@
 Therefore, the wavenumber vector can be considered to represent spatial frequency, similarly to the manner $\omega$ represents temporal frequency.
+\par For example, in the context of ULA, assuming far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.
+The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which is will be shown to provide clues for the signal's DOA as can be seen in Fig.~\ref{fig_ULA_sketch}.
+\begin{figure}[h!]
+    \begin{center}
+        \begin{overpic}[width=0.6\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/arraySketch.png}
+        \put(20,45){\rotatebox{-50}{\tiny{Impinging wavefront}}}
+        \put(33.25,2.25){\rotatebox{0}{\tiny{$d$}}}
+        \put(52.25,26){\rotatebox{38}{\tiny{$c\tau=d\cos{\theta}$}}}
+        \put(49,15.75){\rotatebox{0}{$\theta$}}
+        \put(15,7){\rotatebox{0}{\tiny{0}}}
+        \put(28,7){\rotatebox{0}{\tiny{1}}}
+        \put(41,7){\rotatebox{0}{\tiny{2}}}
+        \put(80,7){\rotatebox{0}{\tiny{$N-1$}}}
+        \put(44,36){\rotatebox{38}{\tiny{$t=\rBrace{N-1}\tau$}}}
+        \put(57,36){\rotatebox{38}{\tiny{$t=\rBrace{N-2}\tau$}}}
+        \put(70,36){\rotatebox{38}{\tiny{$t=\rBrace{N-3}\tau$}}}
+        \put(92,25){\rotatebox{38}{\tiny{$t=0$}}}
+        \end{overpic}
+    \end{center}
+     \caption{An illustration of an $N$ element ULA, impinged with a plane wave arriving from a DOA of $\theta$.}
+    \label{fig_ULA_sketch}
+\end{figure}
+When also considering the narrowband scenario, where TOA difference is merely phase shift, it seems obvious that by phase measuring, one should be able to extract the DOA from the spatially sampled data.

### 2021-02-12 Modules/sec_prlm_sensorArrays.tex
Sent as draft No.2

--- 2020-11-06 Modules/sec_prlm_sensorArrays.tex
@@
-Microphone arrays consist of sets of microphones positioned in a way to function as a directional acoustic antenna. 
-Microphone arrays are utilized for filtering signals in a space-time field. 
-Filtering is enabled by exploitation of the incoming signals spatial characteristics. 
-A desirable spatial filtering, i.e., beamforming, should result in enhancement of signals of interest, originated in a specific direction, while forcing suppression of undesired signals originated in other directions.
-Microphone arrays are utilized for solving many signal processing problems: dereverberation, localization of a single source, noise reduction and source separation \cite{cohen2004multichannel,habets2006dual,pavlidi2013real}.
+Sensor arrays are sets of independently positioned sensors, where each sensor is sampling temporal snapshots of impinging signals.
+The samples from the entire array are then fused together in order to extract the underlying data.
+The spatial diversity of the sampled data allows the extraction of spatial features which are not accessible by mere temporal analysis of the data.
+Sensor arrays are used in numerous applications, ranging from source localization, through communication, medical applications, astronomy etc.
 \par 
-Numerous factors must be taken into consideration when designing a microphone array configuration.
-Initially, the geometry of the microphone array plays an important role in the formulation of the processing algorithms, as it forces fundamental constraints on the array’s operation. 
-In most cases, the array geometry is the first consideration in array design due to practical and physical constraints of the design. 
-Therefore, the degree of freedom in choosing the array geometry is limited. 
-Nevertheless, in some other crucial problems such as noise reduction or source separation, the geometry of the array may have little importance. 
-For instance, Uniform Linear Arrays (ULA) can only handle one source direction at a time resulting in uncertainties and possibly direction ambiguities.
-Therefore, ULA configurations must be ruled out when handling several signal sources.
-Other array geometries such as non-uniform linear arrays and circular arrays, have been studied in the field \cite{liu2008design,van2004optimum}.
-This work is based on ULA and therefore we elaborate on this geometry.
-A conventional beamformer \cite{van2004optimum} is composed of a ULA of microphones. 
-That is, the microphones are positioned on an axis with a uniform spacing between the microphones.
-The general expression of the microphone positioning in a ULA is given by:
+When designing a sensor array, multiple consideration are to be taken into account, ranging from physical characteristics e.g.
+area, weight and carrying platform, through performance related considerations such as accuracy, spatial selectivity, signal to noise ratio and even the financial aspect.
+Obviously, the most fundamental array specification is its geometry, for it dictates the spatial relations between simultaneous samples measured by the array's sensors, which also greatly influences the processing methods of the raw-data.
+A basic example of sensor array is the ULA (see Fig.~\ref{fig_ULA}), where its elements are uniformly spaced on a straight line with distance $d$ between a sensor to its nearest neighbour.
+Considering an array of $N$ elements, the sensors are positioned at
 \begin{equation}
-x_{m}=m\cdot{d}, m=0, 1, \dots, M-1
+p_{n}=nd,\ n=0,\dots,N-1
 \end{equation}
-where $m$ denotes the microphone index; $x_{m}$ denotes the position of the microphone having index $m$, where $x_{m} = 0$ corresponds to the left-hand side of the array, i.e., the location where the microphone indexed by $m = 0$ is positioned; $d$ denotes the spacing between microphones, and $M$ is the array size, i.e., the number of microphones in the array, as demonstrated in Fig.~\ref{fig_ULA}.
+where $n$ is the sensors index; $p_{n}$ denotes the position of the $n$'th sensor,$p_{0} = 0$ corresponds to the left-hand side of the array.
 \begin{figure}[h!]
@@
         %grid, 
-        tics=10,trim=0 0 0 0]{./Media/fig_ULA.png}
-            % \put (50, 62.5) {\footnotesize{$r=0$}}
+        tics=10,trim=0 0 0 0]{./Media/arrayBasic.png}
+        \put (4, 4.5) {\tiny{$N$}}
+        \put (86, 4.5) {\tiny{$N-1$}}
+        \put (83.25, 28.5) {\tiny{$\rBrace{N-1}\cdot{}d$}}
         \end{overpic}
     \end{center}
-     \caption{A uniform linear array of size M and spacing d.}
+     \caption{A uniform linear array of size $N$ and spacing $d$.}
     \label{fig_ULA}
 \end{figure}
+\par To proper formulate the discussed additional spatial information when using sensor array based processors, a quick overview on wave propagation is due and presented in the following section (Sec.~\ref{sec:prlm_propWaveField}).

### 2021-02-12 Modules/sec_prlm_timeSpaceSig.tex
Sent as draft No.2

@@
-% The incoming signals are spatially sampled by the array microphones, then the samples are processed to attenuate signals from undesired directions and extract the signal from a desired direction. 
-% A spatial response of the microphone array is obtained via a beam (main-lobe) directed to the desired signal while nulls are directed to the undesired signals.
-As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken in the same time $t$.
-A basic sensor array based entity is the beamformer, which is designed to enhance signals from certain directions while suppressing other signals from unwanted directions, heuristically forming a beam directed to the enhanced direction.
+As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken the same time $t$.
+A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.
 \begin{figure}[ht!]
     \begin{center}
-        \begin{overpic}[width=0.5\linewidth, 
+        \begin{overpic}[width=0.6\linewidth, 
         %grid, 
-        tics=10,trim=0 0 0 0]{./Media/fig_ULA_imping.png}
-            % \put (50, 62.5) {\footnotesize{$r=0$}}
+        tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
+        \put(20,65){\rotatebox{-50}{\tiny{Impinging wavefront}}}
+        \put(49,33.25){\rotatebox{0}{$\theta$}}
+        \put(15,25){\rotatebox{0}{\tiny{0}}}
+        \put(28,25){\rotatebox{0}{\tiny{1}}}
+        \put(41,25){\rotatebox{0}{\tiny{2}}}
+        \put(80,25){\rotatebox{0}{\tiny{$N-1$}}}
+        \put(16,20){\rotatebox{0}{\tiny{$\omega_{0}$}}}
+        \put(29.5,20){\rotatebox{0}{\tiny{$\omega_{1}$}}}
+        \put(42,20){\rotatebox{0}{\tiny{$\omega_{2}$}}}
+        \put(81,20){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
+        \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
         \end{overpic}
     \end{center}
-     \caption{A simple beamformer design.}
+     \caption{ULA based coherent processing of simultaneous spatially sampled signal, measuring a wavefront impinging from DOA $\theta$}
     \label{fig_ULA_imping}
 \end{figure}
-Fig.~\ref{fig_ULA_imping} illustrates a beamformer design based on a ULA of Fig.~\ref{fig_ULA}.
-% Let $\vecnot{f}\rBrace{t,\vecnot{x}}$ denote the set of signals sampled by the microphone array at time $t$, expressed by
-A temporal snapshot measured by the array at time $t$ is
+In complimentary to Fig.~\ref{fig_ULA_sketch}, Fig.~\ref{fig_ULA_imping} adds the processor layer of the beamformer.
+\par A temporal snapshot measured by the array at time $t$ is
 \begin{equation}
-\vecnot{f}\rBrace{t,\vecnot{x}} = \vBrace{f\rBrace{t,x_{0}},\dots,f\rBrace{t,x_{M-1}}}^{T},
+\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T},
 \end{equation}
-where $x_{m}$ denotes the microphone position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
-Assuming simple, weight-and-sum beamformer, the output ($y\rBrace{t}$) is expressed by:
+where $p_{n}$ denotes the $n$-th sensor position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
+Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($y\rBrace{t}$) is expressed by:
 \begin{equation}
-y\rBrace{t} = \sum_{m=0}^{M-1}{f\rBrace{t,x_{m}}w_{m}^{*}},
+z\rBrace{t} = \sum_{n=0}^{N-1}{f\rBrace{t,p_{n}}\omega_{n}^{*}},
 \end{equation}
-where $w_{m}$ is a complex weight used for the $m$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
+where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
 Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at angular frequency $w$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
@@
 \label{eq_prlm_timeSpace_outputVec}
-\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t-\tau_{0}}, \dots, s\rBrace{t-\tau_{M-1}}}^{T}, \tau_{m} = \frac{\sin{\theta}\cdot{}x_{m}}{c},
+\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
 \end{equation}
-where $\tau_{m}$ is the propagation delay for the incoming signal and $c$ is the wave's velocity in the medium.
-% A value of $\tau_{m}=0, \forall{m}$ implies a DOA of $\theta = 0$, i.e. a plane wave parallel to the array, propagating perpendicularly to the array.
-Let $\kappa=\frac{\omega}{c}\sin{\theta}=\frac{2\pi}{\lambda}\sin{\theta}$ denote the wavenumber for plane waves in a locally homogeneous medium, where $\lambda$ denotes the wavelength corresponding to the angular frequency $\vecnot{d}\rBrace{\kappa}$ denote the \emph{steering vector}, featuring all of the array's spatial characteristics.
-Based on \eqref{eq_prlm_timeSpace_outputVec}, and the definition of $\kappa$ above, the steering vector can be expressed as
+where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
+Considering narrowband signals (i.e. $s\rBrace{t}=\exp^{-j\omega{}t}$), the time delay $\tau$ translates to a mere phase shift and an auxiliary dephased \emph{steering vector} takes the form of
 \begin{equation}
-\vecnot{d}\rBrace{\kappa}=\vBrace{e^{-j\kappa{}x_{0}},\dots,e^{-j\kappa{}x_{M-1}}}^{T}.
+\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\rBrace{N-1}\omega\tau}}^{T}.
 \end{equation}
+As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal sub space in the noiseless scenario.

### 2021-02-12 Modules/sec_stability.tex
Sent as draft No.2

As a preliminary to the following performance discussion in Sec.~\ref{sec_Performance}, we start with simple temporal simulations of the feedback beamformer.
In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms which are then used to define some basic simulation scenarios that will be thoroughly investigated throughout this chapter.  
After the error terms have been defined, we first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.
\subsection{Error terms}
In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
\begin{equation}\label{eq:alpha_beta_hat}
\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
\end{equation}
introducing the estimated steering vector 
\begin{equation}\label{eq:d_hat}
\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
\end{equation}
Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
\begin{equation}\label{eq:SF_CB}
    %\resizebox{.894\linewidth}{!}
    {
        \begin{split}
            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
        \end{split}
    }
\end{equation}
where \[
\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
\]
is the normalized Dirichlet kernel and
\[
\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
r\triangleq g/\hat{g},
\]
are defined as the DOA, range and gain error terms respectively.
In the following, four fundamental scenarios are considered:
\begin{itemize}
    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
\end{itemize}
\subsection{Temporal Simulations}
The analogy of the feedback beamformer to the temporal IIR architecture raises some fundamental questions that should be addressed.
In the following, supported by simulations, we answer those questions.
\par The first question, related to the feedback beamformer's analogy to the temporal IIR architecture, is stability related.
To begin with, we should first ask what does ``stability`` means.
Interestingly, the system's response of \eqref{eqn:GeneralFeedbackTransferFunction} is not frequency dependent, for it is exclusively governed by spatial parameters.
Therefore, in the absence of any previous related work on spatial feedback, we find that the commonly used Bounded-Input-Bounded-Output (BIBO) stability is appropriate. 
As such, assuming the \emph{Perfect alignment} scenario, we identify $r$ in \eqref{eq:SF_CB} to be the most influential for determining the system's stability for it controls the response's denominator - e.g. for $r<1$ the denominator will never be nullified.
As anticipated from \eqref{eq:SF_CB} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude does not converge to a finite value.
Also noticeable is the increase in the final amplitude value as $r$ increases.
In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value with respect to $r$ and find that the increase is substantial as $r$ increases towards 1.
This issue will have to be taken into consideration when one designs such an array for practical applications but is outside the scope of this work.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.55\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_stabilization.png}
            \put (46, -5){\rotatebox{0}{$t/2\tau_{pd}$}}
            \put (-6, 38){\rotatebox{90}{$\abs{z\rBrace{t}}$}}
            \put (46, 18.5){\rotatebox{0}{$r=0.6$}}
            \put (46, 35){\rotatebox{0}{$r=0.9$}}
            \put (46, 54){\rotatebox{0}{$r=1$}}
            \put (18, 60){\rotatebox{0}{$r=1.1$}}
            \put (0.75, 80){\rotatebox{0}{dB}}
        \end{overpic}
    \end{center}
    \caption{
    Simulating a 3 element ULA based feedback beamformer, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
    The horizontal axis ($t/2\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
    }
    \label{fig_stability}
\end{figure}
As a final observation, we address the ``discrete`` behaviour of $z$, i.e. the value (most noticeable in the $r=1.1$ plot) seems to be piecewise constant.
This phenomenon corresponds with the propagation latency of the signal's round trip to the target and back.
In each iteration the spatial focusing is increased, together with the received amplitude, as can be seen in Fig.~\ref{fig_beamThinning}.
The reader may notice that the $t=1\cdot{}\tau_{pd}$ plot is actually the conventional beampattern, for the feedback signal has not yet reimpinged the array.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.55\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_beamThinning.png}
            \put (50, -5){\rotatebox{0}{$\theta_{d}/\pi$}}
            \put (-6, 38){\rotatebox{90}{$H_{r=0.9}$}}
            \put (100, 49){\rotatebox{0}{$t=1\cdot\tau_{pd}$}}
            \put (100, 39){\rotatebox{0}{$t=2\cdot\tau_{pd}$}}
            \put (100, 26.5){\rotatebox{0}{$t=5\cdot\tau_{pd}$}}
            \put (100, 14){\rotatebox{0}{$t=10\cdot\tau_{pd}$}}
            \put (53.5, 27.5){\rotatebox{-75}{$t=50\cdot\tau_{pd}$}}
            \put (4.5, 80){\rotatebox{0}{dB}}
        \end{overpic}
    \end{center}
    \caption{
    Simulation of same setup as in Fig.\ref{fig_stability}.
    We set $r=0.9$ and plot the beampattern for various simulation times.
    }
    \label{fig_beamThinning}
\end{figure}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.55\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_stabilizationVal.png}
            \put (0, 82){\rotatebox{0}{dB}}
            \put (-6, 30){\rotatebox{90}{$\lim_{t\to\infty}\abs{z\rBrace{t}}$}}
            \put (51, -5){\rotatebox{0}{$r$}}
        \end{overpic}
    \end{center}
    \caption{
    Simulation of same setup as in Fig.\ref{fig_stability}.
    For each $r$ (the horizontal axis), we plot the final received amplitude in dB.
    }
    \label{fig_stabilityVal}
\end{figure}
\par The Second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e. $\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
To better understand the phenomenon, we plot the settling time's $r$ dependency in Fig.~\ref{fig_stabilityDur}.
Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:futureResearch}.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.55\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/fig_stabilizationDur.png}
            \put (-3, 35){\rotatebox{90}{$t/2\tau_{pd}$}}
            \put (51, -5){\rotatebox{0}{$r$}}
        \end{overpic}
    \end{center}
    \caption{
    Simulation of same setup as in Fig.\ref{fig_stability}.
    For each $r$ (the horizontal axis), we plot the time (the vertical axis) where the received amplitude entered the $1\%$ sleeve around its final value.
    The plotted time is also normalized as in Fig.\ref{fig_stability}.
    }
    \label{fig_stabilityDur}
\end{figure}
\par Although many interesting questions rise from the initial simulations, most of them are outside the scope of this work.
We choose to add one more note, regarding the influence of the array's number of elements.
Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e. the settling time remains the same as $N$ increases.

### 2021-02-12 Modules/stabilityEnhancement_freqPairApproach.tex
Sent as draft No.2

@@
 
-\subsection*{Intuition}
+\subsection{Intuition}
 Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_generalH} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies.
 Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
-Instead, we suggest simultaneous transmission of several frequencies in order to resolve the range error sensitivity.
-In the following, we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$.
+As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
+Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
+\begin{itemize}
+    \item \textbf{Propagation efficiency}\\
+    Due to the chemical structure of the atmosphere, some frequencies are propagated efficiently while other are absorbed \cite{wen2015foundations} by the atmosphere layers, being unsuitable for localization applications such as RADAR.
+    \item \textbf{Antenna length}\\
+    As described in \cite{barclay2003propagation}, although low ($<30_{\text{Khz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
+    \item \textbf{Signal bandwidth}\\
+    As the carrier signal's frequency decreases, so does the available bandwidth due to aliasing.
+\end{itemize}
+Henceforth, inspired by known trigonometrical identities where mathematical of two harmonics produces new frequencies which are the sum (or subtraction) of the original signals, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies.
+In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved.
 
-\subsection*{Suggested processing scheme}
+\subsection{Suggested processing scheme}
 \begin{figure}[t!]
     \begin{center}
-        \begin{overpic}[width=0.9\linewidth, 
+        \begin{overpic}[width=0.65\linewidth, 
         % grid, 
@@
             \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
-            \put (24.5, 59){\footnotesize{$\Tx_{1}\rBrace{t}$}}
-            \put (73.5, 59){\footnotesize{$\Tx_{2}\rBrace{t}$}}
+            \put (24.5, 59){\footnotesize{$\Tx{}_{1}\rBrace{t}$}}
+            \put (73.5, 59){\footnotesize{$\Tx{}_{2}\rBrace{t}$}}
             \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
             \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
-            \put (18.25, 13){\footnotesize{Harmonic mean}}
+            \put (18.75, 13){\footnotesize{Harmonic mean}}
             \put (32, 2){$Z_{\text{DF}}$}
             \put (54.75, 24){$\Sigma$}
-            \put (21.75, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
+            \put (22, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
             \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
@@
 We also note that throughout the development of \eqref{eqn_H_DF_general}, we did not assume any specific array geometry, hence this result is valid for arbitrary arrays and not just ULA.
-\subsection*{Numerical example}
+\subsection{Numerical example}
 Consider a radio frequency carrier of $10$~GHz and typical range error of $\Delta{}R_{\text{rt}}=10$~m, which is $333\frac{1}{3}\lambda$ (assuming  speed of light, $c=3\cdot 10^{8}$~m/s).
@@
 
-\subsection*{Dual frequency simulation}
+\subsection{Dual frequency simulation}
 We now simulate \eqref{eqn_H_DF_general} for the DF structured FB,
@@
     \label{eqn_H_DF_CB}
-    \resizebox{.89\linewidth}{!}{
+    %\resizebox{.89\linewidth}{!}
+    {
         \begin{split}

### 2021-02-12 front/abbrevs.tex
Sent as draft No.2

@@
 \abbreviationsAndNotation{
-\begin{tabular}{p{2cm}@{:\quad}l}
-QED & quod erat demonstratum \\
-$c$ & the speed of light \\
-$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
-\end{tabular}
+\begin{longtable}{p{2cm}@{:\quad}l}
+DOA & Direction of arrival \\
+RADAR & RAdio Detection And Ranging \\
+FIR & Finite impulse response \\
+IIR & Infinite impulse response \\
+ULA & Uniform linear array \\
+FIM & Fisher information matrix \\
+SNR & Signal to noise ratio \\
+MUSIC & Multiple signal classification (algorithm)\\
+RHS & Right hand side \\
+FB & Feedback beamformer \\
+SF & Single frequency \\
+DF & Dual frequency \\
+HPBW & Half power beamwidth \\
+PDF & Probability density function \\
+CRLB & Cram\'er Rao lower bound \\
+CRB & Cram\'er Rao bound \\
+PCA & Principal component analysis \\
+ICA & Independent components analysis \\
+MVDR & Minimum Variance Distortionless Response \\
+UWB & Ultra wide band \\
+HOS & High order statistics \\
+$\vecnot{v}$ & A vector \\
+$v_{i}$ & The $i$-th element of vector $\vecnot{v}$ \\
+$\vecnot{v}^{T}$ & Transpose of vector $\vecnot{v}$ \\
+$\vecnot{v}^{*}$ & Conjugate of vector $\vecnot{v}$ \\
+$\vecnot{v}^{H}$ & Hermitian (conjugated) transpose of vector $\vecnot{v}$ \\
+$\vecnot{A}$ & A Matrix \\
+$A_{i,j}$ & The $i,j$-th element of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{T}$ & Transpose of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{*}$ & Conjugate of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{H}$ & Hermitian (conjugated) transpose of matrix $\vecnot{A}$ \\
+$N$ & Number of elements in array \\
+$d$ & Array's inter-element spacing \\
+$\omega$ & Radial frequency \\
+$c$ & Wave's propagation velocity \\
+$\delta{}x$ & Small diff in $x$ \\
+$\lambda$ & Wavelength \\
+$t$ & Time \\
+$\theta_{d}$ & Geometrical angle \\
+$\psi$, $\theta$ & Electrical phase \\
+\vecnot{d} & Steering vector \\
+$B$ & beampattern \\
+$R$ & Distance to target \\
+$z\rBrace{t}$ & Array's temporal output \\
+$Z\rBrace{\omega}$ & Array's frequency-domain output \\
+$\mathcal{D}$ & Directivity \\
+$\mathcal{H}$ & Normalized beampattern \\
+\end{longtable}
 }

### 2021-02-12 front/personal-acks.tex
Sent as draft No.2

\personalAcknowledgementEnglish{
% I would like to thank my advisor, my parents, my friends, etc. etc.

% Add any thank-yous, acknowledgements, personal comments you wish to make here (in \texttt{personal-acks.tex}).

% Note that this acknowledgements section only gets printed in the post-exam version of the thesis (i.e. if you leave out the \texttt{beforeDefense} option to your document class in \texttt{thesis.tex}.)
First, I would like to thank my wife, Hadas, for giving me time, space and endless encouragement to finish this work inspite of all the Covid-19 realted difficulties and quarantines.
Also great gratitude is to my parents, who encouraged and helped me to set high goals and achieve them. 
\par I would also like to thank Dr. Tsvi Dvorkind for guiding me to ask the right questions without missing any details, which proved itself worthwhile with the paper being almost accepted with the first submission.
\par Special thanks goes to Prof. Israel Cohen for giving great guidance  and crucial insights from a reviewer point of view, sharing his vast knowledge and experience.
}

\personalAcknowledgementHebrew{
% אני רוצה להודות למנחה שלי, להוריי, לחבריי, וכו' וכו'.

% אפשר להוסיף עוד תודות והערות אישיות כאן.

% שים/י לב: קטע זה של תודות מודפס בפועל רק בגרסת החיבור שלאחר-הבחינה (הווה אומר רק אם הסרת את האפשרות \textenglish{\texttt{beforeDefense}} מן האפשרויות המועברות ל-\textenglish{\texttt{document class}} בקובץ \textenglish{\texttt{thesis.tex}}.)

בראש ובראשונה, תודתי נתונה לאשתי הדס על שנתנה לי את הזמן, המקום והתמיכה האינסופית לסיים את עבודה זו למרות כל הקשיים והסגרים שחווינו בעקבות התפרצות נגיף הקורונה.
הערכתי העמוקה נתונה גם להורי על שעודדו אותי לשאוף גבוה ולהשיג את מטרותי.
\par
ברצוני גם להודות לדר' צבי דבורקינד על ההדרכה הבלתי מתפשרת וההכוונה אל עבר שאילת השאלות הנכונות מבלי לפספס אף פרט, עקרונות שהוכיחו עצמם מעל ומעבר בכך שהמאמר כמעט והתקבל בהגשה הראשונה.
\par
תודה מיוחדת נתונה לפרופ' ישראל כהן על ההכוונה והליווי תוך מתן דגשים מכריעים מנקודת מבט של בוחן תוך שיתוף ידיעותיו ונסיונו הרבים.
}

### 2021-02-12 main/intro.tex
Sent as draft No.2

--- 2020-12-25 main/intro.tex
@@
 The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
-For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.
+\par Early algorithms for DOA estimation were based on the beamforming concept \cite{krim1996two}, where the array's reception beam is steered (mechanically or electronically) to multiple directions in search of received energy peaks which are interpreted as valid emitters.
+One notable improvement to the convectional beamformer \cite{van2004optimum} was Capon's beamformer  (aka MVDR in acoustics related literature) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain
+in the "look direction".
+\par The most practically used approach in DOA estimators, referred as the sub-space based estimation, involves invariant sub-spaces analysis of observed covariance matrices.
+Early research include PCA and errors-in-variables time series analysis \cite{krim1996two}.   
+However, the tremendous interest in the subspace approach is mainly due to the introduction of the
+MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection assuming that the noise space is orthogonal to the array manifold.
+It is interesting to note that while earlier works were mostly derived in the context of time series analysis and later applied to the sensor array problem, MUSIC was indeed originally presented as a DOA estimator.
+\par A Less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the statistical based ML approach which tries to find the most probable DOA assuming a known PDF.
+Though this approach served as a basis for extensive research, leading to more advanced concepts such as the ICA \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
+Adding the fact that sub-optimal methods such as MUSIC were proven achieve the CRB under some practical assumptions (e.g.
+non-coherent signals) \cite{stoica1989music}, such methods (i.e.
+the sub optimal estimators) are substantially more common in practice.
 \par In pursuit of spatial performance improvement, namely higher spatial separation and selectivity of arriving signals, many approaches were suggested.  
 One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
-Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
+\par Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
 Another approach, involving different array geometries, examined minimum redundancy arrays \cite{moffet1968minimum,pillai1985new,pillai1987statistical,Kupershtein2013}, aiming to reduce the spatial ambiguity.
 The basic concept was minimization of the inter-element spacing redundancy in order to increase the overall resolution.
-The main advantage of the first (i.e.
+% The main advantage of the first (i.e.
 virtual array) over the latter (i.e.
 minimum redundancy) is the obtainable analytical expression for the improvement in spatial selectivity when using virtual arrays.
-In the minimum redundancy approach no such expression is available.
-On the other side, the computation effort is considerably higher when the 2-nd order statistics are computed.
+% In the minimum redundancy approach no such expression is available.
+% On the other side, the computation effort is considerably higher when the 2-nd order statistics are computed.
 Although the $q$-th order statistics based approach promises substantial improvement, both noise sensitivity and impractical computation amount are dominant drawbacks, limiting the usage of such methods in practical applications.
-Adaptive processing schemes \cite{frost1972algorithm,manolakis2000statistical}, being a wide and active research area, were also suggested trying to adaptively estimate and suppress the noise component in impinging signals by minimization of the receiver's output energy with some constraints.
+\par Adaptive processing schemes \cite{frost1972algorithm,manolakis2000statistical}, being a wide and active research area, were also suggested trying to adaptively estimate and suppress the noise component in impinging signals by minimization of the receiver's output energy with some constraints.
 In \cite{manolakis2000statistical}, two main approaches to adaptive processing are discussed.
@@
 As in many adaptive processing applications, the two methods rely on steepest descend optimization, which expose the adaptive processing approach to errors related to optimization parameters choices such step size etc.
-\par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g.
-narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?''
+\par In \cite{van1988beamforming}, ULA based beamforming and temporal FIR filtering are shown to be mathematically analogous, where the DOA acts as the spatial version of temporal frequency.
+Inspired by this analogy, which is thoroughly discussed in Sec.~\ref{sec:prlm_FIR_IIR}, we were motivated to find the spatial counterpart of the temporal IIR filter, both from academic curiousness and the known advantages of the IIR filter's frequency (DOA by analogy) response, hoping to gain spatial performance by finding the right architecture.
+Therefore we formulated a question, ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?'' which served as a guide throughout our research.
 \par Achieving spatial IIR response has also motivated other works.
 In \cite{wen2013extending} two methods were considered.
-The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain.
-The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array. 
-The former approach heavily relies on the accuracy of the delay estimation which are amplified due to the fact that both the desired signal and the errors are continuously fed back into the filter.
-Close inspection of the latter approach reveals that even though the sub-arrays are each weighted separately, each sensor's output is eventually linearly weighted when taking into account all related sub-arrays.
+The first one (see Fig.~\ref{fig_intro_wen1}) was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain.
+\begin{figure}[ht!]
+    \begin{center}
+        \begin{overpic}[width=0.5\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/WEN_method1.png}
+            % \put (50, 62.5) {\footnotesize{$r=0$}}
+        \end{overpic}
+    \end{center}
+     \caption{Synthetic delay emulated for the recursive part of the spatial IIR filter.}
+    \label{fig_intro_wen1}
+\end{figure}
+The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array (see Fig.~\ref{fig_intro_wen2}).
+\begin{figure}[ht!]
+    \begin{center}
+        \begin{overpic}[width=0.5\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/WEN_method2.png}
+            % \put (50, 62.5) {\footnotesize{$r=0$}}
+        \end{overpic}
+    \end{center}
+     \caption{Referring to consecutive sub arrays' output as sequential output of the same ULA.}
+    \label{fig_intro_wen2}
+\end{figure}
+Obviously, the former approach is very sensitive to the synthetic delay accuracy and involves temporal domain processing which we try to avoid in this work to achieve purely spatial processing.  
+Also, close inspection of the latter approach reveals that even though the sub-arrays are each weighted separately, each sensor's output is eventually linearly weighted when taking into account all related sub-arrays.
 Clearly, this is just another possible implementation of basic FIR like ULA spatial processor, so in both cases, there is no true spatial feedback between the array and the source of interest.
-Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{Hum2009BeamformingFilters}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.
-\par
-TODO: Elaborate on the 2/3D planar from (by order)
-\begin{itemize}
-    \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
-    \item Three-Dimensional Cone Filter Banks
-    \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
-    \item UWB Beamforming Using 2-D Beam Digital Filters
-\end{itemize}
+\par Other interesting works \cite{Hum2009BeamformingFilters,madanayake2008speed} in the field of ultra-wideband (UWB) treat the spatial and temporal diversity, which reside in multiple consecutive snapshots of the array output, as if the signal is sampled in two independent temporal frequencies.
+Inspired by \cite{bruton1985three}, the authors show that impinging plane waves are represented as straight lines tilted according to their DOA and suggest methods to design line filters in the spatio-temporal plane.
+In \cite{Hum2009BeamformingFilters}, the authors also address the fact that ideal straight line filter may not be achieved due to the fact that the filter is periodic in both frequencies, causing the 2D frequency response the ``bend`` close to the sampling frequencies (see Fig.~\ref{fig_intro_UWB_bend}).
+\begin{figure}[ht!]
+    \begin{center}
+        \begin{overpic}[width=0.5\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/UWB_bend.png}
+            % \put (50, 62.5) {\footnotesize{$r=0$}}
+        \end{overpic}
+    \end{center}
+     \caption{2D spatio-temporal frequency response (dB) of practical UWB filter. The black line is angled according to the desired DOA.}
+    \label{fig_intro_UWB_bend}
+\end{figure}
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.
@@
 Furthermore, as opposed to the passive target case (i.e., a target which merely reflects the impinging signal), one may consider a cooperative target, which receives, enhances and re-transmits the signal back to the array.
-% \par The outline of this paper is as follows.
-We first formulate the classic spatial beamforming setup in Sec.~\ref{sec:setup}.
-Then, in Sec.~\ref{sec_introduceFeedback}, we propose our novel feedback-based architecture, and formulate its spatial response.
-% Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
-% In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback.
-Specifically, we compute the array beamwidth, its peak-to-sidelobe ratio and the array directivity, showing significant improvement compared to traditional beamforming without spatial feedback.
-% In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors.
-We then suggest a strategy which mitigates this sensitivity.
-Finally, concluding remarks are given in Sec.~\ref{sec_conclusions}.
+\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
+$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
+Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
+\par In the followings, we elaborate in Chapter~\ref{chap:prelims} on some relevant theoretic concepts which serve as the foundation of this presentation.
+Then our novel architecture is presented and analysed in Chapter.~\ref{chap:firstchap} followed by a thorough concluding discussion on the findings and future research in Chapter.~\ref{chap:futureResearch}.

### 2021-02-12 main/prelims.tex
1. Intro exapnsion - WIP 2. Move appdxs to end of thesis - DONE
Before implementing Tsvi's comments
Sent as draft No.2

@@
 \label{chap:prelims}
-
-As a preliminary discussion to the presentation of out contribution, we overview some the key theoretical basis of the thesis.
-In Sec.~\ref{sec:prlm_propWaveField}, the wave propagation, being the most basic concept for array processing, is discussed.
-It is then followed by a short overview of array-processing in Sec.~\ref{sec:prlm_sensorArrays}.
+As a preliminary discussion to the presentation of our contribution, we overview some the key theoretical basis of the thesis.
+First, a short overview of array-processing is presented in Sec.~\ref{sec:prlm_sensorArrays}, accompanied by a complementary wave propagation discussion in Sec.~\ref{sec:prlm_propWaveField}.
 To accommodate the discussion for spatial filtering, we also mention the time-space relation of spatially sampled signals in Sec.~\ref{sec:prlm_timeSpaceSig}.
-As an additional theoretical concept, arriving from the information theory, which will be used in the main chapter (Ch.~\ref{chap:firstchap}), is the Fisher Information Matrix, covered in Sec.~\ref{sec:prlm_FIM}.
-\par 
-For an easier reading treat each section as independent, where notations and symbols are each defined in the specific section and are not mutual, nor used in the main chapter.
-
+In Sec.~\ref{sec:prlm_localization}, we further focus the spatial filtering discussion to localization and overview some of its fundamentals.
+Following the FIR/IIR filters related discussion in Chapter.~\ref{chap:intro}, we further elaborate and compare the two architectures in Sec.~\ref{sec:prlm_FIR_IIR}.
+To complete the basics overview, we also discuss array performance measuring in Sec.~\ref{sec:prlm_array_perf} following the classical localization related literature.
 % \begin{definition}
@@
 
-\section{Propagating Wave Fields}
-\label{sec:prlm_propWaveField}
-\input{Modules/sec_prlm_propWaveField}
 % \section{Digital Filter Design - Finite/Infinite Response Filters}
@@
 \input{Modules/sec_prlm_sensorArrays}
-\section{Time-Space Signals}
+\section{Propagating Wave Fields}
+\label{sec:prlm_propWaveField}
+\input{Modules/sec_prlm_propWaveField}
+\section{Spatio-temporal processing}
 \label{sec:prlm_timeSpaceSig}
 \input{Modules/sec_prlm_timeSpaceSig}
+\section{Localization}
+\label{sec:prlm_localization}
+\input{Modules/sec_prlm_localization}
 % \section{Sensor array performance measure}
@@
 % \input{Modules/sec_prlm_arrPerf}
-\section{Fisher Information Matrix}
-\label{sec:prlm_FIM}
-\input{Modules/sec_prlm_FIM}
+\section{The analogy between array processing and temporal digital filtering}
+\label{sec:prlm_FIR_IIR}
+\input{Modules/sec_prlm_FIR_IIR}
+\section{Array spatial performance}
+\label{sec:prlm_array_perf}
+\input{Modules/sec_prlm_array_perf}

### 2021-02-12 Modules/directivityAnalysis.m

@@ -1,0 +1,52 @@
+function [] = directivityAnalysis()
+%% configure
+nVec    = 2:10;
+rVec    = [1/10 1/5 1/3 1/2 5/8 3/4 4/5];
+
+%% symbolics
+syms x real;
+syms r positive;
+
+D = @(x,N) sin(N*x)/(N*sin(x));
+
+hNum = @(t,p,N,r) (1-r)*D(t/2,N);
+hDen = @(t,p,N,r) exp(1i*(p+(N-1)*t/2)) - r*D(t/2,N);
+h = @(t,p,N,r) hNum(t,p,N,r)./hDen(t,p,N,r);
+
+%% simulate
+integralResultMAT   = zeros(length(rVec),length(nVec));
+exprMAT             = zeros(size(integralResultMAT));
+[r_GRID, n_GRID]    = meshgrid(rVec, nVec);
+for rVal = rVec
+    for nVal = nVec    
+        curIntRes = ...
+            vpaintegral(h(x,0,nVal,rVal), 0, 2*pi...
+            ) ...
+            /(2*pi);
+        Dir = 1 / curIntRes;
+        curIntRes_eval = eval(curIntRes);
+        curIntRes_STR = num2str(real(curIntRes_eval));
+        Dir_eval = eval(Dir);
+        Dir_STR = rats(real(Dir_eval));
+        tol = abs(eval(Dir_STR)-Dir_eval);
+        disp([...
+            'r = ', num2str(rVal) ...
+            ,', N = ', num2str(nVal) ...
+            ,', int = ',  curIntRes_STR ...
+            ,', Dir = ', Dir_STR ...
+            ]);
+        integralResultMAT(...
+            rVec == rVal,...
+            nVec == nVal...
+            ) = real(Dir_eval);
+        exprMAT(...
+            rVec == rVal,...
+            nVec == nVal...
+            ) = (nVal-rVal)/(1-rVal);
+    end    
+end
+figure;
+surf(r_GRID, n_GRID, transpose(integralResultMAT), 'EdgeColor', "interp", 'FaceAlpha',0.75);
+hold on;
+plot3(r_GRID, n_GRID, transpose(exprMAT), 'dk', 'MarkerSize', 10, 'LineWidth', 2, 'MarkerFaceColor', 'k');
+legend({'Numeric integration', 'Analytic expression'});

### 2021-02-15 Modules/Spatial_IIR-MathDerivations.tex
rev03

@@
+As in Sec.~\ref{sec:prlm_FIR_IIR}, an $N$-element ULA with inter-element spacing $d$ is considered.
+Its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$ and we set $\vpi{0}$ as the axis reference point while the target of interest is positioned at $\vpt$.
+We also place a transmitter at $\vpi{0}$, where transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds and $R = \norm{\vpt-\vpi{0}}, c$ are the target's range propagation velocity of the signal in the medium respectively.
 Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
@@
 \begin{equation*}
-    \rBrace{I+-g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}^{-1} 
-    = I+\frac{g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
+    \begin{split}
+        \rBrace{I-g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}^{-1} 
+        &= I+\frac{g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
+        \\
+        &= \frac{\rBrace{I-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}+g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}\vecnot{d}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
+        \\
+        &= \frac{
+        \rBrace{I+\rBrace{\vecnot{d}\vecnot{\alpha}^{H}-\vecnot{\alpha}^{H}\vecnot{d}}g\exp{\rBrace{-j\omega\tau}}}\vecnot{d}
+        }{
+        1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}
+        }
+        \\
+        &= \frac{
+        \vecnot{d}+\rBrace{\vecnot{d}\vecnot{\alpha}^{H}\vecnot{d}-\vecnot{\alpha}^{H}\vecnot{d}\vecnot{d}}g\exp{\rBrace{-j\omega\tau}}
+        }{
+        1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}
+        }
+        \\
+        &= \frac{
+        \vecnot{d}+\vecnot{\alpha}^{H}\vecnot{d}\rBrace{\vecnot{d}-\vecnot{d}}g\exp{\rBrace{-j\omega\tau}}
+        }{
+        1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}
+        }
+        \\
+        &= \frac{
+        \vecnot{d}
+        }{
+        1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}
+        }
+    \end{split}
 \end{equation*}
-which results in
-\begin{equation*}
-    \frac{\rBrace{I-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}+g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}\vecnot{d}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}.
-\end{equation*}
-Obviously the numerator's 2nd and 3rd terms vanish using the commutativity concept stating that
-\begin{equation*}
-    \vecnot{\alpha}^{H}\vecnot{d}\vecnot{d} = \vecnot{d}\vecnot{\alpha}^{H}\vecnot{d}
-\end{equation*}
-which finally results in
+leading to
 $$
@@
     % A visualization of the spatial area selectivity concept.
-    Combining both radial selectivity and DOA-based selectivity allows to localize the transmitter.
+    Combining both radial selectivity and DOA-based selectivity allows to localize the target.
     }

### 2021-02-15 Modules/abstractEnglish_LOCAL.tex
rev03

@@
-State-of-the-art array processing methods, ranging from high-order statistics to adaptive configuration, require costly computing efforts in pursuit for spatial performance improvement.
+% State-of-the-art array processing methods, ranging from high-order statistics to adaptive configuration, require costly computing efforts in pursuit for spatial performance improvement.
+The general field of array processing has been thoroughly studied throughout several decades.
+The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications.
+The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
 \par 
 Considering localization related applications, several processing approaches are to be found.
-The most approach is \emph{beamforming}, i.e scanning the area of interest and marking peaks in output energy as targets of interest.
+The most basic approach is \emph{beamforming}, i.e steering the array to different parts of the arena in search of objects.
 Another approach, which is probably the most commonly used, is the subspace-based processing which tries to identify input signals that fit into the array's manifold using the orthogonal projection concept.
-Statistical processing, although costly in terms of computation effort, is also in use, ranging from maximum-likelihood related schemes to higher-order-statistics using cumulants.
-Newer approaches which are still in research stage use neural networking and sparsity algorithms.
+Statistical processing, although costly in terms of computation effort, is also in use, ranging from maximum-likelihood (ML) related schemes to higher-order-statistics (HOS) using cumulants.
+Newer approaches which are still in research stage use neural networking and sparsity-based algorithms.
 \par
-Although mush researched, in this work we revisit the \emph{beamforming} approach and suggest
-a feedback based approach, featuring low complexity and high spatial performance in the mere excess of integrating a transmitter to the array, which in RADAR-like arrays is already in place.
-In the proposed scheme, a signal is continuously re-transmitted between the array and the target of interest, thus creating a spatial loop which is shown to be equivalent of enlarging the array's aperture in terms of spatial resolution.
+Although much researched, in this work we revisit the \emph{beamforming} approach.
+ULA based beamforming and temporal finite impulse response (FIR) filtering are mathematically analogous, where the DOA acts as the spatial version of temporal frequency.
+Inspired by this analogy, we search for the spatial counterpart of the temporal infinite impulse response (IIR) filter.
+To this end, we arbitrarily choose to use localization related problem formulation and suggest a feedback based approach, featuring low complexity and high spatial performance in the mere excess of integrating a transmitter to the array.
+Considering RADAR-like arrays, the transmitter is already in place, hence a mere processing modification suffices.
+Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
+Hence a spatial loop is created, which is shown to be equivalent of enlarging the array's aperture in terms of spatial resolution.
+Also notable is that the achievement of the exclusive IIR-like beampattern is purely done in the spatial domain while avoiding any temporal processing to the signal.
 \par 
@@
 \par
-Taking into account the unavoidable estimation errors and uncertainties, we find that the basic feedback integrated beamformer is very sensitive to even mild errors due to the high frequencies of practical carrier signals.
-Seeking for a solution, bearing in mind that summing multiple harmonics produce also other lower / higher frequencies, we propose a practical and robust implementation of the feedback-based localization concept.
-We then thoroughly analyse this \emph{dual-frequency} method and find that it features low and controllable estimation errors sensitivity in the mere expense of doubling the computation effort.
+Taking into account the unavoidable estimation errors and uncertainties, we find that the basic feedback integrated beamformer is very sensitive to even mild range errors.
+% Also, the system is more sensitive as the carrier frequency increments.
+% Considering practical carrier frequencies, the range sensitivity is of wavelength order. 
+% Seeking for a solution, bearing in mind that summing multiple harmonics produce also other lower / higher frequencies, we propose a practical and robust implementation of the feedback-based localization concept.
+As a solution, we propose a more complex architecture, using two harmonics, which we call \emph{dual-frequency feedback beamformer}.
+We also thoroughly analyse the proposed solution and find that it features low and controllable estimation errors sensitivity in the mere expense of doubling the computation effort.

### 2021-02-15 Modules/abstractHebrew.tex
rev03

@@
 \par
-למשל, עלתה הצעה לשערך את השהיית האות בין רגשים שכנים, וע"י כך לייצר היזון חוזר בצורה מלאכותית.
+למשל, בעבודתו של WEN
+\cite{wen2013extending}
+עלתה הצעה לשערך את השהיית האות בין רגשים שכנים, וע"י כך לייצר היזון חוזר בצורה מלאכותית.
 גישה זו חשופה לשגיאות מדידה וחוטאת למטרת העיבוד המרחבי הטהור - שכן היא מערבת עיבוד זמני.
-הצעה נוספת היתה להתייחס לתת מערכים (מתוך מערך אחד) חופפים כאל הסחות זמניות של מערך אחד קטן יותר ובכך לייצר קירוב סופי לתגובת ההלם האינסופית.
+הצעה נוספת בעבודה הנ"ל 
+\cite{wen2013extending}
+היתה להתייחס לתת מערכים (מתוך מערך אחד) חופפים כאל הסחות זמניות של מערך אחד קטן יותר ובכך לייצר קירוב סופי לתגובת ההלם האינסופית.
 הצעה זו אינה אלא פרשנות שונה לעיבוד מבוסס 
@@
 שכן בסופו של תהליך העיבוד הינו לינארי ומכיל מספר סופי של דגמים במערכת בכל זמן נתון.
-שיטה מעניינת, המהווה בסיס למחקר ענף, מטילה את הדגימה המרחבית והדגימה הזמנית אל מישור התדר, בו גל מישורי מיוצג על ידי קו ישר המוטה לפי זוית ההגעה של הגל הפוגע.
+שיטה מעניינת
+\cite{Hum2009BeamformingFilters,madanayake2008speed}
+, המהווה בסיס למחקר ענף, מטילה את הדגימה המרחבית והדגימה הזמנית אל מישור התדר, בו גל מישורי מיוצג על ידי קו ישר המוטה לפי זוית ההגעה של הגל הפוגע.
 בהמשך לכך, מסננים במרחב התדר הדו מימדי מתוכננים על מנת להגביר אותות שמגיעים מכיוונים רצויים.
@@
 על פניו, מערכת דומה למכ"ם, הפולט אות ומשערך את מיקומי מטרות על פי האות החוזר.
-החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק אות מלאכותי הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך, בכך נוצר היזון חוזר בין מהמערך והמטרה.
+החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק עותק יחיד הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך, בכך נוצר היזון חוזר בין המערך והמטרה.
 ניתוח המערכת מרמז כי ע"י שליטה במשקלות המסנן המייצר את האות החוזר, ניתן להפיק את היתרונות הרבים הטמונים במסנן בעל התגובה האינסופית.
 \par
-לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי - אבן נגף משמעותית בנסיון למציאת הפתרון.
+מחקירת המערכת המתקבלת, מצאנו שיפור משמעותי במגוון מאפיינים כגון רוחב אונה, הנחתת אונות צד ודיכוי רעשים איזוטרופים יעיל - הוה אומר כיווניות גבוהה.
+לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי לשגיאת טווח - אבן נגף משמעותית בנסיון למציאת הפתרון.
 עם זאת, לשמחתנו, נמצא גם פתרון פשוט וזול יחסית לבעיה, המגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.

### 2021-02-15 Modules/apndx_directivityFit.tex
rev03

@@
-In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the numerical evaluation reaches rational fractions when rational values of $r$ were used.
-Following that hint, we numerically swept various values of $N,r$ doublets, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the feedback beamformer.
-In the following, we elaborate on the sweeping process it's technicalities.
+In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were rational.
+Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the feedback beamformer.
+In the following, we elaborate on the technicalities of this sweeping process.
 \par The first step was to formulate the symbolic expression for $H$.
@@
 Afterwards, the 2D sweep range was set, where as mentioned before, $r$ was set to be of rational values.
-In each sweep step, an numerical integration was executed with specific values for $N$ and $r$.
+In each sweep step, a numerical integration was executed with specific values for $N$ and $r$.
 Each result was fitted with it's next closest rational number with the help of MATLAB\textsuperscript{\textregistered}'s \emph{rats} auxiliary command.
-After observing the results, we found that all of then obey the same expression as in \eqref{eq_D_result} for any tolerance, which increased the confidence in the suggested expression.
-\par The printout of the code is presented as Table.~\ref{table_D}
+After observing the results, we found that all of them obey the same expression as in \eqref{eq_D_result} for any tolerance, which increased the confidence in the suggested expression.
+\par The printout of the code is presented as Table.~\ref{table_D} and the text below.
 \begin{table}[h!]

### 2021-02-15 Modules/arrayPerformance_beamwidth_LOCAL.tex
rev03

@@
 Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA.
-To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values (actually slicing a vertical column of Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} at $N=100$) and looked for proper polynomial approximation using MATLAB\textsuperscript{\textregistered}.
-It turns out that the 2-nd order polynomial best suits the computation and that the best fitted expression is 
+To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values (actually slicing a vertical column of Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} at $N=100$) and looked for proper polynomial approximation (using MATLAB\textsuperscript{\textregistered}) for the HPBW.
+It turns out that the 2-nd order polynomial fit satisfies
 \begin{equation}

### 2021-02-15 Modules/paper_sec_prlms.tex
rev03

@@
 The feedback based beamforming concept is introduced in Sec.~\ref{sec_introduceFeedback}.
-Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix.
+Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix (FIM).
 The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
-Considering practical scenarios, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.
+Considering noisy setups, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.
 
@@
         H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}
-        }
-         =
+        }\\
+        &=
         \frac{
@@
         r/\rBrace{1-r}
-        },
-        % \\
-        % &=\frac{\rBrace{1-r}^{2}\Dp{\dTheta/2,N}{2}}{1+r^{2}\Dp{\dTheta/2,N}{2}-2r\D{\dTheta/2}{N}\cos{\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}},
-    \end{split}
-    %}
-\end{equation}
-where the $\Delta\theta,\Delta\phi,r$ subscripts express the DOA, range and gain errors dependency, respectively.
-%Also, $\abs{\HrTPr}$ is defined to be the beampattern.
-Plugging \eqref{eq:SF_CB} into \eqref{eq_narmalized_pattern} yields 
-\begin{equation}\label{eq_generalH}
-    %\resizebox{0.89\linewidth}{!}
-    {
-        \begin{split}
-             \HrTPr=
+        }\\
+        &=
         \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.
     \end{split}
-        }
 \end{equation}

### 2021-02-15 Modules/sec_FIM_and_CRLB.tex
Sent as draft No.2
rev03

@@
 \begin{equation}\label{eq_FIM_kl_full}
-    \resizebox{.9\linewidth}{!}{
+    %\resizebox{.9\linewidth}{!}
+    {
         \begin{split}
@@
     \label{eqn_FIMelements}
-    \resizebox{.91\linewidth}{!}{
+    % \resizebox{.91\linewidth}{!}
+    {
         \begin{split}
@@
 where $\hat{g}$ is the channel gain estimate.
-This choice of weights may be interpreted as a generalized version of the conventional beamformer (CB) \cite{van2004optimum}. 
+Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the \emph{conventional beamformer} (CB) \cite{van2004optimum} which is a mere time shift (phase shift in narrowband signals) of the input signals as if the impinging wave is coming from the array's boresight direction (i.e.
+$\theta_{d}=\pi/2$) as illustrated in Fig.\ref{fig_CB_vanTrees}.
+\begin{figure}[t!]
+    \begin{center}
+        \begin{overpic}[width=0.55\linewidth, 
+        % grid, 
+        tics=10,trim=0 0 0 0]{./Media/fig_CB_vanTrees.PNG}
+            % \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
+        \end{overpic}
+    \end{center}
+    \caption{
+    % A visualization of the spatial area selectivity concept.
+    The \emph{conventional beamformer} - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.
+    }
+    \label{fig_CB_vanTrees}
+\end{figure}
 Furthermore, setting $\vBeta=\vBeta_{\text{CB,opt}}=\vAlpha_{\text{CB,opt}}$, is shown (see App.~\ref{apdx_clacFim}) to nullify the FIM cross terms, such that $J_{12}=J_{\thetaD,\phi}=J_{21}=J_{\phi\thetaD}=0.$

### 2021-02-15 Modules/sec_future_dynamic.tex
rev03

@@
 Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e.
-introducing a general 2D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
-The location dynamics may be translated into a dynamic propagation delay, $\tau_{pd}\rBrace{t}$.
+introducing a general 3D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
+The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
 It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time. 
@@
 \begin{equation}
-    % t_{i}\rBrace{t}=\underset{\tau}{\mathrm{argmin}}\cBrace{\tau=\frac{R\rBrace{\tau}}{c}}.
-    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ t - \tau = \frac{R\rBrace{t-\tau}}{c}}
+\label{eq_fut_dyn_ti}
+    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ \tau = \frac{R\rBrace{t-\tau}}{c}}
 \end{equation}
@@
 \begin{equation}
-    \label{eqn:ftr_dyn_temp}
+    \label{eq_fut_dyn_temp}
     x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
@@
 \end{equation}
-One may consider the following research approaches for further investigation
-\begin{itemize}
-    \item \textbf{Modeling of target's location}
-    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
-    In this manner, other components may be added to the positional equation.
-    \item \textbf{Frame based processing}
-    \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration.
-\end{itemize}
+For example, consider a target with constant, radial only (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
+It follows that
+\begin{equation}
+    \label{eq_fut_constV_Rt}
+    R\rBrace{t} = R_{0} + vt
+\end{equation}
+which when plugged into \eqref{eq_fut_dyn_ti} gives rise to
+\begin{equation}
+    \label{eq_fut_constV_ti}
+    t_{i}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
+\end{equation}
+and it follows that
+\begin{equation}
+    \label{eq_fut_constV_xn}
+    x_{n}(t) = g\rBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
+    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
+\end{equation}
+Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
+It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts as the returning signal is frequency shifted.
+% One may consider the following research approaches for further investigation
+% \begin{itemize}
+%     \item \textbf{Modeling of target's location}
+%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
+%     In this manner, other components may be added to the positional equation.
+%     \item \textbf{Frame based processing}
+%     \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration.
+% \end{itemize}

### 2021-02-15 Modules/sec_future_wavfrom.tex
rev03

@@
-In practical RADAR related systems, the waveform of choice is pulse (chirp) based.
+In practical RADAR related systems, the waveform of choice is pulse (in most cases, chirp) based.
 It holds some obvious advantages over the CW transmission such as
 \begin{itemize}
-    \item Lower power consumption
-    \item Possible match filters should allow the decision of weather to re-transmit or not
-    \item In multi target scenario, there is a smaller chance of interference.
-    \item The most interesting research option is the use of several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions, by merely selecting harmonic couples and filter coefficients, where each harmonic/coefficient set it pointed to a specific area.
-    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution by mere choosing multiple frequency couples which are simultaneously processed independently.
+    \item Lower power consumption due to lower transmissions duty cycle. 
+    \item In multi target scenario, there is a smaller chance of interference for the reflected signals from the targets temporally distinct if the targets are in different distances.
+    \item The use of wide band signals may as in RADAR systems, increase spatial resolution in the radial axis.
+\end{itemize}
+Another interesting option is the using several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions.
+By merely selecting harmonic couples and filter coefficients, each harmonics pair is pointed to a specific area.
+It follows that with the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
 \par 
@@
 Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned feedback beamformer which simultaneously scans the entire arena.
-\end{itemize}

### 2021-02-15 Modules/sec_prlm_FIR_IIR.tex
rev03

@@
 A basic design entity in every signal processing scheme is the digital filter, which is the modern evolution of analog filters.
-The design of the digital filter is very well established and thoroughly studied research field.
-As stated in \cite{oppenheim1975digital} (and numerous other literature), two key filter types are used - i.e. Finite Impulse Response (FIR) and Infinite Impulse Response (IIR) filters.
+The design of the digital filters is very well established and thoroughly studied research field.
+As stated in \cite{oppenheim1975digital} (and numerous other literature), two key filter types are Finite Impulse Response (FIR) and Infinite Impulse Response (IIR) filters.
 This section will briefly overview the design methods and the analogy of ULA based beamforming to the temporal FIR filtering, as implied in Ch.~\ref{chap:intro}.
-\par Each digital filters belong in one of two architectures
 \begin{itemize}
@@
 Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
-\par It is well known \cite{rabiner1974some} that IIR filters have several appealing advantages over their matching (in number of elements) FIR versions.
-A well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant, namely linearly dependent in the phase response derivative of the specific frequency.
+\par It is well known \cite{rabiner1974some} that IIR filters have several appealing advantages over their matching (in terms of number of taps) FIR counterparts.
+The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
+In the spatial processing context, this implies improved spatial performance, using the same or smaller number of sensors.
+However, a well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant, namely linearly dependent in the phase response derivative of the specific frequency.
 Therefore, linear phase implies that the phase response's derivative (i.e.
 signal latency) is constant which implies all input frequencies will reside in the processor for the exact same time, preventing dispersion which practically causes pulse widening.
-Due to this important property, many applications which are sensitive to signal distortions, especially communication based systems, chose the FIR architecture.
+Due to this important property, many applications which are sensitive to signal distortions, especially communication based systems, chose the FIR architecture, for it is possible to design it as linear phase filter.
 Acquainted with the analogy between frequency and DOA, it seems that when localization applications are considered, where the DOA resolution criteria is more important than the consistency of detection latency between separate DOAs, the linear phase property is less relevant.
-\par The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
-Concluding that spatial linear phase response in DOA domain is not a necessity, combined with the known efficiency of the IIR architecture and the need for smaller and cheaper arrays, the motivation for finding the spatial version of the temporal IIR is complete.
+% \par
+% Concluding that spatial linear phase response in DOA domain is not a necessity, combined with the known efficiency of the IIR architecture and the need for smaller and cheaper arrays, the motivation for finding the spatial version of the temporal IIR is complete.
 \par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest.
 Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.).
-As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
+As opposed to the standard scheme, we suggest in Chapter.~\ref{chap:firstchap} a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
 Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals.

### 2021-02-15 Modules/sec_prlm_array_perf.tex
rev03

@@
 As mentioned in Chapter.~\ref{chap:intro}, array processing serves in many different application, each with its unique requirements, setup and constraints - hence performance criteria are application dependent.
-In this work, we focus on localization related applications and suggest a new architecture.
-Hence, to analyse the presented scheme, we use classic localization-related performance measurements as the comparison is to known localization related array processing schemes.
+In this work, we focus on localization related applications and suggest a new architecture for the beamformer design.
+Hence, to analyse the presented scheme, we use classic localization-related performance metrics.
 \par
@@
   In both plots, a comparison between the conventional beamformer's responses of 3,6 and 12 elements arrays is emulated. 
-  In Fig.~\ref{fig_common_bps1}, the response is presented on the interval of 0 to $\pi$ with units of dB.
+  In Fig.~\ref{fig_common_bps1}, the response is presented on the $\vBrace{0,\pi}$ interval with units of dB.
   In Fig.~\ref{fig_common_bps2}, a polar plot is presented with same units for the response gain but the DOA is in degrees.}
@@
 \end{figure}
-Although may be dependant in various parameters, for the sake of simplicity, we consider a planar (i.e. azimuth without elevation) DOA-only dependant array response (i.e. the \emph{beampattern})
+Although for sensors in 3D space the DOA may depend on two angles (azimuth and elevation), for the sake of simplicity, we consider a planar (i.e.
+azimuth without elevation) DOA-only dependant array response (i.e.
+the \emph{beampattern})
 \begin{equation}
@@
 The beampttern is commonly presented in a graphical manner as exemplified in Fig.~\ref{fig_common_bps}.
-It's characteristics, such as lobes width, attenuation and positioning are then analysed and compared between different schemes.
-The analysis can theoretical, when the beampattern's mathematical expression is known or graphical analysis for empirical scenarios.
-In this work, as we deal with 2D planar localization problems, we find the presentation of Fig.~\ref{fig_common_bps1} most suitable.
-The horizontal axis, being the DOAs of the impinging signal, may be presented in various ways where units may be degrees radians etc.
-Also, as the DOA is periodical one should also choose the centering, for example when the beampattern is steered towards different angles and the author wants to center the mainlobe.
-In this work, we follow choose to use \cite{van2004optimum}'s $\psi$-space, i.e.
+It's characteristics, such as main lobe width, position and attenuation of sidelobes are then analysed and compared between different schemes.
+The analysis can be done theoretically, when the beampattern's mathematical expression is known or it can be conducted numerically for empirical scenarios.
+% In this work, as we deal with 2D planar localization problems, we find the presentation of Fig.~\ref{fig_common_bps1} most suitable.
+The DOAs of the impinging signal, may be presented in various ways where units may be degrees or radians.
+% Also, as the DOA is periodical one should also choose the centering, for example when the beampattern is steered towards different angles and the author wants to center the mainlobe.
+In this work, we choose to follow \cite{van2004optimum}'s $\psi$-space, i.e.
 \begin{equation}
@@
 where $\lambda$ is the impinging signal's wavelength.
-The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA}. 
-Also, we choose to plot beampatterns using $\Delta\psi = \psi\rBrace{\theta_{d}} - \psi\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, for it centers the mainlobe, enabling convenient comparison.
+The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
+Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, for it centers the mainlobe, enabling convenient comparison.
 \subsection{The normalized beampattern}
-As the absolute output gain is system dependent, comparing two different is not possible where their maximal gain of the mainlobe are different.
+As the absolute output gain is system dependent, comparing two different beampatterns is not possible where their maximal gain of the mainlobe are different.
 Therefore, a common practice \cite{van2004optimum} when analysing the array's spatial performance, is to normalize the beampattern such that the mainlobe's output gain at it's peak is 1 (0dB), thus enabling convenient comparable measures extraction.
-This quantity will be referred as $\mathcal{H}$.
+This quantity will be referred to as $\mathcal{H}$.
 \subsection{Half power beamwidth}
-Considering localization problems, possibly the main interest is spatial resolution, related to localization accuracy and distinction of spatially close objects, where ``close`` can be interpreted as small physical distance between objects of interest or objects that may be physically distant from each other but from the array's perspective are in relatively similar.
-\par
-Relating to the beampttern, the spatial resolution is obviously linked to the main lobe's width, i.e. higher resolution is acheived as the main lobe thins. 
-Hence to unify the analysis, the Half Power BeamWidth (HPBW) is defined to be the 3-dB beamwidth, i.e. the point where $\abs{B\rBrace{\psi}}^{2} = 0.5$ or $\abs{B\rBrace{\psi}} = 1/\sqrt{2}$.
+% Considering localization problems, possibly the main interest is spatial resolution, related to localization accuracy and distinction of spatially close objects, where ``close`` can be interpreted as small physical distance between objects of interest or objects that may be physically distant from each other but from the array's perspective are in relatively similar.
+% \par
+Considering localization problems, the spatial resolution is obviously linked to the main lobe's width, i.e. higher resolution is achieved for narrower main lobe.
+The Half Power BeamWidth (HPBW), marked as $\Delta\theta_{HPBW}$, is defined to be the 3-dB beamwidth, i.e. the point where $\abs{B\rBrace{\theta}}^{2} = 0.5$ or $\abs{B\rBrace{\theta}} = 1/\sqrt{2}$.
 For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
@@
 \subsection{Sidelobes attenuation}
-As the beampattern consists of multiple harmonics (as the number of elements $N$), sidelobes occur when the some harmonics are summed, showing as peaks other than the mainlobe.
-As this is an unwanted result, the height and their rate of decrease are measured aiming to prefer arrays where their height is reduced and the decrease rate is increased.
+% As the beampattern consists of multiple harmonics (as the number of elements $N$), sidelobes occur when the some harmonics are summed, showing as peaks other than the mainlobe.
+% As this is an unwanted result, the height and their rate of decrease are measured aiming to prefer arrays where their height is reduced and the decrease rate is increased.
+A known \cite{van2004optimum} parasitic phenomenon of beampatterns is sidelobes, which manifests as energy peaks outside the mainlobe, typically highest near the mainlobe and decreasing towards the deges of the beampattern.
+In the context of localization, this can cause false detection or reduction in spatial resolution.
+Related spatial performance metrics are the sidelobes gain and rate of decrease
 %
@@
 \subsection{Directivity}
-The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as
+A common measure of performance of an array or aperture is the directivity $\mathcal{D}$.
+As in \cite{van2004optimum}, in a transmitting array or aperture, $\mathcal{D}$ represents the maximum radiation intensity (power per DOA) divided by the average radiation intensity (averaged over all DOAs).
+Also, in a receiving antenna, the denominator represents the noise power at the array (or aperture) output due to isotropic noise (noise distributed uniformly over all DOAs). 
+The numerator will represent the power due to a signal arriving from a certain DOA ($\theta_{T}$) - Thus, $\mathcal{D}$ can be interpreted as the array gain against isotropic noise.
+We define the power pattern, $P\rBrace{\theta_{d}}$, to be the squared magnitude of the beampattern $B\rBrace{\theta_{d}}$
+\begin{equation}
+    P\rBrace{\theta_{d}} = \abs{B\rBrace{\theta_{d}}}^{2}
+\end{equation}
+where the frequency dependence is suppressed.
+Then the directivity $\mathcal{D}$ is defined as
 \begin{equation}\label{eq_D}
-    \mathcal{D}\rBrace{N,r} = \frac{\Hr_{\Delta\theta=0,\Delta\phi=0,r}}{\frac{1}{2\pi}\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta} = \frac{2\pi}{\int_{0}^{2\pi}\Hr_{\Delta\theta,\Delta\phi=0,r}\ d\Delta\theta},
+    \mathcal{D}\rBrace{\theta_{T}} = \frac{
+    P\rBrace{\theta_{T}}
+    }{
+    \frac{1}{2\pi}\int_{0}^{2\pi}P\rBrace{\theta}d\theta
+    }
 \end{equation}
-measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
-For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
+In the following, as we consider steered (to $\theta_{s}$) arrays, we suppress the DOA dependency such that $\mathcal{D} = \mathcal{D}\rBrace{{\theta_{s}}}$. 
+For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D} = N$.

### 2021-02-15 Modules/sec_prlm_localization.tex
rev03

@@
 In this work, we focus on localization of signal sources in the far-field case, where free space signal propagation is assumed.
-Following the classical methods overview in \cite{krim1996two},localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
+Following the classical methods overview in \cite{krim1996two}, localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
 The spectral based estimators steer the array (mechanically or by beamforming) to a set of DOAs, searching for peaks in the received energy, where each peak is treated as a resolved emitter when greater than a certain threshold.
-This approach of spatial filtering, is considered to suffers from fundamental
+This approach of spatial filtering, is considered to suffer from fundamental
 limitations, namely ``its performance, is directly dependent upon the physical size of the array (the aperture), regardless of the available data collection time and signal-to-noise ratio (SNR)`` \cite{krim1996two}.
-Although trials were made to increase the resolution of an array given a certain aperture, this notion remains intact to these days.
-In this contribution we tackle this statement as will shown in Chapter\ref{chap:firstchap}.
-The later approach, of parameter estimation assumes a physical model of the experimental scenario, which serve a basis for the development of spatio-temporal estimators which takes advantage not only from the spatial diversity but also from the temporal information collected via sequential time separated snapshots in order to increase the overall SNR.
-Such methods, not only enabled the increase of spatial filtering resolution, but also allowed the implementation of data processing algorithms, more sophisticated than a mere search with a steered array.
+Although trials were made to increase the resolution of an array given a certain aperture, this limitation remained intact.
+In this contribution we tackle this issue as will shown in Chapter\ref{chap:firstchap} by introducing a spatial feedback.
+The later approach, of parameter estimation assumes a physical model of the experimental scenario, which serve a basis for the development of spatio-temporal estimators which take advantage not only from the spatial diversity but also from the temporal information collected via sequential time separated snapshots in order to increase the overall SNR.
+Such methods, not only enabled the increase of spatial filtering resolution, but also allowed the implementation of data processing algorithms, which are more sophisticated than a mere search with a steered array.
 In the following, a basic overview of some classical algorithms are presented.
-The earliest localization algorithms, which date back to world war II, are the beamforming based, e.g. the conventional Bartlet \cite{van2004optimum} and Capon's \cite{capon1969high} beamformers.
-Early examples of parametric estimators, are the Maximum-Likelihood \cite{macdonald1969optimum,schweppe1968sensor} and Maximum-Entropy \cite{ables1974maximum} which assume a known PDF to the received signal and estimate the desired parameters according to empirical results and fitting the closest matching PDF.
+The earliest localization algorithms, which date back to world war II, are beamforming based, e.g. the conventional Bartlet \cite{van2004optimum} and Capon's \cite{capon1969high} beamformers.
+Early examples of parametric estimators, are the Maximum-Likelihood \cite{macdonald1969optimum,schweppe1968sensor} and Maximum-Entropy \cite{ables1974maximum} which assume a known PDF to the received signal and estimate the desired parameters according to sampled data and fitting the closest matching PDF.
 Until the mid- 1970's, direction finding techniques required knowledge of the array directional sensitivity pattern in analytical form, and the task of the antenna designer was to build an array of antennas with a prespecified sensitivity pattern.
 Trying to relax the need for such accuracy, also serving as the origin of the sub-space based approach, was the Multiple SIgnal Classification (MUSIC) \cite{schmidt1986multiple} algorithm.
-MUSIC essentially relieved the designer from the need of accurate radiation patterns by exploiting the reduction in analytical complexity that could be achieved by calibrating the array.
-Thus, the array response calculation task was reduced to that of measuring and storing the response. 
+MUSIC essentially relieved the designer from designing accurate radiation patterns by introducing the concept of array calibration.
 Although MUSIC did not mitigate the computational complexity of solution to the DOA estimation problem, it did extend the applicability of high-resolution DOA estimation to arbitrary arrays of sensors.
@@
 In addition to using the rotational invariance of the signal sub-space eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - thus mitigating numerical problems associated with ill-conditioned matrices.
-Following state-of-the-art developments \cite{BOOK-classicalAndModernDOA}, the sub-space based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm MUSIC} but also new and interesting approaches emerged
+Following state-of-the-art developments \cite{tuncer2009classical}, the sub-space based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm_MUSIC} but also new and interesting approaches emerged such as
 \begin{itemize}
-    \item High Order Statistics (HOS, also refereed as cumulants), which extracts more information from the samples' higher order moments, is a very active field of research due to some fundamental issues which are inherently resolved - i.e.
+    \item High Order Statistics (HOS), which extracts more information from the samples' higher order moments, is a very active field of research due to some fundamental issues which are inherently resolved - i.e.
 the Gaussian noise vanishes in the 4th order statistics and the ability to resolve more DOAs than array elements \cite{chevalier2006high}.
-    This approach, being costly in computation effort, became popular probably due to the recently available low-cost powerful computation.
-    \item Inspired by the vast research field of sparse representations some algorithms \cite{nadiri2014localization} use non-Frobenius norm (i.e.
-$L^{p}$ norms where $p<2$), in order improve estimation resolution under high reverberation acoustic scenarios.
+    This approach, being costly in computation effort, became popular probably due to the recently available low-cost powerful computation platforms.
+    \item Inspired by the vast research field of sparse representations, some algorithms \cite{nadiri2014localization} use $L^{p}$ norms (where $p<2$), in order to improve estimation resolution under high reverberation acoustic scenarios.
     \item A very wide and active research field is the concept of cooperative localization related to mobile networks is growing at a very high rate due to the never-ending need for high-bandwidth and low-power communication of the mobile networks.
-    \item Naturally, also many trials of harnessing the promising concept of neural networks are being done, for example \cite{shareef2008localization}.
+    \item Naturally, also many trials of harnessing the promising concept of neural networks are being done, see for example \cite{shareef2008localization}.
 \end{itemize}

### 2021-02-15 Modules/sec_prlm_propWaveField.tex
rev03

@@
 The time domain is represented by $t$.
-An elementary physical phenomenon is the spatial dynamics of waves, referred to as wave-propagation.
+An elementary physical phenomenon is the spatial and temporal dynamics of waves, referred to as wave-propagation.
 The spatial location is noted by the Cartesian coordinates $\rBrace{x,y,z}$ or the three dimensional spherical coordinates $\rBrace{r,\phi,\theta}$, where $0 \leq \phi \leq 2\pi$, $0 \leq \theta \leq \pi$ are the azimuth and elevation angles, respectively.
+The relations between the coordinates are given in Fig.~\ref{fig_coordinates}.
 % Finally, let $f\rBrace{t,\vecnot{r}}$ denote the time-space representation of the input signal, where $\vecnot{r}$ is the radius-vector in the three-dimensional system. 
 % The relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
-Denoting $t$ as the time, the time-space representation of the a signal is $f\rBrace{t,\vecnot{r}}$ or , where the relations between the Cartesian and spherical coordinates are given in Fig.~\ref{fig_coordinates}.
+Denoting $t$ as the time, the time-space representation of the a signal is $f\rBrace{t,\vecnot{r}}$.
 % $f\rBrace{t,x,y,z}$ describes the signal impinging the microphone array. 
@@
 \end{figure}
-A possible solution to \eqref{eq_prlm_waveEq}, $f_p\rBrace{t,x,y,z}$, may be of a complex exponential form:
+A possible solution to \eqref{eq_prlm_waveEq}, $f_p\rBrace{t,x,y,z}$, is a complex exponential of the form:
 \begin{equation}
 \label{eq_prlm_waveEq_pSol}
-f_p\rBrace{t,x,y,z} = A\exp{j\rBrace{\omega{t}-k_{x}x-k_{y}y-k_{z}z}}
+f_p\rBrace{t,x,y,z} = A\exp\rBrace{j\rBrace{\omega{t}-k_{x}x-k_{y}y-k_{z}z}}
 \end{equation}
-Where $A$ is a complex constant, $\omega$ denotes temporal radial frequency and $k_{x}x,k_{y},k_{z}$ are real constants. 
-Plugging \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} results in the \emph{monochromatic plane wave}:
+Where $A$ is a complex constant, $\omega$ denotes temporal radial frequency, $\vecnot{k} = \vBrace{k_{x},k_{y},k_{z}}^{T}$ denote the \emph{wavelength vector} and $k_{x},k_{y},k_{z}$ are real constants.
+Indeed, plugging \eqref{eq_prlm_waveEq_pSol} into \eqref{eq_prlm_waveEq} results in the \emph{monochromatic plane wave} satisfying:
 \begin{equation}
 \label{eq_prlm_waveEq_subs}
-k_{x}^{2}-k_{y}^{2}-k_{z}^{2} = \frac{\omega^{2}}{c^{2}}.
+k_{x}^{2}+k_{y}^{2}+k_{z}^{2} = \frac{\omega^{2}}{c^{2}}.
 \end{equation}
-Using the plane wave notation emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same wave value and the vector notation of \eqref{eq_prlm_waveEq}'s solution is
+Using the plane wave notation 
 \begin{equation}
 \label{eq_prlm_waveEq_finSol}
-f\rBrace{t,\vecnot{x}}=A\exp{j\rBrace{\omega{t}-\vecnot{k}\vecnot{x}}}.
+f\rBrace{t,\vecnot{x}}=A\exp{j\rBrace{\omega{t}-\vecnot{k}^{T}\vecnot{x}}},
 \end{equation}
-where $\vecnot{k}\vecnot{x}=constant$ are planes of constant wave value.
+emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same wave value where $\vecnot{k}\vecnot{x}=constant$ are planes of constant wave value.
 The wave propagation can be described as the traveling of the planes, stating that small steps of both space $\delta{\vecnot{x}}$ and time $\delta{t}$ result in the same wave value i.e.
@@
 \begin{equation}
-\omega\delta{t}-\vecnot{k}\delta\vecnot{x}=0.
+\omega\delta{t}-\vecnot{k}^{T}\delta\vecnot{x}=0.
 \end{equation}
-Assuming $\delta\vecnot{x}$ and $\vecnot{k}$ have the same direction, $\vecnot{k}\delta\vecnot{x} = \abs{\vecnot{k}}\abs{\delta\vecnot{x}}$ and $\frac{\delta{\vecnot{x}}}{\delta{t}} = \frac{\omega}{\abs{\vecnot{k}}}$, where $\frac{\delta{\vecnot{x}}}{\delta{t}}$ can designate the propagation speed of the plane wave.
+Assuming $\delta\vecnot{x}$ and $\vecnot{k}$ have the same direction, $\vecnot{k}^{T}\delta\vecnot{x} = \abs{\vecnot{k}}\abs{\delta\vecnot{x}}$ and $\frac{\abs{\delta{\vecnot{x}}}}{\delta{t}} = \frac{\omega}{\abs{\vecnot{k}}}$, where $\frac{\abs{\delta{\vecnot{x}}}}{\delta{t}}$ can designate the propagation speed of the plane wave.
 Since $\vecnot{k}$ and $\omega$ are related by $\abs{\vecnot{k}}^{2}=\frac{\omega^{2}}{c^{2}}$, we have
@@
 \label{eq_prlm_waveEq_stepsEq}
-\frac{\delta{\vecnot{x}}}{\delta{t}}=c,
+\frac{\abs{\delta{\vecnot{x}}}}{\delta{t}}=c.
 \end{equation}
-where $c>0$ is the wave velocity in the medium.
-The \emph{wavelength} ($\lambda$) denote the distance the plane wave propagated during a single temporal period of $T=\frac{2\pi}{\omega}$.
-Let $\vecnot{k}$ denote the \emph{wavelength vector}. 
+The \emph{wavelength} ($\lambda$) denotes the distance the plane wave propagates during a single temporal period of $T=\frac{2\pi}{\omega}$.
 Its magnitude $\abs{\vecnot{k}}$ expresses the number of cycles in radians per meter of length that the plane wave has exhibited in the propagation direction.
@@
 \begin{equation}
-\lambda=\delta{\vecnot{x}}=\frac{2\pi}{\abs{\vecnot{k}}}.
+\lambda=\abs{\delta{\vecnot{x}}}=\frac{2\pi}{\abs{\vecnot{k}}}.
 \end{equation}
@@
 \par For example, in the context of ULA, assuming far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.
-The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which is will be shown to provide clues for the signal's DOA as can be seen in Fig.~\ref{fig_ULA_sketch}.
+The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which will be shown to provide clues for the signal's DOA as can be seen in Fig.~\ref{fig_ULA_sketch}.
 \begin{figure}[h!]
@@
 \end{figure}
-When also considering the narrowband scenario, where TOA difference is merely phase shift, it seems obvious that by phase measuring, one should be able to extract the DOA from the spatially sampled data.
+When also considering the narrowband scenario, where TOA difference is merely phase shift, it seems obvious that by measuring phases, one should be able to extract the DOA from the spatially sampled data.

### 2021-02-15 Modules/sec_prlm_sensorArrays.tex
rev03

@@
 The samples from the entire array are then fused together in order to extract the underlying data.
-The spatial diversity of the sampled data allows the extraction of spatial features which are not accessible by mere temporal analysis of the data.
-Sensor arrays are used in numerous applications, ranging from source localization, through communication, medical applications, astronomy etc.
+The spatial diversity of the sampled data allows the extraction of spatial features.
+Sensor arrays are used in numerous applications, ranging from source localization, communication, medical applications, astronomy etc.
 \par 
@@
 area, weight and carrying platform, through performance related considerations such as accuracy, spatial selectivity, signal to noise ratio and even the financial aspect.
-Obviously, the most fundamental array specification is its geometry, for it dictates the spatial relations between simultaneous samples measured by the array's sensors, which also greatly influences the processing methods of the raw-data.
-A basic example of sensor array is the ULA (see Fig.~\ref{fig_ULA}), where its elements are uniformly spaced on a straight line with distance $d$ between a sensor to its nearest neighbour.
+The most fundamental array specification is its geometry, for it dictates the spatial relations between simultaneous samples measured by the array's sensors, which also greatly influences the processing methods of the raw-data.
+A basic example of a sensor array is the ULA (see Fig.~\ref{fig_ULA}), where its elements are uniformly spaced on a straight line with distance $d$ between each pair of sensors.
 Considering an array of $N$ elements, the sensors are positioned at
@@
 \end{equation}
-where $n$ is the sensors index; $p_{n}$ denotes the position of the $n$'th sensor,$p_{0} = 0$ corresponds to the left-hand side of the array.
+where $n$ is the sensors index; $p_{n}$ denotes the position of the $n$'th sensor, $p_{0} = 0$ corresponds to the left-hand side of the array as illustrated in Fig.~\ref{fig_ULA}.
 \begin{figure}[h!]
@@
 \end{figure}
-\par To proper formulate the discussed additional spatial information when using sensor array based processors, a quick overview on wave propagation is due and presented in the following section (Sec.~\ref{sec:prlm_propWaveField}).
+\par To properly formulate the discussed additional spatial information when using sensor arrays, a quick overview on wave propagation is due and presented in the following section (Sec.~\ref{sec:prlm_propWaveField}).

### 2021-02-15 Modules/sec_prlm_timeSpaceSig.tex
rev03

@@
 where $p_{n}$ denotes the $n$-th sensor position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
-Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($y\rBrace{t}$) is expressed by:
+Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
 \begin{equation}
@@
 where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
-Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at angular frequency $w$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
-The wave signals spatially sampled by the sensor array inputs are
+Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
+The wave signal, spatially sampled by the sensor array inputs is
 \begin{equation}
@@
 where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
-Considering narrowband signals (i.e. $s\rBrace{t}=\exp^{-j\omega{}t}$), the time delay $\tau$ translates to a mere phase shift and an auxiliary dephased \emph{steering vector} takes the form of
+Considering narrowband signals, the time delay $\tau$ translates to a mere phase shift and the \emph{steering vector} takes the form of
 \begin{equation}
-\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\rBrace{N-1}\omega\tau}}^{T}.
+\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\omega\tau\rBrace{N-1}}}^{T}.
 \end{equation}

### 2021-02-15 Modules/sec_rangeSensitivityError.tex
rev03

@@
 \label{sec_sim}
-In this section, we investigate $\HrTPr$ for the general case, where also range misalignment phase term $\dPhi$ is possibly non zero.
+In this section, we investigate $\HrTPr$ for the general case, where the range misalignment phase term $\dPhi$ may also be non zero.
 In Fig.~\ref{fig_hDUDTContour}, we plot $\abs{\HrTPr}$ in logarithmic scale, with respect to both steer and range misalignments.
 Close inspection of the range error related beampattern behaviour sheds light to some important points.
-First, we notice that although setting $r\to1$ (i.e., close to perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks.
-Next, as evident from \eqref{eq_generalH}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).
+First, we notice that although setting $r\to1$ (i.e., close to a perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks.
+Next, as evident from \eqref{eq_narmalized_pattern}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).
 To establish our final observation, we first recall that

### 2021-02-15 Modules/sec_stability.tex
rev03

@@
 As a preliminary to the following performance discussion in Sec.~\ref{sec_Performance}, we start with simple temporal simulations of the feedback beamformer.
-In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms which are then used to define some basic simulation scenarios that will be thoroughly investigated throughout this chapter.
+In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
+Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.
 After the error terms have been defined, we first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.
-\subsection{Error terms}
-In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
-Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
-\begin{equation}\label{eq:alpha_beta_hat}
-\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
-\end{equation}
-introducing the estimated steering vector 
-\begin{equation}\label{eq:d_hat}
-\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
-\end{equation}
-Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
-\begin{equation}\label{eq:SF_CB}
-    %\resizebox{.894\linewidth}{!}
-    {
-        \begin{split}
-            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
-        \end{split}
-    }
-\end{equation}
-where \[
-\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
-\]
-is the normalized Dirichlet kernel and
-\[
-\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
-r\triangleq g/\hat{g},
-\]
-are defined as the DOA, range and gain error terms respectively.
-In the following, four fundamental scenarios are considered:
-\begin{itemize}
-    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
-    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
-    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
-\end{itemize}
-\subsection{Temporal Simulations}
+\subsection{Gain mismatch}
 The analogy of the feedback beamformer to the temporal IIR architecture raises some fundamental questions that should be addressed.
@@
 To begin with, we should first ask what does ``stability`` means.
-Interestingly, the system's response of \eqref{eqn:GeneralFeedbackTransferFunction} is not frequency dependent, for it is exclusively governed by spatial parameters.
-Therefore, in the absence of any previous related work on spatial feedback, we find that the commonly used Bounded-Input-Bounded-Output (BIBO) stability is appropriate. 
-As such, assuming the \emph{Perfect alignment} scenario, we identify $r$ in \eqref{eq:SF_CB} to be the most influential for determining the system's stability for it controls the response's denominator - e.g.
+% Interestingly, the system's response of \eqref{eqn:GeneralFeedbackTransferFunction} is not frequency dependent, for it is exclusively governed by spatial parameters.
+% Therefore, 
+In the absence of any previous related work on spatial feedback, we find that the commonly used Bounded-Input-Bounded-Output (BIBO) stability is appropriate. 
+% As such, assuming the \emph{Perfect alignment} scenario, we identify $r$ in \eqref{eq:SF_CB} to be the most influential for determining the system's stability for it controls the response's denominator - e.g.
 for $r<1$ the denominator will never be nullified.
-As anticipated from \eqref{eq:SF_CB} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude does not converge to a finite value.
-Also noticeable is the increase in the final amplitude value as $r$ increases.
-In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value with respect to $r$ and find that the increase is substantial as $r$ increases towards 1.
+To this end, the gain mismatch
+\begin{equation}
+    r=g/\hat{g}
+\end{equation}
+and plug \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, giving rise to
+\begin{equation}\label{eq:SF_CB_gainMismatch}
+    %\resizebox{.894\linewidth}{!}
+    {
+        \begin{split}
+            H_{\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}}
+            = &\frac{
+            g\vecnot{\beta}_{\text{CB,opt}}^{H}\vecnot{d}\exp{\rBrace{-j\phi}}
+            }{
+            1 - g\vecnot{\alpha}_{\text{CB,opt}}^{H}\vecnot{d}\exp{\rBrace{-j\phi}}
+            }\\
+            = &\frac{    
+            \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
+            }{
+            1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
+            }\\
+            = & \frac{r}{1-r}.
+        \end{split}
+    }
+\end{equation}
+As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.
+In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value after 100 iterations of the signal being retransmitted between the array and the target of interest and find that the final values substantially increase as $r\to{1}$.
 This issue will have to be taken into consideration when one designs such an array for practical applications but is outside the scope of this work.
@@
         tics=10,trim=0 0 0 0]{./Media/fig_stabilization.png}
-            \put (46, -5){\rotatebox{0}{$t/2\tau_{pd}$}}
+            \put (46, -5){\rotatebox{0}{$t/\tau_{pd}$}}
             \put (-6, 38){\rotatebox{90}{$\abs{z\rBrace{t}}$}}
@@
     Simulating a 3 element ULA based feedback beamformer, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
-    The horizontal axis ($t/2\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
+    The horizontal axis ($t/\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
     }
@@
 This phenomenon corresponds with the propagation latency of the signal's round trip to the target and back.
-In each iteration the spatial focusing is increased, together with the received amplitude, as can be seen in Fig.~\ref{fig_beamThinning}.
-The reader may notice that the $t=1\cdot{}\tau_{pd}$ plot is actually the conventional beampattern, for the feedback signal has not yet reimpinged the array.
+In each iteration the mainlobe sharpens, as can be seen in Fig.~\ref{fig_beamThinning}.
+The reader may notice in Fig.~\ref{fig_beamThinning} that the $t=1\cdot{}\tau_{pd}$ plot is actually the conventional beampattern, for the feedback signal has not yet re-impinged the array.
 \begin{figure}[t!]
@@
     \caption{
-    Simulation of same setup as in Fig.\ref{fig_stability}.
-    We set $r=0.9$ and plot the beampattern for various simulation times.
+    Simulation of same setup as in Fig.\ref{fig_stability} with $r=9$.
+    Several simulations are conducted, where each is simulated with different duration.
+    It actually illustrates the forming of the final beampattern in time as our analysis assumes infinite duration. 
     }
@@
     \caption{
-    Simulation of same setup as in Fig.\ref{fig_stability}.
-    For each $r$ (the horizontal axis), we plot the final received amplitude in dB.
+    After simulating same setup of Fig.\ref{fig_stability} for a fined grid of $r$, we plot the final received amplitude in dB with respect to $r$.
     }
@@
 To better understand the phenomenon, we plot the settling time's $r$ dependency in Fig.~\ref{fig_stabilityDur}.
-Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:futureResearch}.
+Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:conclusion}.
 \begin{figure}[t!]
@@
         tics=10,trim=0 0 0 0]{./Media/fig_stabilizationDur.png}
-            \put (-3, 35){\rotatebox{90}{$t/2\tau_{pd}$}}
+            \put (-3, 35){\rotatebox{90}{$t/\tau_{\text{pd}}$}}
             \put (51, -5){\rotatebox{0}{$r$}}
@@
     For each $r$ (the horizontal axis), we plot the time (the vertical axis) where the received amplitude entered the $1\%$ sleeve around its final value.
-    The plotted time is also normalized as in Fig.\ref{fig_stability}.
+    The plotted time is also in units of $\tau_{\text{pd}}$ normalized as in Fig.\ref{fig_stability}.
     }
@@
 We choose to add one more note, regarding the influence of the array's number of elements.
-Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e.
+Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e.
 the settling time remains the same as $N$ increases.
+\subsection{Phase mismatch}
+Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
+As we intend to compare the results to \cite{van2004optimum}, we consider a ULA, introducing its estimated steering vector
+\begin{equation}\label{eq_est_d_ULA}
+\hat{\vecnot{d}} = \vBrace{1, \exp{\rBrace{-\hat{\theta}}}, \hdots, \exp{\rBrace{-\rBrace{N-1}\hat{\theta}}}}^{T}.
+\end{equation}
+Observing that
+\begin{equation*}
+    \begin{split}
+        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
+        =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\
+        =&\ \frac{\exp{\rBrace{jN\Delta\theta}}-1}{\exp{\rBrace{j\Delta\theta}}-1}\\
+        =&\ \frac{\exp{\rBrace{jN\Delta\theta/2}}}{\exp{\rBrace{j\Delta\theta/2}}}\cdot
+        \frac{\exp{\rBrace{jN\Delta\theta/2}}-\exp{\rBrace{-jN\Delta\theta/2}}}
+        {\exp{\rBrace{j\Delta\theta/2}}-\exp{\rBrace{-j\Delta\theta/2}}}\\
+        =&\ \exp{\rBrace{j\rBrace{N-1}\Delta\theta/2}}\cdot
+        \frac{\sin{\rBrace{N\Delta\theta/2}}}
+        {\sin{\rBrace{\Delta\theta/2}}},
+    \end{split}
+\end{equation*}
+we define Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernel}) as
+\[
+D_{\test{orig}}\rBrace{x,N}\triangleq\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
+\]
+and the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})
+\[
+\D{x}{N}=\frac{1}{N}D_{\test{orig}}\rBrace{x,N}=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}.
+\]
+Now, \eqref{eqn:GeneralFeedbackTransferFunction} takes the form of
+\begin{equation}\label{eq:alpha_beta_hat}
+    \begin{split}
+        H_{\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}}
+        = &\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}.
+    \end{split}
+\end{equation}
+\begin{figure}[t!]
+    \begin{center}
+        \begin{overpic}[width=0.65\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
+            \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
+            \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
+            \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
+            \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
+            \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
+            \put (50, 2.5){\rotatebox{0}{$x$}}
+            \put (12, 5){\rotatebox{0}{$-\pi$}}
+            \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
+            \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
+            \put (89, 5){\rotatebox{0}{$\pi$}}
+        \end{overpic}
+    \end{center}
+    \caption{
+    Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
+    }
+    \label{fig_DirichletKernel}
+\end{figure}
+\begin{figure}[t!]
+    \begin{center}
+        \begin{overpic}[width=0.65\linewidth, 
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/DirichletKernelsNorm.png}
+            \put (3, 32){\rotatebox{90}{$D\rBrace{x,N}$}}
+            \put (86.5, 47){\rotatebox{80}{\tiny{$D\rBrace{x,7}$}}}
+            \put (81.5, 47){\rotatebox{80}{\tiny{$D\rBrace{x,5}$}}}
+            \put (84.5, 30){\rotatebox{-86}{\tiny{$D\rBrace{x,10}$}}}
+            \put (75.5, 30){\rotatebox{-70}{\tiny{$D\rBrace{x,2}$}}}
+            \put (50, 2.5){\rotatebox{0}{$x$}}
+            \put (12, 5){\rotatebox{0}{$-\pi$}}
+            \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
+            \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
+            \put (89, 5){\rotatebox{0}{$\pi$}}
+        \end{overpic}
+    \end{center}
+    \caption{
+    Few illustrations of the normalized Dirichlet kernel, for $N$ values of 2,5,7 and 10.
+    }
+    \label{fig_DirichletKernelNorm}
+\end{figure}
+In the following, four fundamental scenarios are considered:
+\begin{itemize}
+    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
+    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
+    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
+    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
+\end{itemize}

### 2021-02-15 Modules/stabilityEnhancement_freqPairApproach.tex
rev03

@@
-As demonstrated in the previous section, the beampattern \eqref{eq_generalH} is sensitive to range errors.
+As demonstrated in the previous section, the beampattern \eqref{eq_narmalized_pattern} is sensitive to range errors.
 We now propose an architecture which obtains the desired beampattern $\Hr_{\Delta\theta,\Delta\phi\to0,r}$ even for relatively large range errors $\Delta R_{\text{rt}}$.
@@
 \subsection{Intuition}
-Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_generalH} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies.
+Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_narmalized_pattern} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies.
 Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
@@
     \item \textbf{Antenna length}\\
-    As described in \cite{barclay2003propagation}, although low ($<30_{\text{Khz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
+    As described in \cite{barclay2003propagation}, although low ($<30_{\text{KHz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength is large ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
     \item \textbf{Signal bandwidth}\\
@@
 \end{itemize}
-Henceforth, inspired by known trigonometrical identities where mathematical of two harmonics produces new frequencies which are the sum (or subtraction) of the original signals, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies.
-In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved.
+Henceforth, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies. 
+In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved  as it will depend on the frequency difference $\omega_{1}-\omega_{2}$.
 
@@
 where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
-Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again.
+Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_narmalized_pattern}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again.
 This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
@@
 % where $\vdHatI{1}$ is the estimated steering vector, as in \eqref{eq:d_hat}.
-With this choice, and similarly to \eqref{eq:SF_CB}, \eqref{eqn_H_DF_general} becomes
+With this choice, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes
 \begin{equation}

### 2021-02-15 front/abbrevs.tex
rev03

--- 2020-10-31 front/abbrevs.tex
@@
 \abbreviationsAndNotation{
-\begin{tabular}{p{2cm}@{:\quad}l}
-QED & quod erat demonstratum \\
-$c$ & the speed of light \\
-$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
-\end{tabular}
+\begin{longtable}{p{2cm}@{:\quad}l}
+DOA & Direction of arrival \\
+RADAR & RAdio Detection And Ranging \\
+FIR & Finite impulse response \\
+IIR & Infinite impulse response \\
+ULA & Uniform linear array \\
+FIM & Fisher information matrix \\
+SNR & Signal to noise ratio \\
+MUSIC & Multiple signal classification (algorithm)\\
+RHS & Right hand side \\
+FB & Feedback beamformer \\
+SF & Single frequency \\
+DF & Dual frequency \\
+HPBW & Half power beamwidth \\
+PDF & Probability density function \\
+CRLB & Cram\'er Rao lower bound \\
+CRB & Cram\'er Rao bound \\
+PCA & Principal component analysis \\
+ICA & Independent components analysis \\
+MVDR & Minimum Variance Distortionless Response \\
+UWB & Ultra wide band \\
+HOS & High order statistics \\
+$\vecnot{v}$ & A vector \\
+$v_{i}$ & The $i$-th element of vector $\vecnot{v}$ \\
+$\vecnot{v}^{T}$ & Transpose of vector $\vecnot{v}$ \\
+$\vecnot{v}^{*}$ & Conjugate of vector $\vecnot{v}$ \\
+$\vecnot{v}^{H}$ & Hermitian (conjugated) transpose of vector $\vecnot{v}$ \\
+$\vecnot{A}$ & A Matrix \\
+$A_{i,j}$ & The $i,j$-th element of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{T}$ & Transpose of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{*}$ & Conjugate of matrix $\vecnot{A}$ \\
+$\vecnot{A}^{H}$ & Hermitian (conjugated) transpose of matrix $\vecnot{A}$ \\
+$d$ & Array's inter-element spacing \\
+$\omega$ & Radial frequency \\
+$c$ & Wave's propagation velocity \\
+$\lambda$ & Wavelength \\
+$\theta_{d}$ & Geometrical angle \\
+$\theta$ & Electrical phase \\
+\vecnot{d} & Steering vector \\
+$B$ & beampattern \\
+$R$ & Distance to target \\
+$z\rBrace{t}$ & Array's temporal output \\
+$Z\rBrace{\omega}$ & Array's frequency-domain output \\
+$\mathcal{D}$ & Directivity \\
+$\mathcal{H}$ & Normalized beampattern \\
+\end{longtable}
 }

### 2021-02-15 main/chap_futureResearch.tex
Sent as draft No.2
rev03

@@
 In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
-As mentioned in Sec.~\ref{sec:setup}, we assumed a single target stationary scenario where the target's location is fixed.
-Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios which obviously should be followed by a combined general scenario of multiple dynamic targets performance scenario.
+As mentioned in Sec.~\ref{sec_introduceFeedback}, we assumed a single stationary target scenario where the target's location is fixed.
+Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios.
 Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
 We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
-\section{Dynamic target}
+\subsection{Dynamic target}
 \label{sec_future_dynamic}
 \input{Modules/sec_future_dynamic}
-\section{Multi-target scenario}
+\subsection{Multi-target scenario}
 \label{sec_future_multiTarget}
 \input{Modules/sec_future_multiTarget}
-\section{Waveform modifications}
+\subsection{Waveform modifications}
 \label{sec_future_wavfrom}
 \input{Modules/sec_future_wavfrom}
-\section{Coefficients quality criteria}
+\subsection{Coefficients quality criteria}
 \label{sec_future_coef}

### 2021-02-15 main/intro.tex
rev03

@@
 The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
-\par Early algorithms for DOA estimation were based on the beamforming concept \cite{krim1996two}, where the array's reception beam is steered (mechanically or electronically) to multiple directions in search of received energy peaks which are interpreted as valid emitters.
-One notable improvement to the convectional beamformer \cite{van2004optimum} was Capon's beamformer  (aka MVDR in acoustics related literature) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain
-in the "look direction".
+\par Early algorithms for direction of arrival (DOA) estimation were based on the beamforming concept \cite{krim1996two}, where the array's reception beam is steered (mechanically or electronically) to multiple directions in search of received energy peaks which are interpreted as valid emitters.
+One notable improvement to the convectional beamformer \cite{van2004optimum} was Capon's beamformer  (aka minimum variance distortionless response (MVDR) in acoustics related literature) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain
+in the desired direction.
 \par The most practically used approach in DOA estimators, referred as the sub-space based estimation, involves invariant sub-spaces analysis of observed covariance matrices.
@@
 However, the tremendous interest in the subspace approach is mainly due to the introduction of the
-MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection assuming that the noise space is orthogonal to the array manifold.
-It is interesting to note that while earlier works were mostly derived in the context of time series analysis and later applied to the sensor array problem, MUSIC was indeed originally presented as a DOA estimator.
-\par A Less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the statistical based ML approach which tries to find the most probable DOA assuming a known PDF.
+MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise space is orthogonal to the signal subspace.
+It is interesting to note that while earlier works were mostly derived in the context of time series analysis and only later applied to the sensor array problems, MUSIC was originally presented as a DOA estimator.
+\par A less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.
 Though this approach served as a basis for extensive research, leading to more advanced concepts such as the ICA \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
-Adding the fact that sub-optimal methods such as MUSIC were proven achieve the CRB under some practical assumptions (e.g.
-non-coherent signals) \cite{stoica1989music}, such methods (i.e.
-the sub optimal estimators) are substantially more common in practice.
+Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the CRB under some practical assumptions (e.g.
+non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice.
 \par In pursuit of spatial performance improvement, namely higher spatial separation and selectivity of arriving signals, many approaches were suggested.  
-One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
+One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist, by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.
 \par Using a similar approach, the $2q$-MUSIC algorithm \cite{chevalier2006high}, enables the use of $N^{2q}$ ``virtual elements'', by calculating the $q$'th order statistics.
@@
 In both methods, after a certain amount of time, the system refreshes the spatial filter coefficients, trying to better suppress the received noise.
-As in many adaptive processing applications, the two methods rely on steepest descend optimization, which expose the adaptive processing approach to errors related to optimization parameters choices such step size etc.
+As in many adaptive processing applications, the two methods rely on steepest descend optimization, which exposes, the adaptive processing approach to errors related to optimization parameters choices such step size etc.
 \par In \cite{van1988beamforming}, ULA based beamforming and temporal FIR filtering are shown to be mathematically analogous, where the DOA acts as the spatial version of temporal frequency.
-Inspired by this analogy, which is thoroughly discussed in Sec.~\ref{sec:prlm_FIR_IIR}, we were motivated to find the spatial counterpart of the temporal IIR filter, both from academic curiousness and the known advantages of the IIR filter's frequency (DOA by analogy) response, hoping to gain spatial performance by finding the right architecture.
+Inspired by this analogy, which is thoroughly discussed in Sec.~\ref{sec:prlm_FIR_IIR}, we were motivated to find the spatial counterpart of the temporal IIR filter, both from academic curiousness and due to the known advantages of the IIR filter's performance.
 Therefore we formulated a question, ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?'' which served as a guide throughout our research.
@@
     \end{center}
-     \caption{Referring to consecutive sub arrays' output as sequential output of the same ULA.}
+     \caption{In \cite{wen2013extending} subsections on a single large ULA are used to approximate an IIR response}
     \label{fig_intro_wen2}
 \end{figure}
-Obviously, the former approach is very sensitive to the synthetic delay accuracy and involves temporal domain processing which we try to avoid in this work to achieve purely spatial processing.  
+Obviously, the former approach is very sensitive to the synthetic delay accuracy and involves temporal domain processing (which we try to avoid in this work in order to achieve purely spatial processing).
 Also, close inspection of the latter approach reveals that even though the sub-arrays are each weighted separately, each sensor's output is eventually linearly weighted when taking into account all related sub-arrays.
 Clearly, this is just another possible implementation of basic FIR like ULA spatial processor, so in both cases, there is no true spatial feedback between the array and the source of interest.
-\par Other interesting works \cite{Hum2009BeamformingFilters,madanayake2008speed} in the field of ultra-wideband (UWB) treat the spatial and temporal diversity, which reside in multiple consecutive snapshots of the array output, as if the signal is sampled in two independent temporal frequencies.
-Inspired by \cite{bruton1985three}, the authors show that impinging plane waves are represented as straight lines tilted according to their DOA and suggest methods to design line filters in the spatio-temporal plane.
-In \cite{Hum2009BeamformingFilters}, the authors also address the fact that ideal straight line filter may not be achieved due to the fact that the filter is periodic in both frequencies, causing the 2D frequency response the ``bend`` close to the sampling frequencies (see Fig.~\ref{fig_intro_UWB_bend}).
+\par Other interesting works \cite{Hum2009BeamformingFilters,madanayake2008speed} in the field of ultra-wideband (UWB) signals treat the spatial and temporal diversity, which reside in multiple consecutive snapshots of the array output, as if the signal is sampled in two independent temporal frequencies.
+Inspired by \cite{bruton1985three}, the authors show that impinging plane waves are represented as straight lines tilted according to their DOA and suggest methods to design line filters in that spatio-temporal plane.
+In \cite{Hum2009BeamformingFilters}, the authors also address the fact that ideal straight line filter is mathematically unachievable due to spatio-temporal frequencies periodicity.
+This issue manifests as a ``bend`` close to the sampling frequencies (see Fig.~\ref{fig_intro_UWB_bend}).
 \begin{figure}[ht!]
@@
 To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
-\par The novelty, compared to traditional array processing, is the incorporation of spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
+\par The novelty, compared to traditional array processing, is by incorporating spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
 Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
@@
 Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
-\par In the followings, we elaborate in Chapter~\ref{chap:prelims} on some relevant theoretic concepts which serve as the foundation of this presentation.
-Then our novel architecture is presented and analysed in Chapter.~\ref{chap:firstchap} followed by a thorough concluding discussion on the findings and future research in Chapter.~\ref{chap:futureResearch}.
+\par In the followings, we elaborate in Chapter~\ref{chap:prelims} on some relevant theoretic concepts which serve as the foundation of this work.
+Then, our novel architecture is presented and analysed in Chapter.~\ref{chap:firstchap} followed by a thorough concluding discussion of the findings and future research directions in Chapter.~\ref{chap:conclusion}.

### 2021-02-15 main/prelims.tex
rev03

@@
 In Sec.~\ref{sec:prlm_localization}, we further focus the spatial filtering discussion to localization and overview some of its fundamentals.
-Following the FIR/IIR filters related discussion in Chapter.~\ref{chap:intro}, we further elaborate and compare the two architectures in Sec.~\ref{sec:prlm_FIR_IIR}.
-To complete the basics overview, we also discuss array performance measuring in Sec.~\ref{sec:prlm_array_perf} following the classical localization related literature.
+Following the FIR/IIR filters related issue, which was previously mentioned in Chapter.~\ref{chap:intro}, we further elaborate and compare the two architectures in Sec.~\ref{sec:prlm_FIR_IIR}.
+To complete the basics overview, we also discuss array performance measures in Sec.~\ref{sec:prlm_array_perf} following classical array processing literature.
 % \begin{definition}

### 2021-04-23 Modules/abstractEnglish_LOCAL.tex
Before final comments

@@
-% State-of-the-art array processing methods, ranging from high-order statistics to adaptive configuration, require costly computing efforts in pursuit for spatial performance improvement.
 The general field of array processing has been thoroughly studied throughout several decades.
 The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications.
-The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
+The array size and the number of its elements have significant influence on the achievable array performance, such as signal to noise ratio (SNR) improvement, spatial separation capabilities, directivity, array gain, source localization, etc.
 \par 
-Considering localization related applications, several processing approaches are to be found.
-The most basic approach is \emph{beamforming}, i.e steering the array to different parts of the arena in search of objects.
-Another approach, which is probably the most commonly used, is the subspace-based processing which tries to identify input signals that fit into the array's manifold using the orthogonal projection concept.
-Statistical processing, although costly in terms of computation effort, is also in use, ranging from maximum-likelihood (ML) related schemes to higher-order-statistics (HOS) using cumulants.
-Newer approaches which are still in research stage use neural networking and sparsity-based algorithms.
+Localization applications are divided to several groups, each featuring a different approach for estimating the spatial parameters of objects in the arena.
+The most basic approach is \emph{beamforming}, where the arena (or a part of it) is continuously scanned by steering (mechanically or electronically) the array to all possible directions in search for objects.
+Another approach, more commonly used, is the subspace-based processing which exploits the orthogonality between the array manifold (i.e.
+the array's excitations set of impinging planewaves from all directions) and the noise subspace.
+In this scheme the input signal is projected onto the array manifold - thus mitigating non directional noise interference. 
+Statistical processing, although costly in terms of computation effort, is also in use.
+One important example is the maximum-likelihood (ML) approach which assumes a known probability density function (PDF) for the input signal or the noise.
 \par
-Although much researched, in this work we revisit the \emph{beamforming} approach.
-ULA based beamforming and temporal finite impulse response (FIR) filtering are mathematically analogous, where the DOA acts as the spatial version of temporal frequency.
-Inspired by this analogy, we search for the spatial counterpart of the temporal infinite impulse response (IIR) filter.
-To this end, we arbitrarily choose to use localization related problem formulation and suggest a feedback based approach, featuring low complexity and high spatial performance in the mere excess of integrating a transmitter to the array.
+In this work we revisit the \emph{beamforming} approach.
+Inspired by the analogy between spatial processing with uniform linear array (ULA) and temporal finite impulse response (FIR) filtering, we search for the spatial counterpart of the temporal infinite impulse response (IIR) filter.
+To this end, we formulate a localization problem and suggest a feedback based approach, featuring low complexity and high spatial performance in the mere excess of integrating a transmitter to the array.
 Considering RADAR-like arrays, the transmitter is already in place, hence a mere processing modification suffices.
+\par  
 Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.
-Hence a spatial loop is created, which is shown to be equivalent of enlarging the array's aperture in terms of spatial resolution.
-Also notable is that the achievement of the exclusive IIR-like beampattern is purely done in the spatial domain while avoiding any temporal processing to the signal.
+In this manner, a spatial loop is created, which is shown to be equivalent of enlarging the array's aperture in terms of spatial resolution.
 \par 

### 2021-04-23 main/intro.tex
Before final comments

@@
 \label{chap:intro}
+\section{Background and Motivation}
 The general field of array processing has been thoroughly studied throughout several decades.
@@
 However, the tremendous interest in the subspace approach is mainly due to the introduction of the
-MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise space is orthogonal to the signal subspace.
+MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise sub space is orthogonal to the signal subspace.
 It is interesting to note that while earlier works were mostly derived in the context of time series analysis and only later applied to the sensor array problems, MUSIC was originally presented as a DOA estimator.
 \par A less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.
-Though this approach served as a basis for extensive research, leading to more advanced concepts such as the ICA \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
+Though this approach served as a basis for extensive research, leading to more advanced concepts such as the independent component analysis (ICA) \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
 Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the CRB under some practical assumptions (e.g.
@@
 The basic concept was minimization of the inter-element spacing redundancy in order to increase the overall resolution.
-% The main advantage of the first (i.e.
-virtual array) over the latter (i.e.
-minimum redundancy) is the obtainable analytical expression for the improvement in spatial selectivity when using virtual arrays.
-% In the minimum redundancy approach no such expression is available.
-% On the other side, the computation effort is considerably higher when the 2-nd order statistics are computed.
-Although the $q$-th order statistics based approach promises substantial improvement, both noise sensitivity and impractical computation amount are dominant drawbacks, limiting the usage of such methods in practical applications.
+Although the $q$-th order statistics based approach promises substantial improvement, both noise sensitivity and impractical computation costs are dominant drawbacks, limiting the usage of such methods in practical applications.
 \par Adaptive processing schemes \cite{frost1972algorithm,manolakis2000statistical}, being a wide and active research area, were also suggested trying to adaptively estimate and suppress the noise component in impinging signals by minimization of the receiver's output energy with some constraints.
@@
 In both methods, after a certain amount of time, the system refreshes the spatial filter coefficients, trying to better suppress the received noise.
-As in many adaptive processing applications, the two methods rely on steepest descend optimization, which exposes, the adaptive processing approach to errors related to optimization parameters choices such step size etc.
+As in many adaptive processing applications, the two methods rely on steepest descend optimization, which exposes the adaptive processing approach to errors related to optimization parameters choices such step size etc.
 \par In \cite{van1988beamforming}, ULA based beamforming and temporal FIR filtering are shown to be mathematically analogous, where the DOA acts as the spatial version of temporal frequency.
@@
 \end{figure}
+\section{Overview of the Thesis}
+In this thesis, we propose a new feedback based beamformer architecture which acts as an actual spatial IIR filter while avoiding any temporal processing to the signal.
+We aim to guide the reader thorough the key stages of the research where in each stage, a sufficient background is provided followed by the solution composition.
+\par As this research does not closely follows any former work, some of analysis must be rigorously justified, hence we turn to classic literature as guidance.
+As an example, for the configuration of the array, we use the Fisher Information Matrix (FIM) aiming to maximize the residing spatial information in the system.
+\par After presenting the basic approach with it's complementary adjusted classic spatial analysis, we find that it is inherently sensitive to range estimation errors.
+We then suggest a more robust solution which is based on our conclusions from previous analysis.
+With the robust solution in hand, we present simulations and compare it to the basic conventional beamformer and the initial more sensitive approach.
+As expected, we find that it outperforms them, proving to perform well also in low signal to noise ratios (SNR).
+\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
+$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
+Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
+\section{Main Contributions}
 \par In this contribution, we present a low-complexity sensor array processing approach which achieves the desired spatial domain exclusive IIR-like beampattern, while avoiding any temporal processing of the signal.
-To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
+To this end, we arbitrarily choose to formulate the problem in the context of localization, hence our goal is to estimate the direction and the range of some target of interest. 
 \par The novelty, compared to traditional array processing, is by incorporating spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
@@
 Furthermore, as opposed to the passive target case (i.e., a target which merely reflects the impinging signal), one may consider a cooperative target, which receives, enhances and re-transmits the signal back to the array.
-\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
-$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
-Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
-\par In the followings, we elaborate in Chapter~\ref{chap:prelims} on some relevant theoretic concepts which serve as the foundation of this work.
-Then, our novel architecture is presented and analysed in Chapter.~\ref{chap:firstchap} followed by a thorough concluding discussion of the findings and future research directions in Chapter.~\ref{chap:conclusion}.
+\section{Thesis Organization}
+\par This thesis is organized as follows.
+In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize on the localization field of research and finalize with the basic concepts which drive the motivation for this research.
+\par In Chapter.~\ref{chap:firstchap} the basic feedback beamformer is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.
+Simulations are also provided, supporting the analytical analysis.
+\par In Chapter.~\ref{chap:conclusion} we discuss the results and conclude our findings. We finalize by also proposing some leads to future research.

### 2021-04-26 Modules/abstractHebrew.tex
After Israel's comments

--- 2020-12-25 Modules/abstractHebrew.tex
@@
-שיערוך מאפיינים מתוך מדידות הינו מושא לעניין רב עוד מראשית ימי המדע, כשחוקי הפיזיקה נלמדו בעזרת תצפיות ומדידות.
-עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון להלחמת מידע ממספר מדידות בו זמנית.
+שיערוך מאפייני אותות הינו מושא לעניין רב עוד מראשית ימי המדע, כשחוקי הפיזיקה נלמדו בעזרת תצפיות ומדידות.
+עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון לעיבוד מקבילי של מידע ממספר רגשים.
 אחד התחומים בהם עלה משמעותית הצורך בדיוק השיערוך, היה העיבוד המרחבי - קרי שיערוך פרמטרים מרחביים מתוך מדידות. 
-עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה.
+עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה בדמות רדאר ה
+\textenglish{Mammut}
+שנבנה על ידי הגרמנים לזיהוי מוקדם של מטרות טסות בגבהים עד 8 ק"מ ומרחקים של עד 300 ק"מ.
 \par
-מאז ועד ימינו, עיבוד מערכי רגשים
+מאז ועד ימינו, עיבוד מערכי חיישנים
 \textenglish{(sensors arrays)}
-התפתח לכדי תחום מחקר הנותן מענה למגוון רחב של בעיות, ביניהן איכון (מערכות רדאר, סונאר ונגזרותיהן) מטרות על סמך אותות שנפלטים או מוחזרים מהן - הנחשבת לותיקה ביותר בתחום.
+התפתח לכדי תחום מחקר הנותן מענה למגוון רחב של בעיות, ביניהן איכון (מערכות רדאר, סונאר ונגזרותיהן) מטרות על סמך אותות שנפלטים או מוחזרים מהן.
 עם השנים והתקדמות המדע, נעשה שימוש במערכים לפתרון בעיות נוספות.
 \par
-במערכות תקשורת, הצורך בסינון מרחבי הוא מן המעלה הראשונה, שכן במציאות מרובת המשדרים והמקלטים, במידה ולא היה שימוש במערכים, הפרעות הדדיות היו מונעות את פענוח האות הנקלט.
-במקביל, לא רק סינון אלא גם הכוונת אלומת השידור הפכה לאפשרית בזכות השימוש בו-זמנית במספר רב של משדרים
+במערכות תקשורת לדוגמא, הצורך בסינון מרחבי הוא מן המעלה הראשונה לאור המציאות מרובת המשדרים והמקלטים. במקביל, לא רק סינון אלא גם הכוונת אלומת השידור התאפשרה בזכות השימוש במערכי מופע
 \textenglish{(phased array)}
@@
 \par
-מוקד עניין נוסף, הינו האפליקציות הרפואיות שהתאפשרו בזכות השימוש במערכים. 
+מוקד עניין נוסף, הינו האפליקציות הרפואיות. 
 בדימות רפואית למשל, כדוגמת 
 \textenglish{CT, MRI, EEG}
-וכו', רופאים מייצרים באופן בלתי פולשני מודלים של פנים גוף האדם המשמשים לפענוח מצבים רפואיים ותכנון מדויק של הליכים - ובכך מונעים סיכון רב מהמטופלים.
+וכו', רופאים מייצרים מודלים של פנים גוף האדם באופן בלתי פולשני.
+מודלים אלו משמשים לפענוח מצבים רפואיים ותכנון מדויק של הליכים - ובכך מונעים סיכון רב מהמטופלים.
 \par
-בעשורים האחרונים, עם הגחת הטלפונים הניידים לעולם, עלה הצורך בסינון אותות דיבור מתוך בליל מקורות אקוסטיים, שכן הדובר כבר אינו נמצא בין כותלי ביתו בשקט יחסי.
+בעשורים האחרונים, עם הגחת הטלפונים הניידים לעולם, עלה הצורך בסינון אותות דיבור טבולים ברעש, שכן הדובר כבר אינו נמצא בין כותלי ביתו בשקט יחסי.
 לשם כך, המכשירים הניידים מצוידים במערכי מיקרופונים אשר מסננים את אות הדובר על פי כיוון הגעתו ומאפייניו הסטטיסטיים.
 \par
-דוגמא מעניינת נוספת בתחום האסטרונומיה, שם נוכחו המדענים כי תצפיות אופטיות מוגבלות ביכולתן ובכמות המידע שניתן להפיק מהן, היא השימוש במערכי אנטנות, הנפרשים על פני שטחים עצומים בכדי לממש טלסקופים רבי עוצמה ודיוק, העושים שימוש באותות אלקטרומגנטיים באורכי גל שלא בתחום הנראה.
+דוגמא מעניינת נוספת בתחום האסטרונומיה, הינה מערכי אנטנות רדיו הנפרשים על פני שטחים עצומים בכדי לממש טלסקופים רבי עוצמה ודיוק. 
 \par
 ככלל, בין תחומי מחקר אלו, מתקיימת תרומה הדדית רחבת היקף ורב המסקנות העולות מכל תחום בנפרד משמשות בסיס למחקר ופיתוח בתחומים אחרים ולהפך. 
-בנוסף, בבסיס כל מגוון תחומי המחקר, ישנו שימוש בתחום מחקר ותיק ועשיר עוד יותר - הוא השימוש במסננים בכדי להפיק את המידע הרצוי (אות או מאפיין) מהאות הנקלט.  
+בנוסף, בבסיס כל מגוון תחומי המחקר, ישנו שימוש במסננים בכדי להפיק את המידע הרצוי (אות או מאפיין) מהאות הנקלט.  
 \par
@@
 \textenglish{FIR}
-הינו מישקול וסכימת סט דגימות לכדי מוצא "מסונן".
-השני לעומת זאת, משתמש בהיזון חוזר, ובכך מייצר תגובה אינסופית להלם - ועל כך שמו
+שהינו מישקול וסכימת סט דגימות לכדי מוצא "מסונן".
+השני לעומת זאת, משלב היזון חוזר, ובכך מייצר תגובה אינסופית להלם 
 \textenglish{IIR}
-.
-לשם תכן מסננים מסופק מפרט התגובה בתדר, בו מפורטים התדרים שאמורים לעבור, אלו שאמורים לחוות דיכוי ומידת הדיכוי הרצויה.
-על פי מפרט זה, המתכנן בוחר את סוג המסנן ואת המשקלות שבו.
-בעוד המסנן בעל התגובה הסופית להלם מאפשר הימנעות מעיוותים באות (תכונת הפאזה הלינארית - קרי ללא דיספרסיה), המסנן בעל התגובה האינסופית מאפשר חיסכון משמעותי (לעיתים בסדרי גודל) במשאבים לשם עמידה במפרט דומה.
-איך לכך, בהתאם לאפליקציה ולמפרט, על המתכנן לבחור במסנן המתאים ביותר תוך הבאה בחשבון של כלל השיקולים - משאבים, עלות וכו'.
+וידוע כי הוא מאפשר חיסכון משמעותי (לעיתים בסדרי גודל) במשאבים.
 \par
-עד כה, למיטב ידיעתנו, בכל תחומי המחקר המערבים עיבוד מרובה רגשים אבן הבניין היחידה שבשימוש הינה המסנן בעל התגובה הסופית בתדר, שכן בין אם מעורב שידור במערכת (כמו במכם, תקשורת, דימות רפואית וכו') ובין אם לאו, אין היזון חוזר של האות הנקלט חזרה אל מושא המדידה.
-עובדה זו עוררה את תהייתנו ובעטייה חיפשנו את המקביל המרחבי למסנן בעל התגובה האינסופית - בכדי ליהנות מהיתרונות שבו.
-במהלך המחקר המקדים, נוכחנו לדעת כי שאלה זו התעוררה גם במוחם של חוקרים אחרים, אך לאחר בחינת פרסומיהם נוכחנו כי פתרונם אינו מממש בצורה מלאה את רעיון ההיזון החוזר אלא מנסה למצוא דרכים עקיפות - בכך חושף עצמו לשגיאות ועיוותים משמעותיים.
+עד כה, למיטב ידיעתנו, בכל תחומי המחקר המערבים עיבוד מערכי חיישנים אבן הבניין היחידה שבשימוש הינה המסנן בעל התגובה הסופית בתדר, שכן בין אם מעורב שידור במערכת (כמו במכם, תקשורת, דימות רפואית וכו') ובין אם לאו, אין היזון חוזר של האות הנקלט חזרה אל מושא המדידה.
+עובדה זו עוררה את תהייתנו ובעטייה חיפשנו את המקביל המרחבי למסנן בעל התגובה האינסופית.
+במהלך המחקר המקדים, נוכחנו לדעת כי שאלה זו התעוררה גם במוחם של חוקרים אחרים, אך הפתרונות שהציעו אינם מממשים רעיון ההיזון.
 \par
-לשם המחשת הפתרון שמוצע, עבודה זו מתמקדת בתחום האיכון - בסביבה אקוסטית או אלקטרו מגנית.
-מוצעת איפוא, מערכת מבוססת מערך לינארי בעל מרווחים אחידים בין הרגשים
-\textenglish{ULA}
-כאשר בראשיתו, בנוסף על הרגש,  ישנו משדר.
-על פניו, מערכת דומה למכ"ם, השולח אות ומשערך את מיקומי מטרות על פי האות החוזר.
-החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק אות מלאכותי הנוצר ע"י המערכת אלא משולב בו האות המסונן הנקלט ע"י המערך.
+בעבודה זו אנו מציעים פתרון המשלב, בנוסף על חיישני הקליטה, משדר לשם יצירת ההיזון החוזר.
+על פניו, מערכת דומה למכ"ם, הפולט אות ומשערך את מיקומי מטרות על פי האות החוזר.
+החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק עותק יחיד הנוצר ע"י המערכת אלא משולבים בו הדי האותות שהוחזרו מן המטרה.
 ניתוח המערכת מרמז כי ע"י שליטה במשקלות המסנן המייצר את האות החוזר, ניתן להפיק את היתרונות הרבים הטמונים במסנן בעל התגובה האינסופית.
 \par
-לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי - אבן נגף משמעותית בנסיון למציאת הפתרון.
+מחקירת המערכת המתקבלת, מצאנו שיפור משמעותי במגוון מאפיינים כגון רוחב אונה, הנחתת אונות צד ודיכוי רעשים איזוטרופים יעיל - כלומר מערך בעל כיווניות גבוהה.
+לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי לשגיאת טווח - אבן נגף משמעותית בנסיון למציאת הפתרון.
 עם זאת, לשמחתנו, נמצא גם פתרון פשוט וזול יחסית לבעיה, המגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.
 הדמיות וניתוח נוספים מאשררים כי הפתרון קביל ומשיג תוצאות שבתרחישים אידיאלים נוטות לכדי שלמות.
-בנוסף על האיכון הזוויתי שחווה שיפור משמעותי בביצועיו, כתופעת לוואי, מתכנן המערך יכול גם לקבוע גבולות מרחק לסינון ובכך לייצר מערכת איכון שמזהה לא רק כיוון אלא מיקום מדויק של מטרות.

### 2021-04-26 Modules/sec_future_multiTarget.tex
Sent as draft No.2
rev03
After Israel's comments

@@
     \label{eqn:ftr_dyn_temp}
-    x_{n}(t) = \sum_{i=0}^{i=P-1}{\rBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
+    x_{n}(t) = \sum_{i=0}^{i=P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
     +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
@@
     \item Maximal number of simultaneously detected targets with respect to N
-    \item Performance of independent super-positioned dual-frequency (see Sec.~\ref{sec_app}) systems.
+    \item Independent beamforming per target with multiple transmitters steering the feedback signal. 
 \end{itemize}

### 2021-04-26 Modules/sec_prlm_array_perf.tex
After Israel's comments

@@
 \begin{equation}
-B\rBrace{\theta} = 20\log_{10}\abs{Z\rBrace{\theta}}.
+B\rBrace{\theta} = \abs{Z\rBrace{\theta}}.
 \end{equation}
-The beampttern is commonly presented in a graphical manner as exemplified in Fig.~\ref{fig_common_bps}.
+The beampttern is commonly presented in a graphical manner with log scale as exemplified in Fig.~\ref{fig_common_bps}.
 It's characteristics, such as main lobe width, position and attenuation of sidelobes are then analysed and compared between different schemes.
@@
 \begin{equation}\label{eq_D}
-    \mathcal{D}\rBrace{\theta_{T}} = \frac{
-    P\rBrace{\theta_{T}}
+    \mathcal{D}\rBrace{\theta_{d}} = \frac{
+    P\rBrace{\theta_{d}}
     }{
     \frac{1}{2\pi}\int_{0}^{2\pi}P\rBrace{\theta}d\theta
-    }
+    }.
 \end{equation}
-In the following, as we consider steered (to $\theta_{s}$) arrays, we suppress the DOA dependency such that $\mathcal{D} = \mathcal{D}\rBrace{{\theta_{s}}}$. 
-For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D} = N$.
+% In the following, as we consider steered (to $\theta_{s}$) arrays, we suppress the DOA dependency such that $\mathcal{D} = \mathcal{D}\rBrace{{\theta_{s}}}$. 
+and for uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D} = N$.

### 2021-04-26 Modules/sec_prlm_localization.tex
After Israel's comments

@@
 positional parameters estimation of impinging signal which is measured by an array of sensors.
+\par 
 In this work, we focus on localization of signal sources in the far-field case, where free space signal propagation is assumed.
@@
 Although trials were made to increase the resolution of an array given a certain aperture, this limitation remained intact.
-In this contribution we tackle this issue as will shown in Chapter\ref{chap:firstchap} by introducing a spatial feedback.
+In this contribution we tackle this issue as will shown in Chapter.~\ref{chap:firstchap} by introducing a spatial feedback.
+\par
 The later approach, of parameter estimation assumes a physical model of the experimental scenario, which serve a basis for the development of spatio-temporal estimators which take advantage not only from the spatial diversity but also from the temporal information collected via sequential time separated snapshots in order to increase the overall SNR.
@@
 In the following, a basic overview of some classical algorithms are presented.
+\par
 The earliest localization algorithms, which date back to world war II, are beamforming based, e.g. the conventional Bartlet \cite{van2004optimum} and Capon's \cite{capon1969high} beamformers.
@@
 Until the mid- 1970's, direction finding techniques required knowledge of the array directional sensitivity pattern in analytical form, and the task of the antenna designer was to build an array of antennas with a prespecified sensitivity pattern.
-Trying to relax the need for such accuracy, also serving as the origin of the sub-space based approach, was the Multiple SIgnal Classification (MUSIC) \cite{schmidt1986multiple} algorithm.
+\par
+Trying to relax the need for such accuracy, also serving as the origin of the subspace based approach, was the Multiple SIgnal Classification (MUSIC) \cite{schmidt1986multiple} algorithm.
 MUSIC essentially relieved the designer from designing accurate radiation patterns by introducing the concept of array calibration.
 Although MUSIC did not mitigate the computational complexity of solution to the DOA estimation problem, it did extend the applicability of high-resolution DOA estimation to arbitrary arrays of sensors.
-Another, probably even more important breakthrough, was the introduction of the orthogonal array manifold noise spaces, thus allowing the use of orthogonal projection in order to mitigate the noise effects.
+An important breakthrough, was the introduction of the orthogonal array manifold noise spaces, thus allowing the use of orthogonal projection in order to mitigate the noise effects.
+\par
 Another important parametric approach related algorithm, is the ESPRIT (Estimation of Signal Parameters via Rotational Invariance Techniques) \cite{ESPRIT}, serving as a milestone in the path to state-of-the-art algorithms.
-In addition to using the rotational invariance of the signal sub-space eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - thus mitigating numerical problems associated with ill-conditioned matrices.
-Following state-of-the-art developments \cite{tuncer2009classical}, the sub-space based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm_MUSIC} but also new and interesting approaches emerged such as
+In addition to using the rotational invariance of the signal subspace eigenvectors, it also reduced computation and storage costs (especially in the multi-dimensional estimation case) by replacing the covariance matrix calculation and eigendecomposition by a relaxed partial singular value decomposition (SVD) which is employed on the data itself without squaring it - thus mitigating numerical problems associated with ill-conditioned matrices.
+\par
+Following state-of-the-art developments \cite{tuncer2009classical}, the subspace based algorithms are still modified and adjusted to specific scenarios as in \cite{LpNorm_MUSIC} but also new and interesting approaches emerged such as
 \begin{itemize}

### 2021-04-26 Modules/sec_prlm_propWaveField.tex
After Israel's comments

@@
 \label{eq_prlm_waveEq_pSol}
-f_p\rBrace{t,x,y,z} = A\exp\rBrace{j\rBrace{\omega{t}-k_{x}x-k_{y}y-k_{z}z}}
+f_p\rBrace{t,x,y,z} = A\exp\vBrace{j\rBrace{\omega{t}-k_{x}x-k_{y}y-k_{z}z}}
 \end{equation}
@@
 \end{equation}
-emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same wave value where $\vecnot{k}\vecnot{x}=constant$ are planes of constant wave value.
+where $ \vecnot{x} = \vBrace{x,y,z}^{T} $ emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same phase value where $\vecnot{k}\vecnot{x}=constant$ are planes of constant phase value.
 The wave propagation can be described as the traveling of the planes, stating that small steps of both space $\delta{\vecnot{x}}$ and time $\delta{t}$ result in the same wave value i.e.
@@
         \begin{overpic}[width=0.6\linewidth, 
-        %grid, 
+        % grid, 
         tics=10,trim=0 0 0 0]{./Media/arraySketch.png}
-        \put(20,45){\rotatebox{-50}{\tiny{Impinging wavefront}}}
         \put(33.25,2.25){\rotatebox{0}{\tiny{$d$}}}
-        \put(52.25,26){\rotatebox{38}{\tiny{$c\tau=d\cos{\theta}$}}}
-        \put(49,15.75){\rotatebox{0}{$\theta$}}
+        \put(16,26){\rotatebox{-36}{\tiny{$c\tau=d\cos{\theta}$}}}
+        \put(45.5,15.75){\rotatebox{0}{$\theta$}}
         \put(15,7){\rotatebox{0}{\tiny{0}}}
@@
         \put(80,7){\rotatebox{0}{\tiny{$N-1$}}}
-        \put(44,36){\rotatebox{38}{\tiny{$t=\rBrace{N-1}\tau$}}}
-        \put(57,36){\rotatebox{38}{\tiny{$t=\rBrace{N-2}\tau$}}}
-        \put(70,36){\rotatebox{38}{\tiny{$t=\rBrace{N-3}\tau$}}}
-        \put(92,25){\rotatebox{38}{\tiny{$t=0$}}}
+        \put(2,24){\rotatebox{-36}{\tiny{$t=0$}}}
+        \put(2,34){\rotatebox{-36}{\tiny{$t=\tau$}}}
+        \put(2,44){\rotatebox{-36}{\tiny{$t=2\tau$}}}
+        \put(40,44){\rotatebox{-36}{\tiny{$t=\rBrace{N-1}\tau$}}}
         \end{overpic}

### 2021-04-26 Modules/sec_prlm_timeSpaceSig.tex
After Israel's comments

@@
         tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
-        \put(20,65){\rotatebox{-50}{\tiny{Impinging wavefront}}}
-        \put(49,33.25){\rotatebox{0}{$\theta$}}
+        \put(45,33.25){\rotatebox{0}{$\theta$}}
         \put(15,25){\rotatebox{0}{\tiny{0}}}
@@
 \label{eq_prlm_timeSpace_outputVec}
-\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
+\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
 \end{equation}
@@
 \end{equation}
-As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal sub space in the noiseless scenario.
+As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal subspace in the noiseless scenario.

### 2021-04-26 main/intro.tex
After Israel's comments

@@
 in the desired direction.
-\par The most practically used approach in DOA estimators, referred as the sub-space based estimation, involves invariant sub-spaces analysis of observed covariance matrices.
+\par The most practically used approach in DOA estimators, referred as the subspace based estimation, involves invariant subspace analysis of observed covariance matrices.
 Early research include PCA and errors-in-variables time series analysis \cite{krim1996two}.   

### 2021-05-14 Modules/Spatial_IIR-MathDerivations.tex
After Israel's comments
Acronyms added

@@
-As in Sec.~\ref{sec:prlm_FIR_IIR}, an $N$-element ULA with inter-element spacing $d$ is considered.
-Its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$ and we set $\vpi{0}$ as the axis reference point while the target of interest is positioned at $\vpt$.
-We also place a transmitter at $\vpi{0}$, where transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds and $R = \norm{\vpt-\vpi{0}}, c$ are the target's range propagation velocity of the signal in the medium respectively.
+As in Sec.~\ref{sec:prlm_FIR_IIR}, an $N$-element array is considered and some notations are revisited for an easier reading of this chapter.
+The array's $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$ and we set $\vpi{0}$ as the axis reference point while the target of interest is positioned at $\vpt$ and define its distance from the array as $R = \norm{\vpt-\vpi{0}}$.
+The gain of the reimpinging signal is denoted as $g$ which encapsulates both propagation related gain and the target's radar cross section (RCS). 
+We also place a transmitter at $\vpi{0}$, where the transmitted signal $s$, is reflected back from the target and re-impinges the array with a total delay of $\tau_{\text{pd}}=2R/c$ seconds, denoting $c$ as the propagation velocity of the signal in the medium.
 Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
@@
         \begin{split}
-            x_{n}(t) = g\rBrace{s\rBrace{t-\tau_{pd}-\tau_{n}}
+            x_{n}(t) = g\vBrace{s\rBrace{t-\tau_{pd}-\tau_{n}}
             +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd}-\tau_{n}}}},
@@
             X_{n} =
-            g\rBrace{\F{s}
-            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
+            g\cBrace{\F{s}
+            \exp\vBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
             +\sum_{m=0}^{N-1}
@@
             \alpha^{*}_{m}\F{x}_{m}
-            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
+            \exp\vBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
             }},
@@
         \\
-        &= \frac{\rBrace{I-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}+g\vecnot{d}\vecnot{\alpha}^{H}\exp{\rBrace{-j\omega\tau}}}\vecnot{d}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
+        &= \frac{\rBrace{I-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\vBrace{-j\omega\tau}}+g\vecnot{d}\vecnot{\alpha}^{H}\exp{\vBrace{-j\omega\tau}}}\vecnot{d}}{1-g\vecnot{\alpha}^{H}\vecnot{d}\exp{\rBrace{-j\omega\tau}}}
         \\
         &= \frac{
-        \rBrace{I+\rBrace{\vecnot{d}\vecnot{\alpha}^{H}-\vecnot{\alpha}^{H}\vecnot{d}}g\exp{\rBrace{-j\omega\tau}}}\vecnot{d}
+        \vBrace{I+\rBrace{\vecnot{d}\vecnot{\alpha}^{H}-\vecnot{\alpha}^{H}\vecnot{d}}g\exp{\rBrace{-j\omega\tau}}}\vecnot{d}
         }{

### 2021-05-14 Modules/abstractEnglish_LOCAL.tex
Acronyms added

@@
 The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications.
-The array size and the number of its elements have significant influence on the achievable array performance, such as signal to noise ratio (SNR) improvement, spatial separation capabilities, directivity, array gain, source localization, etc.
+The array size and the number of its elements have significant influence on the achievable array performance, such as \gls{SNR} improvement, spatial separation capabilities, directivity, array gain, source localization, etc.
 \par 
@@
 Statistical processing, although costly in terms of computation effort, is also in use.
-One important example is the maximum-likelihood (ML) approach which assumes a known probability density function (PDF) for the input signal or the noise.
+One important example is the maximum-likelihood (ML) approach which assumes a known \gls{PDF} for the input signal or the noise.
 \par
@@
 A significant improvement in all aspects is shown, while thoroughly discussing the conditions for enhanced performance.
-Considering ideal scenarios, the feedback beamformer virtually achieves an infinite aperture, increasing the available spatial information about the target and significantly improves the array's spatial performance.
+Considering ideal scenarios, the feedback beamformer (FB) virtually achieves an infinite aperture, increasing the available spatial information about the target and significantly improves the array's spatial performance.
 \par

### 2021-05-14 Modules/abstractHebrew.tex
Acronyms added

@@
-שיערוך מאפייני אותות הינו מושא לעניין רב עוד מראשית ימי המדע, כשחוקי הפיזיקה נלמדו בעזרת תצפיות ומדידות.
-עם התקדמות המדע, רמת הדיוק הנדרשת בשיערוך עלתה ובכדי לעקוף את הגבולות התיאורטיים (פורייה למשל), עלה הרעיון לעיבוד מקבילי של מידע ממספר רגשים.
-אחד התחומים בהם עלה משמעותית הצורך בדיוק השיערוך, היה העיבוד המרחבי - קרי שיערוך פרמטרים מרחביים מתוך מדידות. 
-עדויות לכך ניתן למצוא עוד בתקופת מלחמת העולם השניה בדמות רדאר ה
+בעבודה זו מוצגת שיטה חדשנית לעיבוד מרחבי של אותות במערכי חיישנים.
+בבסיס השיטה נעשה שימוש במשוב מרחבי הניזון מהאותות הנקלטים במערך כך שלא מתבצע עיבוד זמני על האות הנקלט כי אם עיבוד מרחבי בלבד.
+מניתוח ביצועי המערך עולה שיפור ניכר ביחס למערכים הידועים.
+לשם נוחות, העבודה מוצגת בהקשר של איכון אך ניתנת להרחבה למגוון רחב של אפליקציות המשלבות עיבוד מרחבי של אותות ע"י מערכי חיישנים. 
+\par
+עיבוד מערכי חיישנים הינו תחום מחקר ענף הנותן מענה למגוון רחב של בעיות ועדויות מוקדמות לשימוש בו ניתן למצוא עוד בתקופת מלחמת העולם השניה בדמות רדאר ה
 \textenglish{Mammut}
 שנבנה על ידי הגרמנים לזיהוי מוקדם של מטרות טסות בגבהים עד 8 ק"מ ומרחקים של עד 300 ק"מ.
+במערכות תקשורת לדוגמא, הצורך בסינון מרחבי הוא מן המעלה הראשונה לאור המציאות מרובת המשדרים והמקלטים. בנוסף, הכוונת אלומת השידור מתאפשרת בזכות השימוש במערכי מופע
+\textenglish{(phased array)}
+בכך מושגים חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.
+בדימות רפואית כדוגמת 
+\textenglish{CT, MRI, EEG}
+וכו', רופאים מייצרים מודלים של פנים גוף האדם באופן בלתי פולשני ע"י שימוש בעיבוד מרחבי מבוסס מערכי חיישנים.
+בטלפונים הניידים מצויים מערכי מיקרופונים אשר מסננים את אות הדובר על פי כיוון הגעתו ומאפייניו הסטטיסטיים.
+בתחום האסטרונומיה, מערכי אנטנות רדיו הנפרשים על פני שטחים עצומים משמשים הלכה למעשה טלסקופים רבי עוצמה ודיוק.
+ככלל, בין תחומי מחקר אלו, מתקיימת תרומה הדדית רחבת היקף, כך שמסקנות העולות מתחום כלשהו לעיתים קרובות משמשות בסיס למחקר ופיתוח בתחומים אחרים.
 \par
-מאז ועד ימינו, עיבוד מערכי חיישנים
-\textenglish{(sensors arrays)}
-התפתח לכדי תחום מחקר הנותן מענה למגוון רחב של בעיות, ביניהן איכון (מערכות רדאר, סונאר ונגזרותיהן) מטרות על סמך אותות שנפלטים או מוחזרים מהן.
-עם השנים והתקדמות המדע, נעשה שימוש במערכים לפתרון בעיות נוספות.
+המערך היוניפורמי
+\textenglish{(ULA)}
+בו החיישנים מפוזרים על קו ישר במרחקים קבועים האחד מהשני נחשב למערך הבסיסי בעיבוד המרחבי בשל פשטות העיבוד והיישום שלו.
+בנוסף, מוכרת בספרות ההקבלה בין עיצוב אלומת הסריקה (בהקשר של איכון) של מערך זה לבין תכן מסננים בעלי תגובה סופית להלם
+\textenglish{(FIR)}.
+הקבלה זו נובעת בין היתר מכך שבהינתן כיוון הגעת חזית הגל, הפרש הזמן בין הגעתה מחיישן אחד לשכנו זהה להפרש זמני ההגעה מהחיישן השכן אל הבא אחריו.
+תכונה זו מאפשרת הקבלה בין הפרשי זמני ההגעה לבין יחידות ההשהיה המשמשות למימוש המסננים הזמניים.
+בנוסף, לאחר ניתוח מתמטי, ניתן לראות הקבלה בין כיוון הגעת חזית הגל בעיבוד המרחבי לבין התדר הזמני בעיבוד הזמני, לכן כיוון הגעת הגל נחשבת לתדר המרחבי.
 \par
-במערכות תקשורת לדוגמא, הצורך בסינון מרחבי הוא מן המעלה הראשונה לאור המציאות מרובת המשדרים והמקלטים. במקביל, לא רק סינון אלא גם הכוונת אלומת השידור התאפשרה בזכות השימוש במערכי מופע
-\textenglish{(phased array)}
-ובכך הושגו גם חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.
+קיימת ארכיטקטורה נוספת למסננים, המממשת מסנן בעל תגובה אינסופית להלם 
+\textenglish{IIR}
+ע"י שילוב היזון חוזר.
+מסננים אלו מאופיינים ביעילות מוגברת, כלומר עבור דרישות זהות בתגובת התדר, למסנן ה
+\textenglish{IIR}
+ידרשו פחות משאבים.
+יתרון זה מהווה כבסיס לשאלת המחקר בתזה זו שהיא 
+``מהו המקביל המרחבי למסנן בעל התגובה האינסופית?``, שכן בההקשר של מערכי חיישנים, חיסכון במשאבים מתבטא בהוזלה משמעותית ומאפשר את מזעור המערכת.
 \par
-מוקד עניין נוסף, הינו האפליקציות הרפואיות. 
-בדימות רפואית למשל, כדוגמת 
-\textenglish{CT, MRI, EEG}
-וכו', רופאים מייצרים מודלים של פנים גוף האדם באופן בלתי פולשני.
-מודלים אלו משמשים לפענוח מצבים רפואיים ותכנון מדויק של הליכים - ובכך מונעים סיכון רב מהמטופלים.
+במהלך סקר הספרות, התגלה כי שאלה זו התעוררה גם במוחם של חוקרים אחרים.
+בעבודתו של 
+\textenglish{WEN}~\cite{wen2013extending}
+הוצעו שתי שיטות.
+האחת מערבת שיערוך של כיוון הגעת הגל ויצירה מלאכותית של משוב.
+שיטה זו רגישה לשגיאות שיערוך ומעבר לכך, מערבת עיבוד זמני ולכן אינה מתאימה כתשובה לשאלת המחקר.
+השיטה השניה שהוצעה היתה הגדרת תתי מערכים (חלקים חופפים מהמערך) כך שאל מוצא כל מערך מתייחסים כאל הסחה זמנית של פלט מערך ייחוס כלשהו.
+ניתוח מתמטי מוכיח כי בפועל העיבוד המרחבי לא משתפר היות ובפועל מדובר במערך בעל מספר זהה של  דרגות חופש ל
+\textenglish{FIR}.
 \par
-בעשורים האחרונים, עם הגחת הטלפונים הניידים לעולם, עלה הצורך בסינון אותות דיבור טבולים ברעש, שכן הדובר כבר אינו נמצא בין כותלי ביתו בשקט יחסי.
-לשם כך, המכשירים הניידים מצוידים במערכי מיקרופונים אשר מסננים את אות הדובר על פי כיוון הגעתו ומאפייניו הסטטיסטיים.
+גישה נוספת, אשר מקורה בעיבוד אותו וידאו 
+\cite{bruton1985three}
+, מתייחסת לכיוון ההגעה כאל תדר נוסף.
+במישור הדו תדרי (משמע התדר המרחבי והתדר הזמני) גל מישורי מיוצג ע"י קו ישר המוטה בהתאם לזוית הגעתו אל המערך.
+אי לכך, על מנת להגביר אותות מכיוונים רצויים, יש לתכנן מסננים המעבירים פסים ישרים במישור הדו תדרי התואמים לכיווני הגעה אלו.
+היות ותגובת המסננים מחזורית בשני התדרים, נוצרים עיוותים בקצוות התגובה התדרית ובנוסף לכך, גם שיטה זו מערבת עיבוד זמני לכן אינה מהווה פתרון מספק לשאלת המחקר.
 \par
-דוגמא מעניינת נוספת בתחום האסטרונומיה, הינה מערכי אנטנות רדיו הנפרשים על פני שטחים עצומים בכדי לממש טלסקופים רבי עוצמה ודיוק. 
+כאמור, בעבודה זו מוצג לראשונה עקרון המסנן המשלב משוב מרחבי.
+בעזרת שילוב משדר במערך, משודרת חזרה לזירה גרסה מעובדת של האות הנקלט.
+היות ומניחים שהמטרה מחזירה את האותות המגיעים אליה, השידור בפועל אינו רק של האות הנקלט אלא כולל גם את  הדי האותות שנקלטו בעבר ובכך נוצר חוג סגור בו המידע המרחבי נאסף בהדרגה בכל פעם שהאות חוזר.
+מניתוח המערך עולה כי בשילוב המשוב, תגובתו הינה המקבילה המרחבית למסנן בעל התגובה הזמנית האינסופית.
+בנוסף, עולה כי התגובה אינה מושפעת רק מכיוון הגעת גל כמו במסננים המוכרים, אלא גם ממרחק המטרה מהמערך. 
 \par
-ככלל, בין תחומי מחקר אלו, מתקיימת תרומה הדדית רחבת היקף ורב המסקנות העולות מכל תחום בנפרד משמשות בסיס למחקר ופיתוח בתחומים אחרים ולהפך. 
-בנוסף, בבסיס כל מגוון תחומי המחקר, ישנו שימוש במסננים בכדי להפיק את המידע הרצוי (אות או מאפיין) מהאות הנקלט.  
+בשלב זה, על מנת לקבוע את משקלות המערך, הוגדרו המרחק וכיוון ההגעה כערכים אותם יש לשערך ובהתאם לכך חושבה מטריצת האינפורמציה 
+\textenglish{FIM}.
+בעזרת מטריצה זו נמצאו המקדמים המביאים את האינפורמציה לכדי שיא - בדיעבד, הרחבה טבעית של מקדמי האיסוף הקוהרנטי הבסיסי המוכר בספרות כמסנן הקונבנציונאלי.
+מסנן זה מסיח את הפאזה של האותות המגיעים מחיישנים שונים כך שאות המגיע מכיוון כלשהו יאסף בהתאבכות בונה.
 \par
-בבסיס תורת הסינון, שתי אבני בניין מרכזיות - קרי שני סוגי מסננים.
-האחד, מסנן בעל תגובה להלם סופית 
-\textenglish{FIR}
-שהינו מישקול וסכימת סט דגימות לכדי מוצא "מסונן".
-השני לעומת זאת, משלב היזון חוזר, ובכך מייצר תגובה אינסופית להלם 
-\textenglish{IIR}
-וידוע כי הוא מאפשר חיסכון משמעותי (לעיתים בסדרי גודל) במשאבים.
+ביצועי המערך מנותחים בהקשר של אפליקצית איכון וכוללים ניתוח של רוחב האונה המרכזית, הנחתת אונות הצד וכיווניות המערך.
+לשם ניתוח זה נעשה שימוש בכלים מהספרות הקלאסית על מנת לאפשר השוואה אובייקטיבית אל המערכים המקובלים ללא המשוב.
+כידוע, ביצועי המערך קשורים קשר ישיר למפתח הפיזי שלו לכן לשם המחשת התוצאות, השיפור בביצועי המערך מוצג כהגדלה וירטואלית של מפתח המערך.
+בנוסף על כך הניתוח מראה כי ניתן ליישם את עקרון המשוב בכל מערך ולא רק ב 
+\textenglish{(ULA)}.
 \par
-עד כה, למיטב ידיעתנו, בכל תחומי המחקר המערבים עיבוד מערכי חיישנים אבן הבניין היחידה שבשימוש הינה המסנן בעל התגובה הסופית בתדר, שכן בין אם מעורב שידור במערכת (כמו במכם, תקשורת, דימות רפואית וכו') ובין אם לאו, אין היזון חוזר של האות הנקלט חזרה אל מושא המדידה.
-עובדה זו עוררה את תהייתנו ובעטייה חיפשנו את המקביל המרחבי למסנן בעל התגובה האינסופית.
-במהלך המחקר המקדים, נוכחנו לדעת כי שאלה זו התעוררה גם במוחם של חוקרים אחרים, אך הפתרונות שהציעו אינם מממשים רעיון ההיזון.
-\par
-בעבודה זו אנו מציעים פתרון המשלב, בנוסף על חיישני הקליטה, משדר לשם יצירת ההיזון החוזר.
-על פניו, מערכת דומה למכ"ם, הפולט אות ומשערך את מיקומי מטרות על פי האות החוזר.
-החידוש בהצעה נעוץ בכך שהאות המשודר אינו רק עותק יחיד הנוצר ע"י המערכת אלא משולבים בו הדי האותות שהוחזרו מן המטרה.
-ניתוח המערכת מרמז כי ע"י שליטה במשקלות המסנן המייצר את האות החוזר, ניתן להפיק את היתרונות הרבים הטמונים במסנן בעל התגובה האינסופית.
-\par
-מחקירת המערכת המתקבלת, מצאנו שיפור משמעותי במגוון מאפיינים כגון רוחב אונה, הנחתת אונות צד ודיכוי רעשים איזוטרופים יעיל - כלומר מערך בעל כיווניות גבוהה.
-לאחר מכן, הדמיות ובחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי לשגיאת טווח - אבן נגף משמעותית בנסיון למציאת הפתרון.
-עם זאת, לשמחתנו, נמצא גם פתרון פשוט וזול יחסית לבעיה, המגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.
-הדמיות וניתוח נוספים מאשררים כי הפתרון קביל ומשיג תוצאות שבתרחישים אידיאלים נוטות לכדי שלמות.
+סימולציות בשילוב בחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי לשגיאת טווח.
+היות ושגיאה זו נובעת מהתדרים הנושאים, הוצע שימוש בלתי תלוי בשני תדרים קרובים תוך נסיון לחלץ את המידע המרחבי מהקשר בין האותות הנקלטים.
+הפתרון פשוט וזול יחסית ומגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.
+ניתוח נוסף מאשרר כי הפתרון קביל ומשיג תוצאות שבתרחישים אידיאלים נוטות לכדי שיפור משמעותי בביצועים המרחביים.

### 2021-05-14 Modules/apndx_directivityFit.tex
Acronyms added

@@
 In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were rational.
-Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the feedback beamformer.
+Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the FB.
 In the following, we elaborate on the technicalities of this sweeping process.

### 2021-05-14 Modules/arrayPerformance_beamwidth_LOCAL.tex
Acronyms added

@@
 Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA.
-To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values (actually slicing a vertical column of Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} at $N=100$) and looked for proper polynomial approximation (using MATLAB\textsuperscript{\textregistered}) for the HPBW.
+To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values and looked for proper polynomial approximation (using MATLAB\textsuperscript{\textregistered}) for the HPBW.
 It turns out that the 2-nd order polynomial fit satisfies
@@
 \end{equation}
-Note that for an accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity.
+Note that for an accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity (see Fig.~\ref{fig_feedbackULA_beamwidth_limit_r_dependent}).
 \begin{figure}[t]

### 2021-05-14 Modules/paper_sec_prlms.tex
After Israel's comments
Acronyms added

@@
 In this chapter, we revisit the most basic DOA estimation approach, i.e. beamforming, and present our novel feedback based architecture.
-The feedback based beamforming concept is introduced in Sec.~\ref{sec_introduceFeedback}.
-Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix (FIM).
+The feedback based beamforming concept is elaborated in Sec.~\ref{sec_introduceFeedback}.
+Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the FIM to design the coefficients of the suggested beamformer.
 The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
-Considering noisy setups, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.
+Considering noisy setups, the beamformer's noise sensitivity is exemplified in Sec.~\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer design which is presented in Sec.~\ref{sec_app}.
 
@@
 we propose to use the same concept in the spatial domain.
-The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}.
+The suggested FB architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}.
 The beamformer's output and the feedback signal are synthesized using two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.
 Also, the FB block is marked (dashed line) for later use.
-Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to a plain delay-and-sum (DS) beamformer.
+Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the convectional beamformer (CB) beamformer.
 \begin{figure}[t!]
@@
     \caption{
-    The proposed feedback beamformer.
+    The proposed FB.
     The spatial feedback is obtained by continuous re-transmission of $\Tx$ to the target at $\vpt$.
-    We designate the feedback beamformer block (dashed line) for later use.
+    We designate the FB block (dashed line) for later use.
     }
@@
 \label{sec_Performance}
-In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity.
+In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and were discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity.
 Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.
@@
 \label{subsection_spatialIIR_normBP}
-Applying the \emph{normalized beampattern} concept of Sec.~\ref{sec:prlm_array_perf} to this work, we set $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ giving rise to
+Applying the \emph{normalized beampattern} notation of Sec.~\ref{sec:prlm_array_perf}, we set $\vecnot{\beta}_{\coefSetName}=\vecnot{\alpha}_{\coefSetName}.$ 
+Considering the unavoidable errors mentioned in \ref{subsec_error_trms} (i.e. $\Delta\theta, \Delta\phi$ and $r$), we define $\HrTPr$ as the general scenario normalized array response.
+We choose to normalize the spatial response according to $H_{0}$ (of \eqref{eq:SF_CB_gainMismatch}), giving rise to
 \begin{equation}
@@
         }{
-        H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}
+        H_{0}
         }\\
@@
         &=
-        \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.
+        \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\cBrace{j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}-r\D{\dTheta/2}{N}}.
     \end{split}
@@
 \Hr_{\Delta\theta,\Delta\phi=0,r}=
-             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}},
+             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\cBrace{j\vBrace{\rBrace{N-1}\dTheta/2}}-r\D{\dTheta/2}{N}},
 \end{equation}
@@
 \end{equation}
-\begin{figure}[t]
+\begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
         \begin{center}
-        \begin{overpic}[width=0.75\linewidth, 
+            \begin{overpic}[width=\linewidth, 
                 %grid, 
@@
         \label{fig_directivity}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \begin{center}
+            \begin{overpic}[width=\linewidth, 
+                % grid, 
+                tics=10,trim=0 0 0 0]{./Media/directivityErr.png}
+                    \put (18, 6){\footnotesize{$N$}}
+                    \put (72, 3){\footnotesize{$r$}}
+                    \put (0, 68){\footnotesize{Error}}
+            \end{overpic}
+        \end{center}
+        \caption{The error between numerical calculation and the analytic expression.}
+        \label{fig_directivityErr}
+    \end{minipage}
 \end{figure}
+% \begin{figure}[t]
+%     \begin{center}
+%         \begin{overpic}[width=0.75\linewidth, 
+%         %grid, 
+%         tics=10,trim=0 0 0 0]{./Media/directivity_expr.eps}
+%             \put (20, 10){\footnotesize{$N$}}
+%             \put (72, 6){\footnotesize{$r$}}
+%             \put (16.5, 70){\footnotesize{Numerical integration}}
+%             \put (16.5, 65){\footnotesize{$\rBrace{N-r}/\rBrace{1-r}$}}
+%             \put (-9, 45){\footnotesize{$\mathcal{D}\rBrace{N,r}$}}
+%         \end{overpic}
+%     \end{center}
+%      \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.}
+%     \label{fig_directivity}
+% \end{figure}
 \subsection{Summary}
@@
 Also, in Fig.~\ref{fig_perf} we demonstrate the HPBW and sidelobe attenuation for 3 elements ULA.
-As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA for in Fig.~\ref{fig_perf20}. 
+As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA in Fig.~\ref{fig_perf20}. 
 In Table.~\ref{table_arrayPerfEmp} we show the coherency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.
@@
     \end{center}
-     \caption{Simulating 3 elements ULA based feedback beamformer for $r$ values of 0, 0.3, 0.6 and 0.8.
+     \caption{Simulating 3 elements ULA based FB for $r$ values of 0, 0.3, 0.6 and 0.8.
      The HPBW is marked with vertical red dashed line, where an auxiliary horizontal line of $\abs{H}^{2} = 1/2$ is also provided.
@@
 \begin{table}[h!]
-    \caption{Performances of conventional beamformer $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.
+    \caption{Performances of CB $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.
     Also comparison to expected theoretical expressions is provided.}

### 2021-05-14 Modules/sec_FIM_and_CRLB.tex
Acronyms added

@@
 where $\hat{g}$ is the channel gain estimate.
-Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the \emph{conventional beamformer} (CB) \cite{van2004optimum} which is a mere time shift (phase shift in narrowband signals) of the input signals as if the impinging wave is coming from the array's boresight direction (i.e.
-$\theta_{d}=\pi/2$) as illustrated in Fig.\ref{fig_CB_vanTrees}.
+Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the CB \cite{van2004optimum} which is a mere coherent summation of the feedback signal.
 \begin{figure}[t!]
@@
     % A visualization of the spatial area selectivity concept.
-    The \emph{conventional beamformer} - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.
+    The CB - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.
     }

### 2021-05-14 Modules/sec_conclusions_LOCAL.tex
rev03
Acronyms added

@@
+In this work we have suggested a novel approach to beamforming and localization, which is based on a generating a continuous feedback between the array and the target of interest.
 Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
@@
 It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
-Fortunately, using a dual-frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
-Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
-\par In the following, we overview some interesting leads for future study of the feedback beamforming concept.
+Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
+Also, the DF scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
+\par In the following, we overview some interesting leads for future study of the FB concept.

### 2021-05-14 Modules/sec_future_coef.tex
Sent as draft No.2
rev03
Acronyms added

@@
-As mentioned in Sec.~\ref{sec_introduceFeedback}, the reasoning for the selection of $\vecnot{\alpha}, \vecnot{\beta}$ as the conventional beamformer generalization, was the FIM related information considerations.
+As mentioned in Sec.~\ref{sec_introduceFeedback}, the reasoning for the selection of $\vecnot{\alpha}, \vecnot{\beta}$ as the CB generalization, was the FIM related information considerations.
 Obviously, there are many more possibilities/considerations to choosing the coefficient.
@@
 \begin{itemize}
-    \item Finite word affects
-    \item Nulling of specific DOAs
-    \item Setting all poles in a single DOA may lead to enhanced directivity
-    \item General radiation patterns of the sensors
+    \item Finite word effects
+    \item Nulling of specific DOAs \\
+    For example, it is interesting to see the FB equivalent to Capon's \cite{capon1969high} MVDR. 
 \end{itemize}

### 2021-05-14 Modules/sec_future_dynamic.tex
After Israel's comments
Acronyms added

@@
 The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
-It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time. 
-Hence, we denote the moment of transmission $t_{i}\rBrace{t}$ as
+% It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time.
+\par
+Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, starts with expressing the impinging signal of a single sensor.
+As in the analysis of static target scenario, the signal consists of two contributions, i.e. the reflected emitted signal and the reflected feedback signal.
+Therefore, for each moment $t$, we should resolve the corresponding moment in which the current impinging signals were emitted by the array.
+\par
+To this end, we first denote $t_{\text{ref}}\rBrace{t}$ the moment in which the currently impinging signal was reflected by the target of interest.
+Another auxiliary quantity is reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
 \begin{equation}
-\label{eq_fut_dyn_ti}
-    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ \tau = \frac{R\rBrace{t-\tau}}{c}}
+\label{eq_tRef_relation}
+    t-\frac{R\rBrace{t_{\text{ref}}\rBrace{t}}}{c} = t_{\text{ref}}\rBrace{t}.
 \end{equation}
-With $t_{i}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
+Assuming $t_{\text{ref}}\rBrace{t}$ is resolved, we denote the propagation delay at the reflection moment $\tau_{\text{ref}}\rBrace{t} = R\rBrace{t_{\text{ref}}\rBrace{t}}/c$ and express the emission moment as
+\begin{equation}
+\label{eq_tTX}
+    t_{\text{\tiny{TX}}}\rBrace{t} 
+    = 
+    t_{\text{ref}}\rBrace{t} - \tau_{\text{ref}}\rBrace{t} 
+    =
+    t - 2\tau_{\text{ref}}\rBrace{t}.
+\end{equation}
+With $t_{\text{\tiny{TX}}}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
 \begin{equation}
     \label{eq_fut_dyn_temp}
-    x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
-    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{i}\rBrace{t}}}}.
+    x_{n}(t) = g\rBrace{s\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}
+    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}}}.
 \end{equation}
-For example, consider a target with constant, radial only (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
+\par
+Obviously, to have a closed form expression for $x_{n}(t)$, there should be a model for the target's dynamics (i.e. $\vpt{}$).
+Such an example, is a target with constant radial (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
 It follows that
@@
 \end{equation}
-which when plugged into \eqref{eq_fut_dyn_ti} gives rise to
+which when plugged into \eqref{eq_tRef_relation} gives rise to
 \begin{equation}
     \label{eq_fut_constV_ti}
-    t_{i}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
+    t_{\text{\tiny{TX}}}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
 \end{equation}
@@
     \label{eq_fut_constV_xn}
-    x_{n}(t) = g\rBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
+    x_{n}(t) = g\vBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
     +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
@@
 Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
-It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts as the returning signal is frequency shifted.
+It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts into account.
 % One may consider the following research approaches for further investigation
@@
 %     \item \textbf{Modeling of target's location}
-%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
+%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{\text{\tiny{TX}}}$, $$t_{\text{\tiny{TX}}}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
 %     In this manner, other components may be added to the positional equation.

### 2021-05-14 Modules/sec_future_multiTarget.tex
Acronyms added

@@
-Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious expansion of \eqref{eqn:SingleSensorTemporalEquality} is 
+Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious generalization of \eqref{eqn:SingleSensorTemporalEquality} is 
 \begin{equation}
@@
 \begin{itemize}
-    \item The affects of closely positioned targets
+    \item The effects of closely positioned targets
     \item Localization resolution

### 2021-05-14 Modules/sec_future_wavfrom.tex
Acronyms added

@@
-In practical RADAR related systems, the waveform of choice is pulse (in most cases, chirp) based.
+In modern RADAR related systems, the waveform of choice is pulse based and modulated by CW, or linear/nonlinear frequency scans.
 It holds some obvious advantages over the CW transmission such as
@@
     \item Lower power consumption due to lower transmissions duty cycle. 
-    \item In multi target scenario, there is a smaller chance of interference for the reflected signals from the targets temporally distinct if the targets are in different distances.
-    \item The use of wide band signals may as in RADAR systems, increase spatial resolution in the radial axis.
+    \item The use of wide band signals increases spatial resolution in the radial axis.
 \end{itemize}
-Another interesting option is the using several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions.
+Another interesting option is using several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions.
 By merely selecting harmonic couples and filter coefficients, each harmonics pair is pointed to a specific area.
@@
 \par
-Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned feedback beamformer which simultaneously scans the entire arena.
+Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned FB which simultaneously scans the entire arena.

### 2021-05-14 Modules/sec_prlm_FIR_IIR.tex
After Israel's comments
Acronyms added

@@
 The design of the digital filters is very well established and thoroughly studied research field.
-As stated in \cite{oppenheim1975digital} (and numerous other literature), two key filter types are Finite Impulse Response (FIR) and Infinite Impulse Response (IIR) filters.
-This section will briefly overview the design methods and the analogy of ULA based beamforming to the temporal FIR filtering, as implied in Ch.~\ref{chap:intro}.
+As stated in \cite{oppenheim1975digital} (and numerous other sources), two key filter types are FIR and IIR filters.
+This section will briefly overview the design methods and the analogy of ULA based beamforming to the temporal FIR filtering, as implied in Chapter.~\ref{chap:intro}.
 \begin{itemize}
@@
     \item \textbf{IIR design}\\
-    IIR filters may be viewed as a generalization of the FIR delay-and-sum architecture, where delayed instances of the array's output are fed back to the summation as in Fig.~\ref{fig_IIR_arch}, theoretically generating an infinite loop where each output sample is affected by all past input samples.
+    IIR filters may be viewed as a generalization of the FIR delay-and-sum architecture, where delayed instances of the array's output are fed back to the summation as in Fig.~\ref{fig_IIR_arch}, generating an infinite loop where each output sample is affected by all past input samples.
 \end{itemize}
@@
         %grid, 
-        tics=10,trim=0 0 0 0]{./Media/BASIC_FIR_FILTER_ARCH.png}
-            \put (13, 36){\footnotesize{$s$}}
-            \put (22, 22){\footnotesize{$\beta_{0}$}}
-            \put (38.75, 22){\footnotesize{$\beta_{1}$}}
-            \put (55.5, 22){\footnotesize{$\beta_{2}$}}
-            \put (80.75, 22){\footnotesize{$\beta_{N-1}$}}
-            \put (85, 10){\footnotesize{$z$}}
+        tics=10,trim=0 0 0 0]{./Media/FIR_arch.png}
+            \put (13, 38){$s$}
+            \put (26, 33.5){$Z^{-1}$}
+            \put (47, 33.5){$Z^{-1}$}
+            \put (68, 33.5){$Z^{-1}$}
+            \put (37.5, 3){$+$}
+            \put (59, 3){$+$}
+            \put (80, 3){$+$}
+            \put (20.5, 18){$\beta_{0}$}
+            \put (42, 18){$\beta_{1}$}
+            \put (63, 18){$\beta_{2}$}
+            \put (84, 18){$\beta_{N-1}$}
+            \put (90, 7){$z$}
         \end{overpic}
@@
         \begin{overpic}[width=0.7\linewidth, 
-        % grid, 
-        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
-            \put (60, 50){\footnotesize{$\beta_{0}$}}
-            \put (60, 30){\footnotesize{$\beta_{1}$}}
-            \put (60, 10){\footnotesize{$\beta_{2}$}}
-            \put (36, 30){\footnotesize{$\alpha_{1}$}}
-            \put (36, 10){\footnotesize{$\alpha_{2}$}}
-            \put (10, 50){\footnotesize{$s$}}
-            \put (85, 50){\footnotesize{$z$}}
-            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
-            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
+        %grid, 
+        tics=10,trim=0 0 0 0]{./Media/IIR_arch.png}
+            \put (60, 55){$\beta_{0}$}
+            \put (60, 30){$\beta_{1}$}
+            \put (60, 6){$\beta_{2}$}
+            \put (39, 30){$\alpha_{1}$}
+            \put (39, 6){$\alpha_{2}$}
+            \put (10, 54){$s$}
+            \put (90, 54){$z$}
+            \put (48.5, 37.5){$z^{-1}$}
+            \put (48.5, 13){$z^{-1}$}
+            \put (21, 25){+}
+            \put (21, 50){+}
+            \put (78, 25){+}
+            \put (78, 50){+}
         \end{overpic}
@@
 \end{figure}
-\par In the following, we revisit the basic interpretation of the ULA as the spatial equivalent to the temporal FIR filter \cite{van1988beamforming} where DOA is shown to be the matching spatial entity to the temporal frequency, hence the \emph{conventional beamformer} \cite{van2004optimum} is merely the spatial version of temporal domain FIR filtering.
-To this end, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented next.
-\par Consider an $N$-element ULA with inter-element spacing $d$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$.
+\par In the following, we revisit the basic interpretation of the ULA as the spatial equivalent to the temporal FIR filter \cite{van1988beamforming} where DOA is shown to be the matching spatial entity to the temporal frequency, hence the CB \cite{van2004optimum} is merely the spatial version of temporal domain FIR filtering.
+% To this end, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented next.
+\par 
+% Consider an $N$-element ULA with inter-element spacing $d$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$.
 We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
+We consider the same ULA as in Sec.~\ref{sec:prlm_propWaveField}, where a target of interest is placed at $\vpt$.
 Focusing on a far field localization problem, DOA and target range are to be estimated. 
-Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
 For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
-Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
-\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
+% In the following, we place a transmitter is at $\vpi{0}$, which emits the signal $s$.
+% Also, we also consider a reflective target, with distance $R = \norm{\vpt-\vpi{0}}$ from the array.
+% Then, the reflected signal re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $c$ represents the propagation velocity of the signal in the medium.
+\par As in RADAR applications, the target is assumed to emit a signal $s\rBrace{t}$, where for convenience $s\rBrace{t=0}$ is the signal which impinges $\vpi{0}$ .
+Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
 \begin{equation}
-x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
+x_{n}(t) = s\Brack{t-\tau_{n}},
 \label{eqn:noFeedbackULA_singleSensor_temporal}
 \end{equation}
-where $\tau_{n}=nd\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
+where, $\tau_{n}=n\tau_{\theta_{d}}=nd\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor.
+% and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
 Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write
 \[
-\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}\rBrace{\theta}}}
+\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}
 \]
@@
     \label{eq_Z}
-    Z\rBrace{\omega,\theta_{d}} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
+    Z\rBrace{\omega,\theta_{d}} = \vecnot{\beta}^{T}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}.
 \end{equation}
@@
 \begin{equation}\label{eq:thetaULA}
-\theta=\omega{d\cos\Brack{\thetaD}}/{c},
+\theta=\omega\tau_{\theta_{d}},
 \end{equation}
@@
 \[
-Z\rBrace{\omega,\theta} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
+Z\rBrace{\omega,\theta} = \F{s}\rBrace{\omega}\sum_{n=0}^{N-1}\beta_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
 \]
-hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018}.
-Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
-\par It is well known \cite{rabiner1974some} that IIR filters have several appealing advantages over their matching (in terms of number of taps) FIR counterparts.
-The main advantage of IIR filters is that for a given set of frequency response specifications, the IIR filter will (in most cases) require substantially less coefficients, which may even reach few order of magnitude \cite{rabiner1974some}.
+hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018} as illustrated in Fig.~\ref{fig_analogyULAFIR}.
+\begin{figure}[h!]
+    \begin{center}
+        \begin{overpic}[width=0.7\linewidth, 
+        % grid, 
+        tics=10,trim=0 0 0 0]{./Media/analogyFIRULA.png}
+            \put (19.5, 23){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (42.25, 23){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (55.25, 23){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (70, 23){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (91, 70){$s\rBrace{t}$}
+            \put (85, 72.5){$\vpi{t}$}
+        \end{overpic}
+    \end{center}
+    \caption{An illustration of the analogy between ULA based spatial processing and an FIR temporal filter.
+The propagation of a plane wave from one sensor to its neighbour (solid tilted lines) is equivalent to the temporal time shift in temporal digital processors (dashed lines and rectangular taps).}
+    \label{fig_analogyULAFIR}
+\end{figure}
+Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this thesis, where possible.
+\par It is well known \cite{rabiner1974some} that IIR filters have several appealing advantages over their matching FIR counterparts.
+The main advantage of IIR filters over their FIR counterparts, is their efficiency in terms of the required sensors quantity, which even reaches few orders of magnitude \cite{rabiner1974some} in some cases.
 In the spatial processing context, this implies improved spatial performance, using the same or smaller number of sensors.
-However, a well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant, namely linearly dependent in the phase response derivative of the specific frequency.
-Therefore, linear phase implies that the phase response's derivative (i.e.
-signal latency) is constant which implies all input frequencies will reside in the processor for the exact same time, preventing dispersion which practically causes pulse widening.
-Due to this important property, many applications which are sensitive to signal distortions, especially communication based systems, chose the FIR architecture, for it is possible to design it as linear phase filter.
-Acquainted with the analogy between frequency and DOA, it seems that when localization applications are considered, where the DOA resolution criteria is more important than the consistency of detection latency between separate DOAs, the linear phase property is less relevant.
+However, a well known \cite{oppenheim1975digital} fact in digital signal processing is that the filter latency may be frequency dependant.
+When the dependence is linear, it implies that the phase response derivative (i.e. signal latency) is constant such that there is no dispersion.
+Due to this important property, applications which are sensitive to signal distortions, especially communication based systems, are based on FIR architecture, for it is possible to design it as linear phase filter.
+Also notable is the stability issues of the IIR filter.
+% Acquainted with the analogy between frequency and DOA, it seems that when localization applications are considered, where the DOA resolution criteria is more important than the consistency of detection latency between separate DOAs, the linear phase property is less relevant.
+% This observation, together with the IIR's efficiency motivate the search for the spatial structure which will be analogous to the IIR filter.
+Motivated by the IIR efficiency, we wish to find the spatial structure that will be analogous to the IIR filer design.
+To this end, we aim to incorporate a spatial feedback which will serve as the temporal feedback in the IIR architecture ($\alpha_{1}, \alpha_{2}$ in Fig.~\ref{fig_IIR_arch}) as illustrated in Fig.~\ref{fig_analogyIIRFB}.
+\begin{figure}[h!]
+    \begin{center}
+        \begin{overpic}[width=0.7\linewidth, 
+        % grid, 
+        tics=10,trim=0 0 0 0]{./Media/analogyIIRFB.png}
+            \put (17.5, 20.5){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (38.25, 20.5){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (50, 20.5){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (63.25, 20.5){\footnotesize{$Z^{-\tau_{\theta_{d}}}$}}
+            \put (94.5, 63.5){$s\rBrace{t}$}
+            \put (78, 65.5){$\vpi{t}$}
+        \end{overpic}
+    \end{center}
+    \caption{An illustration of the spatial feedback concept.
+On top of the FIR equivalence (non-bold dashed lines), the incorporation of the feedback is presented with the bold dashed lines, generating the ``IIR`` part of the spatial processor.
+The multipliers with the bold rectangle wrappers act as the feedback coefficients ($\vecnot{\alpha}$) of Fig.~\ref{fig_IIR_arch}.}
+    \label{fig_analogyIIRFB}
+\end{figure}
 % \par
 % Concluding that spatial linear phase response in DOA domain is not a necessity, combined with the known efficiency of the IIR architecture and the need for smaller and cheaper arrays, the motivation for finding the spatial version of the temporal IIR is complete.
-\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest.
+\par In standard radar signal processing schemes, a waveform is transmitted to and reflected from the target of interest. 
 Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.).
-As opposed to the standard scheme, we suggest in Chapter.~\ref{chap:firstchap} a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
-Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals.
+As opposed to the standard scheme (as implied from Fig.~\ref{fig_analogyIIRFB}) we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
+% Another deviation from modern radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals.

### 2021-05-14 Modules/sec_prlm_array_perf.tex
Acronyms added

@@
 To this end, we follow the classic \cite{van2004optimum} performance analysis, elaborated in the following.
-Those criteria are then used to quantify the presented architecture's performance in Chapter.\ref{chap:firstchap}.
+Those criteria are then used to quantify the presented architecture's performance in Chapter.~\ref{chap:firstchap}.
 \subsection{Beampattern}
-Considering DOA estimators, the main tool for assessing an array's localization performance is expressing it's response to impinging signals with respect to the signal's DOA.
+Considering DOA estimators, the main tool for assessing an array's localization performance is expressing it's response to impinging signals with various DOA.
 \begin{figure}
@@
   \caption{Two common ways of visualizing the array's response in the 2D planar case.
-  In both plots, a comparison between the conventional beamformer's responses of 3,6 and 12 elements arrays is emulated. 
+  In both plots, a comparison between the CB's responses of 3,6 and 12 elements arrays is simulated. 
   In Fig.~\ref{fig_common_bps1}, the response is presented on the $\vBrace{0,\pi}$ interval with units of dB.
@@
 \end{figure}
-Although for sensors in 3D space the DOA may depend on two angles (azimuth and elevation), for the sake of simplicity, we consider a planar (i.e.
-azimuth without elevation) DOA-only dependant array response (i.e.
-the \emph{beampattern})
+For sensors in 3D space the DOA depends on two angles (azimuth and elevation).
+However, for the sake of simplicity, we consider a planar (i.e. azimuth without elevation) DOA such that the beampattern is a function of an angle $\theta$
 \begin{equation}
@@
 It's characteristics, such as main lobe width, position and attenuation of sidelobes are then analysed and compared between different schemes.
-The analysis can be done theoretically, when the beampattern's mathematical expression is known or it can be conducted numerically for empirical scenarios.
+The analysis can be done theoretically, when the beampattern's mathematical expression is known or it can be conducted numerically.
 % In this work, as we deal with 2D planar localization problems, we find the presentation of Fig.~\ref{fig_common_bps1} most suitable.
-The DOAs of the impinging signal, may be presented in various ways where units may be degrees or radians.
+The DOAs of the impinging signal may be presented in various ways where units may be degrees or radians.
 % Also, as the DOA is periodical one should also choose the centering, for example when the beampattern is steered towards different angles and the author wants to center the mainlobe.
@@
 The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
-Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, for it centers the mainlobe, enabling convenient comparison.
+Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, it centers the mainlobe, enabling convenient comparison.
 \subsection{The normalized beampattern}
@@
 Therefore, a common practice \cite{van2004optimum} when analysing the array's spatial performance, is to normalize the beampattern such that the mainlobe's output gain at it's peak is 1 (0dB), thus enabling convenient comparable measures extraction.
-This quantity will be referred to as $\mathcal{H}$.
+This quantity will be referred to as $$\mathcal{H}\rBrace{\theta} = H\rBrace{\theta}/H\rBrace{\theta_{s}}$$ where $H$ is the array's response and $\theta_{s}$ is the DOA that the array is steered to.
 \subsection{Half power beamwidth}
@@
 The Half Power BeamWidth (HPBW), marked as $\Delta\theta_{HPBW}$, is defined to be the 3-dB beamwidth, i.e. the point where $\abs{B\rBrace{\theta}}^{2} = 0.5$ or $\abs{B\rBrace{\theta}} = 1/\sqrt{2}$.
-For standard ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
+For standard $N$-element ULA, assuming large $N$ values, it is known \cite{van2004optimum} that
 \begin{equation}
@@
 \par
-Obviously, we aim to show that the presented architecture increases the resolution, comparing to other arrays by proving that the beamwidth shrinks.
+Obviously, we aim to show that the presented architecture increases the resolution, compared to other arrays by proving that the beamwidth shrinks below the $1.4/N$ limit.
 %
@@
 % As this is an unwanted result, the height and their rate of decrease are measured aiming to prefer arrays where their height is reduced and the decrease rate is increased.
-A known \cite{van2004optimum} parasitic phenomenon of beampatterns is sidelobes, which manifests as energy peaks outside the mainlobe, typically highest near the mainlobe and decreasing towards the deges of the beampattern.
+A known \cite{van2004optimum} parasitic phenomenon of beampatterns is sidelobes, which manifests as energy peaks outside the mainlobe, typically highest near the mainlobe and decreasing towards the edges of the beampattern.
 In the context of localization, this can cause false detection or reduction in spatial resolution.
-Related spatial performance metrics are the sidelobes gain and rate of decrease
+Related spatial performance metrics are the sidelobes gain and rate of decrease in sidelobe gain.
 %
@@
 A common measure of performance of an array or aperture is the directivity $\mathcal{D}$.
-As in \cite{van2004optimum}, in a transmitting array or aperture, $\mathcal{D}$ represents the maximum radiation intensity (power per DOA) divided by the average radiation intensity (averaged over all DOAs).
-Also, in a receiving antenna, the denominator represents the noise power at the array (or aperture) output due to isotropic noise (noise distributed uniformly over all DOAs). 
-The numerator will represent the power due to a signal arriving from a certain DOA ($\theta_{T}$) - Thus, $\mathcal{D}$ can be interpreted as the array gain against isotropic noise.
+As in \cite{van2004optimum}, in a transmitting array, $\mathcal{D}$ represents the maximum radiation intensity (power per DOA) divided by the average radiation intensity (averaged over all DOAs).
+Also, in a receiving array, the denominator represents the noise power at the array output due to isotropic noise (noise distributed uniformly over all DOAs). 
+The numerator will represent the power due to a signal arriving from a certain DOA ($\theta_{d}$) - Thus, $\mathcal{D}$ can be interpreted as the array gain against isotropic noise.
 We define the power pattern, $P\rBrace{\theta_{d}}$, to be the squared magnitude of the beampattern $B\rBrace{\theta_{d}}$

### 2021-05-14 Modules/sec_prlm_localization.tex
Acronyms added

@@
-In the wide and very active research field of parametric estimation, one subject of very high relevance to this thesis is the sensor-array based localization - i.e.
+In the wide and very active research field of parametric estimation, one issue of relevance to this thesis is the sensor-array based localization - i.e.
 positional parameters estimation of impinging signal which is measured by an array of sensors.
@@
 This approach of spatial filtering, is considered to suffer from fundamental
-limitations, namely ``its performance, is directly dependent upon the physical size of the array (the aperture), regardless of the available data collection time and signal-to-noise ratio (SNR)`` \cite{krim1996two}.
+limitations, namely ``its performance, is directly dependent upon the physical size of the array (the aperture), regardless of the available data collection time and signal-to-noise ratio`` \cite{krim1996two}.
 Although trials were made to increase the resolution of an array given a certain aperture, this limitation remained intact.
-In this contribution we tackle this issue as will shown in Chapter.~\ref{chap:firstchap} by introducing a spatial feedback.
+In this contribution we tackle this issue as will be shown in Chapter.~\ref{chap:firstchap} by introducing a spatial feedback.
 \par
-The later approach, of parameter estimation assumes a physical model of the experimental scenario, which serve a basis for the development of spatio-temporal estimators which take advantage not only from the spatial diversity but also from the temporal information collected via sequential time separated snapshots in order to increase the overall SNR.
+The later approach, of parameter estimation assumes a physical model of the experimental scenario.
+Then, spatio-temporal estimators take advantage of not only the spatial diversity but also from the temporal information in order to increase the overall SNR.
 Such methods, not only enabled the increase of spatial filtering resolution, but also allowed the implementation of data processing algorithms, which are more sophisticated than a mere search with a steered array.

### 2021-05-14 Modules/sec_prlm_propWaveField.tex
Acronyms added

@@
 \end{equation}
-where $ \vecnot{x} = \vBrace{x,y,z}^{T} $ emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same phase value where $\vecnot{k}\vecnot{x}=constant$ are planes of constant phase value.
+where $ \vecnot{x} = \vBrace{x,y,z}^{T} $ emphasizes the fact that for a given time, $t_{0}$, all points on a plane given by $k_{x}x+k_{y}y+k_{z}z = constant$ are with the same phase value where $\vecnot{k}^{T}\vecnot{x}=constant$ are planes of constant phase value.
 The wave propagation can be described as the traveling of the planes, stating that small steps of both space $\delta{\vecnot{x}}$ and time $\delta{t}$ result in the same wave value i.e.
@@
 \par For example, in the context of ULA, assuming far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.
-The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which will be shown to provide clues for the signal's DOA as can be seen in Fig.~\ref{fig_ULA_sketch}.
+The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which will be shown to provide clues for the signal's DOA (measured from the array's broadside) as can be seen in Fig.~\ref{fig_ULA_sketch}.
 \begin{figure}[h!]
@@
         tics=10,trim=0 0 0 0]{./Media/arraySketch.png}
-        \put(33.25,2.25){\rotatebox{0}{\tiny{$d$}}}
-        \put(16,26){\rotatebox{-36}{\tiny{$c\tau=d\cos{\theta}$}}}
-        \put(45.5,15.75){\rotatebox{0}{$\theta$}}
-        \put(15,7){\rotatebox{0}{\tiny{0}}}
-        \put(28,7){\rotatebox{0}{\tiny{1}}}
-        \put(41,7){\rotatebox{0}{\tiny{2}}}
-        \put(80,7){\rotatebox{0}{\tiny{$N-1$}}}
-        \put(2,24){\rotatebox{-36}{\tiny{$t=0$}}}
-        \put(2,34){\rotatebox{-36}{\tiny{$t=\tau$}}}
-        \put(2,44){\rotatebox{-36}{\tiny{$t=2\tau$}}}
-        \put(40,44){\rotatebox{-36}{\tiny{$t=\rBrace{N-1}\tau$}}}
+        \put(57.5,2.25){\rotatebox{0}{\tiny{$d$}}}
+        \put(42,34){\rotatebox{-36}{\tiny{$c\tau=d\cos{\theta}$}}}
+        \put(19,15.75){\rotatebox{0}{$\theta$}}
+        \put(15,7){\rotatebox{0}{\tiny{$N-1$}}}
+        \put(65,7){\rotatebox{0}{\tiny{1}}}
+        \put(52,7){\rotatebox{0}{\tiny{2}}}
+        \put(80,7){\rotatebox{0}{\tiny{0}}}
+        \put(-5,29){\rotatebox{-36}{\tiny{$t=-\rBrace{N-1}\tau$}}}
+        \put(13,42){\rotatebox{-36}{\tiny{$t=-2\tau$}}}
+        \put(27,42){\rotatebox{-36}{\tiny{$t=-\tau$}}}
+        \put(42,42){\rotatebox{-36}{\tiny{$t=0$}}}
         \end{overpic}

### 2021-05-14 Modules/sec_prlm_sensorArrays.tex
Acronyms added

@@
 When designing a sensor array, multiple consideration are to be taken into account, ranging from physical characteristics e.g.
-area, weight and carrying platform, through performance related considerations such as accuracy, spatial selectivity, signal to noise ratio and even the financial aspect.
+area, weight and carrying platform, through performance related considerations such as accuracy, spatial selectivity, SNR and even the financial aspect.
 The most fundamental array specification is its geometry, for it dictates the spatial relations between simultaneous samples measured by the array's sensors, which also greatly influences the processing methods of the raw-data.
@@
     \end{center}
-     \caption{A uniform linear array of size $N$ and spacing $d$.}
+     \caption{A ULA of size $N$ and spacing $d$.}
     \label{fig_ULA}

### 2021-05-14 Modules/sec_prlm_timeSpaceSig.tex
Acronyms added

@@
         \begin{overpic}[width=0.6\linewidth, 
-        %grid, 
+        % grid, 
         tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
-        \put(45,33.25){\rotatebox{0}{$\theta$}}
-        \put(15,25){\rotatebox{0}{\tiny{0}}}
-        \put(28,25){\rotatebox{0}{\tiny{1}}}
-        \put(41,25){\rotatebox{0}{\tiny{2}}}
-        \put(80,25){\rotatebox{0}{\tiny{$N-1$}}}
-        \put(16,20){\rotatebox{0}{\tiny{$\omega_{0}$}}}
-        \put(29.5,20){\rotatebox{0}{\tiny{$\omega_{1}$}}}
-        \put(42,20){\rotatebox{0}{\tiny{$\omega_{2}$}}}
-        \put(81,20){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
+        \put(19.5,29.5){\rotatebox{0}{$\theta$}}
+        \put(15,21.5){\rotatebox{0}{\tiny{$N-1$}}}
+        \put(65,21.5){\rotatebox{0}{\tiny{1}}}
+        \put(52,21.5){\rotatebox{0}{\tiny{2}}}
+        \put(80,21.5){\rotatebox{0}{\tiny{0}}}
+        \put(16,18){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
+        \put(54,18){\rotatebox{0}{\tiny{$\omega_{2}$}}}
+        \put(67,18){\rotatebox{0}{\tiny{$\omega_{1}$}}}
+        \put(81,18){\rotatebox{0}{\tiny{$\omega_{0}$}}}
         \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
@@
 \begin{equation}
-\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T},
+\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T}.
 \end{equation}
-where $p_{n}$ denotes the $n$-th sensor position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
-Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
+Considering the CB \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
 \begin{equation}
@@
 where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
-Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
+Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the DOA angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
 The wave signal, spatially sampled by the sensor array inputs is

### 2021-05-14 Modules/sec_stability.tex
After Israel's comments
Acronyms added

@@
-As a preliminary to the following performance discussion in Sec.~\ref{sec_Performance}, we start with simple temporal simulations of the feedback beamformer.
-In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
-Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.
-After the error terms have been defined, we first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.
+As a preliminary, we start with simple temporal simulations of the feedback beamformer.
+% In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
+% Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.
+% After the error terms have been defined, 
+We first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.
 \subsection{Gain mismatch}
-The analogy of the feedback beamformer to the temporal IIR architecture raises some fundamental questions that should be addressed.
+The analogy of the FB to the temporal IIR architecture raises some fundamental issues that should be addressed.
 In the following, supported by simulations, we answer those questions.
-\par The first question, related to the feedback beamformer's analogy to the temporal IIR architecture, is stability related.
+\par The first question, related to the FB's analogy to the temporal IIR architecture, is stability related.
 To begin with, we should first ask what does ``stability`` means.
@@
 for $r<1$ the denominator will never be nullified.
-To this end, the gain mismatch
+To this end, the gain mismatch is
 \begin{equation}
-    r=g/\hat{g}
+    r=g/\hat{g}.
 \end{equation}
-and plug \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, giving rise to
+And plugging \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, gives rise to
 \begin{equation}\label{eq:SF_CB_gainMismatch}
@@
             }\\
-            = &\frac{    
-            \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
-            }{
-            1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
-            }\\
-            = & \frac{r}{1-r}.
+            % = &\frac{    
+            % \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
+            % }{
+            % 1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
+            % }\\
+            = & \frac{r}{1-r} \triangleq H_{0}.
         \end{split}
@@
 \end{equation}
-As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.
+As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.
 In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value after 100 iterations of the signal being retransmitted between the array and the target of interest and find that the final values substantially increase as $r\to{1}$.
-This issue will have to be taken into consideration when one designs such an array for practical applications but is outside the scope of this work.
+This issue will have to be taken into consideration when one designs such an array for practical applications but currently this is outside the scope of this work.
 \begin{figure}[t!]
@@
     \caption{
-    Simulating a 3 element ULA based feedback beamformer, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
+    Simulating a 3 element ULA based FB, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
     The horizontal axis ($t/\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
@@
             \put (100, 39){\rotatebox{0}{$t=2\cdot\tau_{pd}$}}
-            \put (100, 26.5){\rotatebox{0}{$t=5\cdot\tau_{pd}$}}
-            \put (100, 14){\rotatebox{0}{$t=10\cdot\tau_{pd}$}}
+            \put (100, 22.5){\rotatebox{0}{$t=5\cdot\tau_{pd}$}}
+            \put (100, 12){\rotatebox{0}{$t=10\cdot\tau_{pd}$}}
             \put (53.5, 27.5){\rotatebox{-75}{$t=50\cdot\tau_{pd}$}}
@@
     \caption{
-    Simulation of same setup as in Fig.\ref{fig_stability} with $r=9$.
+    Simulation of the same setup as in Fig.\ref{fig_stability} with $r=0.9$.
     Several simulations are conducted, where each is simulated with different duration.
     It actually illustrates the forming of the final beampattern in time as our analysis assumes infinite duration.
+    This convergence is analogous to the settling time of the IIR filters' temporal response, where at early stages, the response is not yet in its steady-state.  
     }
@@
     \caption{
-    After simulating same setup of Fig.\ref{fig_stability} for a fined grid of $r$, we plot the final received amplitude in dB with respect to $r$.
+    After simulating the same setup as in Fig.\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.
     }
@@
 \end{figure}
-\par The Second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e.
+\par The second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e.
 $\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
-To better understand the phenomenon, we plot the settling time's $r$ dependency in Fig.~\ref{fig_stabilityDur}.
+To better understand the phenomenon in Fig.~\ref{fig_stabilityDur}, we plot for each $r$ value, its corresponding settling time.
 Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:conclusion}.
@@
 \end{figure}
-\par Although many interesting questions rise from the initial simulations, most of them are outside the scope of this work.
-We choose to add one more note, regarding the influence of the array's number of elements.
-Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e.
+% \par To conclude this section, we choose to add one more note, regarding the influence of the array's number of elements.
+% Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e.
 the settling time remains the same as $N$ increases.
 \subsection{Phase mismatch}
-Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
+\label{subsec_error_trms}
+% Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, 
+We denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
 As we intend to compare the results to \cite{van2004optimum}, we consider a ULA, introducing its estimated steering vector
@@
         \frac{\sin{\rBrace{N\Delta\theta/2}}}
-        {\sin{\rBrace{\Delta\theta/2}}},
+        {\sin{\rBrace{\Delta\theta/2}}}
     \end{split}
 \end{equation*}
-we define Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernel}) as
+and using the definition of the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})
 \[
-D_{\test{orig}}\rBrace{x,N}\triangleq\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
+\D{x}{N}
+% =\frac{1}{N}D_{\test{orig}}\rBrace{x,N}
+=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}},
 \]
-and the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})
-\[
-\D{x}{N}=\frac{1}{N}D_{\test{orig}}\rBrace{x,N}=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}.
-\]
-Now, \eqref{eqn:GeneralFeedbackTransferFunction} takes the form of
+we find that for ULA, \eqref{eqn:GeneralFeedbackTransferFunction} may be expressed as
 \begin{equation}\label{eq:alpha_beta_hat}
     \begin{split}
-        H_{\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}}
-        = &\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}.
+        H_{\vecnot{\beta}_{\text{CB}},\vecnot{\alpha}_{\text{CB}}}
+        = &\frac{r\D{\dTheta/2}{N}\exp\cBrace{-j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\cBrace{-j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}}.
     \end{split}
 \end{equation}
-\begin{figure}[t!]
-    \begin{center}
-        \begin{overpic}[width=0.65\linewidth, 
-        %grid, 
-        tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
-            \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
-            \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
-            \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
-            \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
-            \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
-            \put (50, 2.5){\rotatebox{0}{$x$}}
-            \put (12, 5){\rotatebox{0}{$-\pi$}}
-            \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
-            \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
-            \put (89, 5){\rotatebox{0}{$\pi$}}
-        \end{overpic}
-    \end{center}
-    \caption{
-    Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
-    }
-    \label{fig_DirichletKernel}
-\end{figure}
+% \begin{figure}[t!]
+%     \begin{center}
+%         \begin{overpic}[width=0.65\linewidth, 
+%         %grid, 
+%         tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
+%             \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
+%             \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
+%             \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
+%             \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
+%             \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
+%             \put (50, 2.5){\rotatebox{0}{$x$}}
+%             \put (12, 5){\rotatebox{0}{$-\pi$}}
+%             \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
+%             \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
+%             \put (89, 5){\rotatebox{0}{$\pi$}}
+%         \end{overpic}
+%     \end{center}
+%     \caption{
+%     Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
+%     }
+%     \label{fig_DirichletKernel}
+% \end{figure}
 \begin{figure}[t!]

### 2021-05-14 Modules/stabilityEnhancement_freqPairApproach.tex
Acronyms added

@@
 Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
-As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
+% As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
 Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
@@
     \item \textbf{Signal bandwidth}\\
-    As the carrier signal's frequency decreases, so does the available bandwidth due to aliasing.
+    As the carrier signal's frequency decreases, so does the available bandwidth.
 \end{itemize}
@@
     \end{center}
-    \caption{Dual-frequency beamformer, consisting of two independent FB blocks and narrowband bandpass filters.
-The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the Fourier coefficients in $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF beamformer's output.}
+    \caption{DF BF, consisting of two independent FB blocks and narrowband bandpass filters.
+The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the frequency response at $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF BF's output.}
     \label{fig_app}
@@
 \begin{equation*}
-    \vBetaCI{1}=\frac{-\vdHatIC{1}\exp\rBrace{j\rBrace{\phiIHat{1}-\phiIHat{2}}}}{\hat{\gI{1}}\norm{\vdHatI{1}}^2}.
+    \vBetaCI{1}=\frac{\vdHatIC{1}\exp\rBrace{j\rBrace{\phiIHat{1}-\phiIHat{2}}}}{\hat{\gI{1}}\norm{\vdHatI{1}}^2}.
 \end{equation*}
 % where $\vdHatI{1}$ is the estimated steering vector, as in \eqref{eq:d_hat}.
-With this choice, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes
+With this choice, denoted as the ``DF,CB`` beamformer, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes
 \begin{equation}
@@
 where $\kappa\triangleq{}r_{1}/r_{2}$ is the gain mismatch ratio.
-For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both feedback beamformers are mismatched.
+For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both FBs are mismatched.
 \par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves a near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
-In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer.
-Evidently, even in the noisy case, the DF beamformer achieves a close-to-ideal beampattern, while the SF beamformer suffers from severe distortions.
+In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each FB.
+Evidently, even in the noisy case, the DF BF achieves a close-to-ideal beampattern, while the SF BF suffers from severe distortions.
 \begin{figure}[t!]
@@
     \caption{Simulating a 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR.
-For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$.
+For each target direction $\thetaD$, the DF BF output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$.
     The (modulus $\lambda$) range error is $\Delta{}R_{\text{rt}}=0.3\lambda$.
-    The single frequency (SF) beamformer (red squares) and the dual-frequency (DF) solution (green diamonds) are compared to the ideal response  $\Delta{}R_{\text{rt}}=0$ (blue dots) as a reference. 
+    The SF BF (red squares) and the dual-frequency solution (green diamonds) are compared to the ideal response  $\Delta{}R_{\text{rt}}=0$ (blue dots) as a reference. 
     }
@@
             \put (49, 2){\footnotesize{$\thetaD/\pi$}}
-            \put (16,52){\scriptsize{$\text{SNR}=6_{dB}$}}
-            \put (74,52){\scriptsize{$\text{SNR}=0_{dB}$}}
-            \put (44.5,12){\scriptsize{$\text{SNR}=-6_{dB}$}}
+            \put (19.75,52){\scriptsize{$\text{SNR}=6_{dB}$}}
+            \put (77,52){\scriptsize{$\text{SNR}=0_{dB}$}}
+            \put (47.5,12){\scriptsize{$\text{SNR}=-6_{dB}$}}
             \put (4,42.5){\footnotesize{(a)}}

### 2021-05-14 front/abbrevs.tex
Acronyms added

--- 2020-10-31 front/abbrevs.tex
@@
 
-\abbreviationsAndNotation{
-\begin{tabular}{p{2cm}@{:\quad}l}
-QED & quod erat demonstratum \\
-$c$ & the speed of light \\
-$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
-\end{tabular}
-}
+\newacronym{DOA}{DOA}{direction of arrival}
+\newacronym{RADAR}{RADAR}{dadio Detection And Ranging}
+\newacronym{FIR}{FIR}{finite impulse response}
+\newacronym{IIR}{IIR}{infinite impulse response}
+\newacronym{ULA}{ULA}{uniform linear array}
+\newacronym{FIM}{FIM}{fisher information matrix}
+\newacronym{SNR}{SNR}{signal to noise ratio}
+\newacronym{MUSIC}{MUSIC}{multiple signal classification}
+\newacronym{RHS}{RHS}{right hand side}
+\newacronym{FB}{FB}{feedback beamformer}
+\newacronym{SF}{SF}{single frequency}
+\newacronym{DF}{DF}{dual frequency}
+\newacronym{HPBW}{HPBW}{half power beamwidth}
+\newacronym{PDF}{PDF}{probability density function}
+\newacronym{CRLB}{CRLB}{cram\'er Rao lower bound}
+\newacronym{CRB}{CRB}{cram\'er Rao bound}
+\newacronym{PCA}{PCA}{principal component analysis}
+\newacronym{ICA}{ICA}{independent components analysis}
+\newacronym{MVDR}{MVDR}{minimum Variance Distortionless Response}
+\newacronym{UWB}{UWB}{ultra wide band}
+\newacronym{HOS}{HOS}{high order statistics}
+
+\newglossaryentry{VVEC}{name=$\vecnot{v}$,description={A vector}}
+\newglossaryentry{VI}{name=$v_{i}$,description={The $i$-th element of vector $\vecnot{v}$}}
+\newglossaryentry{VT}{name=$\vecnot{v}^{T}$,description={Transpose of vector $\vecnot{v}$}}
+\newglossaryentry{VCONJ}{name=$\vecnot{v}^{*}$,description={Conjugate of vector $\vecnot{v}$}}
+\newglossaryentry{VH}{name=$\vecnot{v}^{H}$,description={Hermitian (conjugated) transpose of vector $\vecnot{v}$}}
+\newglossaryentry{A}{name=$\vecnot{A}$,description={A Matrix}}
+\newglossaryentry{AIJ}{name=$A_{i,j}$,description={The $i,j$-th element of matrix $\vecnot{A}$}}
+\newglossaryentry{AT}{name=$\vecnot{A}^{T}$,description={Transpose of matrix $\vecnot{A}$}}
+\newglossaryentry{ACONJ}{name=$\vecnot{A}^{*}$,description={Conjugate of matrix $\vecnot{A}$}}
+\newglossaryentry{AH}{name=$\vecnot{A}^{H}$,description={Hermitian (conjugated) transpose of matrix $\vecnot{A}$}}
+\newglossaryentry{DINTERARRAY}{name=$d$,description={Array's inter-element spacing}}
+\newglossaryentry{OMEGA}{name=$\omega$,description={Radial frequency}}
+\newglossaryentry{C}{name=$c$,description={Wave's propagation velocity}}
+\newglossaryentry{LAMBDA}{name=$\lambda$,description={Wavelength}}
+\newglossaryentry{THETAD}{name=$\theta_{d}$,description={Geometrical angle}}
+\newglossaryentry{THETA}{name=$\theta$,description={Electrical phase}}
+\newglossaryentry{DSTEER}{name=\vecnot{d},description={Steering vector}}
+\newglossaryentry{BP}{name=$B$,description={beampattern}}
+\newglossaryentry{RANGE}{name=$R$,description={Distance to target}}
+\newglossaryentry{ZT}{name=$z\rBrace{t}$,description={Array's temporal output}}
+\newglossaryentry{ZW}{name=$Z\rBrace{\omega}$,description={Array's frequency-domain output}}
+\newglossaryentry{D}{name=$\mathcal{D}$,description={Directivity}}
+\newglossaryentry{HNORM}{name=$\mathcal{H}$,description={Normalized beampattern}}

### 2021-05-14 main/chap_futureResearch.tex
Acronyms added

@@
-In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
+In the following chapter, some of the many possibilities for further investigation of the FB are suggested.
 As mentioned in Sec.~\ref{sec_introduceFeedback}, we assumed a single stationary target scenario where the target's location is fixed.
-Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios.
-Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
+Naturally, the first suggested subjects for future research are dynamic (Sec.~\ref{sec_future_dynamic}) and multiple (Sec.~\ref{sec_future_multiTarget}) target scenarios.
+Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and its effect on the overall spatial performance.
 We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 

### 2021-05-14 main/intro.tex
Acronyms added

@@
 The general field of array processing has been thoroughly studied throughout several decades.
-The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving signal to noise ratio (SNR) \cite{verdu1998multiuser}, and many more.
-\par A uniform linear array (ULA) has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
-The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
+The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving SNR \cite{verdu1998multiuser}, and many more.
+\par The ULA has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
+The array size and the number of its elements ($N$) have significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).
 \par Early algorithms for direction of arrival (DOA) estimation were based on the beamforming concept \cite{krim1996two}, where the array's reception beam is steered (mechanically or electronically) to multiple directions in search of received energy peaks which are interpreted as valid emitters.
@@
 \par The most practically used approach in DOA estimators, referred as the subspace based estimation, involves invariant subspace analysis of observed covariance matrices.
-Early research include PCA and errors-in-variables time series analysis \cite{krim1996two}.   
+Early research includes PCA and errors-in-variables time series analysis \cite{krim1996two}.
 However, the tremendous interest in the subspace approach is mainly due to the introduction of the
@@
 It is interesting to note that while earlier works were mostly derived in the context of time series analysis and only later applied to the sensor array problems, MUSIC was originally presented as a DOA estimator.
-\par A less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.
+\par A less practical, but optimal in the sense of root mean square error (RMSE) \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.
 Though this approach served as a basis for extensive research, leading to more advanced concepts such as the independent component analysis (ICA) \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
-Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the CRB under some practical assumptions (e.g.
+Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao bound (CRB) under some practical assumptions (e.g.
 non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice.
@@
 \end{figure}
+
 \section{Overview of the Thesis}
 In this thesis, we propose a new feedback based beamformer architecture which acts as an actual spatial IIR filter while avoiding any temporal processing to the signal.
-We aim to guide the reader thorough the key stages of the research where in each stage, a sufficient background is provided followed by the solution composition.
-\par As this research does not closely follows any former work, some of analysis must be rigorously justified, hence we turn to classic literature as guidance.
-As an example, for the configuration of the array, we use the Fisher Information Matrix (FIM) aiming to maximize the residing spatial information in the system.
-\par After presenting the basic approach with it's complementary adjusted classic spatial analysis, we find that it is inherently sensitive to range estimation errors.
-We then suggest a more robust solution which is based on our conclusions from previous analysis.
-With the robust solution in hand, we present simulations and compare it to the basic conventional beamformer and the initial more sensitive approach.
-As expected, we find that it outperforms them, proving to perform well also in low signal to noise ratios (SNR).
-\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
-$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
-Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
+The reader may observe that the presented research stages lead one to the other as each analysis of the proposed methods uncovered issues that are addressed in the following.
+\par
+First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to translate its advantages from the temporal domain to the spatial domain.
+Also, classic spatial analysis tools have been gathered to serve as objective tests to the proposed solutions.
+\par
+In the second part of the research we present the basic spatial architecture, called FB, introducing the concept of spatial feedback.
+The array configuration is rigorously justified, e.g. the setting of the coefficients is done with the use of the Fisher Information Matrix (FIM).
+Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed with the classic analysis framework.
+As we aim to present a practical architecture, estimation errors were taken into consideration and unveiled some sensitivities that should have been addressed.
+\par
+After close inspection, we conclude in the third part that the carrier frequencies cause this sensitivity and search for ways to mitigate it.
+To this end, we present a more sophisticated design, based on the basic architecture, achieving a practical low sensitivity spatial processor which successfully extracts spatial information from two independent close frequency FB units.
+We then simulate the proposed solution and find that in addition to its low sensitivity, it also outperforms the classic beamformers, such as the conventional beamformer (CB) in low SNR. 
+% In this thesis, we propose a new feedback based beamformer architecture which acts as an actual spatial IIR filter while avoiding any temporal processing to the signal.
+% We aim to guide the reader thorough the key stages of the research where in each stage, a sufficient background is provided followed by the solution composition.
+% \par As this research does not closely follows any former work, some of analysis must be rigorously justified, hence we turn to classic literature as guidance.
+% As an example, for the configuration of the array, we use the Fisher Information Matrix (FIM) aiming to maximize the residing spatial information in the system.
+% \par After presenting the basic approach with it's complementary adjusted classic spatial analysis, we find that it is inherently sensitive to range estimation errors.
+% We then suggest a more robust solution which is based on our conclusions from previous analysis.
+% With the robust solution in hand, we present simulations and compare it to the basic conventional beamformer (CB) and the initial more sensitive approach.
+% As expected, we find that it outperforms them, proving to perform well also in low SNR.
 \section{Main Contributions}
@@
 In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize on the localization field of research and finalize with the basic concepts which drive the motivation for this research.
-\par In Chapter.~\ref{chap:firstchap} the basic feedback beamformer is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.
+\par In Chapter.~\ref{chap:firstchap} the basic FB is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.
 Simulations are also provided, supporting the analytical analysis.
 \par In Chapter.~\ref{chap:conclusion} we discuss the results and conclude our findings. We finalize by also proposing some leads to future research.
+\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
+$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
+Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.

### 2021-05-14 main/prelims.tex
Acronyms added

--- 2021-02-12 main/prelims.tex
@@
 \label{chap:prelims}
-As a preliminary discussion to the presentation of our contribution, we overview some the key theoretical basis of the thesis.
-First, a short overview of array-processing is presented in Sec.~\ref{sec:prlm_sensorArrays}, accompanied by a complementary wave propagation discussion in Sec.~\ref{sec:prlm_propWaveField}.
-To accommodate the discussion for spatial filtering, we also mention the time-space relation of spatially sampled signals in Sec.~\ref{sec:prlm_timeSpaceSig}.
-In Sec.~\ref{sec:prlm_localization}, we further focus the spatial filtering discussion to localization and overview some of its fundamentals.
-Following the FIR/IIR filters related discussion in Chapter.~\ref{chap:intro}, we further elaborate and compare the two architectures in Sec.~\ref{sec:prlm_FIR_IIR}.
-To complete the basics overview, we also discuss array performance measuring in Sec.~\ref{sec:prlm_array_perf} following the classical localization related literature.
-% \begin{definition}
-% The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
-% \end{definition}
-
-% \section{Digital Filter Design - Finite/Infinite Response Filters}
-% \label{sec:prlm_FILTERS}
-% \input{Modules/sec_prlm_FILTERS}
+In this chapter, we discuss the theoretical preliminaries for this thesis.
+First, a short overview of array-processing is presented in Sec.~\ref{sec:prlm_sensorArrays}, accompanied by a complementary wave propagation elementaries in Sec.~\ref{sec:prlm_propWaveField}.
+As a preface to spatial filtering, we mention the time-space relation of spatially sampled signals in Sec.~\ref{sec:prlm_timeSpaceSig}, which is followed by a discussion of classic spatial performance analysis methods in Sec.~\ref{sec:prlm_array_perf} and further elaboration on
+localization in Sec.~\ref{sec:prlm_localization}.
+Finally, Sec.~\ref{sec:prlm_FIR_IIR} reviews the FIR/IIR filters, presents the pros and cons of both architectures and serves as the foundation for this research's motivation.
 \section{Sensor arrays}
@@
 \input{Modules/sec_prlm_timeSpaceSig}
+\section{Array spatial performance}
+\label{sec:prlm_array_perf}
+\input{Modules/sec_prlm_array_perf}
 \section{Localization}
@@
 \input{Modules/sec_prlm_localization}
-% \section{Sensor array performance measure}
-% \label{sec:prlm_sensorArrayPerf}
-% \input{Modules/sec_prlm_arrPerf}
 \section{The analogy between array processing and temporal digital filtering}
@@
 \input{Modules/sec_prlm_FIR_IIR}
-\section{Array spatial performance}
-\label{sec:prlm_array_perf}
-\input{Modules/sec_prlm_array_perf}

### 2021-05-25 Modules/Spatial_IIR-MathDerivations.tex
Final fixes

@@
 The array's $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$ and we set $\vpi{0}$ as the axis reference point while the target of interest is positioned at $\vpt$ and define its distance from the array as $R = \norm{\vpt-\vpi{0}}$.
-The gain of the reimpinging signal is denoted as $g$ which encapsulates both propagation related gain and the target's radar cross section (RCS). 
-We also place a transmitter at $\vpi{0}$, where the transmitted signal $s$, is reflected back from the target and re-impinges the array with a total delay of $\tau_{\text{pd}}=2R/c$ seconds, denoting $c$ as the propagation velocity of the signal in the medium.
+The gain of the reimpinging signal is denoted as $g$ which encapsulates both propagation related attenuation and the target's radar cross section (RCS). 
+We also place a transmitter at $\vpi{0}$.
+The transmitted signal $s$, is reflected back from the target and re-impinges the array with a total delay of $\tau_{\text{pd}}=2R/c$ seconds, denoting $c$ as the propagation velocity of the signal in the medium.
 Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
@@
 $$
-Then, denoting
+We also denote
 \[

### 2021-05-25 Modules/abstractHebrew.tex
Final fixes

@@
 \textenglish{(phased array)}
-בכך מושגים חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.
+ובכך מושגים חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.
 בדימות רפואית כדוגמת 
@@
 \par
-המערך היוניפורמי
+המערך היוניפורמי הלינארי
 \textenglish{(ULA)}
-בו החיישנים מפוזרים על קו ישר במרחקים קבועים האחד מהשני נחשב למערך הבסיסי בעיבוד המרחבי בשל פשטות העיבוד והיישום שלו.
+בו החיישנים מפוזרים על קו ישר במרחקים קבועים האחד מהשני נחשב למערך הבסיסי בעיבוד המרחבי בשל פשטות העיבוד והניתוח האנליטי שלו.
 בנוסף, מוכרת בספרות ההקבלה בין עיצוב אלומת הסריקה (בהקשר של איכון) של מערך זה לבין תכן מסננים בעלי תגובה סופית להלם
@@
 קיימת ארכיטקטורה נוספת למסננים, המממשת מסנן בעל תגובה אינסופית להלם 
-\textenglish{IIR}
+\textenglish{(IIR)}
 ע"י שילוב היזון חוזר.
@@
 \textenglish{IIR}
-ידרשו פחות משאבים.
+ידרשו פחות מקדמים.
 יתרון זה מהווה כבסיס לשאלת המחקר בתזה זו שהיא 
-``מהו המקביל המרחבי למסנן בעל התגובה האינסופית?``, שכן בההקשר של מערכי חיישנים, חיסכון במשאבים מתבטא בהוזלה משמעותית ומאפשר את מזעור המערכת.
+``מהו המקביל המרחבי למסנן בעל התגובה האינסופית?``, שכן בהקשר של מערכי חיישנים, חיסכון במשאבים מתבטא בהוזלה משמעותית ומאפשר את מזעור המערכת.
 \par
@@
 שיטה זו רגישה לשגיאות שיערוך ומעבר לכך, מערבת עיבוד זמני ולכן אינה מתאימה כתשובה לשאלת המחקר.
-השיטה השניה שהוצעה היתה הגדרת תתי מערכים (חלקים חופפים מהמערך) כך שאל מוצא כל מערך מתייחסים כאל הסחה זמנית של פלט מערך ייחוס כלשהו.
+השיטה השניה שהוצעה היתה הגדרת תתי מערכים (חלקים חופפים מהמערך המקורי) כך שאל מוצא כל תת מערך מתייחסים כאל הסחה זמנית של פלט מערך ייחוס כלשהו.
 ניתוח מתמטי מוכיח כי בפועל העיבוד המרחבי לא משתפר היות ובפועל מדובר במערך בעל מספר זהה של  דרגות חופש ל
@@
 \par
-גישה נוספת, אשר מקורה בעיבוד אותו וידאו 
+גישה נוספת, אשר מקורה בעיבוד אותות וידאו 
 \cite{bruton1985three}
@@
 אי לכך, על מנת להגביר אותות מכיוונים רצויים, יש לתכנן מסננים המעבירים פסים ישרים במישור הדו תדרי התואמים לכיווני הגעה אלו.
-היות ותגובת המסננים מחזורית בשני התדרים, נוצרים עיוותים בקצוות התגובה התדרית ובנוסף לכך, גם שיטה זו מערבת עיבוד זמני לכן אינה מהווה פתרון מספק לשאלת המחקר.
+היות ותגובת המסננים מחזורית בשני התדרים, נוצרים עיוותים בקצוות התגובה התדרית ובנוסף לכך, גם שיטה זו מערבת עיבוד זמני ולכן אינה מהווה פתרון מספק לשאלת המחקר.
 \par
@@
 מניתוח המערך עולה כי בשילוב המשוב, תגובתו הינה המקבילה המרחבית למסנן בעל התגובה הזמנית האינסופית.
-בנוסף, עולה כי התגובה אינה מושפעת רק מכיוון הגעת גל כמו במסננים המוכרים, אלא גם ממרחק המטרה מהמערך. 
+בנוסף, עולה כי התגובה אינה מושפעת רק מכיוון הגעת הגל כמו במסננים המוכרים, אלא גם ממרחק המטרה מהמערך. 
 \par
-בשלב זה, על מנת לקבוע את משקלות המערך, הוגדרו המרחק וכיוון ההגעה כערכים אותם יש לשערך ובהתאם לכך חושבה מטריצת האינפורמציה 
-\textenglish{FIM}.
+בשלב זה, על מנת לקבוע את משקלות המערך, הוגדרו המרחק וכיוון ההגעה כערכים אותם יש לשערך ובהתאם לכך חושבה מטריצת אינפורמציית פישר
+\textenglish{(FIM)}.
 בעזרת מטריצה זו נמצאו המקדמים המביאים את האינפורמציה לכדי שיא - בדיעבד, הרחבה טבעית של מקדמי האיסוף הקוהרנטי הבסיסי המוכר בספרות כמסנן הקונבנציונאלי.
@@
 בנוסף על כך הניתוח מראה כי ניתן ליישם את עקרון המשוב בכל מערך ולא רק ב 
-\textenglish{(ULA)}.
+\textenglish{ULA}.
 \par
 סימולציות בשילוב בחינה דקדקנית של המערכת מגלים כי המערכת בעלת רגישות גבוהה למדי לשגיאת טווח.
-היות ושגיאה זו נובעת מהתדרים הנושאים, הוצע שימוש בלתי תלוי בשני תדרים קרובים תוך נסיון לחלץ את המידע המרחבי מהקשר בין האותות הנקלטים.
-הפתרון פשוט וזול יחסית ומגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.
+היות ושגיאה זו שקולה לאורך הגל לפיו פועל המערך, הוצע שימוש בלתי תלוי בשני תדרים קרובים תוך נסיון לחלץ את המידע המרחבי מהקשר בין האותות הנקלטים.
+הפתרון פשוט וזול יחסית ומגדיל בסך הכל את המאמץ החישובי ולא את המערך עצמו.
 ניתוח נוסף מאשרר כי הפתרון קביל ומשיג תוצאות שבתרחישים אידיאלים נוטות לכדי שיפור משמעותי בביצועים המרחביים.

### 2021-05-25 Modules/apndx_directivityFit.tex
Final fixes

@@
-In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were rational.
+In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were a rational expression.
 Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the FB.

### 2021-05-25 Modules/paper_sec_prlms.tex
Final fixes

@@
 Also, the FB block is marked (dashed line) for later use.
-Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the convectional beamformer (CB) beamformer.
+Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the conventional beamformer (CB).
 \begin{figure}[t!]
@@
             \put (54, 39){\footnotesize{$\sum_{n=0}^{N-1}\alpha^{*}_{n}x_{n}$}}
-            \put (24.25, 50){\footnotesize{$x_{0}$}}
-            \put (35, 50){\footnotesize{$x_{1}$}}
-            \put (55, 50){\footnotesize{$x_{N-1}$}}
+            \put (27, 53){\footnotesize{$x_{N-1}$}}
+            \put (37.5, 53){\footnotesize{$x_{N-2}$}}
+            \put (58, 53){\footnotesize{$x_{0}$}}
             \put (30.5, 66){\footnotesize{$\delta$}}
             \put (89, 96){\footnotesize{$\vpt$}}
-            \put (58, 58){\footnotesize{$\vpi{N-1}$}}
-            \put (37, 58){\footnotesize{$\vpi{1}$}}
-            \put (26.5, 58){\footnotesize{$\vpi{0}$}}
+            \put (60, 60.5){\footnotesize{$\vpi{0}$}}
+            \put (39, 60.5){\footnotesize{$\vpi{N-2}$}}
+            \put (28, 60.5){\footnotesize{$\vpi{N-1}$}}
             \put (41.5, 64.5){\footnotesize{$\theta_{d}$}}
@@
 \end{equation}
-Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with
+Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity} and Fig.~\ref{fig_directivityErr}) we suggest to approximate the directivity with
 \begin{equation}\label{eq_D_result}
@@
 \begin{table}[h!]
-    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
+    \caption{Performances of CB and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
     \centering
@@
             \hline
-            & ULA & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 
+            & CB & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 
             \hline\hline
@@
 As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA in Fig.~\ref{fig_perf20}. 
-In Table.~\ref{table_arrayPerfEmp} we show the coherency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.
+In Table.~\ref{table_arrayPerfEmp} we show the consistency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.
 As predicted, the results of Fig.~\ref{fig_perf20} are consistent with the theoretical expressions.

### 2021-05-25 Modules/sec_FIM_and_CRLB.tex
Final fixes

--- 2020-12-25 Modules/sec_FIM_and_CRLB.tex
@@
 where $\hat{g}$ is the channel gain estimate.
-This choice of weights may be interpreted as a generalized version of the conventional beamformer (CB) \cite{van2004optimum}. 
+Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the CB \cite{van2004optimum} which is a mere coherent summation of the feedback signal.
+% \begin{figure}[t!]
+%     \begin{center}
+%         \begin{overpic}[width=0.55\linewidth, 
+%         % grid, 
+%         tics=10,trim=0 0 0 0]{./Media/fig_CB_vanTrees.PNG}
+%             % \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
+%         \end{overpic}
+%     \end{center}
+%     \caption{
+%     % A visualization of the spatial area selectivity concept.
+%     The CB - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.
+%     }
+%     \label{fig_CB_vanTrees}
+% \end{figure}
 Furthermore, setting $\vBeta=\vBeta_{\text{CB,opt}}=\vAlpha_{\text{CB,opt}}$, is shown (see App.~\ref{apdx_clacFim}) to nullify the FIM cross terms, such that $J_{12}=J_{\thetaD,\phi}=J_{21}=J_{\phi\thetaD}=0.$

### 2021-05-25 Modules/sec_conclusions_LOCAL.tex
Final fixes

@@
-In this work we have suggested a novel approach to beamforming and localization, which is based on a generating a continuous feedback between the array and the target of interest.
+In this work we have suggested a novel approach to beamforming and localization, which is based on generating a continuous feedback between the array and the target of interest.
 Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
 It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
-The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
+The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and channel attenuation.
 It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
-Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
+Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, was found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
 Also, the DF scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.

### 2021-05-25 Modules/sec_future_dynamic.tex
Final fixes

@@
 \par
-Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, starts with expressing the impinging signal of a single sensor.
+Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, we start with expressing the impinging signal of a single sensor.
 As in the analysis of static target scenario, the signal consists of two contributions, i.e. the reflected emitted signal and the reflected feedback signal.
@@
 \par
-To this end, we first denote $t_{\text{ref}}\rBrace{t}$ the moment in which the currently impinging signal was reflected by the target of interest.
-Another auxiliary quantity is reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
+To this end, we first denote $t_{\text{ref}}\rBrace{t}$ as the moment in which the currently impinging signal was reflected by the target of interest.
+Another auxiliary quantity is the reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
 \begin{equation}
@@
 which when plugged into \eqref{eq_tRef_relation} gives rise to
+
 \begin{equation}
     \label{eq_fut_constV_ti}
-    t_{\text{\tiny{TX}}}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
+    %\resizebox{.89\linewidth}{!}{
+    \begin{split}
+        t_{\text{ref}}\rBrace{t} &= \frac{c}{c+v}t-\frac{R_{0}}{c+v} \\
+        \tau_{\text{ref}}\rBrace{t} &= \frac{R_{0}+vt}{c+v} \\
+        t_{\text{\tiny{TX}}}\rBrace{t} &= t-2\tau_{\text{ref}}\rBrace{t} \\ 
+        &= \frac{c-v}{c+v}t-\frac{2R_{0}}{c+v} \\
+    \end{split}
 \end{equation}
+
 and it follows that

### 2021-05-25 Modules/sec_future_multiTarget.tex
Final fixes

@@
     \label{eqn:ftr_dyn_temp}
-    x_{n}(t) = \sum_{i=0}^{i=P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
+    x_{n}(t) = \sum_{i=0}^{P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
     +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},

### 2021-05-25 Modules/sec_prlm_FIM.tex
rev03
Final fixes

@@
 A natural question is: how much information can a sample of data provide about the unknown parameter? 
-% This section introduces such a measure for information, and we can also see that this information measure can be used to find bounds on the variance of estimators, and it can be used to approximate the sampling distribution of an estimator obtained from a large sample, and further be used to obtain an approximate confidence interval in case of large sample.
 To this end, the FIM, which is the common tools for assessing the amount of available information in the sampled data is overviewed in the following.
 \par
-Consider a random variable $x$ for which the pdf is $f\rBrace{x|\theta}$, where $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.
+Consider a random variable $x$ for which the PDF is $f\rBrace{x|\theta}$, where $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.
 Intuitively, if an event has small probability, then the occurrence of this event brings us much information.
@@
 We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function which follows that the Fisher information may be expressed \cite{van2004detection} as 
-% We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function, and
-% \begin{equation*}
-%     l^{\prime}\rBrace{x|\theta} = \frac{\partial}{\partial\theta}\log{f\rBrace{x|\theta}}=\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}
-% \end{equation*}
-% where $f^{\prime}\rBrace{x|\theta}$ is the derivative of $f\rBrace{x|\theta}$ with respect to $\theta$.
-% Similarly, we denote the second order derivative of $f\rBrace{x|\theta}$ with respect to $\theta$ as $f^{\prime\prime}\rBrace{x|\theta}$.
-% According to the above analysis, if $l^{\prime}\rBrace{X|\theta}$ is close to zero, then it is expected, thus the random variable does not provide much information about $\theta$;
-% on the other hand, if $\abs{l^{\prime}\rBrace{X|\theta}}$ or $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ is large, the random variable provides much information about $\theta$.
-% Thus, we can use $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ to measure the amount of information provided by $X$.
-% however, since $X$ is a random variable, we should consider the average case. Thus, we introduce the following definition:
-% \begin{definition}
-% \emph{Fisher information} (for $\theta$) contained in the random variable $X$ is defined as:
-% \begin{equation}
-% \label{eq_prlm_FI_def}
-%     I\rBrace{\theta}=E_{\theta}\cBrace{\abs{l^{\prime}\rBrace{X|\theta}}^{2}}=\int{}\abs{l^{\prime}\rBrace{X|\theta}}^{2}f\rBrace{x|\theta}dx.
-% \end{equation}
-% \end{definition}
-% We assume that we can exchange the order of differentiation and integration, then
-% \begin{equation*}
-%     \int{}f^{\prime}\rBrace{x|\theta}dx=\frac{\partial}{\partial\theta}\int{}f\rBrace{x|\theta}dx=0.
-% \end{equation*}
-% Similarly,
-% \begin{equation*}
-%     \int{}f^{\prime\prime}\rBrace{x|\theta}dx=\frac{\partial^{2}}{\partial\theta^{2}}\int{}f\rBrace{x|\theta}dx=0.
-% \end{equation*}
-% It is easy to see that
-% \begin{equation*}
-%     E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=\int{}l^{\prime}\rBrace{x|\theta}f\rBrace{x|\theta}dx=\int{}\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}f\rBrace{x|\theta}dx=\int{}f^{\prime}\rBrace{x|\theta}=0
-% \end{equation*}
-% Therefore, the definition of Fisher information \eqref{eq_prlm_FI_def} can be rewritten as
-% \begin{equation}
-% \label{eq_prlm_IeqVar}
-%     I\rBrace{\theta}=\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}
-% \end{equation}.
-% Also, notice that
-% \begin{equation*}
-%     l^{\prime\prime}\rBrace{x|\theta}=\frac{\partial}{\partial\theta}\vBrace{\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}}=\frac{f^{\prime\prime}\rBrace{x|\theta}f\rBrace{x|\theta}-\abs{f^{\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}=\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}.
-% \end{equation*}
-% Therefore,
-% \begin{equation*}
-%     E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=\int{\vBrace{\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}}f\rBrace{x|\theta}}=\int{f^{\prime\prime}\rBrace{x|\theta}dx}-E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=-I\rBrace{\theta}.
-% \end{equation*}
-% Finally, we have another formula to calculate Fisher information:
 \begin{equation}
@@
 \end{equation}.
-% To summarize, we have three methods to calculate Fisher information: equations \eqref{eq_prlm_FI_def}, \eqref{eq_prlm_IeqVar} and \eqref{eq_prlm_Ifin}.
-% In any problems, using \eqref{eq_prlm_Ifin} is the most convenient choice.
 \subsection{Cram\'er-Rao Lower Bound and Asymptotic Distribution of Maximum Likelihood Estimators}
-% Suppose that we have a random sample $X_{1},\dots,X_{n}$ coming from a distribution for which the pdf or pmf is $f\rBrace{x|\theta},$ where the value of the parameter $\theta$ is unknown. 
-% We will show how to use Fisher information to determine the lower bound for the variance of an estimator of the parameter $\theta$.
-% \par
-% Let $\hat{\theta}=r\rBrace{X_{1},\dots,X_{n}}=r\rBrace{\vecnot{X}}$ be an arbitrary estimator of $\theta$.
-% Assume $E_{\theta}\rBrace{\hat{\theta}}=m\rBrace{\theta}$ and the variance of $\hat{\theta}$ is finite.
-% Let us consider the random variable $l^{\prime}\rBrace{\vecnot{X}|\theta}$, it can be shown that $E_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=0$ and that
-% \begin{equation}
-% \label{eq_prlm_covThetaLTag}
-%     \text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}=m^{\prime}\rBrace{\theta}.
-% \end{equation}.
-% By Cauchy-Schwartz inequality and the definition of $I_{n}\rBrace{\theta},$
-% \begin{equation*}
-%     \vBrace{\text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}
-% \end{equation*}
-% i.e.
-In practical applications, where signal is noised and parameters cannot be accurately estimated, having a closed form expression for the FIM naturally leads to seek for a performance bound that will help the user to know when available information is fully utilized.
-% \begin{equation*}
-%     \vBrace{m^{\prime}\rBrace{\theta}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}=nI\rBrace{\theta}=\text{Var}_{\theta}{\cBrace{\hat{\theta}}}
-% \end{equation*}
-% Finally, we get the lower bound of variance of an arbitrary estimator $\hat{\theta}$ as
+In practical applications, where signal is noisy and parameters cannot be accurately estimated, having a closed form expression for the FIM naturally leads to seek for a performance bound that will help the user to know when available information is fully utilized.
 Such a bound for unbiased estimators is \cite{van2004detection}
-% \begin{equation}
-% \label{eq_prlm_CramerRao_lim}
-%     \text{Var}_{\theta}{\cBrace{\hat{\theta}}}\geq{}\frac{\vBrace{m^{\prime}\rBrace{\theta}}^{2}}{nI\rBrace{\theta}}
-% \end{equation}
-% where 
-% The inequality \eqref{eq_prlm_CramerRao_lim} is called the \emph{information inequality}, and also known as the \emph{Cram\'er-Rao inequality} in honor of the Sweden statistician H.
-Cram\'er Indian statistician C.
-R.
-Rao who independently developed this inequality during the 1940s.
-% The information inequality shows that as $I_{\theta}$ increases, the variance of the estimator decreases, therefore, the quality of the estimator increases, that is why the quantity is called “information”.
-% \par
-% If $\hat{\theta}$ is an unbiased estimator, then $m\rBrace{\theta}=E_{\theta}\rBrace{\hat{\theta}}=\theta$, $m^{\prime}\rBrace{\theta}=1$.
-% Hence, by the information inequality, for unbiased estimator $\hat{\theta}$,
 \begin{equation*}
-    \text{Var}_{\theta}\cBrace{\hat{\theta}}\geq\frac{1}{nI\rBrace{\theta}}.
+    \text{Var}_{\theta}\cBrace{\hat{\theta}}\geq{}I^{-1}\rBrace{\theta}.%\frac{1}{nI\rBrace{\theta}}.
 \end{equation*}
-The right hand side is always called the Cram\'er-Rao lower bound (CRLB): under certain conditions, no other unbiased estimator of the parameter $\theta$ based on an i.i.d sample of size $n$ can have a variance smaller than CRLB.
+The right hand side is the CRLB: under certain conditions, no other unbiased estimator of the parameter $\theta$ can have a variance smaller than CRLB.
 \subsection{The Multiple Parameter Case}
-Suppose now there are more than one parameters in the distribution model, that is, the random variable $X\sim{}f\rBrace{x|\vecnot{\theta}}$ with $\vecnot{\theta}=\rBrace{\theta_{0},\dot,\theta_{k-1}}^{T}$.
+Suppose now there are more than one parameter in the distribution model, that is, the random variable $X\sim{}f\rBrace{x|\vecnot{\theta}}$ with $\vecnot{\theta}=\rBrace{\theta_{0},\dot,\theta_{k-1}}^{T}$.
 We denote the log-likelihood function as
@@
 where the matrix inequality $A\geq{}B$ means that $A-B$ is positive semi-definite.
-From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the measuring is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.
+From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the data is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.
 \subsection{Frequency Domain Cram\'er-Rao Bound for Gaussian Processes}

### 2021-05-25 Modules/sec_prlm_FIR_IIR.tex
Final fixes

@@
     \item \textbf{FIR design}\\
-    The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equal to the number of taps in the final filter's configuration as in Fig.~\ref{fig_FIR_arch}.
+    The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equals to the number of taps in the final filter's configuration as in Fig.~\ref{fig_FIR_arch}.
     \item \textbf{IIR design}\\
@@
 We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
-We consider the same ULA as in Sec.~\ref{sec:prlm_propWaveField}, where a target of interest is placed at $\vpt$.
-Focusing on a far field localization problem, DOA and target range are to be estimated. 
-For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
+% We consider the same ULA as in Sec.~\ref{sec:prlm_propWaveField}, where a target of interest is placed at $\vpt$.
+% Focusing on a far field localization problem, DOA and target range are to be estimated. 
+% For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
 % In the following, we place a transmitter is at $\vpi{0}$, which emits the signal $s$.
@@
 % Then, the reflected signal re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $c$ represents the propagation velocity of the signal in the medium.
-\par As in RADAR applications, the target is assumed to emit a signal $s\rBrace{t}$, where for convenience $s\rBrace{t=0}$ is the signal which impinges $\vpi{0}$ .
+% \par As in RADAR applications, the target is assumed to emit a signal $s\rBrace{t}$, where for convenience $s\rBrace{t=0}$ is the signal which impinges $\vpi{0}$ .
 Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
@@
 \[
-\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}
+\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=\vecnot{d}\rBrace{\omega,\theta_{d}}\F{s}\rBrace{\omega}
 \]
-where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
+where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vecnot{d}_{\theta_{d}}$ denotes the steering vector whose $n$'th element is
 \begin{equation}
     \label{eq:d}
-    d_{n}\rBrace{\omega,\theta_{d}} = \exp{\rBrace{-j\omega\tau_{n}\rBrace{\theta}}}.
+    d_{n}\rBrace{\omega,\theta_{d}} = \exp{\rBrace{-j\omega\tau_{n}\rBrace{\theta_{d}}}}.
 \end{equation}
@@
     \label{eq_Z}
-    Z\rBrace{\omega,\theta_{d}} = \vecnot{\beta}^{T}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}.
+    Z\rBrace{\omega,\theta_{d}} = \vecnot{\beta}^{T}\rBrace{\omega}\vecnot{d}_{\theta_{d}}\rBrace{\omega}\F{s}\rBrace{\omega}.
 \end{equation}
@@
 \[
-Z\rBrace{\omega,\theta} = \F{s}\rBrace{\omega}\sum_{n=0}^{N-1}\beta_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
+Z\rBrace{\omega,\theta} = \F{s}\rBrace{\omega}\sum_{n=0}^{N-1}\beta_{n}\rBrace{\omega}\exp\Brack{-jn\theta\rBrace{\omega}},
 \]
@@
 Due to this important property, applications which are sensitive to signal distortions, especially communication based systems, are based on FIR architecture, for it is possible to design it as linear phase filter.
-Also notable is the stability issues of the IIR filter.
+Also notable is the inherent stability of the FIR filter.
 % Acquainted with the analogy between frequency and DOA, it seems that when localization applications are considered, where the DOA resolution criteria is more important than the consistency of detection latency between separate DOAs, the linear phase property is less relevant.
 % This observation, together with the IIR's efficiency motivate the search for the spatial structure which will be analogous to the IIR filter.
-Motivated by the IIR efficiency, we wish to find the spatial structure that will be analogous to the IIR filer design.
+Nevertheless, motivated by the IIR efficiency, we wish to find the spatial structure that will be analogous to the IIR filter design.
 To this end, we aim to incorporate a spatial feedback which will serve as the temporal feedback in the IIR architecture ($\alpha_{1}, \alpha_{2}$ in Fig.~\ref{fig_IIR_arch}) as illustrated in Fig.~\ref{fig_analogyIIRFB}.

### 2021-05-25 Modules/sec_prlm_array_perf.tex
Final fixes

@@
 where $\lambda$ is the impinging signal's wavelength.
-The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
-Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, it centers the mainlobe, enabling convenient comparison.
+% The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
+% Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, it centers the mainlobe, enabling convenient comparison.
 \subsection{The normalized beampattern}
@@
 % In the following, as we consider steered (to $\theta_{s}$) arrays, we suppress the DOA dependency such that $\mathcal{D} = \mathcal{D}\rBrace{{\theta_{s}}}$. 
-and for uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D} = N$.
+and for uniformly weighted ULAs, it is known \cite{van2004optimum} that $\mathcal{D} = N$.

### 2021-05-25 Modules/sec_prlm_localization.tex
Final fixes

@@
-In the wide and very active research field of parametric estimation, one issue of relevance to this thesis is the sensor-array based localization - i.e.
-positional parameters estimation of impinging signal which is measured by an array of sensors.
+In the wide and very active research field of parametric estimation, one issue of relevance to this thesis is localization.
 \par 
 In this work, we focus on localization of signal sources in the far-field case, where free space signal propagation is assumed.
-Following the classical methods overview in \cite{krim1996two}, localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.
+Following the classical methods overview in \cite{krim1996two}, localization estimators may be divided to two main groups - \textit{spectral-based} and \textit{parametric}.
 The spectral based estimators steer the array (mechanically or by beamforming) to a set of DOAs, searching for peaks in the received energy, where each peak is treated as a resolved emitter when greater than a certain threshold.
@@
 \par
-The later approach, of parameter estimation assumes a physical model of the experimental scenario.
-Then, spatio-temporal estimators take advantage of not only the spatial diversity but also from the temporal information in order to increase the overall SNR.
+The later approach, of parameter estimation, assumes a physical model of the experimental scenario.
+% Then, spatio-temporal estimators take advantage of not only the spatial diversity but also from the temporal information in order to increase the overall SNR.
 Such methods, not only enabled the increase of spatial filtering resolution, but also allowed the implementation of data processing algorithms, which are more sophisticated than a mere search with a steered array.
-In the following, a basic overview of some classical algorithms are presented.
+In the following, a basic overview of some classical algorithms is presented.
 \par

### 2021-05-25 Modules/sec_prlm_propWaveField.tex
Final fixes

@@
 Therefore, the wavenumber vector can be considered to represent spatial frequency, similarly to the manner $\omega$ represents temporal frequency.
-\par For example, in the context of ULA, assuming far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.
+\par For example, in the context of ULA, assuming a far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.
 The spatial diversity of the ULA elements is expressed as a TOA difference of the impinging signal in each sensor which will be shown to provide clues for the signal's DOA (measured from the array's broadside) as can be seen in Fig.~\ref{fig_ULA_sketch}.

### 2021-05-25 Modules/sec_prlm_timeSpaceSig.tex
Final fixes

@@
-As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken the same time $t$.
+As mentioned before, the measurements of the sensor array's elements are utilized together, where spatial information resides in the relations between samples taken the same time $t$.
 A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.

### 2021-05-25 Modules/sec_stability.tex
Final fixes

@@
 \end{equation}
-As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.
+As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinity.
 In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value after 100 iterations of the signal being retransmitted between the array and the target of interest and find that the final values substantially increase as $r\to{1}$.
 This issue will have to be taken into consideration when one designs such an array for practical applications but currently this is outside the scope of this work.
-\begin{figure}[t!]
-    \begin{center}
-        \begin{overpic}[width=0.55\linewidth, 
-        %grid, 
-        tics=10,trim=0 0 0 0]{./Media/fig_stabilization.png}
-            \put (46, -5){\rotatebox{0}{$t/\tau_{pd}$}}
-            \put (-6, 38){\rotatebox{90}{$\abs{z\rBrace{t}}$}}
-            \put (46, 18.5){\rotatebox{0}{$r=0.6$}}
-            \put (46, 35){\rotatebox{0}{$r=0.9$}}
-            \put (46, 54){\rotatebox{0}{$r=1$}}
-            \put (18, 60){\rotatebox{0}{$r=1.1$}}
-            \put (0.75, 80){\rotatebox{0}{dB}}
-        \end{overpic}
-    \end{center}
-    \caption{
-    Simulating a 3 element ULA based FB, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
-    The horizontal axis ($t/\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
-    }
-    \label{fig_stability}
-\end{figure}
-As a final observation, we address the ``discrete`` behaviour of $z$, i.e. the value (most noticeable in the $r=1.1$ plot) seems to be piecewise constant.
+As a final observation, we address the ``discrete`` behaviour of $z$, i.e. the value (most noticeable in the $r=1.1$ plot in Fig.~\ref{fig_stability}) seems to be piecewise constant.
 This phenomenon corresponds with the propagation latency of the signal's round trip to the target and back.
@@
         %grid, 
+        tics=10,trim=0 0 0 0]{./Media/fig_stabilization.png}
+            \put (46, -5){\rotatebox{0}{$t/\tau_{pd}$}}
+            \put (-6, 38){\rotatebox{90}{$\abs{z\rBrace{t}}$}}
+            \put (46, 18.5){\rotatebox{0}{$r=0.6$}}
+            \put (46, 35){\rotatebox{0}{$r=0.9$}}
+            \put (46, 54){\rotatebox{0}{$r=1$}}
+            \put (18, 60){\rotatebox{0}{$r=1.1$}}
+            \put (0.75, 80){\rotatebox{0}{dB}}
+        \end{overpic}
+    \end{center}
+    \caption{
+    Simulating a 3 element ULA based FB, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.
+    The horizontal axis ($t/\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.
+    }
+    \label{fig_stability}
+\end{figure}
+\begin{figure}[t!]
+    \begin{center}
+        \begin{overpic}[width=0.55\linewidth, 
+        %grid, 
         tics=10,trim=0 0 0 0]{./Media/fig_stabilizationVal.png}
@@
     \caption{
-    After simulating the same setup as in Fig.\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.
+    After simulating the same setup as in Fig.~\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.
     }
@@
 \end{figure}
-\par The second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e.
-$\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
-To better understand the phenomenon in Fig.~\ref{fig_stabilityDur}, we plot for each $r$ value, its corresponding settling time.
+\par The second question to be asked regards the settling time of the system.
+For example, in Fig.~\ref{fig_stability} we easily observe that the settling time for $r=0.6$ ($\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
+To better understand the phenomenon, we plot for each $r$ value, its corresponding settling time in Fig.~\ref{fig_stabilityDur}.
 Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:conclusion}.
@@
     \caption{
-    Simulation of same setup as in Fig.\ref{fig_stability}.
+    Simulation of same setup as in Fig.~\ref{fig_stability}.
     For each $r$ (the horizontal axis), we plot the time (the vertical axis) where the received amplitude entered the $1\%$ sleeve around its final value.
-    The plotted time is also in units of $\tau_{\text{pd}}$ normalized as in Fig.\ref{fig_stability}.
+    The plotted time is also normalized in units of $\tau_{\text{pd}}$ as in Fig.~\ref{fig_stability}.
     }
@@
     \begin{split}
-        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
-        =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\
+        % \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
+        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\
         =&\ \frac{\exp{\rBrace{jN\Delta\theta}}-1}{\exp{\rBrace{j\Delta\theta}}-1}\\

### 2021-05-25 main/intro.tex
Final fixes

@@
 \par Early algorithms for direction of arrival (DOA) estimation were based on the beamforming concept \cite{krim1996two}, where the array's reception beam is steered (mechanically or electronically) to multiple directions in search of received energy peaks which are interpreted as valid emitters.
-One notable improvement to the convectional beamformer \cite{van2004optimum} was Capon's beamformer  (aka minimum variance distortionless response (MVDR) in acoustics related literature) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain
+One notable improvement to the conventional beamformer \cite{van2004optimum} was Capon's beamformer  (aka minimum variance distortionless response (MVDR)) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain
 in the desired direction.
@@
 However, the tremendous interest in the subspace approach is mainly due to the introduction of the
-MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise sub space is orthogonal to the signal subspace.
+MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise subspace is orthogonal to the signal subspace.
 It is interesting to note that while earlier works were mostly derived in the context of time series analysis and only later applied to the sensor array problems, MUSIC was originally presented as a DOA estimator.
@@
 Though this approach served as a basis for extensive research, leading to more advanced concepts such as the independent component analysis (ICA) \cite{hyvarinen1999survey}, in the context of practical DOA estimation it's computational effort is high.
-Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao bound (CRB) under some practical assumptions (e.g.
+Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao lower bound (CRLB) under some practical assumptions (e.g.
 non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice.
@@
 \par
-First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to translate its advantages from the temporal domain to the spatial domain.
-Also, classic spatial analysis tools have been gathered to serve as objective tests to the proposed solutions.
+First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to transfer its advantages from the temporal domain to the spatial domain.
+Also, classic spatial analysis tools have been gathered to serve as performance measures to asses to the proposed solutions.
 \par
@@
 The array configuration is rigorously justified, e.g. the setting of the coefficients is done with the use of the Fisher Information Matrix (FIM).
-Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed with the classic analysis framework.
+Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed within the classical analysis framework.
 As we aim to present a practical architecture, estimation errors were taken into consideration and unveiled some sensitivities that should have been addressed.
 \par
-After close inspection, we conclude in the third part that the carrier frequencies cause this sensitivity and search for ways to mitigate it.
+After close inspection, we conclude in the third part that the range estimation errors cause this sensitivity and search for ways to mitigate it.
 To this end, we present a more sophisticated design, based on the basic architecture, achieving a practical low sensitivity spatial processor which successfully extracts spatial information from two independent close frequency FB units.
@@
 \par This thesis is organized as follows.
-In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize on the localization field of research and finalize with the basic concepts which drive the motivation for this research.
+In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize in the field of localization and finalize with the basic concepts which drive the motivation for this research.
 \par In Chapter.~\ref{chap:firstchap} the basic FB is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.
@@
 \par In Chapter.~\ref{chap:conclusion} we discuss the results and conclude our findings. We finalize by also proposing some leads to future research.
-\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
-$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
-Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
+% \par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
+% $v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
+% Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
